### 2018-04-22 MiP3.Rmd
Adding MiP3

---
title: "MPI3"
author: "Mark Hand"
date: "12/12/2017"
output: html_document
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = TRUE) # Something about loading stuff more quickly

setwd("~/Dropbox/PhD_data/MiP")
library(tidyverse) # For data manipulation and visualization
library(stargazer) # For output tables 
library(plm) # For linear panel regression
library(car) # For logging the dependent variable; might be in tidyverse already 
library(gridExtra) # For multi-plot outputs 
library(maps) # Map data. May also be in tidyverse? 
library(mapdata) # More map data? 
library(R.utils) # capitalizing? 
library(MASS) # Boxcox? May also be in tidyverse? 
```

```{r Data import, include=F}
#### Data ####
# Data from Michael Barber's work on political polarization: 
# https://doi.org/10.1086/683453
Barber <- read_csv("~/Dropbox/PhD_data/MiP/data/Barber/Barber Limits Data.csv")
# Getting 2008 only data (reasons for which will become clear in the next sections)
Barber2008 <- Barber %>% filter(year==2008)

# Data from ICC greasethewheels.org/cci/
# Downloaded as .csv, imported as is. 
convictions <- read_csv("~/Dropbox/PhD_data/MiP/data/ICS/CCI19762015.csv")
perceptions <- read_csv("~/Dropbox/PhD_data/MiP/data/ICS/CPS20142016.csv")
#Doesn't havetime series data 
reflections <- read_csv("~/Dropbox/PhD_data/MiP/data/ICS/CRI19772013.csv")
# Though I don't like the name reflections--it implies an unproven causal relationship.

#### Plotting Barber #### 
ind_limits_2010.plot <- ggplot(Barber, aes(ind_limits_2010)) + geom_density() + theme_minimal()
ind2pty_limits_2010.plot <- ggplot(Barber, aes(ind2pty_limits_2010)) + geom_density() + theme_minimal()
pac_limits_2010.plot <- ggplot(Barber, aes(pac_limits_2010)) + geom_density() + theme_minimal()
Barber.plots <- grid.arrange(ind_limits_2010.plot, ind2pty_limits_2010.plot, pac_limits_2010.plot, nrow=1)
# ![](Barber.plots.png)
```

```{r wrangling, include=FALSE}
#### Wrangling Barber and ICS ####
corruption <- full_join(convictions, reflections)
corruption <- corruption %>% 
  rename("st"="State", "year"="Year")
corruption$st <- state.abb[match(corruption$st,state.name)]
BarberICC <- left_join(Barber, corruption)

BarberICC <- BarberICC %>% 
  mutate(
    ind_limits_dummy = ifelse(ind_limits_2010==99999,0,1),
    ind2pty_limits_dummy = ifelse(ind2pty_limits_2010==99999,0,1),
    pac_limits_dummy = ifelse(pac_limits_2010==99999,0,1),
    total_limits_dummy = ifelse(total_limits_2010==99999,0,1)
  )

#### Plotting ICS ####
CRIdensity <- ggplot(BarberICC,aes(CRI)) + geom_density() + theme_minimal()
CCIdensity <- ggplot(BarberICC,aes(CCI)) + geom_density() + theme_minimal()
grid.arrange(CCIdensity, CRIdensity, nrow=1)
```

```{r ICS density plots, include=F=F}
grid.arrange(CCIdensity, CRIdensity, nrow=1)
```

```{r corruption plots, include=F}
CCI1<-ggplot(BarberICC,aes(ind_limits_2010,CCI)) + geom_point() + theme_minimal()
CCI2<-ggplot(BarberICC,aes(ind2pty_limits_2010,CCI)) + geom_point() + theme_minimal()
CCI3<-ggplot(BarberICC,aes(pac_limits_2010,CCI)) + geom_point() + theme_minimal()
CRI1<-ggplot(BarberICC,aes(ind_limits_2010,CRI)) + geom_point() + theme_minimal()
CRI2<-ggplot(BarberICC,aes(ind2pty_limits_2010,CRI)) + geom_point() + theme_minimal()
CRI3<-ggplot(BarberICC,aes(pac_limits_2010,CRI)) + geom_point() + theme_minimal()
CCIandCRI <- grid.arrange(CCI1, CCI2, CCI3, CRI1,CRI2,CRI3, nrow=2)
```

```{r govtrustgrid, include=F}
govtrustgrid
```

```{r models, include=F}
## Plotting 
hist(BarberICC$CCI)
hist(BarberICC$CRI)
hist(BarberICC$ind_limits_2010[BarberICC$ind_limits_2010<99999])

## Modeling

## CCI 
# Individual limits and corruption
CCIreg1  <- plm(CCI ~ ind_limits_2010*ind_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
summary(CCIreg1)
# No signifigance

# Individual-to-party limits and corruption
CCIreg2  <- plm(CCI ~ ind2pty_limits_2010*ind2pty_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
summary(CCIreg2)
# No Signifigance

# PAC Limits and corruption
CCIreg3  <- plm(CCI ~ pac_limits_2010*pac_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
summary(CCIreg3)
# No Signifigance

# Total Limits and corruption
CCIreg4  <- plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
summary(CCIreg4)
# One star. Hmm...

# Everybody? 
CCIreg5 <- plm(CCI ~ ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = BarberICC, index = c("st","year"), effect="twoways")

## CRI
CRIreg1  <- plm(CRI ~ ind_limits_2010*ind_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
summary(CRIreg1)
# No signifigance

# Individual-to-party limits and reflection
CRIreg2  <- plm(CRI ~ ind2pty_limits_2010*ind2pty_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
summary(CRIreg2)
# One star. Hmm...

# PAC Limits and reflection
CRIreg3  <- plm(CRI ~ pac_limits_2010*pac_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
summary(CRIreg3)
# No Signifigance

# All Limits and reflection
CRIreg4  <- plm(CRI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
summary(CRIreg4)
# No Signifigance

# Everybody? 
CRIreg5 <- plm(CRI ~ ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = BarberICC, index = c("st","year"), effect="twoways")

## CRI and CCI? 
CRIonCCI <- plm(CRI ~ CCI,data = BarberICC, index = c("st","year"), effect="twoways")
summary(CRIonCCI)
CCIonCRI <- plm(CCI ~ CRI,data = BarberICC, index = c("st","year"), effect="twoways")
summary(CCIonCRI)
cor(BarberICC$CCI, BarberICC$CCI, method="pearson") # Why didn't this work? 
ggplot(BarberICC, aes(CCI,CRI)) + geom_point(alpha=.1) + geom_smooth(method="lm", se=T)
# How does one interpret these??

```

```{r stargazer, include=F}
stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,
  type="text", 
  title = "Are campaign limits and corruption convictions correlated?",
  out="CCI.htm",
  dep.var.labels = c("Corruption Convictions Index"),
  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)",
  notes = "I make this look good!")
          )

stargazer(CRIreg1, CRIreg2, CRIreg3, CRIreg5,
  type="text", 
  title = "Are campaign limits and corruption reflections correlated?",
  out="CRI.htm",
  dep.var.labels = c("Corruption Reflections Index"),
  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)",
  notes = "I make this look good!")
          )
```

```{r Sandbox, include=F}
BarberICC %>% 
  mutate(
        CRI=replace(CRI, which(CRI==0), NA),
        CCI=replace(CCI, which(CCI==0), NA)
  ) -> test

CCIreg1.2  <- plm(CCI ~ ind_limits_2010*ind_limits_dummy,data = test, index = c("st","year"), effect="twoways")
summary(CCIreg1.2)
#

# Individual-to-party limits and reflection
CCIreg2.2  <- plm(CCI ~ ind2pty_limits_2010*ind2pty_limits_dummy,data = test, index= c("st","year"), effect="twoways")
summary(CCIreg2.2)
#

# PAC Limits and reflection
CCIreg3.2  <- plm(CCI ~ pac_limits_2010*pac_limits_dummy,data = test, index = c("st","year"), effect="twoways")
summary(CCIreg3.2)
#

# Double checking those dummy variables # 
summary(plm(CCI ~ ind_limits_dummy + ind2pty_limits_dummy + pac_limits_dummy, data = BarberICC, index = c("st","year"), effect="twoways"))
summary(plm(CRI ~ ind_limits_dummy + ind2pty_limits_dummy + pac_limits_dummy, data = BarberICC, index = c("st","year"), effect="twoways"))
BarberICC %>% filter(ind_limits_dummy==1) -> Dummytest
summary(plm(CCI ~ ind_limits_2010*ind_limits_dummy, data = BarberICC, index = c("st","year"), effect="twoways"))
summary(plm(CCI ~ ind_limits_2010, data = Dummytest, index = c("st","year"), effect="twoways"))
# Why in the world would these two be different?

# Did I do logs? 
summary(plm(CCI ~ log(ind_limits_2010)*ind_limits_dummy + log(ind2pty_limits_2010)*ind2pty_limits_dummy + log(pac_limits_2010)*pac_limits_dummy, data = BarberICC, index = c("st","year"), effect="twoways"))
summary(plm(CRI ~ ind_limits_2010*ind_limits_dummy + log(ind2pty_limits_2010)*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = BarberICC, index = c("st","year"), effect="twoways"))
# No change in stars

# Boxcox, maybe? 
summary(boxcox(plm(CRI ~ ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = BarberICC, index = c("st","year"), effect="twoways"),lambda=seq(0,1,by=.1)))
summary(boxcox(plm(CCI ~ ind_limits_2010, data = Dummytest, index = c("st","year"), effect="twoways")))
# Umm #

summary(reflections$CRI)
reflections %>% 
  summarize(
    mean=mean(CRI),
    sd=sd(CRI)) 
ggplot(data=subset(reflections,State=="South Dakota"), aes(CRI)) + geom_histogram()
ggplot(data=subset(reflections,State=="New York"), aes(CRI)) + geom_histogram()
ggplot(data=subset(reflections,State=="South Dakota"), aes(Year, CRI)) + geom_line()
ggplot(data=reflections, aes(CRI)) + geom_histogram()
ggplot(reflections, aes(Year, CRI, group=Year)) + geom_boxplot()
```

### 2018-04-22 data/Barber/dataverse_files/Figure_1.R
Add files via upload

@@ -1,0 +1,48 @@
+data <- read.csv("~/Figure_1.csv")
+#each observation is one donor.
+
+
+#Figure 1
+data$bipartisan <- ifelse(data$pct.rep.donations != 0 & data$pct.dem.donations != 0, 1, 0)
+
+years <- seq(1990, 2012, 2)
+
+bipartisanship.ind <- NULL
+for (i in 1:length(years)){
+	year <- years[i]
+	
+summary(model1 <- lm(bipartisan ~ 1, data = data[data$cycle == year & data$individual == 1 & data$num.donations > 2,]))
+a <- model1$coef[1]
+alower <- a - 1.96*sqrt(vcov(model1)[1])
+aupper <- a + 1.96*sqrt(vcov(model1)[1])
+
+bipartisanship.ind <- c(bipartisanship.ind, a)
+
+print(year)
+}
+
+
+bipartisanship.group <- NULL
+for (i in 1:length(years)){
+	year <- years[i]
+	
+summary(model1 <- lm(bipartisan ~ 1, data = data[data$cycle == year & data$group == 1  & data$num.donations > 2,]))
+a <- model1$coef[1]
+alower <- a - 1.96*sqrt(vcov(model1)[1])
+aupper <- a + 1.96*sqrt(vcov(model1)[1])
+
+bipartisanship.group <- c(bipartisanship.group, a)
+
+print(year)
+}
+
+
+dev.new(width = 7, height = 4)
+par(mar = c(3, 4, 4, 1))
+plot(years, bipartisanship.ind, ylim = c(0,1), cex = 0, ylab = "Percent", axes = F, main = "Bipartisan Giving - State Legislative Donors", cex.main = .9)
+lines(years, bipartisanship.ind, lty = 1, lwd = 1)
+lines(years, bipartisanship.group, lty = 2, lwd = 1)
+axis(2, at = c(0, .2, .4, .6, .8, 1), labels = c("0", "20", "40", "60", "80", "100"), cex.axis = .7, las = 2)
+axis(1, at = years, cex.axis = .7)
+text(2002, .20, "Individuals")
+text(2002, .8, "PACs")

### 2018-04-22 data/Barber/dataverse_files/Figure_2.R

@@ -1,0 +1,377 @@
+#Run this code first to make stipple plots along x-axis of plots
+#From: http://www.cl.cam.ac.uk/~sjm217/projects/graphics/fancyaxis.R
+
+fancyaxis <- function(side, summ, at=NULL, mingap=0.5, digits=2,
+                      shiftfac=0.003, gapfac=0.003) {
+  # side: like axis()
+  # summ: a summary object, for example returned by summary()
+  # mingap: the smallest gap permitted between two tickmarks,
+  #         expressed as a fraction of the default tickmark gap
+  # digits: the number of digits to round minimum and maximum to
+  # shiftfac: proportion of plot width used to offset the broken axis
+  # gapfac: proportion of plot width used to leave for median gap
+  
+  # TODO:
+  # Deal with case where length(axTicks)<2
+  # Deal with logarithmic axis case properly, as axTicks difference
+  #  is not uniform.
+  
+  # Get summary information
+  amin <- summ[1]
+  aq1 <- summ[2]
+  amed <- summ[3]
+  amean <- summ[4]
+  aq3 <- summ[5]
+  amax <- summ[6]
+
+  # Find out the properties of the side we are doing
+  parside <-
+    if (side==1){
+      # Does the outside of the plot have larger or smaller vales
+      flip <- 1
+      # Are we on the xaxis
+      xaxis <- TRUE
+      # Is this axis logarithmic
+      islog <- par("xlog")
+      # Is the other axis logarithmic
+      otherlog <- par("ylog")
+      # Relevant index of par("usr")
+      3
+    }
+    else if (side==2) {
+      flip <- 1
+      xaxis <- FALSE
+      islog <- par("ylog")
+      otherlog <- par("xlog")
+      1
+    }
+    else if (side==3) {
+      flip <- -1
+      xaxis <- TRUE
+      islog <- par("xlog")
+      otherlog <- par("ylog")
+      4
+    }
+    else if (side==4) {
+      flip <- -1
+      xaxis <- FALSE
+      islog <- par("ylog")
+      otherlog <- par("xlog")
+      2
+    }
+ # Calculate default positions of ticks
+  if (is.null(at))
+    ticks <- axTicks(side)
+  else
[…]

### 2018-04-22 data/Barber/dataverse_files/Figure_A6.R

@@ -1,0 +1,30 @@
+data <- read.csv("Figure_A6.csv")
+
+years <- sort(unique(data$year))
+
+#Figure A6 - left panel
+ind.cont.prof <- tapply(data$ind.contributions[data$high.median.prof == 1], data$year[data$high.median.prof == 1], function(x) mean(x, na.rm = T))
+
+ind.cont.unprof <- tapply(data$ind.contributions[data$high.median.prof == 0], data$year[data$high.median.prof == 0], function(x) mean(x, na.rm = T))
+
+plot(years, ind.cont.prof, cex = 0, ylim = c(0, 50000), axes = F, ylab = "Average Raised (in thousands $)", main = "Average Individual Money Raised")
+lines(years, ind.cont.prof, lwd = 2)
+lines(years, ind.cont.unprof, lwd = 2, lty = 2)
+axis(2, at = seq(0, 50000, 10000), labels = seq(0, 50, 10), las = 2)
+axis(1, at = years)
+text(2002, 45000, "Professionalized Legislatures")
+text(2006, 3000, "Citizen Legislatures")
+
+
+#Figure A6 - right panel
+pac.cont.prof <- tapply(data$group.contributions[data$high.median.prof == 1], data$year[data$high.median.prof == 1], function(x) mean(x, na.rm = T))
+
+pac.cont.unprof <- tapply(data$group.contributions[data$high.median.prof == 0], data$year[data$high.median.prof == 0], function(x) mean(x, na.rm = T))
+
+plot(years, pac.cont.prof, cex = 0, ylim = c(0, 55000), axes = F, ylab = "Average Raised (in thousands $)", main = "Average PAC Money Raised")
+lines(years, pac.cont.prof, lwd = 2)
+lines(years, pac.cont.unprof, lwd = 2, lty = 2)
+axis(2, at = seq(0, 50000, 10000), labels = seq(0, 50, 10), las = 2)
+axis(1, at = years)
+text(1998, 47000, "Professionalized Legislatures")
+text(2006, 3000, "Citizen Legislatures")

### 2018-04-22 data/Barber/dataverse_files/Figure_A7.R

@@ -1,0 +1,38 @@
+data <- read.csv("Figure_A7.csv")
+
+#MEAN Candidate Portfolio
+share.ind <- tapply(data$share.ind, data$cycle, function(x) mean(x, na.rm = T))
+
+share.pac <- tapply(data$share.group, data$cycle, function(x) mean(x, na.rm = T))
+
+share.single <- tapply(data$share.single, data$cycle, function(x) mean(x, na.rm = T))
+
+years <- sort(as.numeric(as.character(unique(data$cycle))))
+
+#Figure A7
+dev.new(width = 7, height = 3.5)
+par(mar = c(3, 4, 1, 1))
+plot(years, share.ind, ylim = c(0,1), cex = 0, ylab = "Percentage", axes = F, main = "Average Fundraising Porfolios of State Legislative Candidates")
+lines(years, share.ind, lty = 1, lwd = 1)
+lines(years, share.pac, lty = 2, lwd = 1)
+lines(years, share.single, lty = 3, lwd = 1)
+axis(2, at = c(0, .2, .4, .6, .8, 1), labels = c("0", "20", "40", "60", "80", "100"), cex.axis = .7, las = 2)
+axis(1, at = years, cex.axis = .7)
+text(2008, .55, "Individuals")
+text(2008, .34, "PACs")
+text(2008, .11, "Single Issue Groups")
+
+
+#Figure A8
+pac.time <- tapply(data$group.contributions, data$cycle, sum)
+single.time <- tapply(data$singleissue.contributions, data$cycle, sum)
+
+share.access <- pac.time / (pac.time + single.time)
+
+dev.new(width = 7, height = 3.5)
+par(mar = c(3, 4, 1, 1))
+plot(years, share.access, ylim = c(0,1), cex = 0, ylab = "Percentage", axes = F, main = "Percent of PAC Money Coming From Access-Seeking PACs")
+lines(years, share.access, lty = 1, lwd = 1)
+axis(2, at = c(0, .2, .4, .6, .8, 1), labels = c("0", "20", "40", "60", "80", "100"), cex.axis = .7, las = 2)
+axis(1, at = years, cex.axis = .7)
+box()

### 2018-04-22 data/Barber/dataverse_files/Figure_A9.R

@@ -1,0 +1,31 @@
+legislators <- read.dta("Table_2.dta")
+
+#######################
+#LEAVE ONE STATE OUT - FIGURE A9
+#######################
+
+#leave one state out
+states <- unique(legislators$state)
+rep.coef <- NULL
+
+library(lme4)
+for (i in 1:length(states)){
+state <- states[i]
+
+summary(model2 <- lmer(npscore_all ~ (1|state) + (1|year) + ind_unlimited + limited_int_ind_log_limit + pac_unlimited + limited_int_pac_log_limit + compete + pres_vote + dist_income2 + term_limit + republican + majority_party + chamber_pct_dem + professionalism, data = legislators[legislators$state != state,]))
+
+a <- c(fixef(model2)[2:5])
+rep.coef <- rbind(rep.coef, a)
+print(state)
+}
+
+dev.new(width = 12, height = 4)
+par(mfrow = c(1, 4), oma = c(0,2,0,0))
+plot(density(rep.coef[,1], bw = .03), main = "Individual Unimited", xlim = c(-.01, .4), ylab = "Density", xlab = "Effect Size")
+abline(v = .11, lty = 3)
+plot(density(rep.coef[,2], bw = .003), main = "Individual Limit", xlim = c(-.01, .04), ylab = "", xlab = "Effect Size")
+abline(v = .018, lty = 3)
+plot(density(rep.coef[,3], bw = .03), main = "PAC Unlimited", xlim = c(-.4, .01), ylab = "", xlab = "Effect Size")
+abline(v = -.07, lty = 3)
+plot(density(rep.coef[,4], bw = .003), main = "PAC Limit", xlim = c(-.04,.01), ylab = "", xlab = "Effect Size")
+abline(v = -.006, lty = 3)

### 2018-04-22 data/Barber/dataverse_files/Table_3.R

@@ -1,0 +1,8 @@
+#CCES
+cces <- read.csv("cces2012.csv")
+
+summary(model1 <- lm(ideology ~ as.factor(inputstate) + donor + vote + attend.event + put.up.sign + work.for.cand + attend.event + news.interest + income + male + education + white, data = cces[(cces$donate.other == 0 | cces$donate.state == 1) & cces$pid3 == "Republican",]))
+length(model1$resid)
+
+summary(model1 <- lm(ideology ~ as.factor(inputstate) + donor + vote + attend.event + put.up.sign + work.for.cand + attend.event + news.interest + income + male + education + white, data = cces[(cces$donate.other == 0 | cces$donate.state == 1) & cces$pid3 == "Democrat",]))
+length(model1$resid)

### 2018-04-22 data/Barber/dataverse_files/Table_A2.R

@@ -1,0 +1,222 @@
+data <- read.csv("Table_A2.csv")
+
+##################################
+#Table A2
+
+summary(model1 <- lm(log.cpi.ave.ind.contribution ~ as.factor(recipient_state) + as.factor(year) + ind.unlimited + limited_int_ind_log_limit + limited_int_pac_log_limit + pres.vote + district.inc + republican + majority.party + chamber_pct_dem, data = data))
+length(resid(model1))
+
+summary(model2 <- lm(pct.ind.maximizing ~ as.factor(recipient_state) + as.factor(year) + log.cpi.ind.limits + log.cpi.pac.limits + pres.vote + district.inc + republican + majority.party + chamber_pct_dem, data = data[data$ind.unlimited == 0,]))
+length(resid(model2))
+
+summary(model3 <- lm(log.cpi.ind.raised ~ as.factor(recipient_state) + as.factor(year) + ind.unlimited + limited_int_ind_log_limit + limited_int_pac_log_limit + pres.vote + district.inc + republican + majority.party + chamber_pct_dem, data = data))
+length(resid(model3))
+
+summary(model4 <- lm(log.cpi.ave.pac.contribution ~ as.factor(recipient_state) + as.factor(year) + pac.unlimited + limited_int_ind_log_limit + limited_int_pac_log_limit + pres.vote + district.inc + republican + majority.party + chamber_pct_dem, data = data))
+length(resid(model4))
+
+summary(model5 <- lm(pct.pac.maximizing ~ as.factor(recipient_state) + as.factor(year) + log.cpi.pac.limits + log.cpi.ind.limits + pres.vote + district.inc + republican + majority.party + chamber_pct_dem, data = data[data$pac.unlimited == 0,]))
+length(resid(model5))
+
+summary(model6 <- lm(log.cpi.pac.raised ~ as.factor(recipient_state) + as.factor(year) + pac.unlimited + limited_int_ind_log_limit + limited_int_pac_log_limit + pres.vote + district.inc + republican + majority.party + chamber_pct_dem, data = data))
+length(resid(model6))
+
+
+###############FIGURES######################
+
+#Figure A1 - left panel
[…]

### 2018-04-23 MiP3.Rmd
Finished, maybe?

@@
 knitr::opts_chunk$set(echo = TRUE) # Something about loading stuff more quickly 
-
-setwd("~/Dropbox/PhD_data/MiP")
 library(tidyverse) # For data manipulation and visualization
@@
 library(MASS) # Boxcox? May also be in tidyverse? 
+theme_set(theme_minimal()) # Sets default theme, I think  
 ```
@@
 # https://doi.org/10.1086/683453
-Barber <- read_csv("~/Dropbox/PhD_data/MiP/data/Barber/Barber Limits Data.csv")
+Barber <- read_csv("~/Documents/GitHub/Money-in-Politics/data/Barber/Barber_Limits_Data.csv")
 # Getting 2008 only data (reasons for which will become clear in the next sections)
-Barber2008 <- Barber %>% filter(year==2008)
+# They didn't get clearer. 
+# Barber2008 <- Barber %>% filter(year==2008)
 
@@
 # Downloaded as .csv, imported as is. 
-convictions <- read_csv("~/Dropbox/PhD_data/MiP/data/ICS/CCI19762015.csv")
-perceptions <- read_csv("~/Dropbox/PhD_data/MiP/data/ICS/CPS20142016.csv")
+convictions <- read_csv("~/Documents/GitHub/Money-in-Politics/data/ICS/CCI19762015.csv")
+perceptions <- read_csv("~/Documents/GitHub/Money-in-Politics/data/ICS/CPS20142016.csv")
 #Doesn't havetime series data 
-reflections <- read_csv("~/Dropbox/PhD_data/MiP/data/ICS/CRI19772013.csv")
+reflections <- read_csv("~/Documents/GitHub/Money-in-Politics/data/ICS/CRI19772013.csv")
 # Though I don't like the name reflections--it implies an unproven causal relationship.
@@
 ```{r govtrustgrid, include=F}
-govtrustgrid
+# What's this? Leftover from preivous plots, maybe 
+# govtrustgrid
 ```
@@
 ```
+
+```{r plots and charts for poster, hopefully}
+stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5, CRIreg1, CRIreg2, CRIreg3, CRIreg5,
+  type="text", 
+  out="CCICRI.htm",
+  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
+  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)",
+  notes = "I make this look good!")
+          )
+
+ind_limits_2010.histo <- ggplot() + geom_histogram(data=Barber, aes(ind_limits_2010), fill="#bf5700", binwidth = 5000) + theme_minimal() + labs(x = "Individual dollar limits", y= "Count of state-years")
+ind2pty_limits_2010.histo <- ggplot() + geom_histogram(data=Barber, aes(ind2pty_limits_2010), fill="#bf5700", binwidth = 5000) + theme_minimal() + labs(x = "Individual-to-party dollar limits", y="")
+pac_limits_2010.histo <- ggplot() + geom_histogram(data=Barber, aes(pac_limits_2010), fill="#bf5700", binwidth = 5000) + theme_minimal() + labs(x = "PAC dollar limits", y="")
+
+Barber.histos <- grid.arrange(ind_limits_2010.histo, ind2pty_limits_2010.histo, pac_limits_2010.histo, nrow=1, bottom="Data from 1990-2012; 99999 indicates no limit", top="How Common Are Different Levels of State-Level Campaign Finance Limits?")
+
+CCI1<-ggplot() + geom_point(data=subset(BarberICC, ind_limits_2010 != 99999), aes(ind_limits_2010,CCI), col="#bf5700")  + labs(x = "Individual dollar limits", y= "Corruption Convictions Index")
+CCI2<-ggplot(data=subset(BarberICC, ind2pty_limits_2010 != 99999), aes(ind2pty_limits_2010,CCI)) + geom_point(col="#bf5700") + labs(x = "Individual-to-party dollar limits", y="")
+CCI3<-ggplot(data=subset(BarberICC, pac_limits_2010 != 99999), aes(pac_limits_2010,CCI)) + geom_point(col="#bf5700") + labs(x = "PAC dollar limits", y="")
+
+CRI1<-ggplot(data=subset(BarberICC, ind_limits_2010 != 99999), aes(ind_limits_2010,CRI)) + geom_point(col="#bf5700") + labs(x = "Individual dollar limits", y= "Corruption Reflections Index")
+CRI2<-ggplot(data=subset(BarberICC, ind2pty_limits_2010 != 99999), aes(ind2pty_limits_2010,CRI)) + geom_point(col="#bf5700") + labs(x = "Individual-to-party dollar limits", y="")
+CRI3<-ggplot(data=subset(BarberICC, pac_limits_2010 != 99999), aes(pac_limits_2010,CRI)) + geom_point(col="#bf5700") + labs(x = "PAC dollar limits", y="")
+CCIandCRI <- grid.arrange(CCI1, CCI2, CCI3, CRI1,CRI2,CRI3, nrow=2)
+
+# All together now 
+grid.arrange(ind_limits_2010.histo, ind2pty_limits_2010.histo, pac_limits_2010.histo, CCI1, CCI2, CCI3, CRI1,CRI2,CRI3, nrow=3)
+```
+
+grid.arrange(ind_limits_2010.histo, ind2pty_limits_2010.histo, pac_limits_2010.histo, CCI1, CCI2, CCI3, CRI1,CRI2,CRI3, nrow=3, bottom="Data from 1990-2012; in the top three graphs, 99999 indicates a state-year with no limit in that category")

### 2018-04-23 MiP3.Rmd
Can I go home now?

@@
 # All together now 
-grid.arrange(ind_limits_2010.histo, ind2pty_limits_2010.histo, pac_limits_2010.histo, CCI1, CCI2, CCI3, CRI1,CRI2,CRI3, nrow=3)
+grid.arrange(ind_limits_2010.histo, ind2pty_limits_2010.histo, pac_limits_2010.histo, CCI1, CCI2, CCI3, CRI1,CRI2,CRI3, nrow=3, bottom="Data from 1990-2012; in the top three graphs, 99999 indicates a state-year with no limit in that category")
 ```
-
-grid.arrange(ind_limits_2010.histo, ind2pty_limits_2010.histo, pac_limits_2010.histo, CCI1, CCI2, CCI3, CRI1,CRI2,CRI3, nrow=3, bottom="Data from 1990-2012; in the top three graphs, 99999 indicates a state-year with no limit in that category")

### 2018-05-21 MiP3.Rmd
Adding data, sources, models

@@
 
-```{r setup, include=F}
+```{r setup, include=F, warning=FALSE}
 knitr::opts_chunk$set(echo = TRUE) # Something about loading stuff more quickly 
@@
 
-```{r Data import, include=F}
+```{r Data import, include=FALSE}
 #### Data ####
@@
 ind_limits_2010.plot <- ggplot(Barber, aes(ind_limits_2010)) + geom_density() + theme_minimal()
+ind_limits_2010.plot
 ind2pty_limits_2010.plot <- ggplot(Barber, aes(ind2pty_limits_2010)) + geom_density() + theme_minimal()
+ind_limits_2010.plot
 pac_limits_2010.plot <- ggplot(Barber, aes(pac_limits_2010)) + geom_density() + theme_minimal()
 Barber.plots <- grid.arrange(ind_limits_2010.plot, ind2pty_limits_2010.plot, pac_limits_2010.plot, nrow=1)
+pac_limits_2010.plot
 # ![](Barber.plots.png)
@@
 
-```{r ICS density plots, include=F=F}
+```{r ICS density plots, include=F}
 grid.arrange(CCIdensity, CRIdensity, nrow=1)
@@
 ```
+
+```{r replication data maybe}
+library(haven)
+Campante <- read_dta("data/Replication/CampanteDo_MainData.dta")
+```

### 2018-05-21 MiP4.Rmd
Adding data, sources, models

---
title: "MiP4"
author: "Mark Hand"
date: "5/21/2018"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, message=FALSE, warning=FALSE)
library(haven) # import .dta
library(tidyverse) # everything 
library(plm) # For linear panel regression
```

```{r data import, include=FALSE}
# Alt and Lassen's "Enforcement and Public Corruption: Evidence from US States"
# http://epstein.wustl.edu/research/LPE.Alt.pdf
AltLassen <- read_dta("data/Replication/AltLassenJLEO.dta")

# Michael Barber's "Ideological Donors, Contribution Limits, and the Polarization of American Legislatures"  
# https://doi.org/10.1086/683453
Barber <- read_csv("~/Documents/GitHub/Money-in-Politics/data/Barber/Barber_Limits_Data.csv")

# Data from ICC 
# www.greasethewheels.org/cci/
convictions <- read_csv("~/Documents/GitHub/Money-in-Politics/data/ICS/CCI19762015.csv")
reflections <- read_csv("~/Documents/GitHub/Money-in-Politics/data/ICS/CRI19772013.csv")
```

```{r data wrangling}
# Combining Barber and ICS 
corruption <- full_join(convictions, reflections)
corruption <- corruption %>% 
  rename("st"="State", "year"="Year")
corruption$st <- state.abb[match(corruption$st,state.name)]
BarberICC <- left_join(Barber, corruption)

BarberICC <- BarberICC %>% 
  mutate(
    ind_limits_dummy = ifelse(ind_limits_2010==99999,0,1),
    ind2pty_limits_dummy = ifelse(ind2pty_limits_2010==99999,0,1),
    pac_limits_dummy = ifelse(pac_limits_2010==99999,0,1),
    total_limits_dummy = ifelse(total_limits_2010==99999,0,1)
  )

# Adding AltLassen
table(AltLassen$state_name)
AltLassen$state_name[AltLassen$state_name=="Californ"] = "California"
AltLassen$state_name[AltLassen$state_name=="Connecti"] = "Connecticut"
AltLassen$state_name[AltLassen$state_name=="Louisian"] = "Louisiana"
AltLassen$state_name[AltLassen$state_name=="Massachu"] = "Massachusetts"
AltLassen$state_name[AltLassen$state_name=="Minnesot"] = "Minnesota"
AltLassen$state_name[AltLassen$state_name=="Mississi"] = "Mississippi"
AltLassen$state_name[AltLassen$state_name=="NewHamps"] = "New Hampshire"
AltLassen$state_name[AltLassen$state_name=="NewJerse"] = "New Jersey"
AltLassen$state_name[AltLassen$state_name=="NewMexic"] = "New Mexico"
AltLassen$state_name[AltLassen$state_name=="NewYork"] = "New York"
AltLassen$state_name[AltLassen$state_name=="NorthCar"] = "North Carolina"
AltLassen$state_name[AltLassen$state_name=="NorthDak"] = "North Dakota"
AltLassen$state_name[AltLassen$state_name=="Pennsylv"] = "Pennsylvania"
AltLassen$state_name[AltLassen$state_name=="RhodeIsl"] = "Rhode Island"
AltLassen$state_name[AltLassen$state_name=="SouthCar"] = "South Carolina"
AltLassen$state_name[AltLassen$state_name=="SouthDak"] = "South Dakota"
AltLassen$state_name[AltLassen$state_name=="Tennesse"] = "Tennessee"
AltLassen$state_name[AltLassen$state_name=="Washingt"] = "Washington"
AltLassen$state_name[AltLassen$state_name=="WestVirg"] = "West Virginia"
AltLassen$state_name[AltLassen$state_name=="Wisconsi"] = "Wisconsin"
AltLassen$state_name <- state.abb[match(AltLassen$state_name,state.name)]
table(AltLassen$state_name)
AltLassen <- AltLassen %>% 
  rename("st"="state_name")
AltLassen$year <-as.integer(AltLassen$year)

AltBarber <- inner_join(BarberICC, AltLassen)
```

```{r modeling, echo=FALSE}
#Next: Panel model of corruption against unemployment and high school? 
testmodel01 <- plm(CCI ~ rpcinc_annual_new + unemp + high_school + logNumpop + citi6006 + grelimp, data = AltBarber, index = c("st","year"), effect="twoways")
summary(testmodel01)

testmodel02 <- plm(CCI ~ jdiv + bindingonetermlimit + bindingtwotermlimit + rpcinc_annual_new + eousa + unemp + citi6006 + high_school + rgenrevpc + logNumpop + eopop + men_ineqincwag + grelimp + fedrepcons + urbanization_2 + logpop + inspop, data = AltBarber, index = c("st","year"), effect="twoways")
summary(testmodel02)

testmodel03 <- plm(CCI ~ jdiv + bindingonetermlimit + bindingtwotermlimit + rpcinc_annual_new + eousa + unemp + citi6006 + high_school + rgenrevpc + logNumpop + eopop + men_ineqincwag + grelimp + fedrepcons + urbanization_2 + logpop + inspop + ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = AltBarber, index = c("st","year"), effect="twoways")
summary(testmodel03)

testmodel05 <- plm(CCI ~ jdiv + bindingonetermlimit + bindingtwotermlimit + rpcinc_annual_new + eousa + unemp + citi6006 + high_school + rgenrevpc + logNumpop + eopop + men_ineqincwag + grelimp + urbanization_2 + logpop + inspop, data = AltBarber, index = c("st","year"), effect="twoways")
summary(testmodel05)

testmodel06 <- plm(CCI ~ jdiv + bindingonetermlimit + bindingtwotermlimit + rpcinc_annual_new + eousa + unemp + citi6006 + high_school + rgenrevpc + logNumpop + eopop + men_ineqincwag + grelimp + urbanization_2 + logpop + inspop + ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = AltBarber, index = c("st","year"), effect="twoways")
summary(testmodel06)

```

### 2018-05-22 MiP4.Rmd
panel modeling

@@
 
-```{r data import, include=FALSE}
+```{r data import, include=F}
 # Alt and Lassen's "Enforcement and Public Corruption: Evidence from US States"
@@
 
-```{r data wrangling}
+```{r panel data wrangling, include=F}
 # Combining Barber and ICS 
@@
 
-```{r modeling, echo=FALSE}
+```{r panel modeling, include=F}
 #Next: Panel model of corruption against unemployment and high school? 
@@
 ```
+
+```{r DiD wrangling, include=F}
+# Creating DiD dataframe 
+AltBarberDiD <- transform(BarberICC, ind_limits_2010_d = ave(ind_limits_2010, st, FUN = function(x) c(NA, diff(x))))
+AltBarberDiD <- transform(AltBarberDiD, ind_limits_dummy_d = ave(ind_limits_dummy , st, FUN = function(x) c(NA, diff(x))))
+AltBarberDiD <- transform(AltBarberDiD, pac_limits_2010_d = ave(pac_limits_2010, st, FUN = function(x) c(NA, diff(x))))
+AltBarberDiD <- transform(AltBarberDiD, pac_limits_dummy_d = ave(pac_limits_dummy, st, FUN = function(x) c(NA, diff(x))))
+AltBarberDiD <- transform(AltBarberDiD, ind2pty_limits_2010_d = ave(ind2pty_limits_2010, st, FUN = function(x) c(NA, diff(x))))
+AltBarberDiD <- transform(AltBarberDiD, ind2pty_limits_dummy_d = ave(ind2pty_limits_dummy, st, FUN = function(x) c(NA, diff(x))))
+
+AltBarberDiD %>% select(1:2,8,11,3:7,12:21) -> DiDsmall 
+```
+
+```{r DiD modeling, include=F}
+
+```

### 2018-05-22 MiP4.Rmd
Difference in difference modeling. Don't know what happened when I hit "stage all."

--- 2018-05-21 MiP4.Rmd
@@
 
-```{r setup, include=FALSE, warning=FALSE}
+```{r setup}
 knitr::opts_chunk$set(echo = TRUE, cache = TRUE, message=FALSE, warning=FALSE)
@@
 
-```{r data import, include=FALSE}
+```{r data import}
 # Alt and Lassen's "Enforcement and Public Corruption: Evidence from US States"
@@
 
-```{r data wrangling}
+```{r panel data wrangling}
 # Combining Barber and ICS 
@@
 
-```{r modeling, echo=FALSE}
+```{r panel modeling}
 #Next: Panel model of corruption against unemployment and high school? 
@@
 ```
+
+```{r DiD wrangling}
+BarberICC %>% arrange(year) %>% group_by(st) %>% mutate(
+  ind_d = (ind_limits_2010 - dplyr::lag(ind_limits_2010)),
+  ind_dummy_d = (ind_limits_dummy - dplyr::lag(ind_limits_dummy)),
+  pac_d = (pac_limits_2010 - dplyr::lag(pac_limits_2010)),
+  pac_dummy_d = (pac_limits_dummy - dplyr::lag(pac_limits_dummy)),
+  ind2pty_d = (ind2pty_limits_2010 - dplyr::lag(ind2pty_limits_2010)),
+  ind2pty_dummy_d = (ind2pty_limits_dummy - dplyr::lag(ind2pty_limits_dummy))
+  ) -> testframe
+
+testframe %>% select(1:2,8,11,3:7,12:21) -> DiDsmall 
+summary(DiDsmall)
+
+# Now I have what I think are three multi-level categorical independent variables. 
+# https://stats.idre.ucla.edu/r/modules/coding-for-categorical-variables-in-regression-models/
+#1. When limits were imposed (1) or went down, did corruption go down? 
+#2. When limits were removed (-1) or went up, did corruption go up?
+
+DiDsmall$ind_dummy_f <- factor(DiDsmall$ind_dummy_d)
+DiDsmall <- within(DiDsmall, ind_dummy_f <- relevel(ind_dummy_f, ref = "0"))
+DiDsmall$pac_dummy_f <- factor(DiDsmall$pac_dummy_d)
+DiDsmall <- within(DiDsmall, pac_dummy_f <- relevel(pac_dummy_f, ref = "0"))
+DiDsmall$ind2pty_dummy_f <- factor(DiDsmall$ind2pty_dummy_d)
+DiDsmall <- within(DiDsmall, ind2pty_dummy_f <- relevel(ind2pty_dummy_f, ref = "0"))
+```
+
+```{r DiD modeling}
+summary(lm(CCI ~ ind_dummy_f, data = DiDsmall))
+summary(lm(CCI ~ pac_dummy_f, data = DiDsmall))
+summary(lm(CCI ~ ind2pty_dummy_f, data = DiDsmall))
+summary(lm(CRI ~ ind_dummy_f, data = DiDsmall))
+summary(lm(CRI ~ pac_dummy_f, data = DiDsmall))
+summary(lm(CRI ~ ind2pty_dummy_f, data = DiDsmall))
+# No effects
+
+summary(lm(CCI ~ ind_dummy_f*ind_d, data = DiDsmall))
+summary(lm(CCI ~ pac_dummy_f*pac_d, data = DiDsmall))
+summary(lm(CCI ~ ind2pty_dummy_f*ind2pty_d, data = DiDsmall))
+summary(lm(CRI ~ ind_dummy_f*ind_d, data = DiDsmall))
+summary(lm(CRI ~ pac_dummy_f*pac_d, data = DiDsmall))
+summary(lm(CRI ~ ind2pty_dummy_f*ind2pty_d, data = DiDsmall))
+# No effects
+
+# Next: Lag, write up. 
+```

### 2018-05-23 MiP4.Rmd
Rearranging files, starting new knitr document, crossing fingers.

@@
 ---
-title: "MiP4"
-author: "Mark Hand"
+title: "| Do campaign contribution limits limit corruption? \n| Evidence from the
+  50 states\n"
+author: "Mark C. Hand"
 date: "5/21/2018"
-output: html_document
+output:
+  pdf_document: default
+  html_document: default
 ---
@@
 # Adding AltLassen
-table(AltLassen$state_name)
+# table(AltLassen$state_name)
 AltLassen$state_name[AltLassen$state_name=="Californ"] = "California"
@@
 AltLassen$state_name <- state.abb[match(AltLassen$state_name,state.name)]
-table(AltLassen$state_name)
 AltLassen <- AltLassen %>% 

### 2018-05-23 MiP4.tex
Rearranging files, starting new knitr document, crossing fingers.

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdfauthor={Mark C. Hand},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{Do campaign contribution limits limit corruption?\\
Evidence from the 50 states}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Mark C. Hand}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \predate{\centering\large\emph}
  \postdate{\par}
  \date{5/21/2018}

\begin{document}
\maketitle

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{knitr}\OperatorTok{::}\NormalTok{opts_chunk}\OperatorTok{$}\KeywordTok{set}\NormalTok{(}\DataTypeTok{echo =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{cache =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{message=}\OtherTok{FALSE}\NormalTok{, }\DataTypeTok{warning=}\OtherTok{FALSE}\NormalTok{)}
\KeywordTok{library}\NormalTok{(haven) }\CommentTok{# import .dta}
\KeywordTok{library}\NormalTok{(tidyverse) }\CommentTok{# everything }
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## -- Attaching packages ---------------------------------------------------- tidyverse 1.2.1 --
\end{verbatim}

\begin{verbatim}
## √ ggplot2 2.2.1     √ purrr   0.2.4
## √ tibble  1.4.2     √ dplyr   0.7.5
## √ tidyr   0.8.1     √ stringr 1.3.0
## √ readr   1.1.1     √ forcats 0.3.0
\end{verbatim}

\begin{verbatim}
## -- Conflicts ------------------------------------------------------- tidyverse_conflicts() --
## x dplyr::filter() masks stats::filter()
## x dplyr::lag()    masks stats::lag()
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(plm) }\CommentTok{# For linear panel regression}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Loading required package: Formula
\end{verbatim}

\begin{verbatim}
## 
## Attaching package: 'plm'
\end{verbatim}

\begin{verbatim}
## The following objects are masked from 'package:dplyr':
## 
##     between, lag, lead
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Alt and Lassen's "Enforcement and Public Corruption: Evidence from US States"}
\CommentTok{# http://epstein.wustl.edu/research/LPE.Alt.pdf}
\NormalTok{AltLassen <-}\StringTok{ }\KeywordTok{read_dta}\NormalTok{(}\StringTok{"data/Replication/AltLassenJLEO.dta"}\NormalTok{)}

\CommentTok{# Michael Barber's "Ideological Donors, Contribution Limits, and the Polarization of American Legislatures"  }
\CommentTok{# https://doi.org/10.1086/683453}
\NormalTok{Barber <-}\StringTok{ }\KeywordTok{read_csv}\NormalTok{(}\StringTok{"~/Documents/GitHub/Money-in-Politics/data/Barber/Barber_Limits_Data.csv"}\NormalTok{)}

\CommentTok{# Data from ICC }
\CommentTok{# www.greasethewheels.org/cci/}
\NormalTok{convictions <-}\StringTok{ }\KeywordTok{read_csv}\NormalTok{(}\StringTok{"~/Documents/GitHub/Money-in-Politics/data/ICS/CCI19762015.csv"}\NormalTok{)}
\NormalTok{reflections <-}\StringTok{ }\KeywordTok{read_csv}\NormalTok{(}\StringTok{"~/Documents/GitHub/Money-in-Politics/data/ICS/CRI19772013.csv"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Combining Barber and ICS }
\NormalTok{corruption <-}\StringTok{ }\KeywordTok{full_join}\NormalTok{(convictions, reflections)}
\NormalTok{corruption <-}\StringTok{ }\NormalTok{corruption }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{rename}\NormalTok{(}\StringTok{"st"}\NormalTok{=}\StringTok{"State"}\NormalTok{, }\StringTok{"year"}\NormalTok{=}\StringTok{"Year"}\NormalTok{)}
\NormalTok{corruption}\OperatorTok{$}\NormalTok{st <-}\StringTok{ }\NormalTok{state.abb[}\KeywordTok{match}\NormalTok{(corruption}\OperatorTok{$}\NormalTok{st,state.name)]}
\NormalTok{BarberICC <-}\StringTok{ }\KeywordTok{left_join}\NormalTok{(Barber, corruption)}

\NormalTok{BarberICC <-}\StringTok{ }\NormalTok{BarberICC }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}
    \DataTypeTok{ind_limits_dummy =} \KeywordTok{ifelse}\NormalTok{(ind_limits_}\DecValTok{2010}\OperatorTok{==}\DecValTok{99999}\NormalTok{,}\DecValTok{0}\NormalTok{,}\DecValTok{1}\NormalTok{),}
    \DataTypeTok{ind2pty_limits_dummy =} \KeywordTok{ifelse}\NormalTok{(ind2pty_limits_}\DecValTok{2010}\OperatorTok{==}\DecValTok{99999}\NormalTok{,}\DecValTok{0}\NormalTok{,}\DecValTok{1}\NormalTok{),}
    \DataTypeTok{pac_limits_dummy =} \KeywordTok{ifelse}\NormalTok{(pac_limits_}\DecValTok{2010}\OperatorTok{==}\DecValTok{99999}\NormalTok{,}\DecValTok{0}\NormalTok{,}\DecValTok{1}\NormalTok{),}
    \DataTypeTok{total_limits_dummy =} \KeywordTok{ifelse}\NormalTok{(total_limits_}\DecValTok{2010}\OperatorTok{==}\DecValTok{99999}\NormalTok{,}\DecValTok{0}\NormalTok{,}\DecValTok{1}\NormalTok{)}
\NormalTok{  )}

\CommentTok{# Adding AltLassen}
\CommentTok{# table(AltLassen$state_name)}
\NormalTok{AltLassen}\OperatorTok{$}\NormalTok{state_name[AltLassen}\OperatorTok{$}\NormalTok{state_name}\OperatorTok{==}\StringTok{"Californ"}\NormalTok{] =}\StringTok{ "California"}
\NormalTok{AltLassen}\OperatorTok{$}\NormalTok{state_name[AltLassen}\OperatorTok{$}\NormalTok{state_name}\OperatorTok{==}\StringTok{"Connecti"}\NormalTok{] =}\StringTok{ "Connecticut"}
\NormalTok{AltLassen}\OperatorTok{$}\NormalTok{state_name[AltLassen}\OperatorTok{$}\NormalTok{state_name}\OperatorTok{==}\StringTok{"Louisian"}\NormalTok{] =}\StringTok{ "Louisiana"}
\NormalTok{AltLassen}\OperatorTok{$}\NormalTok{state_name[AltLassen}\OperatorTok{$}\NormalTok{state_name}\OperatorTok{==}\StringTok{"Massachu"}\NormalTok{] =}\StringTok{ "Massachusetts"}
\NormalTok{AltLassen}\OperatorTok{$}\NormalTok{state_name[AltLassen}\OperatorTok{$}\NormalTok{state_name}\OperatorTok{==}\StringTok{"Minnesot"}\NormalTok{] =}\StringTok{ "Minnesota"}
\NormalTok{AltLassen}\OperatorTok{$}\NormalTok{state_name[AltLassen}\OperatorTok{$}\NormalTok{state_name}\OperatorTok{==}\StringTok{"Mississi"}\NormalTok{] =}\StringTok{ "Mississippi"}
\NormalTok{AltLassen}\OperatorTok{$}\NormalTok{state_name[AltLassen}\OperatorTok{$}\NormalTok{state_name}\OperatorTok{==}\StringTok{"NewHamps"}\NormalTok{] =}\StringTok{ "New Hampshire"}
\NormalTok{AltLassen}\OperatorTok{$}\NormalTok{state_name[AltLassen}\OperatorTok{$}\NormalTok{state_name}\OperatorTok{==}\StringTok{"NewJerse"}\NormalTok{] =}\StringTok{ "New Jersey"}
\NormalTok{AltLassen}\OperatorTok{$}\NormalTok{state_name[AltLassen}\OperatorTok{$}\NormalTok{state_name}\OperatorTok{==}\StringTok{"NewMexic"}\NormalTok{] =}\StringTok{ "New Mexico"}
\NormalTok{AltLassen}\OperatorTok{$}\NormalTok{state_name[AltLassen}\OperatorTok{$}\NormalTok{state_name}\OperatorTok{==}\StringTok{"NewYork"}\NormalTok{] =}\StringTok{ "New York"}
\NormalTok{AltLassen}\OperatorTok{$}\NormalTok{state_name[AltLassen}\OperatorTok{$}\NormalTok{state_name}\OperatorTok{==}\StringTok{"NorthCar"}\NormalTok{] =}\StringTok{ "North Carolina"}
\NormalTok{AltLassen}\OperatorTok{$}\NormalTok{state_name[AltLassen}\OperatorTok{$}\NormalTok{state_name}\OperatorTok{==}\StringTok{"NorthDak"}\NormalTok{] =}\StringTok{ "North Dakota"}
\NormalTok{AltLassen}\OperatorTok{$}\NormalTok{state_name[AltLassen}\OperatorTok{$}\NormalTok{state_name}\OperatorTok{==}\StringTok{"Pennsylv"}\NormalTok{] =}\StringTok{ "Pennsylvania"}
\NormalTok{AltLassen}\OperatorTok{$}\NormalTok{state_name[AltLassen}\OperatorTok{$}\NormalTok{state_name}\OperatorTok{==}\StringTok{"RhodeIsl"}\NormalTok{] =}\StringTok{ "Rhode Island"}
\NormalTok{AltLassen}\OperatorTok{$}\NormalTok{state_name[AltLassen}\OperatorTok{$}\NormalTok{state_name}\OperatorTok{==}\StringTok{"SouthCar"}\NormalTok{] =}\StringTok{ "South Carolina"}
\NormalTok{AltLassen}\OperatorTok{$}\NormalTok{state_name[AltLassen}\OperatorTok{$}\NormalTok{state_name}\OperatorTok{==}\StringTok{"SouthDak"}\NormalTok{] =}\StringTok{ "South Dakota"}
\NormalTok{AltLassen}\OperatorTok{$}\NormalTok{state_name[AltLassen}\OperatorTok{$}\NormalTok{state_name}\OperatorTok{==}\StringTok{"Tennesse"}\NormalTok{] =}\StringTok{ "Tennessee"}
\NormalTok{AltLassen}\OperatorTok{$}\NormalTok{state_name[AltLassen}\OperatorTok{$}\NormalTok{state_name}\OperatorTok{==}\StringTok{"Washingt"}\NormalTok{] =}\StringTok{ "Washington"}
\NormalTok{AltLassen}\OperatorTok{$}\NormalTok{state_name[AltLassen}\OperatorTok{$}\NormalTok{state_name}\OperatorTok{==}\StringTok{"WestVirg"}\NormalTok{] =}\StringTok{ "West Virginia"}
\NormalTok{AltLassen}\OperatorTok{$}\NormalTok{state_name[AltLassen}\OperatorTok{$}\NormalTok{state_name}\OperatorTok{==}\StringTok{"Wisconsi"}\NormalTok{] =}\StringTok{ "Wisconsin"}
\NormalTok{AltLassen}\OperatorTok{$}\NormalTok{state_name <-}\StringTok{ }\NormalTok{state.abb[}\KeywordTok{match}\NormalTok{(AltLassen}\OperatorTok{$}\NormalTok{state_name,state.name)]}
\NormalTok{AltLassen <-}\StringTok{ }\NormalTok{AltLassen }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{rename}\NormalTok{(}\StringTok{"st"}\NormalTok{=}\StringTok{"state_name"}\NormalTok{)}
\NormalTok{AltLassen}\OperatorTok{$}\NormalTok{year <-}\KeywordTok{as.integer}\NormalTok{(AltLassen}\OperatorTok{$}\NormalTok{year)}

\NormalTok{AltBarber <-}\StringTok{ }\KeywordTok{inner_join}\NormalTok{(BarberICC, AltLassen)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#Next: Panel model of corruption against unemployment and high school? }
\NormalTok{testmodel01 <-}\StringTok{ }\KeywordTok{plm}\NormalTok{(CCI }\OperatorTok{~}\StringTok{ }\NormalTok{rpcinc_annual_new }\OperatorTok{+}\StringTok{ }\NormalTok{unemp }\OperatorTok{+}\StringTok{ }\NormalTok{high_school }\OperatorTok{+}\StringTok{ }\NormalTok{logNumpop }\OperatorTok{+}\StringTok{ }\NormalTok{citi6006 }\OperatorTok{+}\StringTok{ }\NormalTok{grelimp, }\DataTypeTok{data =}\NormalTok{ AltBarber, }\DataTypeTok{index =} \KeywordTok{c}\NormalTok{(}\StringTok{"st"}\NormalTok{,}\StringTok{"year"}\NormalTok{), }\DataTypeTok{effect=}\StringTok{"twoways"}\NormalTok{)}
\KeywordTok{summary}\NormalTok{(testmodel01)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Twoways effects Within Model
## 
## Call:
## plm(formula = CCI ~ rpcinc_annual_new + unemp + high_school + 
##     logNumpop + citi6006 + grelimp, data = AltBarber, effect = "twoways", 
##     index = c("st", "year"))
## 
## Unbalanced Panel: n = 48, T = 13-15, N = 713
## 
## Residuals:
##     Min.  1st Qu.   Median  3rd Qu.     Max. 
## -4.81797 -1.00621 -0.18884  0.81311 13.77887 
## 
## Coefficients:
##                      Estimate  Std. Error t-value Pr(>|t|)    
## rpcinc_annual_new -4.0754e-04  1.8335e-04 -2.2228  0.02658 *  
## unemp             -6.3066e-02  1.2605e-01 -0.5003  0.61703    
## high_school       -1.2978e+00  5.5780e+00 -0.2327  0.81610    
## logNumpop          2.2137e-01  1.6150e-02 13.7072  < 2e-16 ***
## citi6006           2.1570e-03  1.6662e-02  0.1295  0.89704    
## grelimp           -1.1922e+01  3.6482e+01 -0.3268  0.74393    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Total Sum of Squares:    3132
## Residual Sum of Squares: 2404
## R-Squared:      0.23244
## Adj. R-Squared: 0.1527
## F-statistic: 32.5533 on 6 and 645 DF, p-value: < 2.22e-16
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{testmodel02 <-}\StringTok{ }\KeywordTok{plm}\NormalTok{(CCI }\OperatorTok{~}\StringTok{ }\NormalTok{jdiv }\OperatorTok{+}\StringTok{ }\NormalTok{bindingonetermlimit }\OperatorTok{+}\StringTok{ }\NormalTok{bindingtwotermlimit }\OperatorTok{+}\StringTok{ }\NormalTok{rpcinc_annual_new }\OperatorTok{+}\StringTok{ }\NormalTok{eousa }\OperatorTok{+}\StringTok{ }\NormalTok{unemp }\OperatorTok{+}\StringTok{ }\NormalTok{citi6006 }\OperatorTok{+}\StringTok{ }\NormalTok{high_school }\OperatorTok{+}\StringTok{ }\NormalTok{rgenrevpc }\OperatorTok{+}\StringTok{ }\NormalTok{logNumpop }\OperatorTok{+}\StringTok{ }\NormalTok{eopop }\OperatorTok{+}\StringTok{ }\NormalTok{men_ineqincwag }\OperatorTok{+}\StringTok{ }\NormalTok{grelimp }\OperatorTok{+}\StringTok{ }\NormalTok{fedrepcons }\OperatorTok{+}\StringTok{ }\NormalTok{urbanization_}\DecValTok{2} \OperatorTok{+}\StringTok{ }\NormalTok{logpop }\OperatorTok{+}\StringTok{ }\NormalTok{inspop, }\DataTypeTok{data =}\NormalTok{ AltBarber, }\DataTypeTok{index =} \KeywordTok{c}\NormalTok{(}\StringTok{"st"}\NormalTok{,}\StringTok{"year"}\NormalTok{), }\DataTypeTok{effect=}\StringTok{"twoways"}\NormalTok{)}
\KeywordTok{summary}\NormalTok{(testmodel02)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Twoways effects Within Model
## 
## Call:
## plm(formula = CCI ~ jdiv + bindingonetermlimit + bindingtwotermlimit + 
##     rpcinc_annual_new + eousa + unemp + citi6006 + high_school + 
##     rgenrevpc + logNumpop + eopop + men_ineqincwag + grelimp + 
##     fedrepcons + urbanization_2 + logpop + inspop, data = AltBarber, 
##     effect = "twoways", index = c("st", "year"))
## 
## Unbalanced Panel: n = 48, T = 11-13, N = 618
## 
## Residuals:
##     Min.  1st Qu.   Median  3rd Qu.     Max. 
## -5.25732 -1.06561 -0.12498  0.83593 13.44049 
## 
## Coefficients:
##                        Estimate  Std. Error t-value  Pr(>|t|)    
## jdiv                -0.20190256  0.20282511 -0.9955  0.319962    
## bindingonetermlimit -0.39118843  1.27029686 -0.3080  0.758239    
## bindingtwotermlimit -0.04300755  0.22054353 -0.1950  0.845461    
## rpcinc_annual_new   -0.00056598  0.00025004 -2.2636  0.023995 *  
## eousa                0.00535221  0.01069341  0.5005  0.616916    
## unemp               -0.10017217  0.15209202 -0.6586  0.510414    
## citi6006            -0.01032798  0.01913966 -0.5396  0.589687    
## high_school         -5.14098696  7.01773427 -0.7326  0.464138    
## rgenrevpc            0.00041420  0.00112210  0.3691  0.712178    
## logNumpop            0.22566553  0.01828559 12.3412 < 2.2e-16 ***
## eopop                0.01548702  0.06500440  0.2382  0.811781    
## men_ineqincwag       0.13088787  0.04447225  2.9431  0.003388 ** 
## grelimp             22.11759146 43.75544159  0.5055  0.613426    
## fedrepcons          -0.06259835  0.02282555 -2.7425  0.006300 ** 
## urbanization_2       0.14630029  0.10887078  1.3438  0.179577    
## logpop              -3.05635200  3.16861625 -0.9646  0.335191    
## inspop              -0.00162197  0.00226241 -0.7169  0.473732    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Total Sum of Squares:    2911.7
## Residual Sum of Squares: 2136.5
## R-Squared:      0.26624
## Adj. R-Squared: 0.16316
## F-statistic: 11.5467 on 17 and 541 DF, p-value: < 2.22e-16
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{testmodel03 <-}\StringTok{ }\KeywordTok{plm}\NormalTok{(CCI }\OperatorTok{~}\StringTok{ }\NormalTok{jdiv }\OperatorTok{+}\StringTok{ }\NormalTok{bindingonetermlimit }\OperatorTok{+}\StringTok{ }\NormalTok{bindingtwotermlimit }\OperatorTok{+}\StringTok{ }\NormalTok{rpcinc_annual_new }\OperatorTok{+}\StringTok{ }\NormalTok{eousa }\OperatorTok{+}\StringTok{ }\NormalTok{unemp }\OperatorTok{+}\StringTok{ }\NormalTok{citi6006 }\OperatorTok{+}\StringTok{ }\NormalTok{high_school }\OperatorTok{+}\StringTok{ }\NormalTok{rgenrevpc }\OperatorTok{+}\StringTok{ }\NormalTok{logNumpop }\OperatorTok{+}\StringTok{ }\NormalTok{eopop }\OperatorTok{+}\StringTok{ }\NormalTok{men_ineqincwag }\OperatorTok{+}\StringTok{ }\NormalTok{grelimp }\OperatorTok{+}\StringTok{ }\NormalTok{fedrepcons }\OperatorTok{+}\StringTok{ }\NormalTok{urbanization_}\DecValTok{2} \OperatorTok{+}\StringTok{ }\NormalTok{logpop }\OperatorTok{+}\StringTok{ }\NormalTok{inspop }\OperatorTok{+}\StringTok{ }\NormalTok{ind_limits_}\DecValTok{2010}\OperatorTok{*}\NormalTok{ind_limits_dummy }\OperatorTok{+}\StringTok{ }\NormalTok{ind2pty_limits_}\DecValTok{2010}\OperatorTok{*}\NormalTok{ind2pty_limits_dummy }\OperatorTok{+}\StringTok{ }\NormalTok{pac_limits_}\DecValTok{2010}\OperatorTok{*}\NormalTok{pac_limits_dummy, }\DataTypeTok{data =}\NormalTok{ AltBarber, }\DataTypeTok{index =} \KeywordTok{c}\NormalTok{(}\StringTok{"st"}\NormalTok{,}\StringTok{"year"}\NormalTok{), }\DataTypeTok{effect=}\StringTok{"twoways"}\NormalTok{)}
\KeywordTok{summary}\NormalTok{(testmodel03)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Twoways effects Within Model
## 
## Call:
## plm(formula = CCI ~ jdiv + bindingonetermlimit + bindingtwotermlimit + 
##     rpcinc_annual_new + eousa + unemp + citi6006 + high_school + 
##     rgenrevpc + logNumpop + eopop + men_ineqincwag + grelimp + 
##     fedrepcons + urbanization_2 + logpop + inspop + ind_limits_2010 * 
##     ind_limits_dummy + ind2pty_limits_2010 * ind2pty_limits_dummy + 
##     pac_limits_2010 * pac_limits_dummy, data = AltBarber, effect = "twoways", 
##     index = c("st", "year"))
## 
## Unbalanced Panel: n = 48, T = 11-13, N = 618
## 
## Residuals:
##     Min.  1st Qu.   Median  3rd Qu.     Max. 
## -5.22029 -1.08852 -0.12102  0.83586 13.38407 
## 
## Coefficients: (3 dropped because of singularities)
##                         Estimate  Std. Error t-value  Pr(>|t|)    
## jdiv                 -1.7767e-01  2.0591e-01 -0.8628  0.388617    
## bindingonetermlimit  -7.2323e-01  1.3644e+00 -0.5301  0.596282    
## bindingtwotermlimit  -1.8335e-02  2.2332e-01 -0.0821  0.934595    
## rpcinc_annual_new    -5.8467e-04  2.5598e-04 -2.2840  0.022761 *  
## eousa                 5.5245e-03  1.0849e-02  0.5092  0.610809    
## unemp                -1.0827e-01  1.5814e-01 -0.6846  0.493881    
## citi6006             -7.6448e-03  1.9416e-02 -0.3937  0.693931    
## high_school          -4.5817e+00  7.2155e+00 -0.6350  0.525707    
## rgenrevpc             6.8401e-04  1.1443e-03  0.5978  0.550251    
## logNumpop             2.2471e-01  1.8497e-02 12.1486 < 2.2e-16 ***
## eopop                 2.1830e-02  6.6799e-02  0.3268  0.743944    
## men_ineqincwag        1.3021e-01  4.5213e-02  2.8800  0.004137 ** 
## grelimp               2.4629e+01  4.6362e+01  0.5312  0.595488    
## fedrepcons           -6.4202e-02  2.3003e-02 -2.7910  0.005442 ** 
## urbanization_2        1.4034e-01  1.1000e-01  1.2758  0.202593    
## logpop               -3.8183e+00  3.4541e+00 -1.1054  0.269467    
## inspop               -1.2946e-03  2.4236e-03 -0.5342  0.593442    
## ind_limits_2010       4.6294e-05  8.2230e-05  0.5630  0.573685    
## ind_limits_dummy      4.2620e+00  7.9863e+00  0.5337  0.593794    
## ind2pty_limits_2010   3.5794e-06  6.6072e-06  0.5417  0.588223    
## ind2pty_limits_dummy  1.8875e-02  7.0763e-01  0.0267  0.978730    
## pac_limits_2010      -6.8521e-06  3.3117e-05 -0.2069  0.836160    
## pac_limits_dummy     -8.1158e-02  2.9465e+00 -0.0275  0.978036    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Total Sum of Squares:    2911.7
## Residual Sum of Squares: 2128.6
## R-Squared:      0.26896
## Adj. R-Squared: 0.15692
## F-statistic: 8.55816 on 23 and 535 DF, p-value: < 2.22e-16
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{testmodel05 <-}\StringTok{ }\KeywordTok{plm}\NormalTok{(CCI }\OperatorTok{~}\StringTok{ }\NormalTok{jdiv }\OperatorTok{+}\StringTok{ }\NormalTok{bindingonetermlimit }\OperatorTok{+}\StringTok{ }\NormalTok{bindingtwotermlimit }\OperatorTok{+}\StringTok{ }\NormalTok{rpcinc_annual_new }\OperatorTok{+}\StringTok{ }\NormalTok{eousa }\OperatorTok{+}\StringTok{ }\NormalTok{unemp }\OperatorTok{+}\StringTok{ }\NormalTok{citi6006 }\OperatorTok{+}\StringTok{ }\NormalTok{high_school }\OperatorTok{+}\StringTok{ }\NormalTok{rgenrevpc }\OperatorTok{+}\StringTok{ }\NormalTok{logNumpop }\OperatorTok{+}\StringTok{ }\NormalTok{eopop }\OperatorTok{+}\StringTok{ }\NormalTok{men_ineqincwag }\OperatorTok{+}\StringTok{ }\NormalTok{grelimp }\OperatorTok{+}\StringTok{ }\NormalTok{urbanization_}\DecValTok{2} \OperatorTok{+}\StringTok{ }\NormalTok{logpop }\OperatorTok{+}\StringTok{ }\NormalTok{inspop, }\DataTypeTok{data =}\NormalTok{ AltBarber, }\DataTypeTok{index =} \KeywordTok{c}\NormalTok{(}\StringTok{"st"}\NormalTok{,}\StringTok{"year"}\NormalTok{), }\DataTypeTok{effect=}\StringTok{"twoways"}\NormalTok{)}
\KeywordTok{summary}\NormalTok{(testmodel05)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Twoways effects Within Model
## 
## Call:
## plm(formula = CCI ~ jdiv + bindingonetermlimit + bindingtwotermlimit + 
##     rpcinc_annual_new + eousa + unemp + citi6006 + high_school + 
##     rgenrevpc + logNumpop + eopop + men_ineqincwag + grelimp + 
##     urbanization_2 + logpop + inspop, data = AltBarber, effect = "twoways", 
##     index = c("st", "year"))
## 
## Unbalanced Panel: n = 48, T = 11-13, N = 618
## 
## Residuals:
##     Min.  1st Qu.   Median  3rd Qu.     Max. 
## -5.19413 -1.07814 -0.11191  0.84387 13.69793 
## 
## Coefficients:
##                        Estimate  Std. Error t-value  Pr(>|t|)    
## jdiv                -0.17829000  0.20385769 -0.8746  0.382189    
## bindingonetermlimit -0.37832749  1.27790716 -0.2961  0.767303    
## bindingtwotermlimit -0.10234395  0.22079607 -0.4635  0.643176    
## rpcinc_annual_new   -0.00059742  0.00025127 -2.3776  0.017772 *  
## eousa                0.00496122  0.01075659  0.4612  0.644821    
## unemp               -0.12961622  0.15262255 -0.8493  0.396112    
## citi6006            -0.00882295  0.01924654 -0.4584  0.646837    
## high_school         -4.43957589  7.05513532 -0.6293  0.529438    
## rgenrevpc            0.00057200  0.00112735  0.5074  0.612089    
## logNumpop            0.22637491  0.01839343 12.3074 < 2.2e-16 ***
## eopop                0.02908226  0.06520384  0.4460  0.655760    
## men_ineqincwag       0.12693924  0.04471553  2.8388  0.004698 ** 
## grelimp             13.18285583 43.89569361  0.3003  0.764046    
## urbanization_2       0.15342180  0.10949261  1.4012  0.161725    
## logpop              -2.40376676  3.17861979 -0.7562  0.449840    
## inspop              -0.00145727  0.00227518 -0.6405  0.522112    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Total Sum of Squares:    2911.7
## Residual Sum of Squares: 2166.2
## R-Squared:      0.25603
## Adj. R-Squared: 0.15309
## F-statistic: 11.6581 on 16 and 542 DF, p-value: < 2.22e-16
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{testmodel06 <-}\StringTok{ }\KeywordTok{plm}\NormalTok{(CCI }\OperatorTok{~}\StringTok{ }\NormalTok{jdiv }\OperatorTok{+}\StringTok{ }\NormalTok{bindingonetermlimit }\OperatorTok{+}\StringTok{ }\NormalTok{bindingtwotermlimit }\OperatorTok{+}\StringTok{ }\NormalTok{rpcinc_annual_new }\OperatorTok{+}\StringTok{ }\NormalTok{eousa }\OperatorTok{+}\StringTok{ }\NormalTok{unemp }\OperatorTok{+}\StringTok{ }\NormalTok{citi6006 }\OperatorTok{+}\StringTok{ }\NormalTok{high_school }\OperatorTok{+}\StringTok{ }\NormalTok{rgenrevpc }\OperatorTok{+}\StringTok{ }\NormalTok{logNumpop }\OperatorTok{+}\StringTok{ }\NormalTok{eopop }\OperatorTok{+}\StringTok{ }\NormalTok{men_ineqincwag }\OperatorTok{+}\StringTok{ }\NormalTok{grelimp }\OperatorTok{+}\StringTok{ }\NormalTok{urbanization_}\DecValTok{2} \OperatorTok{+}\StringTok{ }\NormalTok{logpop }\OperatorTok{+}\StringTok{ }\NormalTok{inspop }\OperatorTok{+}\StringTok{ }\NormalTok{ind_limits_}\DecValTok{2010}\OperatorTok{*}\NormalTok{ind_limits_dummy }\OperatorTok{+}\StringTok{ }\NormalTok{ind2pty_limits_}\DecValTok{2010}\OperatorTok{*}\NormalTok{ind2pty_limits_dummy }\OperatorTok{+}\StringTok{ }\NormalTok{pac_limits_}\DecValTok{2010}\OperatorTok{*}\NormalTok{pac_limits_dummy, }\DataTypeTok{data =}\NormalTok{ AltBarber, }\DataTypeTok{index =} \KeywordTok{c}\NormalTok{(}\StringTok{"st"}\NormalTok{,}\StringTok{"year"}\NormalTok{), }\DataTypeTok{effect=}\StringTok{"twoways"}\NormalTok{)}
\KeywordTok{summary}\NormalTok{(testmodel06)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Twoways effects Within Model
## 
## Call:
## plm(formula = CCI ~ jdiv + bindingonetermlimit + bindingtwotermlimit + 
##     rpcinc_annual_new + eousa + unemp + citi6006 + high_school + 
##     rgenrevpc + logNumpop + eopop + men_ineqincwag + grelimp + 
##     urbanization_2 + logpop + inspop + ind_limits_2010 * ind_limits_dummy + 
##     ind2pty_limits_2010 * ind2pty_limits_dummy + pac_limits_2010 * 
##     pac_limits_dummy, data = AltBarber, effect = "twoways", index = c("st", 
##     "year"))
## 
## Unbalanced Panel: n = 48, T = 11-13, N = 618
## 
## Residuals:
##     Min.  1st Qu.   Median  3rd Qu.     Max. 
## -5.15526 -1.04988 -0.11867  0.84917 13.64210 
## 
## Coefficients: (3 dropped because of singularities)
##                         Estimate  Std. Error t-value Pr(>|t|)    
## jdiv                 -1.5601e-01  2.0706e-01 -0.7534   0.4515    
## bindingonetermlimit  -6.9102e-01  1.3730e+00 -0.5033   0.6150    
## bindingtwotermlimit  -8.3880e-02  2.2348e-01 -0.3753   0.7076    
## rpcinc_annual_new    -6.1889e-04  2.5730e-04 -2.4053   0.0165 *  
## eousa                 4.9832e-03  1.0916e-02  0.4565   0.6482    
## unemp                -1.4377e-01  1.5862e-01 -0.9064   0.3652    
## citi6006             -6.0887e-03  1.9530e-02 -0.3118   0.7553    
## high_school          -3.7101e+00  7.2542e+00 -0.5114   0.6093    
## rgenrevpc             8.2850e-04  1.1503e-03  0.7202   0.4717    
## logNumpop             2.2595e-01  1.8608e-02 12.1423   <2e-16 ***
## eopop                 3.3961e-02  6.7078e-02  0.5063   0.6129    
## men_ineqincwag        1.2678e-01  4.5481e-02  2.7875   0.0055 ** 
## grelimp               1.6483e+01  4.6563e+01  0.3540   0.7235    
## urbanization_2        1.4689e-01  1.1067e-01  1.3272   0.1850    
## logpop               -3.1599e+00  3.4678e+00 -0.9112   0.3626    
## inspop               -1.0530e-03  2.4374e-03 -0.4320   0.6659    
## ind_limits_2010       4.1554e-05  8.2732e-05  0.5023   0.6157    
## ind_limits_dummy      3.8560e+00  8.0354e+00  0.4799   0.6315    
## ind2pty_limits_2010   3.5071e-06  6.6489e-06  0.5275   0.5981    
## ind2pty_limits_dummy -4.3971e-02  7.1174e-01 -0.0618   0.9508    
## pac_limits_2010      -2.2065e-06  3.3283e-05 -0.0663   0.9472    
## pac_limits_dummy      2.5907e-01  2.9626e+00  0.0874   0.9303    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Total Sum of Squares:    2911.7
## Residual Sum of Squares: 2159.6
## R-Squared:      0.25832
## Adj. R-Squared: 0.14624
## F-statistic: 8.48559 on 22 and 536 DF, p-value: < 2.22e-16
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{BarberICC }\OperatorTok{%>%}\StringTok{ }\KeywordTok{arrange}\NormalTok{(year) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{group_by}\NormalTok{(st) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{mutate}\NormalTok{(}
  \DataTypeTok{ind_d =}\NormalTok{ (ind_limits_}\DecValTok{2010} \OperatorTok{-}\StringTok{ }\NormalTok{dplyr}\OperatorTok{::}\KeywordTok{lag}\NormalTok{(ind_limits_}\DecValTok{2010}\NormalTok{)),}
  \DataTypeTok{ind_dummy_d =}\NormalTok{ (ind_limits_dummy }\OperatorTok{-}\StringTok{ }\NormalTok{dplyr}\OperatorTok{::}\KeywordTok{lag}\NormalTok{(ind_limits_dummy)),}
  \DataTypeTok{pac_d =}\NormalTok{ (pac_limits_}\DecValTok{2010} \OperatorTok{-}\StringTok{ }\NormalTok{dplyr}\OperatorTok{::}\KeywordTok{lag}\NormalTok{(pac_limits_}\DecValTok{2010}\NormalTok{)),}
  \DataTypeTok{pac_dummy_d =}\NormalTok{ (pac_limits_dummy }\OperatorTok{-}\StringTok{ }\NormalTok{dplyr}\OperatorTok{::}\KeywordTok{lag}\NormalTok{(pac_limits_dummy)),}
  \DataTypeTok{ind2pty_d =}\NormalTok{ (ind2pty_limits_}\DecValTok{2010} \OperatorTok{-}\StringTok{ }\NormalTok{dplyr}\OperatorTok{::}\KeywordTok{lag}\NormalTok{(ind2pty_limits_}\DecValTok{2010}\NormalTok{)),}
  \DataTypeTok{ind2pty_dummy_d =}\NormalTok{ (ind2pty_limits_dummy }\OperatorTok{-}\StringTok{ }\NormalTok{dplyr}\OperatorTok{::}\KeywordTok{lag}\NormalTok{(ind2pty_limits_dummy))}
\NormalTok{  ) ->}\StringTok{ }\NormalTok{testframe}

\NormalTok{testframe }\OperatorTok{%>%}\StringTok{ }\KeywordTok{select}\NormalTok{(}\DecValTok{1}\OperatorTok{:}\DecValTok{2}\NormalTok{,}\DecValTok{8}\NormalTok{,}\DecValTok{11}\NormalTok{,}\DecValTok{3}\OperatorTok{:}\DecValTok{7}\NormalTok{,}\DecValTok{12}\OperatorTok{:}\DecValTok{21}\NormalTok{) ->}\StringTok{ }\NormalTok{DiDsmall }
\KeywordTok{summary}\NormalTok{(DiDsmall)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##       st                 year           CCI              CRI        
##  Length:1173        Min.   :1990   Min.   : 0.000   Min.   :0.0000  
##  Class :character   1st Qu.:1995   1st Qu.: 1.348   1st Qu.:0.1577  
##  Mode  :character   Median :2001   Median : 2.562   Median :0.2585  
##                     Mean   :2001   Mean   : 3.226   Mean   :0.2911  
##                     3rd Qu.:2007   3rd Qu.: 4.296   3rd Qu.:0.3862  
##                     Max.   :2012   Max.   :33.846   Max.   :2.1587  
##                                    NA's   :24       NA's   :23      
##  ind_limits_2010 ind2pty_limits_2010 pty_limits_2010  pac_limits_2010
##  Min.   :  143   Min.   :   834      Min.   :   246   Min.   :  223  
##  1st Qu.: 1397   1st Qu.: 24238      1st Qu.: 11707   1st Qu.: 2103  
##  Median : 4310   Median : 99999      Median : 99999   Median :10128  
##  Mean   :32911   Mean   : 72592      Mean   : 64022   Mean   :39604  
##  3rd Qu.:99999   3rd Qu.: 99999      3rd Qu.: 99999   3rd Qu.:99999  
##  Max.   :99999   Max.   :196470      Max.   :150904   Max.   :99999  
##  NA's   :23      NA's   :23          NA's   :23       NA's   :23     
##  total_limits_2010 ind_limits_dummy ind2pty_limits_dummy pac_limits_dummy
##  Min.   :  4772    Min.   :0.0000   Min.   :0.0000       Min.   :0.0000  
##  1st Qu.: 99999    1st Qu.:0.0000   1st Qu.:0.0000       1st Qu.:0.0000  
##  Median : 99999    Median :1.0000   Median :0.0000       Median :1.0000  
##  Mean   : 96196    Mean   :0.6974   Mean   :0.4104       Mean   :0.6452  
##  3rd Qu.: 99999    3rd Qu.:1.0000   3rd Qu.:1.0000       3rd Qu.:1.0000  
##  Max.   :500511    Max.   :1.0000   Max.   :1.0000       Max.   :1.0000  
##  NA's   :23        NA's   :23       NA's   :23           NA's   :23      
##  total_limits_dummy     ind_d           ind_dummy_d      
##  Min.   :0.0000     Min.   :-99856.0   Min.   :-1.00000  
##  1st Qu.:0.0000     1st Qu.:   -77.0   1st Qu.: 0.00000  
##  Median :0.0000     Median :   -20.0   Median : 0.00000  
##  Mean   :0.1635     Mean   :  -913.4   Mean   : 0.00909  
##  3rd Qu.:0.0000     3rd Qu.:     0.0   3rd Qu.: 0.00000  
##  Max.   :1.0000     Max.   : 99731.0   Max.   : 1.00000  
##  NA's   :23         NA's   :73         NA's   :73        
##      pac_d           pac_dummy_d         ind2pty_d        
##  Min.   :-99713.0   Min.   :-1.00000   Min.   :-115296.0  
##  1st Qu.:  -113.0   1st Qu.: 0.00000   1st Qu.:   -263.2  
##  Median :   -19.5   Median : 0.00000   Median :      0.0  
##  Mean   : -1194.4   Mean   : 0.01364   Mean   :   -533.7  
##  3rd Qu.:     0.0   3rd Qu.: 0.00000   3rd Qu.:      0.0  
##  Max.   : 99721.0   Max.   : 1.00000   Max.   : 120086.0  
##  NA's   :73         NA's   :73         NA's   :73         
##  ind2pty_dummy_d   
##  Min.   :-1.00000  
##  1st Qu.: 0.00000  
##  Median : 0.00000  
##  Mean   : 0.00818  
##  3rd Qu.: 0.00000  
##  Max.   : 1.00000  
##  NA's   :73
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Now I have what I think are three multi-level categorical independent variables. }
\CommentTok{# https://stats.idre.ucla.edu/r/modules/coding-for-categorical-variables-in-regression-models/}
\CommentTok{#1. When limits were imposed (1) or went down, did corruption go down? }
\CommentTok{#2. When limits were removed (-1) or went up, did corruption go up? }

\NormalTok{DiDsmall}\OperatorTok{$}\NormalTok{ind_dummy_f <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(DiDsmall}\OperatorTok{$}\NormalTok{ind_dummy_d)}
\NormalTok{DiDsmall <-}\StringTok{ }\KeywordTok{within}\NormalTok{(DiDsmall, ind_dummy_f <-}\StringTok{ }\KeywordTok{relevel}\NormalTok{(ind_dummy_f, }\DataTypeTok{ref =} \StringTok{"0"}\NormalTok{))}
\NormalTok{DiDsmall}\OperatorTok{$}\NormalTok{pac_dummy_f <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(DiDsmall}\OperatorTok{$}\NormalTok{pac_dummy_d)}
\NormalTok{DiDsmall <-}\StringTok{ }\KeywordTok{within}\NormalTok{(DiDsmall, pac_dummy_f <-}\StringTok{ }\KeywordTok{relevel}\NormalTok{(pac_dummy_f, }\DataTypeTok{ref =} \StringTok{"0"}\NormalTok{))}
\NormalTok{DiDsmall}\OperatorTok{$}\NormalTok{ind2pty_dummy_f <-}\StringTok{ }\KeywordTok{factor}\NormalTok{(DiDsmall}\OperatorTok{$}\NormalTok{ind2pty_dummy_d)}
\NormalTok{DiDsmall <-}\StringTok{ }\KeywordTok{within}\NormalTok{(DiDsmall, ind2pty_dummy_f <-}\StringTok{ }\KeywordTok{relevel}\NormalTok{(ind2pty_dummy_f, }\DataTypeTok{ref =} \StringTok{"0"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{summary}\NormalTok{(}\KeywordTok{lm}\NormalTok{(CCI }\OperatorTok{~}\StringTok{ }\NormalTok{ind_dummy_f, }\DataTypeTok{data =}\NormalTok{ DiDsmall))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Call:
## lm(formula = CCI ~ ind_dummy_f, data = DiDsmall)
## 
## Residuals:
##     Min      1Q  Median      3Q     Max 
## -3.1979 -1.8494 -0.6355  1.0862 30.6483 
## 
## Coefficients:
##               Estimate Std. Error t value Pr(>|t|)    
## (Intercept)    3.19792    0.08943  35.758   <2e-16 ***
## ind_dummy_f-1 -0.73316    1.20153  -0.610    0.542    
## ind_dummy_f1  -0.46753    0.73917  -0.633    0.527    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 2.935 on 1096 degrees of freedom
##   (74 observations deleted due to missingness)
## Multiple R-squared:  0.000698,   Adjusted R-squared:  -0.001126 
## F-statistic: 0.3827 on 2 and 1096 DF,  p-value: 0.6821
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{summary}\NormalTok{(}\KeywordTok{lm}\NormalTok{(CCI }\OperatorTok{~}\StringTok{ }\NormalTok{pac_dummy_f, }\DataTypeTok{data =}\NormalTok{ DiDsmall))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Call:
## lm(formula = CCI ~ pac_dummy_f, data = DiDsmall)
## 
## Residuals:
##     Min      1Q  Median      3Q     Max 
## -3.1969 -1.8484 -0.6345  1.0814 30.6493 
## 
## Coefficients:
##               Estimate Std. Error t value Pr(>|t|)    
## (Intercept)    3.19693    0.08965  35.659   <2e-16 ***
## pac_dummy_f-1 -0.39146    1.20169  -0.326    0.745    
## pac_dummy_f1  -0.40231    0.64679  -0.622    0.534    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 2.935 on 1096 degrees of freedom
##   (74 observations deleted due to missingness)
## Multiple R-squared:  0.0004459,  Adjusted R-squared:  -0.001378 
## F-statistic: 0.2444 on 2 and 1096 DF,  p-value: 0.7832
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{summary}\NormalTok{(}\KeywordTok{lm}\NormalTok{(CCI }\OperatorTok{~}\StringTok{ }\NormalTok{ind2pty_dummy_f, }\DataTypeTok{data =}\NormalTok{ DiDsmall))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Call:
## lm(formula = CCI ~ ind2pty_dummy_f, data = DiDsmall)
## 
## Residuals:
##     Min      1Q  Median      3Q     Max 
## -3.1870 -1.8367 -0.6887  1.0878 30.6592 
## 
## Coefficients:
##                   Estimate Std. Error t value Pr(>|t|)    
## (Intercept)        3.18704    0.08896  35.827   <2e-16 ***
## ind2pty_dummy_f-1 -3.18704    2.93559  -1.086    0.278    
## ind2pty_dummy_f1   0.32578    0.93214   0.349    0.727    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 2.934 on 1096 degrees of freedom
##   (74 observations deleted due to missingness)
## Multiple R-squared:  0.001187,   Adjusted R-squared:  -0.0006352 
## F-statistic: 0.6515 on 2 and 1096 DF,  p-value: 0.5215
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{summary}\NormalTok{(}\KeywordTok{lm}\NormalTok{(CRI }\OperatorTok{~}\StringTok{ }\NormalTok{ind_dummy_f, }\DataTypeTok{data =}\NormalTok{ DiDsmall))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Call:
## lm(formula = CRI ~ ind_dummy_f, data = DiDsmall)
## 
## Residuals:
##      Min       1Q   Median       3Q      Max 
## -0.29085 -0.13371 -0.03591  0.09706  1.86780 
## 
## Coefficients:
##               Estimate Std. Error t value Pr(>|t|)    
## (Intercept)   0.290846   0.005898  49.317   <2e-16 ***
## ind_dummy_f-1 0.079369   0.079270   1.001    0.317    
## ind_dummy_f1  0.008152   0.048766   0.167    0.867    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 0.1936 on 1097 degrees of freedom
##   (73 observations deleted due to missingness)
## Multiple R-squared:  0.0009358,  Adjusted R-squared:  -0.0008857 
## F-statistic: 0.5138 on 2 and 1097 DF,  p-value: 0.5984
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{summary}\NormalTok{(}\KeywordTok{lm}\NormalTok{(CRI }\OperatorTok{~}\StringTok{ }\NormalTok{pac_dummy_f, }\DataTypeTok{data =}\NormalTok{ DiDsmall))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Call:
## lm(formula = CRI ~ pac_dummy_f, data = DiDsmall)
## 
## Residuals:
##      Min       1Q   Median       3Q      Max 
## -0.29082 -0.13369 -0.03575  0.09653  1.86783 
## 
## Coefficients:
##               Estimate Std. Error t value Pr(>|t|)    
## (Intercept)   0.290823   0.005911  49.202   <2e-16 ***
## pac_dummy_f-1 0.086208   0.079265   1.088    0.277    
## pac_dummy_f1  0.005480   0.042662   0.128    0.898    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 0.1936 on 1097 degrees of freedom
##   (73 observations deleted due to missingness)
## Multiple R-squared:  0.00109,    Adjusted R-squared:  -0.0007316 
## F-statistic: 0.5983 on 2 and 1097 DF,  p-value: 0.5499
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{summary}\NormalTok{(}\KeywordTok{lm}\NormalTok{(CRI }\OperatorTok{~}\StringTok{ }\NormalTok{ind2pty_dummy_f, }\DataTypeTok{data =}\NormalTok{ DiDsmall))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Call:
## lm(formula = CRI ~ ind2pty_dummy_f, data = DiDsmall)
## 
## Residuals:
##      Min       1Q   Median       3Q      Max 
## -0.29159 -0.13382 -0.03481  0.09631  1.86706 
## 
## Coefficients:
##                    Estimate Std. Error t value Pr(>|t|)    
## (Intercept)        0.291590   0.005870  49.674   <2e-16 ***
## ind2pty_dummy_f-1 -0.004768   0.193803  -0.025    0.980    
## ind2pty_dummy_f1  -0.020676   0.061538  -0.336    0.737    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 0.1937 on 1097 degrees of freedom
##   (73 observations deleted due to missingness)
## Multiple R-squared:  0.0001034,  Adjusted R-squared:  -0.00172 
## F-statistic: 0.05672 on 2 and 1097 DF,  p-value: 0.9449
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# No effects }

\KeywordTok{summary}\NormalTok{(}\KeywordTok{lm}\NormalTok{(CCI }\OperatorTok{~}\StringTok{ }\NormalTok{ind_dummy_f}\OperatorTok{*}\NormalTok{ind_d, }\DataTypeTok{data =}\NormalTok{ DiDsmall))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Call:
## lm(formula = CCI ~ ind_dummy_f * ind_d, data = DiDsmall)
## 
## Residuals:
##     Min      1Q  Median      3Q     Max 
## -3.2595 -1.8493 -0.6567  1.0889 30.6486 
## 
## Coefficients:
##                       Estimate Std. Error t value Pr(>|t|)    
## (Intercept)          3.198e+00  8.969e-02  35.660   <2e-16 ***
## ind_dummy_f-1        2.759e+01  1.171e+02   0.236    0.814    
## ind_dummy_f1         4.038e+00  2.599e+01   0.155    0.877    
## ind_d                1.053e-05  1.088e-04   0.097    0.923    
## ind_dummy_f-1:ind_d -2.966e-04  1.187e-03  -0.250    0.803    
## ind_dummy_f1:ind_d   3.601e-05  2.896e-04   0.124    0.901    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 2.939 on 1093 degrees of freedom
##   (74 observations deleted due to missingness)
## Multiple R-squared:  0.0007875,  Adjusted R-squared:  -0.003783 
## F-statistic: 0.1723 on 5 and 1093 DF,  p-value: 0.9729
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{summary}\NormalTok{(}\KeywordTok{lm}\NormalTok{(CCI }\OperatorTok{~}\StringTok{ }\NormalTok{pac_dummy_f}\OperatorTok{*}\NormalTok{pac_d, }\DataTypeTok{data =}\NormalTok{ DiDsmall))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Call:
## lm(formula = CCI ~ pac_dummy_f * pac_d, data = DiDsmall)
## 
## Residuals:
##     Min      1Q  Median      3Q     Max 
## -3.3006 -1.8479 -0.6341  1.0861 30.6491 
## 
## Coefficients:
##                       Estimate Std. Error t value Pr(>|t|)    
## (Intercept)          3.196e+00  8.987e-02  35.566   <2e-16 ***
## pac_dummy_f-1       -4.699e+00  4.269e+01  -0.110    0.912    
## pac_dummy_f1        -9.769e-01  2.786e+00  -0.351    0.726    
## pac_d               -8.187e-06  7.209e-05  -0.114    0.910    
## pac_dummy_f-1:pac_d  5.208e-05  4.407e-04   0.118    0.906    
## pac_dummy_f1:pac_d   1.622e-06  7.844e-05   0.021    0.984    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 2.939 on 1093 degrees of freedom
##   (74 observations deleted due to missingness)
## Multiple R-squared:  0.0005082,  Adjusted R-squared:  -0.004064 
## F-statistic: 0.1111 on 5 and 1093 DF,  p-value: 0.9899
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{summary}\NormalTok{(}\KeywordTok{lm}\NormalTok{(CCI }\OperatorTok{~}\StringTok{ }\NormalTok{ind2pty_dummy_f}\OperatorTok{*}\NormalTok{ind2pty_d, }\DataTypeTok{data =}\NormalTok{ DiDsmall))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Call:
## lm(formula = CCI ~ ind2pty_dummy_f * ind2pty_d, data = DiDsmall)
## 
## Residuals:
##     Min      1Q  Median      3Q     Max 
## -3.2029 -1.8359 -0.6813  1.0865 30.6493 
## 
## Coefficients: (1 not defined because of singularities)
##                               Estimate Std. Error t value Pr(>|t|)    
## (Intercept)                  3.184e+00  8.904e-02  35.765   <2e-16 ***
## ind2pty_dummy_f-1           -1.944e+00  3.317e+00  -0.586    0.558    
## ind2pty_dummy_f1            -2.523e-01  1.133e+00  -0.223    0.824    
## ind2pty_d                   -1.313e-05  1.631e-05  -0.805    0.421    
## ind2pty_dummy_f-1:ind2pty_d         NA         NA      NA       NA    
## ind2pty_dummy_f1:ind2pty_d   6.468e-07  2.139e-05   0.030    0.976    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 2.935 on 1094 degrees of freedom
##   (74 observations deleted due to missingness)
## Multiple R-squared:  0.00252,    Adjusted R-squared:  -0.001127 
## F-statistic: 0.691 on 4 and 1094 DF,  p-value: 0.5983
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{summary}\NormalTok{(}\KeywordTok{lm}\NormalTok{(CRI }\OperatorTok{~}\StringTok{ }\NormalTok{ind_dummy_f}\OperatorTok{*}\NormalTok{ind_d, }\DataTypeTok{data =}\NormalTok{ DiDsmall))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Call:
## lm(formula = CRI ~ ind_dummy_f * ind_d, data = DiDsmall)
## 
## Residuals:
##      Min       1Q   Median       3Q      Max 
## -0.29128 -0.13350 -0.03540  0.09671  1.86737 
## 
## Coefficients:
##                       Estimate Std. Error t value Pr(>|t|)    
## (Intercept)          2.913e-01  5.908e-03  49.301   <2e-16 ***
## ind_dummy_f-1       -3.567e+00  7.717e+00  -0.462    0.644    
## ind_dummy_f1         1.324e+00  1.713e+00   0.773    0.440    
## ind_d                9.312e-06  7.168e-06   1.299    0.194    
## ind_dummy_f-1:ind_d  2.750e-05  7.826e-05   0.351    0.725    
## ind_dummy_f1:ind_d   4.280e-06  1.908e-05   0.224    0.823    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 0.1937 on 1094 degrees of freedom
##   (73 observations deleted due to missingness)
## Multiple R-squared:  0.003215,   Adjusted R-squared:  -0.001341 
## F-statistic: 0.7057 on 5 and 1094 DF,  p-value: 0.6192
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{summary}\NormalTok{(}\KeywordTok{lm}\NormalTok{(CRI }\OperatorTok{~}\StringTok{ }\NormalTok{pac_dummy_f}\OperatorTok{*}\NormalTok{pac_d, }\DataTypeTok{data =}\NormalTok{ DiDsmall))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Call:
## lm(formula = CRI ~ pac_dummy_f * pac_d, data = DiDsmall)
## 
## Residuals:
##      Min       1Q   Median       3Q      Max 
## -0.29115 -0.13375 -0.03518  0.09523  1.86789 
## 
## Coefficients:
##                       Estimate Std. Error t value Pr(>|t|)    
## (Intercept)          2.908e-01  5.923e-03  49.089   <2e-16 ***
## pac_dummy_f-1       -1.586e+00  2.815e+00  -0.563    0.573    
## pac_dummy_f1         1.285e-01  1.837e-01   0.700    0.484    
## pac_d               -1.018e-06  4.753e-06  -0.214    0.830    
## pac_dummy_f-1:pac_d  1.806e-05  2.906e-05   0.621    0.534    
## pac_dummy_f1:pac_d   2.422e-06  5.172e-06   0.468    0.640    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 0.1938 on 1094 degrees of freedom
##   (73 observations deleted due to missingness)
## Multiple R-squared:  0.001886,   Adjusted R-squared:  -0.002676 
## F-statistic: 0.4135 on 5 and 1094 DF,  p-value: 0.8396
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{summary}\NormalTok{(}\KeywordTok{lm}\NormalTok{(CRI }\OperatorTok{~}\StringTok{ }\NormalTok{ind2pty_dummy_f}\OperatorTok{*}\NormalTok{ind2pty_d, }\DataTypeTok{data =}\NormalTok{ DiDsmall))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Call:
## lm(formula = CRI ~ ind2pty_dummy_f * ind2pty_d, data = DiDsmall)
## 
## Residuals:
##      Min       1Q   Median       3Q      Max 
## -0.29198 -0.13371 -0.03515  0.09587  1.86716 
## 
## Coefficients: (1 not defined because of singularities)
##                               Estimate Std. Error t value Pr(>|t|)    
## (Intercept)                  2.915e-01  5.877e-03  49.595   <2e-16 ***
## ind2pty_dummy_f-1            4.441e-02  2.191e-01   0.203    0.839    
## ind2pty_dummy_f1             1.013e-02  7.483e-02   0.135    0.892    
## ind2pty_d                   -5.197e-07  1.077e-06  -0.483    0.630    
## ind2pty_dummy_f-1:ind2pty_d         NA         NA      NA       NA    
## ind2pty_dummy_f1:ind2pty_d   1.180e-06  1.413e-06   0.835    0.404    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 0.1938 on 1095 degrees of freedom
##   (73 observations deleted due to missingness)
## Multiple R-squared:  0.0007914,  Adjusted R-squared:  -0.002859 
## F-statistic: 0.2168 on 4 and 1095 DF,  p-value: 0.9291
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# No effects }

\CommentTok{# Next: Lag, write up. }
\end{Highlighting}
\end{Shaded}

\end{document}

### 2018-05-23 Paper.Rmd
Rearranging files, starting new knitr document, crossing fingers.

---
title: | 
  | Do campaign contribution limits limit corruption? 
  | Evidence from the 50 states
author: "Mark Hand"
date: "5/23/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, message=FALSE, warning=FALSE)
library(haven) # import .dta
library(tidyverse) # everything 
library(plm) # For linear panel regression
```

Since the 1970s, the U.S. Supreme Court has frustrated efforts at campaign finance reform by holding that nearly all limits on political spending violate the first amendment’s protection of free speech, with only one exception: to prevent “corruption of the appearance of corruption.” Using state-level data from 1990-2012 on contribution limits, corruption arrests, and media mentions of corruption, this paper employs a linear panel regression and a difference-in-differences analysis to test whether campaign contribution limits are associated with lower levels of corruption arrests or media mentions of corruption. These methods find no relationship between the presence or level of campaign finance laws and quid pro quo corruption. As current challenges to contribution limits wind their way through federal courts, the answer to this question will inform the Supreme Court’s decision to uphold or strike down remaining limits on political campaign contributions.

\newpage

##Introduction
In 1976, the Supreme Court ruled in Buckley v. Valeo that political campaign contributions are the equivalent of free speech, and therefore protected by the first amendment. At the same time, the Court laid out one mechanism and one justification for limiting those contributions. First, it argued that more money spent doesn’t amount of “more” speech, allowing for campaign contribution dollar amount limits. Donating one dollar or $5,000 to a political campaign amounts to a speech act, the Court held, and so it is permissible to impose limits on the amount of contributions as long as contributions are not prevented. Second, having laid out the mechanism by which money in politics might be limited, the court laid out the only justification for limiting contributions that it would accept moving forward: To prevent corruption or the appearance thereof. As Kang (2012) argues, the holdings in Buckley v. Valeo provided “the basic framework of contribution limits and disclosure requirements” for the following four decades. Since Buckley v. Valeo, Congress has passed only one campaign finance law, the Bipartisan Campaign Reform Act of 2002. Better know as McCain-Feingold, the bill took aim at unlimited “soft money” contributions to political parties and expanded the Federal Election Commission’s disclosure requirements to what it called “electioneering communications,” political ads not paid for by campaigns themselves.

Apart from McCain-Feingold, for forty years all changes in the landscape of campaign finance have come from the courts, the majority being decided upon how to balance questions of free political speech versus corruption. Those rulings have often been driven by the question of corporations’ participation in the political process. In 1978, the Court extended free speech protections to corporations (First National Bank of Boston v. Bellotti). In 1986, it  and struck down efforts to restrict their expenditures to FEC-registered Political Action Committees (FEC v. Massachusetts Right to Life). Then in 1990, it upheld a ban on corporations using treasury funds to pay for issue advertisements, arguing for an extended definition of corruption, "the corrosive and distorting effects of immense aggregations of wealth that are accumulated with the help of the corporate form and that have little or no correlation to the public's support for the corporation's political ideas" (Austin v. Michigan State Chamber of Commerce, later overturned).

The passage of the McCain-Feingold in 2002 inspired a wave of challenges to campaign contributions and expenditures, driven mostly by conservative and religious groups. In 2007, the Court examined the McCain-Feingold ban on airing issue advertisements close to election. Banning such ads, the Court argued, would have a chilling effect on free speech, and it struck down the ban (FEC v. Wisconsin Right to Life). Then, in 2010, the Court issued what has become one of its most well-known rulings: In Citizens United v. FEC (2010), it struck down limits on independent expenditures by outside groups, including corporations and unions. One critical aspect of Citizens United is the establishment of the principle that, according to Justice Anthony Kennedy, “independent expenditures do not lead to, or create the appearance of, quid pro quo corruption.” The Court’s emphasis on quid pro quo corruption as the only justification for contribution limits extended the following year, as it struck down an Arizona effort to level the political playing field with matching state campaign funds (Arizona Free Enterprise Club v. Bennett, 2011).

Since 2011, the network of conservative legal groups behind Citizens United has continued to take aim at contribution limits as an unnecessary restriction of political speech, with a focus on individual contribution limits. The 1971 Federal Election Campaign Act placed a limit on the amount an individual could give to one campaign, in addition to two-year limits on the total amount an individual could give to political campaigns. In McCutcheon v. FEC (2014) James Bopp, one of the attorneys behind the Citizens United challenge, convinced the Court of the unconstitutionality of total individual limits. Another case, Holmes v. FEC (2017), targeted the distribution of individual campaign contribution across primary and general elections. In yet another, Lair v. Motl (2017), Bopp once again took aim at individual contribution limits, arguing that the state of Montana had not shown compelling evidence that campaign contribution limits decreased the risk of corruption.

The Ninth Circuit Court of Appeals upheld Montana’s campaign contribution limits, but further challenges to contribution limits are likely. Bopp said that he planned to appeal the Ninth Circuit’s ruling. Even if that fails, Bopp and other conservative groups plan to carry on. “I handle a lot of cases,” he said after the 2014 McCutcheon ruling, “and I‘m not done yet.” Supreme Court Justice Clarence Thomas laid the groundwork for future challenges in his commentary on the McCutcheon decision by arguing that more dollars did, in fact, equate to more speech. Once established, that principle supports the argument that campaign contribution dollar amount limits are a potentially unconstitutional restriction on speech (Hurley & Debenedetti 2014, Zall 2017).

### 2018-05-23 Paper.Rmd
Nervous committing

@@
 
+```{r data import, include=F}
+# Alt and Lassen's "Enforcement and Public Corruption: Evidence from US States"
+# http://epstein.wustl.edu/research/LPE.Alt.pdf
+AltLassen <- read_dta("data/Replication/AltLassenJLEO.dta")
+
+# Michael Barber's "Ideological Donors, Contribution Limits, and the Polarization of American Legislatures"  
+# https://doi.org/10.1086/683453
+Barber <- read_csv("~/Documents/GitHub/Money-in-Politics/data/Barber/Barber_Limits_Data.csv")
+
+# Data from ICC 
+# www.greasethewheels.org/cci/
+convictions <- read_csv("~/Documents/GitHub/Money-in-Politics/data/ICS/CCI19762015.csv")
+reflections <- read_csv("~/Documents/GitHub/Money-in-Politics/data/ICS/CRI19772013.csv")
+```
+
+```{r panel data wrangling, include=F}
+# Combining Barber and ICS 
+corruption <- full_join(convictions, reflections)
+corruption <- corruption %>% 
+  rename("st"="State", "year"="Year")
+corruption$st <- state.abb[match(corruption$st,state.name)]
+BarberICC <- left_join(Barber, corruption)
+
+BarberICC <- BarberICC %>% 
+  mutate(
+    ind_limits_dummy = ifelse(ind_limits_2010==99999,0,1),
+    ind2pty_limits_dummy = ifelse(ind2pty_limits_2010==99999,0,1),
+    pac_limits_dummy = ifelse(pac_limits_2010==99999,0,1),
+    total_limits_dummy = ifelse(total_limits_2010==99999,0,1)
+  )
+
+# Adding AltLassen
+# table(AltLassen$state_name)
+AltLassen$state_name[AltLassen$state_name=="Californ"] = "California"
+AltLassen$state_name[AltLassen$state_name=="Connecti"] = "Connecticut"
+AltLassen$state_name[AltLassen$state_name=="Louisian"] = "Louisiana"
+AltLassen$state_name[AltLassen$state_name=="Massachu"] = "Massachusetts"
+AltLassen$state_name[AltLassen$state_name=="Minnesot"] = "Minnesota"
+AltLassen$state_name[AltLassen$state_name=="Mississi"] = "Mississippi"
+AltLassen$state_name[AltLassen$state_name=="NewHamps"] = "New Hampshire"
+AltLassen$state_name[AltLassen$state_name=="NewJerse"] = "New Jersey"
+AltLassen$state_name[AltLassen$state_name=="NewMexic"] = "New Mexico"
+AltLassen$state_name[AltLassen$state_name=="NewYork"] = "New York"
+AltLassen$state_name[AltLassen$state_name=="NorthCar"] = "North Carolina"
+AltLassen$state_name[AltLassen$state_name=="NorthDak"] = "North Dakota"
+AltLassen$state_name[AltLassen$state_name=="Pennsylv"] = "Pennsylvania"
+AltLassen$state_name[AltLassen$state_name=="RhodeIsl"] = "Rhode Island"
+AltLassen$state_name[AltLassen$state_name=="SouthCar"] = "South Carolina"
+AltLassen$state_name[AltLassen$state_name=="SouthDak"] = "South Dakota"
+AltLassen$state_name[AltLassen$state_name=="Tennesse"] = "Tennessee"
+AltLassen$state_name[AltLassen$state_name=="Washingt"] = "Washington"
+AltLassen$state_name[AltLassen$state_name=="WestVirg"] = "West Virginia"
+AltLassen$state_name[AltLassen$state_name=="Wisconsi"] = "Wisconsin"
+AltLassen$state_name <- state.abb[match(AltLassen$state_name,state.name)]
+AltLassen <- AltLassen %>% 
+  rename("st"="state_name")
+AltLassen$year <-as.integer(AltLassen$year)
+
+AltBarber <- inner_join(BarberICC, AltLassen)
+```
+
+```{r DiD wrangling, include=F}
+BarberICC %>% arrange(year) %>% group_by(st) %>% mutate(
+  ind_d = (ind_limits_2010 - dplyr::lag(ind_limits_2010)),
+  ind_dummy_d = (ind_limits_dummy - dplyr::lag(ind_limits_dummy)),
+  pac_d = (pac_limits_2010 - dplyr::lag(pac_limits_2010)),
+  pac_dummy_d = (pac_limits_dummy - dplyr::lag(pac_limits_dummy)),
+  ind2pty_d = (ind2pty_limits_2010 - dplyr::lag(ind2pty_limits_2010)),
+  ind2pty_dummy_d = (ind2pty_limits_dummy - dplyr::lag(ind2pty_limits_dummy))
+  ) -> testframe
+
+testframe %>% select(1:2,8,11,3:7,12:21) -> DiDsmall 
+summary(DiDsmall)
+
+# Now I have what I think are three multi-level categorical independent variables. 
+# https://stats.idre.ucla.edu/r/modules/coding-for-categorical-variables-in-regression-models/
+#1. When limits were imposed (1) or went down, did corruption go down? 
+#2. When limits were removed (-1) or went up, did corruption go up?
+
+DiDsmall$ind_dummy_f <- factor(DiDsmall$ind_dummy_d)
+DiDsmall <- within(DiDsmall, ind_dummy_f <- relevel(ind_dummy_f, ref = "0"))
+DiDsmall$pac_dummy_f <- factor(DiDsmall$pac_dummy_d)
+DiDsmall <- within(DiDsmall, pac_dummy_f <- relevel(pac_dummy_f, ref = "0"))
+DiDsmall$ind2pty_dummy_f <- factor(DiDsmall$ind2pty_dummy_d)
+DiDsmall <- within(DiDsmall, ind2pty_dummy_f <- relevel(ind2pty_dummy_f, ref = "0"))
+```
+
+```{r panel modeling, include=F}
+#Next: Panel model of corruption against unemployment and high school? 
+testmodel01 <- plm(CCI ~ rpcinc_annual_new + unemp + high_school + logNumpop + citi6006 + grelimp, data = AltBarber, index = c("st","year"), effect="twoways")
+summary(testmodel01)
+
+testmodel02 <- plm(CCI ~ jdiv + bindingonetermlimit + bindingtwotermlimit + rpcinc_annual_new + eousa + unemp + citi6006 + high_school + rgenrevpc + logNumpop + eopop + men_ineqincwag + grelimp + fedrepcons + urbanization_2 + logpop + inspop, data = AltBarber, index = c("st","year"), effect="twoways")
+summary(testmodel02)
+
+testmodel03 <- plm(CCI ~ jdiv + bindingonetermlimit + bindingtwotermlimit + rpcinc_annual_new + eousa + unemp + citi6006 + high_school + rgenrevpc + logNumpop + eopop + men_ineqincwag + grelimp + fedrepcons + urbanization_2 + logpop + inspop + ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = AltBarber, index = c("st","year"), effect="twoways")
+summary(testmodel03)
+
+testmodel05 <- plm(CCI ~ jdiv + bindingonetermlimit + bindingtwotermlimit + rpcinc_annual_new + eousa + unemp + citi6006 + high_school + rgenrevpc + logNumpop + eopop + men_ineqincwag + grelimp + urbanization_2 + logpop + inspop, data = AltBarber, index = c("st","year"), effect="twoways")
+summary(testmodel05)
+
+testmodel06 <- plm(CCI ~ jdiv + bindingonetermlimit + bindingtwotermlimit + rpcinc_annual_new + eousa + unemp + citi6006 + high_school + rgenrevpc + logNumpop + eopop + men_ineqincwag + grelimp + urbanization_2 + logpop + inspop + ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = AltBarber, index = c("st","year"), effect="twoways")
+summary(testmodel06)
+
+```
+
+```{r DiD modeling, include=F}
+summary(lm(CCI ~ ind_dummy_f, data = DiDsmall))
+summary(lm(CCI ~ pac_dummy_f, data = DiDsmall))
+summary(lm(CCI ~ ind2pty_dummy_f, data = DiDsmall))
+summary(lm(CRI ~ ind_dummy_f, data = DiDsmall))
+summary(lm(CRI ~ pac_dummy_f, data = DiDsmall))
+summary(lm(CRI ~ ind2pty_dummy_f, data = DiDsmall))
+# No effects
+
+summary(lm(CCI ~ ind_dummy_f*ind_d, data = DiDsmall))
+summary(lm(CCI ~ pac_dummy_f*pac_d, data = DiDsmall))
+summary(lm(CCI ~ ind2pty_dummy_f*ind2pty_d, data = DiDsmall))
+summary(lm(CRI ~ ind_dummy_f*ind_d, data = DiDsmall))
+summary(lm(CRI ~ pac_dummy_f*pac_d, data = DiDsmall))
+summary(lm(CRI ~ ind2pty_dummy_f*ind2pty_d, data = DiDsmall))
+# No effects
+
+# Next: Lag, write up. 
+```
+
 Since the 1970s, the U.S.
@@
 \newpage 
-
 ##Introduction
+###Shorten? 
 In 1976, the Supreme Court ruled in Buckley v.
@@
 Once established, that principle supports the argument that campaign contribution dollar amount limits are a potentially unconstitutional restriction on speech (Hurley & Debenedetti 2014, Zall 2017).
+
+##Prior Work 
+Since the Buckley v.
+Valeo decision, a wave of scholarship has taken advantage of the campaign contribution data collected by the Federal Election Commission to examine the causes and consequences of political campaign contributions, including whether contributions buy access (not to a meaningful degree, find Welch 1982 and Langbein 1986) and the effectiveness of contributions relative to lobbying efforts (yes, according to Wright 1990).
+Since the 2010 Citizens United and speechnow.org decisions, another arm of scholarship has examined the flows of money to groups engaging in independent expenditures (Spencer and Wood 2014, Werner and Coleman 2014).
+
+But lobbying, money for access, and independent expenditures all fall outside of the narrow definition of quid pro corruption that the Supreme Court considers a compelling enough state interest to justify campaign contribution limits.
+The scholarly research on corruption thus narrowly defined is mixed and heated.
+Stratmann finds evidence that donations determined votes in at least one instance (1991); he also finds that the timing of political action committees (PAC) donations suggests that corporations believe those donations do affect legislators’ votes (1998).
+Reacting to the absence of evidence that donations lead to favorable final votes on bills, Hall and Wayman (1990) look for and find a positive relationship between political donations and the amount of attention that legislators give to a particular issue.
+Other scholars, however, are not so convinced.
+Wright (1990) finds that once lobbying efforts are factored in, the effects of contributions on voting outcomes washes out.
+And it is notoriously difficult to tease out whether political donations change legislators’ minds or instead flow to legislators with established, friendly positions (Ansolabehere et al 2003).
+
+As mentioned above, the Court is also interested in the appearance of corruption.
+On this score, results are more consonant: There seems to be little association between campaign spending and public trust in government (Primo 2002).
+Other factors, including media coverage of campaign finance law and the professionalization of legislatures, are more predictive of public perceptions of corruptions (Rosenson 2009).
+And while the public does seem to report viewing campaign finance as a contributor to corruption, there is not evidence that reform efforts will have an effect on those views (Persily & Lammie 2004).
+
+One fundamental limitation of these federal level studies on campaign contributions and corruption, however, is the absence of a counterfactual: Given that contribution limits have been in place since the 1970s, it is difficult to argue what might have happened in their absence.
+Recent work on campaign finance has attempted to address this problem by focusing on the effects of differences in campaign finance laws at the state level.
+Variation across states and over time allows room for studying the causes and consequences of campaign finance limits.
+Studies suggest that campaign finance limits are associated with less electoral competition (Gross et al 2002, Lott 2006), but that disclosure rules and some organizational limits are associated with greater levels of government trust (Primo and Milyo 2006) and may increase the return on campaign expenditures (Stratmann 2006).
+As mentioned, Michael Barber’s 2016 work finds that lower limits on PAC donations relative to individual donations are associated with higher polarization.
+
+A largely separate body of work has examined the causes and consequences of corruption at the state level.
+Most use the Department of Justice’s Annual Public Integrity Report, which correlate highly with state level perceptions of corruption (Walker and Calcagno 2011, Glaeser and Saks 2006, Liu & Mikesell 2014).
+Using that data, researchers have found evidence that political corruption leads to inflated state budgets and that the presence of casinos and subsequent corruption (Liu & Mikesell 2014, Walker & Calcagno 2013).
+They have also shown the absence of a link between state ethics commissions and reduced corruption (Crider and Milyo 2013).
+Researchers have also developed alternative measures of state level corruption, including surveys of state reporters (Boylan and Long 2003) and the recently available Transactional Records Access Clearinghouse (TRAC) database of political corruption (Cordis & Milyo 2016).
+
+Very little work, however, has connected the literature on state-level campaign finance regulations to measures of political corruption--the one question of import to the Supreme Court as it considers the constitutionality of contribution limits.
+The exception to this is one 2013 working paper by Cordis and Milyo.
+In line with Persily and Lammie (2004), Milyo argues that campaign reform efforts have little effect on public perceptions of corruption.
+This paper seeks to address this gap, putting state level campaign finance data in direct conversation with state level corruption data.
+
+##Design and Data 
+###Rework to include new datasets; move datasets into the right folders. 
+This paper builds upon the growing body of state-level political science research to ask the question: Are campaign contribution limits at the state level associated with lower levels of corruption?
+Given open debate about the proper measure of state-level corruption, this paper uses two.
+The first, a Corruptions Convictions Index, is the traditional measure of state level corruption, built from Department of Justice convictions data.
+The second, the Corruptions Reflection Index, is a new measure put forward by Dincer and Johnston (2016).
+I combine these measures with another dataset from Michael Barber’s 2016 work on campaign contribution limits and political polarization.
+
+Barber’s dataset is a panel of contribution limits from 1990-2012 for the lower house of every state legislature.
+Barber compiled this dataset from the FEC, Westlaw, and the Nation Council of State Legislatures.
+Each dollar amount is inflation indexed to 2010 dollar amounts, and bi-annualized.
+There are three different types of limits in the Barber database: Individual contribution limits, individual-to-party limits, and PAC limits.
+Barber utilized individual and PAC contributions in his analysis of polarization, leaving out individual-to-party limits given that party contributions typically make up less than 10% of total political fundraising; I include it this analysis to determine whether parties, rather than PACs or individuals, might be the locus of corruption as measured by our other two datasets (Barber 2016).
+
+The second dataset comes from the Department of Justice’s “Report to Congress on the Activities and Operations of the Public Integrity Section” by way of the Institute for Corruption Studies.[^Koch]  Since 1976, the FBI has tracked political corruption at the state level, and the Corruption Convictions Index (CCI) used here includes the number of corruption convictions in a year normalized by the population in each state.
+This measure of corruption is widely used in academic research.
+
+The third dataset is the Institute for Corruption Studies’ Corruption Reflections Index (CRI), put together by Dincer and Johnston for their 2016 article on state-level corruption, and which they create in response to the limitations of the Corruption Convictions.
+The Corruption Reflections Index represents the fraction of Associated Press stories about politics in a particular state that mention political corruption (Dincer and Johnston 2016).
+
+This analysis has its limitations, beginning with the data.
+Barber’s state campaign contributions data lacks information about upper houses of state legislatures, which are included in both the CCI and CRI.
+The Corruption Convictions Index suffers from a number of issues, outlined by Dincer and Johnston as motivation for estachling the Corruption Reflections Index.
+They argue that the CCI includes only federal data; the resources available to prosecutors varies from state to state (see Alt and Lassen 2012); US Attorneys are political appointees; and the measure records only convictions, which is at best a reflection of underlying corruption.
+
+The Corruption Reflections Index, too, has its limits: It relies on a single news source, the Associated Press which, similar to federal prosecutors’ offices, likely has variation in the resources available to each office.
+It also demonstrates high variation in the data; Utah, for example, has a mean CRI score of 0.46 and standard deviation of 0.38, in a dataset with an overall mean of 0.28 and standard deviation of 0.19.
+The Corruption Reflections Index also seems to assume in its name that media reports of corruption are a mere reflection of corruption, rather than an endogenous variable in the ecosystem that enables corrupt behavior.
+Previous work, in contrast, has argued that media have a clear bias and play an important role in shaping public perceptions of corruption (Sorauf 1987; Ansolabehere, Snowberg and Snyder 2005).
+
+More broadly, this analysis does not address the “appearance of corruption,” the second of the Supreme Court’s reasons for allowing campaign contribution limits; to do so effectively would require time series, state-level data specifically about quid pro quo corruption.
+Finally, while this analysis looks to the states intentionally in order to address the issue of the counterfactual inherent in looking at federal data, it may not be the case that statewide results are generalizable to, or distinct from, what is occurring at the federal level.
+
+[^Koch]: N.B.
+According to one of the researchers’ [curricula vitae](https://about.illinoisstate.edu/odincer/Documents/CVDincerApril2016.docx), the Institute for Corruption Studies is funded in part by a grant from the Charles Koch Research Foundation.
+Organizations funded by Charles and David Koch are also funders of legal groups driving legal battles mentioned in the introduction, according to a [report](https://www.publicintegrity.org/2017/11/15/21279/kochs-key-among-small-group-quietly-funding-legal-assault-campaign-finance) by the Center for Public Integrity.
+
+##Methods
+###Learn to write equations. Add new methods. 
+Having constructed a full 1990-2012 panel dataset from these three datasets, I then run a set of time series regressions testing the relationship between contribution limits and both dependent variables, the Corruption Convictions Index and the Corruption Reflections Index.
+
+I include three independent variables in both sets of models: Individual contribution limits, individual-to-party contribution limits, and PAC contribution limits.
+For each of these independent variables, I construct two variables to use in the model.
+The first is a dummy variable indicating whether there are contribution limits in that state in that year, coded as “0” if there are no limits and “1” if there are.
+The second is a continuous variable indicating the dollar amount of the limit in the state in that year.
+By interacting these two variables, I test two separate associations.
+The dummy variable tests whether there is a difference in the CCI and CRI in states with limits versus states without limits.
+The continuous variable tests whether higher or lower limits are associated with higher or lower CCI and CRI scores, within the group of states that have limits in a given year.
+After performing this transformation on all three independent variables, I test two sets of models:
+
+Corruption Convictions Index versus campaign contribution limits in a given state-year:
+
+CCI  ~	Individual limits (dummy) * Individual limits (amount) + 
+	Individual-to-party limits (dummy) * Individual-to-party limits (amount) + 
+	PAC contribution limits (dummy) * PAC contribution (amount)
+
+Corruption Reflections Index versus campaign contributions in a given state-year:
+
+CRI  ~	Individual limits (dummy) * Individual limits (amount) + 
+	Individual-to-party limits (dummy) * Individual-to-party limits (amount) + 
+	PAC contribution limits (dummy) * PAC contribution (amount)
+
+##Results 
+###Include other results and reorganize. 
+The results of the regression reveal show no correlation between state-level campaign contribution limits and corruption, with one exception: There is a statistically significant relationship between the presence of individual-to-party limits and the Corruption Reflections Index.
+
+The first set of models (below) measures the association of various campaign contribution limits with the Corruption Convictions Index.
+The sign of each coefficient is negative, indicating that the presence of limits is associated with lower corruption levels, but that where limits exist, higher (weaker) donation limits are associated with lower levels of corruption.
+None of those results are significant at the p<0.05 level, however, meaning that we cannot claim their effect is statistically distinguishable from zero.
+I interpret these results as showing no relationship between the presence or amount of state-level contribution limits and levels of corruption as measured by the Corruption Convictions Index.
+
+[CCI table here]
+
+The second set of models (below) also fails to find a relationship between state-level campaign contribution limits and media mentions of corruption as measured by the Corruption Reflections Index, with one exception: The presence of limits on what an individual can give to a party is associated with a 0.087 point decline in the Corruption Reflection Index.
+The Corruption Reflections Index operates on a scale of zero to one (with a few outlying exceptions), meaning that the presence of individual-to-party limits is associated with an 8.7% point decrease in the index.
+
+[CRI table here]
+
+##Discussion
+###Rework. 
+Over two thousand years ago, pre-Socratic Greek thinker Protagoras said that for any event, at least two distinct and opposing accounts will appear.
+There at least two distinct and opposing ways to explain these results, viewpoints that will come into direct and public conflict if the Court chooses to hear a first amendment challenge to campaign contribution limits.
+
+The first interpretation is that campaign finance and quid pro quo corruption simply aren’t related.
+The legal implications of this are clear and system-altering.
+The Supreme Court presently equates political donations with political speech, meaning that it is protected by the first amendment, but that preventing corruption or its appearance in the political system is so important that first amendment rights can be abridged to ensure it.
+No other justification--not a more informed electorate, or more competitive elections, or anything else--is an important enough concern that we should limit speech.
+If there is no link between campaign contribution limits and corruption, then there is no reason to abridge US citizens’ first amendment rights by limiting campaign donations.
+
+In order to make this anti-reform argument, some important limitations must be dealt with.
+First, the Corruptions Conviction Index used above has multiple limitations, as summarized above.
+Second, Dincer and Johnston’s Corruption Reflections Index, while a worthy effort, needs to be developed further.
+It relies on a single news source; a second version could examine state-level reporting, or include outlets from across the political spectrum.
+Second, the Corruption Reflections Index carries with it the assumption that media mentions are a mere reflection of corruption, whereas other work has demonstrated that media reporting on corruption has its own biases, and its own effects on perceptions of corruption.
+Further research could more fully explore these relationships, including the manner in which public perceptions of corruption provide enabling or constraining environments for corruption itself.
+Given the importance of these limitations, all that can be concluded from the analysis above is that no link between contribution limits and corruption has been demonstrated with this data; not that no link exists.
+
+The anti-reform/pro-free-speech interpretation must also more fully take into account the second half of the court’s reasoning for limiting free speech, the “appearance of corruption.” Cordis and Milyo’s working paper on confidence and trust in state government is an important step in that direction, though they acknowledges that “survey measures that relate to opinion on the integrity of democracy are likely to reflect a much more expansive view of ‘corruption’ than what any Court would consider appropriate (2012).
+Dincer and Johnston’s surveys of state reporters is another step, but is limited by its design: Though a clever proxy, state reporters’ perceptions are just a proxy, not a direct measure, of public perceptions of corruption (2017).
+
+The second, pro-reform interpretation of these results would reiterate and add to these limitations.
+Using corruption convictions as a measure is inherently flawed, as effectively corrupt officials would never be arrested.
+The Corruption Reflections Index, likewise, sits uncomfortably between measuring actual corruption and its appearance, saying nothing conclusive about either.
+Furthermore, this design does not speak to causality: It could very well be that in states with high levels of corruption, the public agitates for campaign contribution limits.
+Further research could examine this hypothesis by looking at changes in corruption and perception of corruption following the imposition and removal of state-level limits.
+Lastly, it may be the case that contribution limits are more or less effective under certain circumstances; further research could control for party control, prosecutorial resources, or other factors that might affect the effectiveness of contribution limits or measures of corruption.
+
+Both of these interpretations must wrestle with one awkward pair of stars in the regression above: The pair of stars that suggest that the presence of individual-to-party limits is associated with a decrease in the Corruption Reflections Index.
+There is a less than 1% probability that the results are due to chance.
+How could this be, given that (a) the presence of individual-to-party limits has no association with a change the Corruption Convictions Index; (b) none of the other contribution limits are associated with a chance in the Corruption Reflections Index; and (c) there is no correlation between the level of the individual-to-party limit and the Corruption Reflections Index?
+In practice, this would mean that states with individual-to-party limits also see lower levels of Associated Press reporting on corruption, but that once limits of any kind are imposed, the level of limit doesn’t matter; and that only individual-to-party limits matter, not individual-to-candidate or PAC-to-candidate limits.
+
+It is possible that there is some theoretical explanation for this, but it would hang by a particularly thin theoretical thread.
+For example, it could be that AP reporters are somehow more likely to report on conviction allegations against political parties than against individual candidates or corporations, even where those allegations don’t result in greater levels of convictions, and only in states where the absence of contribution limits allows for a clean, “no limits on contributions” narrative.
+It is more likely, however, that these results call into question the robustness of Dincer and Johnston’s Corruption Reflections Index.
+As mentioned above, further research could carry forward their text-mining method into a greater number and variety of outlets, in order to find a measure of corruption reporting more tightly correlated with other measures.
+
+##Conclusion
+###Beef up. 
+If Jim Bopp and other conservative legal scholars have their way, the Supreme Court will soon take a closer look at the logic laid out by their predecessors in 1976 in support of campaign contribution limits.
+Signs suggest that commitment to the Buckley v.
+Valeo structure are weakening, and not in the way that liberal reformers hope.
+Despite effort, scholars have failed to provide compelling evidence of a link between campaign contribution limits and corruption as defined by the Court.
+The measures of corruption that academics have used to date have serious limitations.
+Yet if the Court decides the burden of proof is on those looking to restrict political spending on narrow corruption grounds, reform advocates worried about money in politics have a steep empirical hill to climb, and likely only a few years to do it.
+
+\newpage
+##References 
+###Add new authors (see Google doc) and data. R packages?
+Ansolabehere, Stephen, John M de Figueiredo, and James M Snyder Jr. 2003. “Why is there so Little Money in US Politics?” Journal of Economic Perspectives. 17(1): 105–130.
+
+Alt, J. E., & Lassen, D. D. (2012). Enforcement and public corruption: evidence from the American states. The Journal of Law, Economics, and Organization, 30(2), 306-338.
+
+Barber, Michael J. "Ideological Donors, Contribution Limits, and the Polarization of American Legislatures." The Journal of Politics 78.1 (2016): 296-310.
+
+Boylan, R. T., & Long, C. X. (2003). Measuring public corruption in the American states: A survey of state house reporters. State Politics & Policy Quarterly, 3(4), 420-438.
+
+Cordis, A., & Milyo, J. (2013). Do state campaign finance reforms reduce public corruption?. George Mason University, Mercatus Center, Working Paper, (13-09).
+
+Cordis, A. S., & Milyo, J. (2016). Measuring public corruption in the United States: evidence from administrative records of federal prosecutions. Public Integrity, 18(2), 127-148.
+
+Crider, K., & Milyo, J. (2013). Do State Ethics Commissions Reduce Political Corruption: An Exploratory Investigation. UC Irvine L. Rev., 3, 717.
+
+Dincer, O., & Johnston, M.
+(2016).
+Political Culture and Corruption Issues in State Politics: A New Measure of Corruption Issues and a Test of Relationships to Political Culture.
+Publius: The Journal of Federalism, 47(1), 131-148.
+
+Glaeser, E. L., & Saks, R. E. (2006). Corruption in america. Journal of public Economics, 90(6), 1053-1072.
+
+Gross, D. A., Goidel, R. K., & Shields, T. G. (2002). State campaign finance regulations and electoral competition. American Politics Research, 30(2), 143-165.
+
+Hall, R. L., & Wayman, F. W. (1990). Buying time: Moneyed interests and the mobilization of bias in congressional committees. American political science review, 84(3), 797-820.
+
+Hurley, L.
+& Debenedetti, G.
+(2014, April 04).
+Legal victory for big-money campaign donors to be felt in states, courts.
+Retrieved December 16, 2017, from https://www.reuters.com/article/us-usa-court-election-analysis/legal-victory-for-big-money-campaign-donors-to-be-felt-in-states-courts-idUSBREA3308620140404
+
+Langbein, L. I. (1986). Money and access: Some empirical evidence. The journal of politics, 48(4), 1052-1062.
+
+Liu, C., & Mikesell, J. L. (2014). The impact of public officials’ corruption on the size and allocation of US state spending. Public Administration Review, 74(3), 346-359.
+
+Lott, J. R. (2006). Campaign finance reform and electoral competition. Public Choice, 129(3-4), 263-300.
+
+Persily, N., & Lammie, K. (2004). Perceptions of corruption and campaign finance: When public opinion determines constitutional law. University of Pennsylvania Law Review, 119-180.
+
+Primo, D. M. (2002). Public opinion and campaign finance: Reformers versus reality. The independent review, 7(2), 207-219.
+
+Primo, D. M., & Milyo, J. (2006). Campaign finance laws and political efficacy: evidence from the states. Election Law Journal, 5(1), 23-39.
+
+Rosenson, B. A. (2009). The effect of political reform measures on perceptions of corruption. Election Law Journal, 8(1), 31-46.
+
+Spencer, Douglas M., and Abby K. Wood. 2014. "Citizens United, states divided: an empirical analysis of independent political spending." LJ 89: 315.
+
+Stratmann, Thomas. 1991. “What Do Campaign Contributions Buy? Deciphering Causal Effects of Money and Votes.” Southern Economic Journal. Pp.606-620.
+
+Stratmann, T. (1998). The market for congressional votes: Is timing of contributions everything?. The Journal of Law and Economics, 41(1), 85-114.
+
+Stratmann, T. (2006). Contribution limits and the effectiveness of campaign spending. Public Choice, 129(3), 461-474.
+
+Walker, D. M., & Calcagno, P. T. (2013). Casinos and political corruption in the United States: A Granger causality analysis. Applied Economics, 45(34), 4781-4795.
+
+Walker, D. M., & Jackson, J. D. (2011). The effect of legalized gambling on state government revenue. Contemporary Economic Policy, 29(1), 101-114.
+
+Werner, Timothy, and John J.
+Coleman.
+2014.
+"Citizens United, independent expenditures, and agency costs: Reexamining the political economy of state antitakeover statutes." The Journal of Law, Economics, & Organization.
+127-159.
+
+Welch, W. P. (1982). Campaign contributions and legislative voting: Milk money and dairy price supports. Western Political Quarterly, 35(4), 478-495.
+
+Zall, B.
+(2017, October 24).
+Ninth Circuit Tees Up Latest Challenge to Citizens United and McCutcheon.
+Retrieved November 22, 2017, from https://publicpolicylegal.com/2017/10/24/ninth-circuit-tees-up-latest-challenge-to-citizens-united-and-mccutcheon/

### 2018-05-24 Paper.Rmd
Clean-up

@@
 title: | 
-  | Do campaign contribution limits limit corruption? 
+  | Campaign Contribution Limits and Corruption: 
   | Evidence from the 50 states
@@
 ##Prior Work 
+###Add in more references 
 Since the Buckley v.
@@
 The second, the Corruptions Reflection Index, is a new measure put forward by Dincer and Johnston (2016).
-I combine these measures with another dataset from Michael Barber’s 2016 work on campaign contribution limits and political polarization.
+I combine these measures with a third dataset from Michael Barber’s 2016 work on campaign contribution limits and political polarization; and a fourth dataset from James Alt and David Dryer Lassen, to provide controls for the full model (Alt and Lassen 2012).
 
@@
 
+The fourth dataset provides controls for the panel model.
+In their 2012 work examining variation in prosecutorial resources, Alt and Lassen follow Glaeser and Saks (2006) in controlling for _______.
+Alt and Lassen's dataset runs from 1976-2004.
+
 This analysis has its limitations, beginning with the data.
@@
 The Corruption Convictions Index suffers from a number of issues, outlined by Dincer and Johnston as motivation for estachling the Corruption Reflections Index.
-They argue that the CCI includes only federal data; the resources available to prosecutors varies from state to state (see Alt and Lassen 2012); US Attorneys are political appointees; and the measure records only convictions, which is at best a reflection of underlying corruption.
+They argue that the CCI includes only federal data; the resources available to prosecutors varies from state to state; US Attorneys are political appointees; and the measure records only convictions, which is at best a reflection of underlying corruption.
 
-The Corruption Reflections Index, too, has its limits: It relies on a single news source, the Associated Press which, similar to federal prosecutors’ offices, likely has variation in the resources available to each office.
+The Corruption Reflections Index, too, has its limits: It relies on a single news source, the Associated Press.
+Similar to federal prosecutors’ offices, the resources available to each AP office vary.
 It also demonstrates high variation in the data; Utah, for example, has a mean CRI score of 0.46 and standard deviation of 0.38, in a dataset with an overall mean of 0.28 and standard deviation of 0.19.
@@
 
-More broadly, this analysis does not address the “appearance of corruption,” the second of the Supreme Court’s reasons for allowing campaign contribution limits; to do so effectively would require time series, state-level data specifically about quid pro quo corruption.
+More broadly, this analysis does not directly address the “appearance of corruption,” the second of the Supreme Court’s reasons for allowing campaign contribution limits; to do so effectively would require time series, state-level data specifically about quid pro quo corruption.
 Finally, while this analysis looks to the states intentionally in order to address the issue of the counterfactual inherent in looking at federal data, it may not be the case that statewide results are generalizable to, or distinct from, what is occurring at the federal level.
@@
 The continuous variable tests whether higher or lower limits are associated with higher or lower CCI and CRI scores, within the group of states that have limits in a given year.
-After performing this transformation on all three independent variables, I test two sets of models:
+After performing this transformation on all three independent variables, I test two initial sets of models:
 
@@
 
-CCI  ~	Individual limits (dummy) * Individual limits (amount) + 
-	Individual-to-party limits (dummy) * Individual-to-party limits (amount) + 
-	PAC contribution limits (dummy) * PAC contribution (amount)
+$Convictions = \alpha + \beta_{indiv.dummy} + \beta_{indiv.dummy}*\beta_{indiv.limit} + \beta_{pac.dummy} + \beta_{pac.dummy}*\beta_{pac.limit} + \beta_{indiv-to-party.dummy} + \beta_{indiv-to-party.dummy}*\beta_{indiv-to-party.limit} + \epsilon$
 
@@
 
-CRI  ~	Individual limits (dummy) * Individual limits (amount) + 
-	Individual-to-party limits (dummy) * Individual-to-party limits (amount) + 
-	PAC contribution limits (dummy) * PAC contribution (amount)
+$Reflections = \alpha + \beta_{indiv.dummy} + \beta_{indiv.dummy}*\beta_{indiv.limit} + \beta_{pac.dummy} + \beta_{pac.dummy}*\beta_{pac.limit} + \beta_{indiv-to-party.dummy} + \beta_{indiv-to-party.dummy}*\beta_{indiv-to-party.limit} + \epsilon$
 

### 2018-06-06 Stargazer test.Rmd
FEC files, but without large datasets I hope

---
title: "Stargazer"
author: "Mark Hand"
date: "6/11/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stargazer)
library(texreg)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
screenreg(attitude)
```

### 2018-06-12 paper/Paper.Rmd
Reorganizing

--- 2018-05-24 Paper.Rmd
@@
 
+Since the 1970s, the U.S.
+Supreme Court has frustrated efforts at campaign finance reform by maintaining that nearly all limits on political spending violate the first amendment’s protection of free speech.
+The Court makes only two exceptions: The state has a compelling enough interesting in preventing “corruption of the appearance of corruption” to limit political donations.
+But do campaign finance laws actually prevent corruption or its appearance?
+Using state-level data from 1990-2012 on contribution limits, corruption arrests, and media mentions of corruption, this paper employs a linear panel regression and a difference-in-differences analysis to test whether campaign contribution limits are associated with lower levels of corruption convictions or media mentions of corruption.
+These methods find no relationship between the presence or level of campaign finance laws and quid pro quo corruption, suggesting that would-be reformers must keep looking for evidence to support their efforts.
+As current challenges to contribution limits wind their way through federal courts, the answer to this question will inform the Supreme Court’s decision to uphold or strike down remaining limits on political campaign contributions.
+
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, cache = TRUE, message=FALSE, warning=FALSE)
+knitr::opts_chunk$set(echo = FALSE, eval=FALSE, cache = TRUE, message=FALSE, warning=FALSE)
 library(haven) # import .dta
-library(tidyverse) # everything 
+suppressMessages(library("tidyverse")) # everything 
 library(plm) # For linear panel regression
+library(stargazer) # For regression outputs 
+library(texreg) # For regression outputs
+
 ```
 
-```{r data import, include=F}
+```{r data import, eval=T, message=F, warning=F}
 # Alt and Lassen's "Enforcement and Public Corruption: Evidence from US States"
@@
 
-```{r panel data wrangling, include=F}
+```{r panel data wrangling, eval=T}
 # Combining Barber and ICS 
@@
 
-```{r DiD wrangling, include=F}
+```{r panel modeling, eval=T}
+## CCI 
+# Individual limits and corruption
+CCIreg1  <- plm(CCI ~ ind_limits_2010*ind_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
+# No signifigance
+
+# Individual-to-party limits and corruption
+CCIreg2  <- plm(CCI ~ ind2pty_limits_2010*ind2pty_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
+# No Signifigance
+
+# PAC Limits and corruption
+CCIreg3  <- plm(CCI ~ pac_limits_2010*pac_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
+# No Signifigance
+
+# Total Limits and corruption
+CCIreg4  <- plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
+# One star. Hmm...
+
+# Everybody? 
+CCIreg5 <- plm(CCI ~ ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = BarberICC, index = c("st","year"), effect="twoways")
+
+## CRI
+CRIreg1  <- plm(CRI ~ ind_limits_2010*ind_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
+# No signifigance
+
+# Individual-to-party limits and reflection
+CRIreg2  <- plm(CRI ~ ind2pty_limits_2010*ind2pty_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
+# One star. Hmm...
+
+# PAC Limits and reflection
+CRIreg3  <- plm(CRI ~ pac_limits_2010*pac_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
+# No Signifigance
+
+# All Limits and reflection
+CRIreg4  <- plm(CRI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
+# No Signifigance
+
+# Everybody? 
+CRIreg5 <- plm(CRI ~ ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = BarberICC, index = c("st","year"), effect="twoways")
+```
+
+```{r (old) controlled panel modeling}
+#Next: Panel model of corruption against unemployment and high school? 
+testmodel01 <- plm(CCI ~ rpcinc_annual_new + unemp + high_school + logNumpop + citi6006 + grelimp, data = AltBarber, index = c("st","year"), effect="twoways")
+
+testmodel02 <- plm(CCI ~ jdiv + bindingonetermlimit + bindingtwotermlimit + rpcinc_annual_new + eousa + unemp + citi6006 + high_school + rgenrevpc + logNumpop + eopop + men_ineqincwag + grelimp + fedrepcons + urbanization_2 + logpop + inspop, data = AltBarber, index = c("st","year"), effect="twoways")
+
+testmodel03 <- plm(CCI ~ jdiv + bindingonetermlimit + bindingtwotermlimit + rpcinc_annual_new + eousa + unemp + citi6006 + high_school + rgenrevpc + logNumpop + eopop + men_ineqincwag + grelimp + fedrepcons + urbanization_2 + logpop + inspop + ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = AltBarber, index = c("st","year"), effect="twoways")
+
+testmodel05 <- plm(CCI ~ jdiv + bindingonetermlimit + bindingtwotermlimit + rpcinc_annual_new + eousa + unemp + citi6006 + high_school + rgenrevpc + logNumpop + eopop + men_ineqincwag + grelimp + urbanization_2 + logpop + inspop, data = AltBarber, index = c("st","year"), effect="twoways")
+```
+
+```{r controlled panel modeling, eval=T}
+
+CCIcontrol01 <- plm(CCI ~ jdiv  # Divided government 
+                   + bindingonetermlimit # Binding one-term limit 
+                   + bindingtwotermlimit # Binding two-term limit 
+                   + rpcinc_annual_new # Real per capita income ($1000)
+                   + eopop # AUSAs per million population
+                   + unemp # Unemployment 
+                   + citi6006 # Citizen ideology measure 
+                   + high_school + # Percent high school graduates
+                   + rgenrevpc # Real per capita gov revenues ($1000)
+                   + men_ineqincwag # Inequality: Male wages
+                   + grelimp # Relative government wages
+                   + urbanization_2 # Urbanization 
+                   + logpop, # Log of population (millions)
+                   data = AltBarber, 
+                   index = c("st","year"), 
+                   effect="twoways")
+
+CCIcontrol02 <- plm(CCI ~ jdiv  # Divided government 
+                   + bindingonetermlimit # Binding one-term limit 
+                   + bindingtwotermlimit # Binding two-term limit 
+                   + rpcinc_annual_new # Real per capita income ($1000)
+                   + eopop # AUSAs per million population
+                   + unemp # Unemployment 
+                   + citi6006 # Citizen ideology measure 
+                   + high_school + # Percent high school graduates
+                   + rgenrevpc # Real per capita gov revenues ($1000)
+                   + men_ineqincwag # Inequality: Male wages
+                   + grelimp # Relative government wages
+                   + urbanization_2 # Urbanization 
+                   + logpop # Log of population (millions)
+                   + ind_limits_2010*ind_limits_dummy 
+                   + ind2pty_limits_2010*ind2pty_limits_dummy 
+                   + pac_limits_2010*pac_limits_dummy, 
+                   data = AltBarber, 
+                   index = c("st","year"), 
+                   effect="twoways")
+
+CRIcontrol01 <- plm(CRI ~ jdiv  # Divided government 
+                   + bindingonetermlimit # Binding one-term limit 
+                   + bindingtwotermlimit # Binding two-term limit 
+                   + rpcinc_annual_new # Real per capita income ($1000)
+                   + eopop # AUSAs per million population
+                   + unemp # Unemployment 
+                   + citi6006 # Citizen ideology measure 
+                   + high_school + # Percent high school graduates
+                   + rgenrevpc # Real per capita gov revenues ($1000)
+                   + men_ineqincwag # Inequality: Male wages
+                   + grelimp # Relative government wages
+                   + urbanization_2 # Urbanization 
+                   + logpop, # Log of population (millions)
+                   data = AltBarber, 
+                   index = c("st","year"), 
+                   effect="twoways")
+
+CRIcontrol02 <- plm(CRI ~ jdiv  # Divided government 
+                   + bindingonetermlimit # Binding one-term limit 
+                   + bindingtwotermlimit # Binding two-term limit 
+                   + rpcinc_annual_new # Real per capita income ($1000)
+                   + eopop # AUSAs per million population
+                   + unemp # Unemployment 
+                   + citi6006 # Citizen ideology measure 
+                   + high_school + # Percent high school graduates
+                   + rgenrevpc # Real per capita gov revenues ($1000)
+                   + men_ineqincwag # Inequality: Male wages
+                   + grelimp # Relative government wages
+                   + urbanization_2 # Urbanization 
+                   + logpop # Log of population (millions)
+                   + ind_limits_2010*ind_limits_dummy 
+                   + ind2pty_limits_2010*ind2pty_limits_dummy 
+                   + pac_limits_2010*pac_limits_dummy, 
+                   data = AltBarber, 
+                   index = c("st","year"), 
+                   effect="twoways")
+
+```
+
+```{r DiD wrangling, eval=T}
 BarberICC %>% arrange(year) %>% group_by(st) %>% mutate(
@@
 
-testframe %>% select(1:2,8,11,3:7,12:21) -> DiDsmall 
-summary(DiDsmall)
+testframe %>% dplyr::select(1:2,8,11,3:7,12:21) -> DiDsmall
 
@@
 
-```{r panel modeling, include=F}
-#Next: Panel model of corruption against unemployment and high school? 
-testmodel01 <- plm(CCI ~ rpcinc_annual_new + unemp + high_school + logNumpop + citi6006 + grelimp, data = AltBarber, index = c("st","year"), effect="twoways")
-summary(testmodel01)
-
-testmodel02 <- plm(CCI ~ jdiv + bindingonetermlimit + bindingtwotermlimit + rpcinc_annual_new + eousa + unemp + citi6006 + high_school + rgenrevpc + logNumpop + eopop + men_ineqincwag + grelimp + fedrepcons + urbanization_2 + logpop + inspop, data = AltBarber, index = c("st","year"), effect="twoways")
-summary(testmodel02)
-
-testmodel03 <- plm(CCI ~ jdiv + bindingonetermlimit + bindingtwotermlimit + rpcinc_annual_new + eousa + unemp + citi6006 + high_school + rgenrevpc + logNumpop + eopop + men_ineqincwag + grelimp + fedrepcons + urbanization_2 + logpop + inspop + ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = AltBarber, index = c("st","year"), effect="twoways")
-summary(testmodel03)
-
-testmodel05 <- plm(CCI ~ jdiv + bindingonetermlimit + bindingtwotermlimit + rpcinc_annual_new + eousa + unemp + citi6006 + high_school + rgenrevpc + logNumpop + eopop + men_ineqincwag + grelimp + urbanization_2 + logpop + inspop, data = AltBarber, index = c("st","year"), effect="twoways")
-summary(testmodel05)
-
-testmodel06 <- plm(CCI ~ jdiv + bindingonetermlimit + bindingtwotermlimit + rpcinc_annual_new + eousa + unemp + citi6006 + high_school + rgenrevpc + logNumpop + eopop + men_ineqincwag + grelimp + urbanization_2 + logpop + inspop + ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = AltBarber, index = c("st","year"), effect="twoways")
-summary(testmodel06)
-
-```
-
-```{r DiD modeling, include=F}
-summary(lm(CCI ~ ind_dummy_f, data = DiDsmall))
-summary(lm(CCI ~ pac_dummy_f, data = DiDsmall))
-summary(lm(CCI ~ ind2pty_dummy_f, data = DiDsmall))
-summary(lm(CRI ~ ind_dummy_f, data = DiDsmall))
-summary(lm(CRI ~ pac_dummy_f, data = DiDsmall))
-summary(lm(CRI ~ ind2pty_dummy_f, data = DiDsmall))
+```{r DiD modeling, eval=T}
+#summary(lm(CCI ~ ind_dummy_f, data = DiDsmall))
+#summary(lm(CCI ~ pac_dummy_f, data = DiDsmall))
+#summary(lm(CCI ~ ind2pty_dummy_f, data = DiDsmall))
+#summary(lm(CRI ~ ind_dummy_f, data = DiDsmall))
+#summary(lm(CRI ~ pac_dummy_f, data = DiDsmall))
+#summary(lm(CRI ~ ind2pty_dummy_f, data = DiDsmall))
 # No effects
 
-summary(lm(CCI ~ ind_dummy_f*ind_d, data = DiDsmall))
-summary(lm(CCI ~ pac_dummy_f*pac_d, data = DiDsmall))
-summary(lm(CCI ~ ind2pty_dummy_f*ind2pty_d, data = DiDsmall))
-summary(lm(CRI ~ ind_dummy_f*ind_d, data = DiDsmall))
-summary(lm(CRI ~ pac_dummy_f*pac_d, data = DiDsmall))
-summary(lm(CRI ~ ind2pty_dummy_f*ind2pty_d, data = DiDsmall))
+CCIDID01 <- lm(CCI ~ ind_dummy_f*ind_d, data = DiDsmall)
+CCIDID02 <- lm(CCI ~ pac_dummy_f*pac_d, data = DiDsmall)
+CCIDID03 <- lm(CCI ~ ind2pty_dummy_f*ind2pty_d, data = DiDsmall)
+
+CRIDID01 <- lm(CRI ~ ind_dummy_f*ind_d, data = DiDsmall)
+CRIDID02 <- lm(CRI ~ pac_dummy_f*pac_d, data = DiDsmall)
+CRIDID03 <- lm(CRI ~ ind2pty_dummy_f*ind2pty_d, data = DiDsmall)
 # No effects 
-
-# Next: Lag, write up. 
+# Next: Lag?  
 ```
-
-Since the 1970s, the U.S.
-Supreme Court has frustrated efforts at campaign finance reform by holding that nearly all limits on political spending violate the first amendment’s protection of free speech, with only one exception: to prevent “corruption of the appearance of corruption.” Using state-level data from 1990-2012 on contribution limits, corruption arrests, and media mentions of corruption, this paper employs a linear panel regression and a difference-in-differences analysis to test whether campaign contribution limits are associated with lower levels of corruption arrests or media mentions of corruption.
-These methods find no relationship between the presence or level of campaign finance laws and quid pro quo corruption.
-As current challenges to contribution limits wind their way through federal courts, the answer to this question will inform the Supreme Court’s decision to uphold or strike down remaining limits on political campaign contributions.
 
@@
 ##Introduction
-###Shorten? 
+<!--Shorten?-->
 In 1976, the Supreme Court ruled in Buckley v.
@@
 ##Prior Work 
-###Add in more references 
+<!--Add in more references--> 
 Since the Buckley v.
@@
 ##Design and Data 
-###Rework to include new datasets; move datasets into the right folders. 
+<!--Add in summary statistics?-->
 This paper builds upon the growing body of state-level political science research to ask the question: Are campaign contribution limits at the state level associated with lower levels of corruption?
@@
 The fourth dataset provides controls for the panel model.
-In their 2012 work examining variation in prosecutorial resources, Alt and Lassen follow Glaeser and Saks (2006) in controlling for _______.
+In their 2012 work examining variation in prosecutorial resources, Alt and Lassen follow Glaeser and Saks (2006) in controlling for income and education levels, size of government, legislature control, and urbanization.
 Alt and Lassen's dataset runs from 1976-2004.
+When included in the second and third models, this limits the analysis to the years from 1990-2004.
 
-This analysis has its limitations, beginning with the data.
+This analysis has its limitations, beginning with the datasets themselves.
 Barber’s state campaign contributions data lacks information about upper houses of state legislatures, which are included in both the CCI and CRI.
-The Corruption Convictions Index suffers from a number of issues, outlined by Dincer and Johnston as motivation for estachling the Corruption Reflections Index.
+The Corruption Convictions Index suffers from a number of issues, as outlined by Dincer and Johnston in their introduction to the Corruption Reflections Index.
 They argue that the CCI includes only federal data; the resources available to prosecutors varies from state to state; US Attorneys are political appointees; and the measure records only convictions, which is at best a reflection of underlying corruption.
@@
 
-More broadly, this analysis does not directly address the “appearance of corruption,” the second of the Supreme Court’s reasons for allowing campaign contribution limits; to do so effectively would require time series, state-level data specifically about quid pro quo corruption.
-Finally, while this analysis looks to the states intentionally in order to address the issue of the counterfactual inherent in looking at federal data, it may not be the case that statewide results are generalizable to, or distinct from, what is occurring at the federal level.
+Most broadly, this analysis does not directly address the “appearance of corruption,” the second of the Supreme Court’s reasons for allowing campaign contribution limits; to do so effectively would require time series, state-level data specifically about quid pro quo corruption.
+It is also the case that this analysis looks to the states intentionally in order to address the issue of the counterfactual inherent in looking at federal data, it may not be the case that statewide results are generalizable to, or distinct from, what is occurring at the federal level.
+Finally, the period in question (1990-2004) is short enough that there may be some factor that influences corruption arrest across a meaningful portion of the dataset.
 
@@
 ##Methods
-###Learn to write equations. Add new methods. 
+### Model I: Panel Regression
 Having constructed a full 1990-2012 panel dataset from these three datasets, I then run a set of time series regressions testing the relationship between contribution limits and both dependent variables, the Corruption Convictions Index and the Corruption Reflections Index.
@@
 The continuous variable tests whether higher or lower limits are associated with higher or lower CCI and CRI scores, within the group of states that have limits in a given year.
-After performing this transformation on all three independent variables, I test two initial sets of models:
+After performing this transformation on all three independent variables, I test two initial sets of models: (1) Corruption Convictions Index versus campaign contribution limits in a given state-year, and (2) Corruption Reflections Index versus campaign contributions in a given state-year.
 
+<!--
 Corruption Convictions Index versus campaign contribution limits in a given state-year:
@@
 $Reflections = \alpha + \beta_{indiv.dummy} + \beta_{indiv.dummy}*\beta_{indiv.limit} + \beta_{pac.dummy} + \beta_{pac.dummy}*\beta_{pac.limit} + \beta_{indiv-to-party.dummy} + \beta_{indiv-to-party.dummy}*\beta_{indiv-to-party.limit} + \epsilon$
+-->
+
+If the model above fails to show an initial correlation, this may be due to the confounding effect of absent variables.
+In order to test that, I build a model of political corruption using control variables previously demonstrated to be correlated with corruption arrests, resulting in a dataset covering 1990-2004, the period of overlap between Barber's and Alt and Lassen's data.
+These include controlling for the size and education levels of the population, the ideology of a population, income levels and inequality, education levels, the number and relative income of government employees, and urbanization.
+Building a model of corruption that includes variables previously demonstrated to be correlated with corruption levels, then adding in campaign finance data, can better identify the association of campaign finance laws with corruption levels.
+
+### Model II: Difference-in-Difference Model
+<!--Add specification, formulas?-->
+Even if the panel models above fail to capture correlation between state level campaign finance laws and corruption arrests, it could be the case that changes in campaign finance laws, rather than relative campaign finance limits, could be correlated with decreases in corruption.
+A difference-in-difference regression can help identify this by comparing the state-years in which campaign finance laws changed to state-years where they remained constant.
+If tighter campaign finance laws are correlated with lower corruption levels, then a change in one year should lead to lower corruption convictions in the years following.
 
 ##Results 
-###Include other results and reorganize. 
-The results of the regression reveal show no correlation between state-level campaign contribution limits and corruption, with one exception: There is a statistically significant relationship between the presence of individual-to-party limits and the Corruption Reflections Index.
+### Modeling campaign limits and corruption arrests 
+The results of the initial panel regression reveal no correlation between state-level campaign contribution limits and corruption, with one exception: There is a statistically significant relationship between the presence of individual-to-party limits and the Corruption Reflections Index.
 
@@
 
-[CCI table here]
-
+### INSERT FIGURE 1 HERE 
+```{r panel stargazer CCI}
+stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,
+  type="text", 
+  title = "Are campaign limits and corruption convictions correlated?",
+  out="collateral/CCI.htm",
+  dep.var.labels = c("Corruption Convictions Index"),
+  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
+```
 The second set of models (below) also fails to find a relationship between state-level campaign contribution limits and media mentions of corruption as measured by the Corruption Reflections Index, with one exception: The presence of limits on what an individual can give to a party is associated with a 0.087 point decline in the Corruption Reflection Index.
@@
 
-[CRI table here]
+### INSERT FIGURE 2 HERE 
+```{r stargazer CRI}
+stargazer(CRIreg1, CRIreg2, CRIreg3, CRIreg5,
+  type="text", 
+  title = "Are campaign limits and corruption reflections correlated?",
+  out="collateral/CRI.htm",
+  dep.var.labels = c("Corruption Reflections Index"),
+  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
+
+# stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5, CRIreg1, CRIreg2, CRIreg3, CRIreg5,
+#   type="text", 
+#   out="collateral/CCICRI.htm",
+#   dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
+#   covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
+```
+
+The third set of models incorporates a number of control variables in order to isolate the effect of campaign finance laws on corruption arrest levels.
+As in the models above, the only correlation significant at the p<0.05 level is the presence of limits on what an individual can give to a party; again, the presence of limits in what an individual can give to a party is associated with a decline in the Corruption Reflections Index.
+
+### INSERT FIGURE 3 HERE 
+```{r stargazer controlled panel}
+stargazer(CCIcontrol01,CCIcontrol02,CRIcontrol01,CRIcontrol02,
+  type="text", 
+  out="collateral/CCICRIcontrol.htm",
+  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
+  covariate.labels=c("Divided government", "Binding one-term limit"," Binding two-term limit","Real per capita income ($1000)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues ($1000)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)","Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)")
+  )
+```
+
+### Modeling changes in campaign limits and corruption arrests
+
+The final set of models is a set of difference-in-difference models designed to isolate the effect of changes in campaign finance laws on corruption arrests.
+None of the models find correlation between campagin finance limits and either corruption convictions or corruption reflections.
+
+### INSERT FIGURE 4 HERE
+```{r stargazer DiD}
+stargazer(CCIDID01, CCIDID02, CCIDID03, CRIDID01, CRIDID02, CRIDID03,
+  type="text", 
+  title = "Do changes in limits lead to lower levels of corruption?",
+  out="collateral/DiD.htm",
+  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
+  covariate.labels=c("Individual limits removed","Individual limits imposed","Individual limit amount","Individual limits removed*amount","Individual limits imposed*amount",
+                     "PAC limits removed","PAC limits imposed","PAC limit amount","PAC limits removed*amount","PAC limits imposed*amount",
+                     "Individual-to-party limits removed","Individual-to-party limits imposed","Individual-to-party limit amount","Individual-to-party limits removed*amount","Individual-to-party limits imposed*amount"))
+
+```
 
 ##Discussion
-###Rework. 
-Over two thousand years ago, pre-Socratic Greek thinker Protagoras said that for any event, at least two distinct and opposing accounts will appear.
+How might we interpret these results?
+The relationship between campaign finance laws and the Corruption Convictions Index is most clear: None of these methods reveal any correlation between state level campaign finance laws and levels of corruption as measured by corruptions convictions, even controlling for variation in enforcement across the states.
+
+Interpreting the results for the Corruption Reflections Index must wrestle with one awkward result: The pair of stars that suggest the presence of individual-to-party limits is associated with a decrease in the Corruption Reflections Index.
+There is a less than 1% probability that the results are due to chance.
+How could this be, given that (a) the presence of individual-to-party limits has no association with a change the Corruption Convictions Index; (b) none of the other contribution limits are associated with a change in the Corruption Reflections Index; and (c) there is no correlation between the level of the individual-to-party limit and the Corruption Reflections Index?
+In practice, this would mean that states with individual-to-party limits also see lower levels of Associated Press reporting on corruption, but that once limits of any kind are imposed, the level of limit doesn’t matter.
+It would also mean that only individual-to-party limits matter, not individual-to-candidate or PAC-to-candidate limits.
+Lastly, it would imply that the presence of such limits has an effect on reporting about corruption, but not corruption convictions.
+
+There is limited theoretical explanation for this outcome.
+It could be that AP reporters are somehow more likely to report on conviction allegations against political parties than against individual candidates or corporations, even where those allegations don’t result in greater levels of convictions, and only in states where the absence of contribution limits allows for a clean, “no limits on contributions” narrative.
+It is more likely, however, that these results call into question the robustness of Dincer and Johnston’s Corruption Reflections Index.
+As mentioned above, further research could carry forward their text-mining method into a greater number and variety of outlets, in order to find a measure of corruption reporting more tightly correlated with other measures.
+
+##Conclusion
 There at least two distinct and opposing ways to explain these results, viewpoints that will come into direct and public conflict if the Court chooses to hear a first amendment challenge to campaign contribution limits.
 
-The first interpretation is that campaign finance and quid pro quo corruption simply aren’t related.
-The legal implications of this are clear and system-altering.
+The first interpretation is that campaign finance and quid pro quo corruption are simply not related.
+How could this be?
+One explanation is that the measures of corruption used here fail to capture most corruption, which is never prosecuted; this explanation, however, would rest on the assumption that corruption is _unequally_ captured across states over time.
+A second explanation is that corruption occurs regardless of campaign finance laws: Those politicians likely to engage in corrupt behavior will do so outside of the campaign finance regime, where their transactions would be most visible.
+A third explanation is the simplest one: Politics is simply less corrupt than is popularly believed.
+
+The legal implications of the second and third interpretations are clear and wide-reaching.
 The Supreme Court presently equates political donations with political speech, meaning that it is protected by the first amendment, but that preventing corruption or its appearance in the political system is so important that first amendment rights can be abridged to ensure it.
-No other justification--not a more informed electorate, or more competitive elections, or anything else--is an important enough concern that we should limit speech.
+No other justification--not a more informed electorate, or more competitive elections, or anything else--is an important enough concern that we should limit political speech in the form of campaign donations.
 If there is no link between campaign contribution limits and corruption, then there is no reason to abridge US citizens’ first amendment rights by limiting campaign donations.
@@
 In order to make this anti-reform argument, some important limitations must be dealt with.
-First, the Corruptions Conviction Index used above has multiple limitations, as summarized above.
+First, the Corruptions Conviction Index used above has multiple issues, as summarized above.
 Second, Dincer and Johnston’s Corruption Reflections Index, while a worthy effort, needs to be developed further.
@@
 
-Both of these interpretations must wrestle with one awkward pair of stars in the regression above: The pair of stars that suggest that the presence of individual-to-party limits is associated with a decrease in the Corruption Reflections Index.
-There is a less than 1% probability that the results are due to chance.
-How could this be, given that (a) the presence of individual-to-party limits has no association with a change the Corruption Convictions Index; (b) none of the other contribution limits are associated with a chance in the Corruption Reflections Index; and (c) there is no correlation between the level of the individual-to-party limit and the Corruption Reflections Index?
-In practice, this would mean that states with individual-to-party limits also see lower levels of Associated Press reporting on corruption, but that once limits of any kind are imposed, the level of limit doesn’t matter; and that only individual-to-party limits matter, not individual-to-candidate or PAC-to-candidate limits.
-
-It is possible that there is some theoretical explanation for this, but it would hang by a particularly thin theoretical thread.
-For example, it could be that AP reporters are somehow more likely to report on conviction allegations against political parties than against individual candidates or corporations, even where those allegations don’t result in greater levels of convictions, and only in states where the absence of contribution limits allows for a clean, “no limits on contributions” narrative.
-It is more likely, however, that these results call into question the robustness of Dincer and Johnston’s Corruption Reflections Index.
-As mentioned above, further research could carry forward their text-mining method into a greater number and variety of outlets, in order to find a measure of corruption reporting more tightly correlated with other measures.
-
-##Conclusion
-###Beef up. 
 If Jim Bopp and other conservative legal scholars have their way, the Supreme Court will soon take a closer look at the logic laid out by their predecessors in 1976 in support of campaign contribution limits.

### 2018-06-12 paper/Paper.Rmd
Inserting charts; next step is to fix them in Latex

@@
 
-### INSERT FIGURE 1 HERE 
-```{r panel stargazer CCI}
+```{r stargzer CCI html}
 stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,
@@
 ```
+
+```{r stargazer CCI latex, results="asis", include=F}
+stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,
+  type="latex", 
+  title = "Are campaign limits and corruption convictions correlated?",
+  dep.var.labels = c("Corruption Convictions Index"),
+  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
+```
+
+\begin{table}[!htbp] \centering 
+  \caption{Are campaign limits and corruption convictions correlated?} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-5} 
+\\[-1.8ex] & \multicolumn{4}{c}{Corruption Convictions Index} \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
+\hline \\[-1.8ex] 
+ Individual limit amounts & $-$0.00004 &  &  & $-$0.00003 \\ 
+  & (0.00005) &  &  & (0.0001) \\ 
+  & & & & \\ 
+ Individual limits (dummy) & $-$4.021 &  &  & $-$2.989 \\ 
+  & (4.572) &  &  & (5.076) \\ 
+  & & & & \\ 
+ Individual-to-party limit amount &  & $-$0.00000 &  & 0.00000 \\ 
+  &  & (0.00001) &  & (0.00001) \\ 
+  & & & & \\ 
+ Individual-to-party limits (dummy) &  & $-$0.019 &  & 0.363 \\ 
+  &  & (0.626) &  & (0.684) \\ 
+  & & & & \\ 
+ PAC limit amounts &  &  & $-$0.00002 & $-$0.00002 \\ 
+  &  &  & (0.00002) & (0.00002) \\ 
+  & & & & \\ 
+ PAC limits (dummy) &  &  & $-$1.762 & $-$1.339 \\ 
+  &  &  & (1.519) & (1.743) \\ 
+  & & & & \\ 
+\hline \\[-1.8ex] 
+Observations & 1,149 & 1,149 & 1,149 & 1,149 \\ 
+R$^{2}$ & 0.002 & 0.00002 & 0.002 & 0.002 \\ 
+Adjusted R$^{2}$ & $-$0.066 & $-$0.068 & $-$0.066 & $-$0.069 \\ 
+F Statistic & 0.826 (df = 2; 1075) & 0.012 (df = 2; 1075) & 0.843 (df = 2; 1075) & 0.426 (df = 6; 1071) \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
+
 The second set of models (below) also fails to find a relationship between state-level campaign contribution limits and media mentions of corruption as measured by the Corruption Reflections Index, with one exception: The presence of limits on what an individual can give to a party is associated with a 0.087 point decline in the Corruption Reflection Index.
@@
 
-### INSERT FIGURE 2 HERE 
-```{r stargazer CRI}
+```{r stargazer CRI html}
 stargazer(CRIreg1, CRIreg2, CRIreg3, CRIreg5,
@@
   covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
+```
 
-# stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5, CRIreg1, CRIreg2, CRIreg3, CRIreg5,
-#   type="text", 
-#   out="collateral/CCICRI.htm",
-#   dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
-#   covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
+```{r stargazer CRI latex, results="asis", include=F}
+stargazer(CRIreg1, CRIreg2, CRIreg3, CRIreg5,
+  title = "Are campaign limits and corruption reflections correlated?",
+  dep.var.labels = c("Corruption Reflections Index"),
+  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
 ```
+
+\begin{table}[!htbp] \centering 
+  \caption{Are campaign limits and corruption reflections correlated?} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-5} 
+\\[-1.8ex] & \multicolumn{4}{c}{Corruption Reflections Index} \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
+\hline \\[-1.8ex] 
+ Individual limit amounts & $-$0.00000 &  &  & $-$0.00000 \\ 
+  & (0.00000) &  &  & (0.00000) \\ 
+  & & & & \\ 
+ Individual limits (dummy) & $-$0.316 &  &  & $-$0.328 \\ 
+  & (0.257) &  &  & (0.284) \\ 
+  & & & & \\ 
+ Individual-to-party limit amount &  & $-$0.00000 &  & $-$0.00000 \\ 
+  &  & (0.00000) &  & (0.00000) \\ 
+  & & & & \\ 
+ Individual-to-party limits (dummy) &  & $-$0.087$^{**}$ &  & $-$0.099$^{***}$ \\ 
+  &  & (0.035) &  & (0.038) \\ 
+  & & & & \\ 
+ PAC limit amounts &  &  & 0.00000 & 0.00000 \\ 
+  &  &  & (0.00000) & (0.00000) \\ 
+  & & & & \\ 
+ PAC limits (dummy) &  &  & 0.009 & 0.096 \\ 
+  &  &  & (0.085) & (0.098) \\ 
+  & & & & \\ 
+\hline \\[-1.8ex] 
+Observations & 1,150 & 1,150 & 1,150 & 1,150 \\ 
+R$^{2}$ & 0.002 & 0.007 & 0.0001 & 0.010 \\ 
+Adjusted R$^{2}$ & $-$0.066 & $-$0.060 & $-$0.068 & $-$0.061 \\ 
+F Statistic & 0.842 (df = 2; 1076) & 3.937$^{**}$ (df = 2; 1076) & 0.037 (df = 2; 1076) & 1.858$^{*}$ (df = 6; 1072) \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
 
@@
 
-### INSERT FIGURE 3 HERE 
 ```{r stargazer controlled panel}
@@
 ```
+
+```{r stargazer controlled panel latex, results="asis", include=F}
+stargazer(CCIcontrol01,CCIcontrol02,CRIcontrol01,CRIcontrol02,
+  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
+  covariate.labels=c("Divided government", "Binding one-term limit"," Binding two-term limit","Real per capita income (thousands)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (thousands)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)","Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)")
+  )
+```
+
+Too big to include?
+
+\begin{table}[!htbp] \centering 
+  \caption{} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-5} 
+\\[-1.8ex] & \multicolumn{2}{c}{Corruption Convictions Index} & \multicolumn{2}{c}{Corruption Reflections Index} \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
+\hline \\[-1.8ex] 
+ Divided government & $-$0.371$^{*}$ & $-$0.332 & 0.012 & 0.014 \\ 
+  & (0.208) & (0.211) & (0.014) & (0.014) \\ 
+  & & & & \\ 
+ Binding one-term limit & 0.228 & $-$0.294 & 0.056 & 0.112 \\ 
+  & (1.399) & (1.494) & (0.093) & (0.098) \\ 
+  & & & & \\ 
+  Binding two-term limit & 0.013 & 0.048 & 0.002 & $-$0.0004 \\ 
+  & (0.232) & (0.234) & (0.015) & (0.015) \\ 
+  & & & & \\ 
+ Real per capita income (thousands) & $-$0.001$^{**}$ & $-$0.001$^{**}$ & 0.00001 & 0.00001 \\ 
+  & (0.0002) & (0.0002) & (0.00002) & (0.00002) \\ 
+  & & & & \\ 
+ AUSAs per million population & 0.064 & 0.077 & 0.0003 & $-$0.001 \\ 
+  & (0.060) & (0.061) & (0.004) & (0.004) \\ 
+  & & & & \\ 
+ Unemployment & 0.007 & 0.029 & 0.015 & 0.013 \\ 
+  & (0.155) & (0.161) & (0.010) & (0.011) \\ 
+  & & & & \\ 
+ Citizen ideology measure & $-$0.001 & 0.001 & $-$0.001 & $-$0.001 \\ 
+  & (0.020) & (0.021) & (0.001) & (0.001) \\ 
+  & & & & \\ 
+ Percent high school graduates & $-$2.187 & $-$1.955 & $-$0.707 & $-$0.901$^{*}$ \\ 
+  & (7.236) & (7.455) & (0.477) & (0.488) \\ 
+  & & & & \\ 
+ Real per capita gov revenues (thousands) & 0.002 & 0.002$^{*}$ & 0.0002$^{**}$ & 0.0002$^{***}$ \\ 
+  & (0.001) & (0.001) & (0.0001) & (0.0001) \\ 
+  & & & & \\ 
+ Inequality: Male wages & 0.131$^{***}$ & 0.125$^{***}$ & $-$0.004 & $-$0.003 \\ 
+  & (0.048) & (0.048) & (0.003) & (0.003) \\ 
+  & & & & \\ 
+ Relative government wages & 32.384 & 28.128 & 4.163 & 7.262$^{**}$ \\ 
+  & (45.126) & (47.558) & (2.984) & (3.123) \\ 
+  & & & & \\ 
+ Urbanization & 0.074 & 0.073 & $-$0.013$^{*}$ & $-$0.016$^{**}$ \\ 
+  & (0.114) & (0.115) & (0.007) & (0.008) \\ 
+  & & & & \\ 
+ Log of population (millions) & 3.883 & 2.988 & 0.098 & 0.018 \\ 
+  & (3.032) & (3.231) & (0.200) & (0.212) \\ 
+  & & & & \\ 
+ Individual limit amounts &  & 0.0001 &  & $-$0.00001 \\ 
+  &  & (0.0001) &  & (0.00001) \\ 
+  & & & & \\ 
+ Individual limits (dummy) &  & 8.012 &  & $-$0.561 \\ 
+  &  & (8.409) &  & (0.550) \\ 
+  & & & & \\ 
+ Individual-to-party limit amount &  & 0.00000 &  & 0.00000 \\ 
+  &  & (0.00001) &  & (0.00000) \\ 
+  & & & & \\ 
+ Individual-to-party limits (dummy) &  & 0.260 &  & $-$0.111$^{**}$ \\ 
+  &  & (0.744) &  & (0.049) \\ 
+  & & & & \\ 
+ PAC limit amounts &  & $-$0.00002 &  & $-$0.00000 \\ 
+  &  & (0.00004) &  & (0.00000) \\ 
+  & & & & \\ 
+ PAC limits (dummy) &  & $-$1.547 &  & $-$0.192 \\ 
+  &  & (3.176) &  & (0.209) \\ 
+  & & & & \\ 
+\hline \\[-1.8ex] 
+Observations & 671 & 671 & 672 & 672 \\ 
+R$^{2}$ & 0.038 & 0.043 & 0.029 & 0.047 \\ 
+Adjusted R$^{2}$ & $-$0.080 & $-$0.084 & $-$0.090 & $-$0.080 \\ 
+F Statistic & 1.818$^{**}$ (df = 13; 597) & 1.413 (df = 19; 591) & 1.368 (df = 13; 598) & 1.549$^{*}$ (df = 19; 592) \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
 
@@
 ```
+
+```{r stargazer DiD latex, results="asis", include=F}
+stargazer(CCIDID01, CCIDID02, CCIDID03, CRIDID01, CRIDID02, CRIDID03,
+  title = "Do changes in limits lead to lower levels of corruption?",
+  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
+  covariate.labels=c("Individual limits removed","Individual limits imposed","Individual limit amount","Individual limits removed*amount","Individual limits imposed*amount",
+                     "PAC limits removed","PAC limits imposed","PAC limit amount","PAC limits removed*amount","PAC limits imposed*amount",
+                     "Individual-to-party limits removed","Individual-to-party limits imposed","Individual-to-party limit amount","Individual-to-party limits removed*amount","Individual-to-party limits imposed*amount"))
+
+```
+
+\begin{table}[!htbp] \centering 
+  \caption{Do changes in limits lead to lower levels of corruption?} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-7} 
+\\[-1.8ex] & \multicolumn{3}{c}{Corruption Convictions Index} & \multicolumn{3}{c}{Corruption Reflections Index} \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
+\hline \\[-1.8ex] 
+ Individual limits removed & 27.590 &  &  & $-$3.567 &  &  \\ 
+  & (117.102) &  &  & (7.717) &  &  \\ 
+  & & & & & & \\ 
+ Individual limits imposed & 4.038 &  &  & 1.324 &  &  \\ 
+  & (25.993) &  &  & (1.713) &  &  \\ 
+  & & & & & & \\ 
+ Individual limit amount & 0.00001 &  &  & 0.00001 &  &  \\ 
+  & (0.0001) &  &  & (0.00001) &  &  \\ 
+  & & & & & & \\ 
+ Individual limits removed*amount & $-$0.0003 &  &  & 0.00003 &  &  \\ 
+  & (0.001) &  &  & (0.0001) &  &  \\ 
+  & & & & & & \\ 
+ Individual limits imposed*amount & 0.00004 &  &  & 0.00000 &  &  \\ 
+  & (0.0003) &  &  & (0.00002) &  &  \\ 
+  & & & & & & \\ 
+ PAC limits removed &  & $-$4.699 &  &  & $-$1.586 &  \\ 
+  &  & (42.691) &  &  & (2.815) &  \\ 
+  & & & & & & \\ 
+ PAC limits imposed &  & $-$0.977 &  &  & 0.129 &  \\ 
+  &  & (2.786) &  &  & (0.184) &  \\ 
+  & & & & & & \\ 
+ PAC limit amount &  & $-$0.00001 &  &  & $-$0.00000 &  \\ 
+  &  & (0.0001) &  &  & (0.00000) &  \\ 
+  & & & & & & \\ 
+ PAC limits removed*amount &  & 0.0001 &  &  & 0.00002 &  \\ 
+  &  & (0.0004) &  &  & (0.00003) &  \\ 
+  & & & & & & \\ 
+ PAC limits imposed*amount &  & 0.00000 &  &  & 0.00000 &  \\ 
+  &  & (0.0001) &  &  & (0.00001) &  \\ 
+  & & & & & & \\ 
+ Individual-to-party limits removed &  &  & $-$1.944 &  &  & 0.044 \\ 
+  &  &  & (3.317) &  &  & (0.219) \\ 
+  & & & & & & \\ 
+ Individual-to-party limits imposed &  &  & $-$0.252 &  &  & 0.010 \\ 
+  &  &  & (1.133) &  &  & (0.075) \\ 
+  & & & & & & \\ 
+ Individual-to-party limit amount &  &  & $-$0.00001 &  &  & $-$0.00000 \\ 
+  &  &  & (0.00002) &  &  & (0.00000) \\ 
+  & & & & & & \\ 
+ Individual-to-party limits removed*amount &  &  &  &  &  &  \\ 
+  &  &  &  &  &  &  \\ 
+  & & & & & & \\ 
+ Individual-to-party limits imposed*amount &  &  & 0.00000 &  &  & 0.00000 \\ 
+  &  &  & (0.00002) &  &  & (0.00000) \\ 
+  & & & & & & \\ 
+ Constant & 3.198$^{***}$ & 3.196$^{***}$ & 3.184$^{***}$ & 0.291$^{***}$ & 0.291$^{***}$ & 0.291$^{***}$ \\ 
+  & (0.090) & (0.090) & (0.089) & (0.006) & (0.006) & (0.006) \\ 
+  & & & & & & \\ 
+\hline \\[-1.8ex] 
+Observations & 1,099 & 1,099 & 1,099 & 1,100 & 1,100 & 1,100 \\ 
+R$^{2}$ & 0.001 & 0.001 & 0.003 & 0.003 & 0.002 & 0.001 \\ 
+Adjusted R$^{2}$ & $-$0.004 & $-$0.004 & $-$0.001 & $-$0.001 & $-$0.003 & $-$0.003 \\ 
+Residual Std. Error & 2.939 (df = 1093) & 2.939 (df = 1093) & 2.935 (df = 1094) & 0.194 (df = 1094) & 0.194 (df = 1094) & 0.194 (df = 1095) \\ 
+F Statistic & 0.172 (df = 5; 1093) & 0.111 (df = 5; 1093) & 0.691 (df = 4; 1094) & 0.706 (df = 5; 1094) & 0.413 (df = 5; 1094) & 0.217 (df = 4; 1095) \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
 

### 2018-06-15 Latex test.Rmd
Mostly failing to stargazing

--- 2018-06-12 paper/Paper.Rmd
@@
 ---
-title: | 
-  | Campaign Contribution Limits and Corruption: 
-  | Evidence from the 50 states
+title: "Latex test"
 author: "Mark Hand"
-date: "5/23/2018"
+date: "6/15/2018"
 output: pdf_document
 ---
-
-Since the 1970s, the U.S.
-Supreme Court has frustrated efforts at campaign finance reform by maintaining that nearly all limits on political spending violate the first amendment’s protection of free speech.
-The Court makes only two exceptions: The state has a compelling enough interesting in preventing “corruption of the appearance of corruption” to limit political donations.
-But do campaign finance laws actually prevent corruption or its appearance?
-Using state-level data from 1990-2012 on contribution limits, corruption arrests, and media mentions of corruption, this paper employs a linear panel regression and a difference-in-differences analysis to test whether campaign contribution limits are associated with lower levels of corruption convictions or media mentions of corruption.
-These methods find no relationship between the presence or level of campaign finance laws and quid pro quo corruption, suggesting that would-be reformers must keep looking for evidence to support their efforts.
-As current challenges to contribution limits wind their way through federal courts, the answer to this question will inform the Supreme Court’s decision to uphold or strike down remaining limits on political campaign contributions.
 
@@
 library(plm) # For linear panel regression
-library(stargazer) # For regression outputs 
-library(texreg) # For regression outputs
+library(stargazer) # For regression outputs #fail 
+library(texreg) # For regression outputs #fail 
+library(kableExtra) # For regression outputs 
+library(broom) # Because Matt Worthington said so 
+library(knitr) # Because Matt Worthington said so
 
@@
 
-\newpage 
-##Introduction
-<!--Shorten?-->
-In 1976, the Supreme Court ruled in Buckley v.
-Valeo that political campaign contributions are the equivalent of free speech, and therefore protected by the first amendment.
-At the same time, the Court laid out one mechanism and one justification for limiting those contributions.
-First, it argued that more money spent doesn’t amount of “more” speech, allowing for campaign contribution dollar amount limits.
-Donating one dollar or $5,000 to a political campaign amounts to a speech act, the Court held, and so it is permissible to impose limits on the amount of contributions as long as contributions are not prevented.
-Second, having laid out the mechanism by which money in politics might be limited, the court laid out the only justification for limiting contributions that it would accept moving forward: To prevent corruption or the appearance thereof.
-As Kang (2012) argues, the holdings in Buckley v.
-Valeo provided “the basic framework of contribution limits and disclosure requirements” for the following four decades.
-Since Buckley v.
-Valeo, Congress has passed only one campaign finance law, the Bipartisan Campaign Reform Act of 2002.
-Better know as McCain-Feingold, the bill took aim at unlimited “soft money” contributions to political parties and expanded the Federal Election Commission’s disclosure requirements to what it called “electioneering communications,” political ads not paid for by campaigns themselves.
-
-Apart from McCain-Feingold, for forty years all changes in the landscape of campaign finance have come from the courts, the majority being decided upon how to balance questions of free political speech versus corruption.
-Those rulings have often been driven by the question of corporations’ participation in the political process.
-In 1978, the Court extended free speech protections to corporations (First National Bank of Boston v.
-Bellotti).
-In 1986, it  and struck down efforts to restrict their expenditures to FEC-registered Political Action Committees (FEC v.
-Massachusetts Right to Life).
-Then in 1990, it upheld a ban on corporations using treasury funds to pay for issue advertisements, arguing for an extended definition of corruption, "the corrosive and distorting effects of immense aggregations of wealth that are accumulated with the help of the corporate form and that have little or no correlation to the public's support for the corporation's political ideas" (Austin v.
-Michigan State Chamber of Commerce, later overturned).
-
-The passage of the McCain-Feingold in 2002 inspired a wave of challenges to campaign contributions and expenditures, driven mostly by conservative and religious groups.
-In 2007, the Court examined the McCain-Feingold ban on airing issue advertisements close to election.
-Banning such ads, the Court argued, would have a chilling effect on free speech, and it struck down the ban (FEC v.
-Wisconsin Right to Life).
-Then, in 2010, the Court issued what has become one of its most well-known rulings: In Citizens United v.
-FEC (2010), it struck down limits on independent expenditures by outside groups, including corporations and unions.
-One critical aspect of Citizens United is the establishment of the principle that, according to Justice Anthony Kennedy, “independent expenditures do not lead to, or create the appearance of, quid pro quo corruption.” The Court’s emphasis on quid pro quo corruption as the only justification for contribution limits extended the following year, as it struck down an Arizona effort to level the political playing field with matching state campaign funds (Arizona Free Enterprise Club v.
-Bennett, 2011).
-
-Since 2011, the network of conservative legal groups behind Citizens United has continued to take aim at contribution limits as an unnecessary restriction of political speech, with a focus on individual contribution limits.
-The 1971 Federal Election Campaign Act placed a limit on the amount an individual could give to one campaign, in addition to two-year limits on the total amount an individual could give to political campaigns.
-In McCutcheon v.
-FEC (2014) James Bopp, one of the attorneys behind the Citizens United challenge, convinced the Court of the unconstitutionality of total individual limits.
-Another case, Holmes v.
-FEC (2017), targeted the distribution of individual campaign contribution across primary and general elections.
-In yet another, Lair v.
-Motl (2017), Bopp once again took aim at individual contribution limits, arguing that the state of Montana had not shown compelling evidence that campaign contribution limits decreased the risk of corruption.
-
-The Ninth Circuit Court of Appeals upheld Montana’s campaign contribution limits, but further challenges to contribution limits are likely.
-Bopp said that he planned to appeal the Ninth Circuit’s ruling.
-Even if that fails, Bopp and other conservative groups plan to carry on.
-“I handle a lot of cases,” he said after the 2014 McCutcheon ruling, “and I‘m not done yet.” Supreme Court Justice Clarence Thomas laid the groundwork for future challenges in his commentary on the McCutcheon decision by arguing that more dollars did, in fact, equate to more speech.
-Once established, that principle supports the argument that campaign contribution dollar amount limits are a potentially unconstitutional restriction on speech (Hurley & Debenedetti 2014, Zall 2017).
-
-##Prior Work 
-<!--Add in more references--> 
-Since the Buckley v.
-Valeo decision, a wave of scholarship has taken advantage of the campaign contribution data collected by the Federal Election Commission to examine the causes and consequences of political campaign contributions, including whether contributions buy access (not to a meaningful degree, find Welch 1982 and Langbein 1986) and the effectiveness of contributions relative to lobbying efforts (yes, according to Wright 1990).
-Since the 2010 Citizens United and speechnow.org decisions, another arm of scholarship has examined the flows of money to groups engaging in independent expenditures (Spencer and Wood 2014, Werner and Coleman 2014).
-
-But lobbying, money for access, and independent expenditures all fall outside of the narrow definition of quid pro corruption that the Supreme Court considers a compelling enough state interest to justify campaign contribution limits.
-The scholarly research on corruption thus narrowly defined is mixed and heated.
-Stratmann finds evidence that donations determined votes in at least one instance (1991); he also finds that the timing of political action committees (PAC) donations suggests that corporations believe those donations do affect legislators’ votes (1998).
-Reacting to the absence of evidence that donations lead to favorable final votes on bills, Hall and Wayman (1990) look for and find a positive relationship between political donations and the amount of attention that legislators give to a particular issue.
-Other scholars, however, are not so convinced.
-Wright (1990) finds that once lobbying efforts are factored in, the effects of contributions on voting outcomes washes out.
-And it is notoriously difficult to tease out whether political donations change legislators’ minds or instead flow to legislators with established, friendly positions (Ansolabehere et al 2003).
-
-As mentioned above, the Court is also interested in the appearance of corruption.
-On this score, results are more consonant: There seems to be little association between campaign spending and public trust in government (Primo 2002).
-Other factors, including media coverage of campaign finance law and the professionalization of legislatures, are more predictive of public perceptions of corruptions (Rosenson 2009).
-And while the public does seem to report viewing campaign finance as a contributor to corruption, there is not evidence that reform efforts will have an effect on those views (Persily & Lammie 2004).
-
-One fundamental limitation of these federal level studies on campaign contributions and corruption, however, is the absence of a counterfactual: Given that contribution limits have been in place since the 1970s, it is difficult to argue what might have happened in their absence.
-Recent work on campaign finance has attempted to address this problem by focusing on the effects of differences in campaign finance laws at the state level.
-Variation across states and over time allows room for studying the causes and consequences of campaign finance limits.
-Studies suggest that campaign finance limits are associated with less electoral competition (Gross et al 2002, Lott 2006), but that disclosure rules and some organizational limits are associated with greater levels of government trust (Primo and Milyo 2006) and may increase the return on campaign expenditures (Stratmann 2006).
-As mentioned, Michael Barber’s 2016 work finds that lower limits on PAC donations relative to individual donations are associated with higher polarization.
-
-A largely separate body of work has examined the causes and consequences of corruption at the state level.
-Most use the Department of Justice’s Annual Public Integrity Report, which correlate highly with state level perceptions of corruption (Walker and Calcagno 2011, Glaeser and Saks 2006, Liu & Mikesell 2014).
-Using that data, researchers have found evidence that political corruption leads to inflated state budgets and that the presence of casinos and subsequent corruption (Liu & Mikesell 2014, Walker & Calcagno 2013).
-They have also shown the absence of a link between state ethics commissions and reduced corruption (Crider and Milyo 2013).
-Researchers have also developed alternative measures of state level corruption, including surveys of state reporters (Boylan and Long 2003) and the recently available Transactional Records Access Clearinghouse (TRAC) database of political corruption (Cordis & Milyo 2016).
-
-Very little work, however, has connected the literature on state-level campaign finance regulations to measures of political corruption--the one question of import to the Supreme Court as it considers the constitutionality of contribution limits.
-The exception to this is one 2013 working paper by Cordis and Milyo.
-In line with Persily and Lammie (2004), Milyo argues that campaign reform efforts have little effect on public perceptions of corruption.
-This paper seeks to address this gap, putting state level campaign finance data in direct conversation with state level corruption data.
-
-##Design and Data 
-<!--Add in summary statistics?-->
-This paper builds upon the growing body of state-level political science research to ask the question: Are campaign contribution limits at the state level associated with lower levels of corruption?
-Given open debate about the proper measure of state-level corruption, this paper uses two.
-The first, a Corruptions Convictions Index, is the traditional measure of state level corruption, built from Department of Justice convictions data.
-The second, the Corruptions Reflection Index, is a new measure put forward by Dincer and Johnston (2016).
-I combine these measures with a third dataset from Michael Barber’s 2016 work on campaign contribution limits and political polarization; and a fourth dataset from James Alt and David Dryer Lassen, to provide controls for the full model (Alt and Lassen 2012).
-
-Barber’s dataset is a panel of contribution limits from 1990-2012 for the lower house of every state legislature.
-Barber compiled this dataset from the FEC, Westlaw, and the Nation Council of State Legislatures.
-Each dollar amount is inflation indexed to 2010 dollar amounts, and bi-annualized.
-There are three different types of limits in the Barber database: Individual contribution limits, individual-to-party limits, and PAC limits.
-Barber utilized individual and PAC contributions in his analysis of polarization, leaving out individual-to-party limits given that party contributions typically make up less than 10% of total political fundraising; I include it this analysis to determine whether parties, rather than PACs or individuals, might be the locus of corruption as measured by our other two datasets (Barber 2016).
-
-The second dataset comes from the Department of Justice’s “Report to Congress on the Activities and Operations of the Public Integrity Section” by way of the Institute for Corruption Studies.[^Koch]  Since 1976, the FBI has tracked political corruption at the state level, and the Corruption Convictions Index (CCI) used here includes the number of corruption convictions in a year normalized by the population in each state.
-This measure of corruption is widely used in academic research.
-
-The third dataset is the Institute for Corruption Studies’ Corruption Reflections Index (CRI), put together by Dincer and Johnston for their 2016 article on state-level corruption, and which they create in response to the limitations of the Corruption Convictions.
-The Corruption Reflections Index represents the fraction of Associated Press stories about politics in a particular state that mention political corruption (Dincer and Johnston 2016).
-
-The fourth dataset provides controls for the panel model.
-In their 2012 work examining variation in prosecutorial resources, Alt and Lassen follow Glaeser and Saks (2006) in controlling for income and education levels, size of government, legislature control, and urbanization.
-Alt and Lassen's dataset runs from 1976-2004.
-When included in the second and third models, this limits the analysis to the years from 1990-2004.
-
-This analysis has its limitations, beginning with the datasets themselves.
-Barber’s state campaign contributions data lacks information about upper houses of state legislatures, which are included in both the CCI and CRI.
-The Corruption Convictions Index suffers from a number of issues, as outlined by Dincer and Johnston in their introduction to the Corruption Reflections Index.
-They argue that the CCI includes only federal data; the resources available to prosecutors varies from state to state; US Attorneys are political appointees; and the measure records only convictions, which is at best a reflection of underlying corruption.
-
-The Corruption Reflections Index, too, has its limits: It relies on a single news source, the Associated Press.
-Similar to federal prosecutors’ offices, the resources available to each AP office vary.
-It also demonstrates high variation in the data; Utah, for example, has a mean CRI score of 0.46 and standard deviation of 0.38, in a dataset with an overall mean of 0.28 and standard deviation of 0.19.
-The Corruption Reflections Index also seems to assume in its name that media reports of corruption are a mere reflection of corruption, rather than an endogenous variable in the ecosystem that enables corrupt behavior.
-Previous work, in contrast, has argued that media have a clear bias and play an important role in shaping public perceptions of corruption (Sorauf 1987; Ansolabehere, Snowberg and Snyder 2005).
-
-Most broadly, this analysis does not directly address the “appearance of corruption,” the second of the Supreme Court’s reasons for allowing campaign contribution limits; to do so effectively would require time series, state-level data specifically about quid pro quo corruption.
-It is also the case that this analysis looks to the states intentionally in order to address the issue of the counterfactual inherent in looking at federal data, it may not be the case that statewide results are generalizable to, or distinct from, what is occurring at the federal level.
-Finally, the period in question (1990-2004) is short enough that there may be some factor that influences corruption arrest across a meaningful portion of the dataset.
-
-[^Koch]: N.B.
-According to one of the researchers’ [curricula vitae](https://about.illinoisstate.edu/odincer/Documents/CVDincerApril2016.docx), the Institute for Corruption Studies is funded in part by a grant from the Charles Koch Research Foundation.
-Organizations funded by Charles and David Koch are also funders of legal groups driving legal battles mentioned in the introduction, according to a [report](https://www.publicintegrity.org/2017/11/15/21279/kochs-key-among-small-group-quietly-funding-legal-assault-campaign-finance) by the Center for Public Integrity.
-
-##Methods
-### Model I: Panel Regression
-Having constructed a full 1990-2012 panel dataset from these three datasets, I then run a set of time series regressions testing the relationship between contribution limits and both dependent variables, the Corruption Convictions Index and the Corruption Reflections Index.
-
-I include three independent variables in both sets of models: Individual contribution limits, individual-to-party contribution limits, and PAC contribution limits.
-For each of these independent variables, I construct two variables to use in the model.
-The first is a dummy variable indicating whether there are contribution limits in that state in that year, coded as “0” if there are no limits and “1” if there are.
-The second is a continuous variable indicating the dollar amount of the limit in the state in that year.
-By interacting these two variables, I test two separate associations.
-The dummy variable tests whether there is a difference in the CCI and CRI in states with limits versus states without limits.
-The continuous variable tests whether higher or lower limits are associated with higher or lower CCI and CRI scores, within the group of states that have limits in a given year.
-After performing this transformation on all three independent variables, I test two initial sets of models: (1) Corruption Convictions Index versus campaign contribution limits in a given state-year, and (2) Corruption Reflections Index versus campaign contributions in a given state-year.
-
-<!--
-Corruption Convictions Index versus campaign contribution limits in a given state-year:
-
-$Convictions = \alpha + \beta_{indiv.dummy} + \beta_{indiv.dummy}*\beta_{indiv.limit} + \beta_{pac.dummy} + \beta_{pac.dummy}*\beta_{pac.limit} + \beta_{indiv-to-party.dummy} + \beta_{indiv-to-party.dummy}*\beta_{indiv-to-party.limit} + \epsilon$
-
-Corruption Reflections Index versus campaign contributions in a given state-year:
-
-$Reflections = \alpha + \beta_{indiv.dummy} + \beta_{indiv.dummy}*\beta_{indiv.limit} + \beta_{pac.dummy} + \beta_{pac.dummy}*\beta_{pac.limit} + \beta_{indiv-to-party.dummy} + \beta_{indiv-to-party.dummy}*\beta_{indiv-to-party.limit} + \epsilon$
--->
-
-If the model above fails to show an initial correlation, this may be due to the confounding effect of absent variables.
-In order to test that, I build a model of political corruption using control variables previously demonstrated to be correlated with corruption arrests, resulting in a dataset covering 1990-2004, the period of overlap between Barber's and Alt and Lassen's data.
-These include controlling for the size and education levels of the population, the ideology of a population, income levels and inequality, education levels, the number and relative income of government employees, and urbanization.
-Building a model of corruption that includes variables previously demonstrated to be correlated with corruption levels, then adding in campaign finance data, can better identify the association of campaign finance laws with corruption levels.
-
-### Model II: Difference-in-Difference Model
-<!--Add specification, formulas?-->
-Even if the panel models above fail to capture correlation between state level campaign finance laws and corruption arrests, it could be the case that changes in campaign finance laws, rather than relative campaign finance limits, could be correlated with decreases in corruption.
-A difference-in-difference regression can help identify this by comparing the state-years in which campaign finance laws changed to state-years where they remained constant.
-If tighter campaign finance laws are correlated with lower corruption levels, then a change in one year should lead to lower corruption convictions in the years following.
-
-##Results 
-### Modeling campaign limits and corruption arrests 
-The results of the initial panel regression reveal no correlation between state-level campaign contribution limits and corruption, with one exception: There is a statistically significant relationship between the presence of individual-to-party limits and the Corruption Reflections Index.
-
-The first set of models (below) measures the association of various campaign contribution limits with the Corruption Convictions Index.
-The sign of each coefficient is negative, indicating that the presence of limits is associated with lower corruption levels, but that where limits exist, higher (weaker) donation limits are associated with lower levels of corruption.
-None of those results are significant at the p<0.05 level, however, meaning that we cannot claim their effect is statistically distinguishable from zero.
-I interpret these results as showing no relationship between the presence or amount of state-level contribution limits and levels of corruption as measured by the Corruption Convictions Index.
-
-### INSERT FIGURE 1 HERE 
-```{r panel stargazer CCI}
+```{r stargzer CCI html}
 stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,
@@
 ```
-The second set of models (below) also fails to find a relationship between state-level campaign contribution limits and media mentions of corruption as measured by the Corruption Reflections Index, with one exception: The presence of limits on what an individual can give to a party is associated with a 0.087 point decline in the Corruption Reflection Index.
-The Corruption Reflections Index operates on a scale of zero to one (with a few outlying exceptions), meaning that the presence of individual-to-party limits is associated with an 8.7% point decrease in the index.
 
-### INSERT FIGURE 2 HERE 
-```{r stargazer CRI}
+```{r stargazer CCI latex, results="asis", eval=T}
+stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,
+  type="latex", 
+  title = "Are campaign limits and corruption convictions correlated?",
+  dep.var.labels = c("Corruption Convictions Index"),
+  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
+```
+
+```{r stargazer CRI html}
 stargazer(CRIreg1, CRIreg2, CRIreg3, CRIreg5,
@@
   covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
-
-# stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5, CRIreg1, CRIreg2, CRIreg3, CRIreg5,
-#   type="text", 
-#   out="collateral/CCICRI.htm",
-#   dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
-#   covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
 ```
 
-The third set of models incorporates a number of control variables in order to isolate the effect of campaign finance laws on corruption arrest levels.
-As in the models above, the only correlation significant at the p<0.05 level is the presence of limits on what an individual can give to a party; again, the presence of limits in what an individual can give to a party is associated with a decline in the Corruption Reflections Index.
+```{r stargazer CRI latex, results="asis", eval=T}
+stargazer(CRIreg1, CRIreg2, CRIreg3, CRIreg5,
+  title = "Are campaign limits and corruption reflections correlated?",
+  dep.var.labels = c("Corruption Reflections Index"),
+  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
+```
 
-### INSERT FIGURE 3 HERE 
 ```{r stargazer controlled panel}
@@
 
-### Modeling changes in campaign limits and corruption arrests
+```{r stargazer controlled panel latex, results="asis", eval=T}
+stargazer(CCIcontrol01,CCIcontrol02,CRIcontrol01,CRIcontrol02,
+  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
+  covariate.labels=c("Divided government", "Binding one-term limit"," Binding two-term limit","Real per capita income (thousands)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (thousands)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)","Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)")
+  )
+```
 
-The final set of models is a set of difference-in-difference models designed to isolate the effect of changes in campaign finance laws on corruption arrests.
-None of the models find correlation between campagin finance limits and either corruption convictions or corruption reflections.
-
-### INSERT FIGURE 4 HERE
 ```{r stargazer DiD}
@@
 
-##Discussion
-How might we interpret these results?
-The relationship between campaign finance laws and the Corruption Convictions Index is most clear: None of these methods reveal any correlation between state level campaign finance laws and levels of corruption as measured by corruptions convictions, even controlling for variation in enforcement across the states.
+```{r stargazer DiD latex, results="asis", eval=T}
+stargazer(CCIDID01, CCIDID02, CCIDID03, CRIDID01, CRIDID02, CRIDID03,
+  title = "Do changes in limits lead to lower levels of corruption?",
+  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
+  covariate.labels=c("Individual limits removed","Individual limits imposed","Individual limit amount","Individual limits removed*amount","Individual limits imposed*amount",
+                     "PAC limits removed","PAC limits imposed","PAC limit amount","PAC limits removed*amount","PAC limits imposed*amount",
+                     "Individual-to-party limits removed","Individual-to-party limits imposed","Individual-to-party limit amount","Individual-to-party limits removed*amount","Individual-to-party limits imposed*amount"))
 
-Interpreting the results for the Corruption Reflections Index must wrestle with one awkward result: The pair of stars that suggest the presence of individual-to-party limits is associated with a decrease in the Corruption Reflections Index.
-There is a less than 1% probability that the results are due to chance.
-How could this be, given that (a) the presence of individual-to-party limits has no association with a change the Corruption Convictions Index; (b) none of the other contribution limits are associated with a change in the Corruption Reflections Index; and (c) there is no correlation between the level of the individual-to-party limit and the Corruption Reflections Index?
-In practice, this would mean that states with individual-to-party limits also see lower levels of Associated Press reporting on corruption, but that once limits of any kind are imposed, the level of limit doesn’t matter.
-It would also mean that only individual-to-party limits matter, not individual-to-candidate or PAC-to-candidate limits.
-Lastly, it would imply that the presence of such limits has an effect on reporting about corruption, but not corruption convictions.
-
-There is limited theoretical explanation for this outcome.
-It could be that AP reporters are somehow more likely to report on conviction allegations against political parties than against individual candidates or corporations, even where those allegations don’t result in greater levels of convictions, and only in states where the absence of contribution limits allows for a clean, “no limits on contributions” narrative.
-It is more likely, however, that these results call into question the robustness of Dincer and Johnston’s Corruption Reflections Index.
-As mentioned above, further research could carry forward their text-mining method into a greater number and variety of outlets, in order to find a measure of corruption reporting more tightly correlated with other measures.
-
-##Conclusion
-There at least two distinct and opposing ways to explain these results, viewpoints that will come into direct and public conflict if the Court chooses to hear a first amendment challenge to campaign contribution limits.
-
-The first interpretation is that campaign finance and quid pro quo corruption are simply not related.
-How could this be?
-One explanation is that the measures of corruption used here fail to capture most corruption, which is never prosecuted; this explanation, however, would rest on the assumption that corruption is _unequally_ captured across states over time.
-A second explanation is that corruption occurs regardless of campaign finance laws: Those politicians likely to engage in corrupt behavior will do so outside of the campaign finance regime, where their transactions would be most visible.
-A third explanation is the simplest one: Politics is simply less corrupt than is popularly believed.
-
-The legal implications of the second and third interpretations are clear and wide-reaching.
-The Supreme Court presently equates political donations with political speech, meaning that it is protected by the first amendment, but that preventing corruption or its appearance in the political system is so important that first amendment rights can be abridged to ensure it.
-No other justification--not a more informed electorate, or more competitive elections, or anything else--is an important enough concern that we should limit political speech in the form of campaign donations.
-If there is no link between campaign contribution limits and corruption, then there is no reason to abridge US citizens’ first amendment rights by limiting campaign donations.
-
-In order to make this anti-reform argument, some important limitations must be dealt with.
-First, the Corruptions Conviction Index used above has multiple issues, as summarized above.
-Second, Dincer and Johnston’s Corruption Reflections Index, while a worthy effort, needs to be developed further.
-It relies on a single news source; a second version could examine state-level reporting, or include outlets from across the political spectrum.
-Second, the Corruption Reflections Index carries with it the assumption that media mentions are a mere reflection of corruption, whereas other work has demonstrated that media reporting on corruption has its own biases, and its own effects on perceptions of corruption.
-Further research could more fully explore these relationships, including the manner in which public perceptions of corruption provide enabling or constraining environments for corruption itself.
-Given the importance of these limitations, all that can be concluded from the analysis above is that no link between contribution limits and corruption has been demonstrated with this data; not that no link exists.
-
-The anti-reform/pro-free-speech interpretation must also more fully take into account the second half of the court’s reasoning for limiting free speech, the “appearance of corruption.” Cordis and Milyo’s working paper on confidence and trust in state government is an important step in that direction, though they acknowledges that “survey measures that relate to opinion on the integrity of democracy are likely to reflect a much more expansive view of ‘corruption’ than what any Court would consider appropriate (2012).
-Dincer and Johnston’s surveys of state reporters is another step, but is limited by its design: Though a clever proxy, state reporters’ perceptions are just a proxy, not a direct measure, of public perceptions of corruption (2017).
-
-The second, pro-reform interpretation of these results would reiterate and add to these limitations.
-Using corruption convictions as a measure is inherently flawed, as effectively corrupt officials would never be arrested.
-The Corruption Reflections Index, likewise, sits uncomfortably between measuring actual corruption and its appearance, saying nothing conclusive about either.
-Furthermore, this design does not speak to causality: It could very well be that in states with high levels of corruption, the public agitates for campaign contribution limits.
-Further research could examine this hypothesis by looking at changes in corruption and perception of corruption following the imposition and removal of state-level limits.
-Lastly, it may be the case that contribution limits are more or less effective under certain circumstances; further research could control for party control, prosecutorial resources, or other factors that might affect the effectiveness of contribution limits or measures of corruption.
-
-If Jim Bopp and other conservative legal scholars have their way, the Supreme Court will soon take a closer look at the logic laid out by their predecessors in 1976 in support of campaign contribution limits.
-Signs suggest that commitment to the Buckley v.
-Valeo structure are weakening, and not in the way that liberal reformers hope.
-Despite effort, scholars have failed to provide compelling evidence of a link between campaign contribution limits and corruption as defined by the Court.
-The measures of corruption that academics have used to date have serious limitations.
-Yet if the Court decides the burden of proof is on those looking to restrict political spending on narrow corruption grounds, reform advocates worried about money in politics have a steep empirical hill to climb, and likely only a few years to do it.
-
-\newpage
-##References 
-###Add new authors (see Google doc) and data. R packages?
-Ansolabehere, Stephen, John M de Figueiredo, and James M Snyder Jr. 2003. “Why is there so Little Money in US Politics?” Journal of Economic Perspectives. 17(1): 105–130.
-
-Alt, J. E., & Lassen, D. D. (2012). Enforcement and public corruption: evidence from the American states. The Journal of Law, Economics, and Organization, 30(2), 306-338.
-
-Barber, Michael J. "Ideological Donors, Contribution Limits, and the Polarization of American Legislatures." The Journal of Politics 78.1 (2016): 296-310.
-
-Boylan, R. T., & Long, C. X. (2003). Measuring public corruption in the American states: A survey of state house reporters. State Politics & Policy Quarterly, 3(4), 420-438.
-
-Cordis, A., & Milyo, J. (2013). Do state campaign finance reforms reduce public corruption?. George Mason University, Mercatus Center, Working Paper, (13-09).
-
-Cordis, A. S., & Milyo, J. (2016). Measuring public corruption in the United States: evidence from administrative records of federal prosecutions. Public Integrity, 18(2), 127-148.
-
-Crider, K., & Milyo, J. (2013). Do State Ethics Commissions Reduce Political Corruption: An Exploratory Investigation. UC Irvine L. Rev., 3, 717.
-
-Dincer, O., & Johnston, M.
-(2016).
-Political Culture and Corruption Issues in State Politics: A New Measure of Corruption Issues and a Test of Relationships to Political Culture.
-Publius: The Journal of Federalism, 47(1), 131-148.
-
-Glaeser, E. L., & Saks, R. E. (2006). Corruption in america. Journal of public Economics, 90(6), 1053-1072.
-
-Gross, D. A., Goidel, R. K., & Shields, T. G. (2002). State campaign finance regulations and electoral competition. American Politics Research, 30(2), 143-165.
-
-Hall, R. L., & Wayman, F. W. (1990). Buying time: Moneyed interests and the mobilization of bias in congressional committees. American political science review, 84(3), 797-820.
-
-Hurley, L.
-& Debenedetti, G.
-(2014, April 04).
-Legal victory for big-money campaign donors to be felt in states, courts.
-Retrieved December 16, 2017, from https://www.reuters.com/article/us-usa-court-election-analysis/legal-victory-for-big-money-campaign-donors-to-be-felt-in-states-courts-idUSBREA3308620140404
-
-Langbein, L. I. (1986). Money and access: Some empirical evidence. The journal of politics, 48(4), 1052-1062.
-
-Liu, C., & Mikesell, J. L. (2014). The impact of public officials’ corruption on the size and allocation of US state spending. Public Administration Review, 74(3), 346-359.
-
-Lott, J. R. (2006). Campaign finance reform and electoral competition. Public Choice, 129(3-4), 263-300.
-
-Persily, N., & Lammie, K. (2004). Perceptions of corruption and campaign finance: When public opinion determines constitutional law. University of Pennsylvania Law Review, 119-180.
-
-Primo, D. M. (2002). Public opinion and campaign finance: Reformers versus reality. The independent review, 7(2), 207-219.
-
-Primo, D. M., & Milyo, J. (2006). Campaign finance laws and political efficacy: evidence from the states. Election Law Journal, 5(1), 23-39.
-
-Rosenson, B. A. (2009). The effect of political reform measures on perceptions of corruption. Election Law Journal, 8(1), 31-46.
-
-Spencer, Douglas M., and Abby K. Wood. 2014. "Citizens United, states divided: an empirical analysis of independent political spending." LJ 89: 315.
-
-Stratmann, Thomas. 1991. “What Do Campaign Contributions Buy? Deciphering Causal Effects of Money and Votes.” Southern Economic Journal. Pp.606-620.
-
-Stratmann, T. (1998). The market for congressional votes: Is timing of contributions everything?. The Journal of Law and Economics, 41(1), 85-114.
-
-Stratmann, T. (2006). Contribution limits and the effectiveness of campaign spending. Public Choice, 129(3), 461-474.
-
-Walker, D. M., & Calcagno, P. T. (2013). Casinos and political corruption in the United States: A Granger causality analysis. Applied Economics, 45(34), 4781-4795.
-
-Walker, D. M., & Jackson, J. D. (2011). The effect of legalized gambling on state government revenue. Contemporary Economic Policy, 29(1), 101-114.
-
-Werner, Timothy, and John J.
-Coleman.
-2014.
-"Citizens United, independent expenditures, and agency costs: Reexamining the political economy of state antitakeover statutes." The Journal of Law, Economics, & Organization.
-127-159.
-
-Welch, W. P. (1982). Campaign contributions and legislative voting: Milk money and dairy price supports. Western Political Quarterly, 35(4), 478-495.
-
-Zall, B.
-(2017, October 24).
-Ninth Circuit Tees Up Latest Challenge to Citizens United and McCutcheon.
-Retrieved November 22, 2017, from https://publicpolicylegal.com/2017/10/24/ninth-circuit-tees-up-latest-challenge-to-citizens-united-and-mccutcheon/
+```

### 2018-06-15 Paper backup.Rmd
Mostly failing to stargazing

--- 2018-06-12 paper/Paper.Rmd
@@
 
-```{r stargazer CCI latex, results="asis", include=F}
+```{r stargazer CCI latex, results="asis", include=FALSE}
 stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,

### 2018-06-15 Paper.Rmd
Mostly failing to stargazing

@@
 
+Since the 1970s, the U.S.
+Supreme Court has frustrated efforts at campaign finance reform by maintaining that nearly all limits on political spending violate the first amendment’s protection of free speech.
+The Court makes only two exceptions: The state has a compelling enough interesting in preventing “corruption of the appearance of corruption” to limit political donations.
+But do campaign finance laws actually prevent corruption or its appearance?
+Using state-level data from 1990-2012 on contribution limits, corruption arrests, and media mentions of corruption, this paper employs a linear panel regression and a difference-in-differences analysis to test whether campaign contribution limits are associated with lower levels of corruption convictions or media mentions of corruption.
+These methods find no relationship between the presence or level of campaign finance laws and quid pro quo corruption, suggesting that would-be reformers must keep looking for evidence to support their efforts.
+As current challenges to contribution limits wind their way through federal courts, the answer to this question will inform the Supreme Court’s decision to uphold or strike down remaining limits on political campaign contributions.
+
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, cache = TRUE, message=FALSE, warning=FALSE)
+knitr::opts_chunk$set(echo = FALSE, eval=FALSE, cache = TRUE, message=FALSE, warning=FALSE)
 library(haven) # import .dta
-library(tidyverse) # everything 
+suppressMessages(library("tidyverse")) # everything 
 library(plm) # For linear panel regression
+library(stargazer) # For regression outputs #fail 
+library(texreg) # For regression outputs #fail 
+library(kableExtra) # For regression outputs 
+library(broom) # Because Matt Worthington said so 
+library(knitr) # Because Matt Worthington said so
+
 ```
 
-```{r data import, include=F}
+```{r data import, eval=T, message=F, warning=F}
 # Alt and Lassen's "Enforcement and Public Corruption: Evidence from US States"
@@
 
-[CCI table here]
+```{r stargzer CCI html}
+stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,
+  type="text", 
+  title = "Are campaign limits and corruption convictions correlated?",
+  out="collateral/CCI.htm",
+  dep.var.labels = c("Corruption Convictions Index"),
+  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
+```
+
+```{r stargazer CCI latex, results="asis", eval=TRUE}
+stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,
+  type="latex", 
+  title = "Are campaign limits and corruption convictions correlated?",
+  dep.var.labels = c("Corruption Convictions Index"),
+  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
+```
 
@@
 
-[CRI table here]
+```{r stargazer CRI html}
+stargazer(CRIreg1, CRIreg2, CRIreg3, CRIreg5,
+  type="text", 
+  title = "Are campaign limits and corruption reflections correlated?",
+  out="collateral/CRI.htm",
+  dep.var.labels = c("Corruption Reflections Index"),
+  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
+```
+
+```{r stargazer CRI latex, results="asis", eval=TRUE}
+stargazer(CRIreg1, CRIreg2, CRIreg3, CRIreg5,
+  title = "Are campaign limits and corruption reflections correlated?",
+  dep.var.labels = c("Corruption Reflections Index"),
+  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
+```
+
+The third set of models incorporates a number of control variables in order to isolate the effect of campaign finance laws on corruption arrest levels.
+As in the models above, the only correlation significant at the p<0.05 level is the presence of limits on what an individual can give to a party; again, the presence of limits in what an individual can give to a party is associated with a decline in the Corruption Reflections Index.
+
+```{r stargazer controlled panel}
+stargazer(CCIcontrol01,CCIcontrol02,CRIcontrol01,CRIcontrol02,
+  type="text", 
+  title = "Are campaign limits and correlated with corruption convictions or reflections?",
+  out="collateral/CCICRIcontrol.htm",
+  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
+  covariate.labels=c("Divided government", "Binding one-term limit"," Binding two-term limit","Real per capita income ($1000)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues ($1000)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)","Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)")
+  )
+```
+
+```{r stargazer controlled panel latex, results="asis", eval=TRUE}
+stargazer(CCIcontrol01,CCIcontrol02,CRIcontrol01,CRIcontrol02,
+  title = "Are campaign limits and correlated with corruption convictions or reflections?",
+  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
+  covariate.labels=c("Divided government", "Binding one-term limit"," Binding two-term limit","Real per capita income (thousands)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (thousands)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)","Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)")
+  )
+```
+
+### Modeling changes in campaign limits and corruption arrests
+
+The final set of models is a set of difference-in-difference models designed to isolate the effect of changes in campaign finance laws on corruption arrests.
+None of the models find correlation between campagin finance limits and either corruption convictions or corruption reflections.
+
+```{r stargazer DiD}
+stargazer(CCIDID01, CCIDID02, CCIDID03, CRIDID01, CRIDID02, CRIDID03,
+  type="text", 
+  title = "Do changes in limits lead to lower levels of corruption?",
+  out="collateral/DiD.htm",
+  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
+  covariate.labels=c("Individual limits removed","Individual limits imposed","Individual limit amount","Individual limits removed*amount","Individual limits imposed*amount",
+                     "PAC limits removed","PAC limits imposed","PAC limit amount","PAC limits removed*amount","PAC limits imposed*amount",
+                     "Individual-to-party limits removed","Individual-to-party limits imposed","Individual-to-party limit amount","Individual-to-party limits removed*amount","Individual-to-party limits imposed*amount"))
+
+```
+
+```{r stargazer DiD latex, results="asis", eval=TRUE}
+stargazer(CCIDID01, CCIDID02, CCIDID03, CRIDID01, CRIDID02, CRIDID03,
+  title = "Do changes in limits lead to lower levels of corruption?",
+  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
+  covariate.labels=c("Individual limits removed","Individual limits imposed","Individual limit amount","Individual limits removed*amount","Individual limits imposed*amount",
+                     "PAC limits removed","PAC limits imposed","PAC limit amount","PAC limits removed*amount","PAC limits imposed*amount",
+                     "Individual-to-party limits removed","Individual-to-party limits imposed","Individual-to-party limit amount","Individual-to-party limits removed*amount","Individual-to-party limits imposed*amount"))
+
+```
 
 ##Discussion
-###Rework. 
-Over two thousand years ago, pre-Socratic Greek thinker Protagoras said that for any event, at least two distinct and opposing accounts will appear.
+How might we interpret these results?
+The relationship between campaign finance laws and the Corruption Convictions Index is most clear: None of these methods reveal any correlation between state level campaign finance laws and levels of corruption as measured by corruptions convictions, even controlling for variation in enforcement across the states.
+
+Interpreting the results for the Corruption Reflections Index must wrestle with one awkward result: The pair of stars that suggest the presence of individual-to-party limits is associated with a decrease in the Corruption Reflections Index.
+There is a less than 1% probability that the results are due to chance.
+How could this be, given that (a) the presence of individual-to-party limits has no association with a change the Corruption Convictions Index; (b) none of the other contribution limits are associated with a change in the Corruption Reflections Index; and (c) there is no correlation between the level of the individual-to-party limit and the Corruption Reflections Index?
+In practice, this would mean that states with individual-to-party limits also see lower levels of Associated Press reporting on corruption, but that once limits of any kind are imposed, the level of limit doesn’t matter.
+It would also mean that only individual-to-party limits matter, not individual-to-candidate or PAC-to-candidate limits.
+Lastly, it would imply that the presence of such limits has an effect on reporting about corruption, but not corruption convictions.
+
+There is limited theoretical explanation for this outcome.
+It could be that AP reporters are somehow more likely to report on conviction allegations against political parties than against individual candidates or corporations, even where those allegations don’t result in greater levels of convictions, and only in states where the absence of contribution limits allows for a clean, “no limits on contributions” narrative.
+It is more likely, however, that these results call into question the robustness of Dincer and Johnston’s Corruption Reflections Index.
+As mentioned above, further research could carry forward their text-mining method into a greater number and variety of outlets, in order to find a measure of corruption reporting more tightly correlated with other measures.
+
+##Conclusion
 There at least two distinct and opposing ways to explain these results, viewpoints that will come into direct and public conflict if the Court chooses to hear a first amendment challenge to campaign contribution limits.
 
-The first interpretation is that campaign finance and quid pro quo corruption simply aren’t related.
-The legal implications of this are clear and system-altering.
+The first interpretation is that campaign finance and quid pro quo corruption are simply not related.
+How could this be?
+One explanation is that the measures of corruption used here fail to capture most corruption, which is never prosecuted; this explanation, however, would rest on the assumption that corruption is _unequally_ captured across states over time.
+A second explanation is that corruption occurs regardless of campaign finance laws: Those politicians likely to engage in corrupt behavior will do so outside of the campaign finance regime, where their transactions would be most visible.
+A third explanation is the simplest one: Politics is simply less corrupt than is popularly believed.
+
+The legal implications of the second and third interpretations are clear and wide-reaching.
 The Supreme Court presently equates political donations with political speech, meaning that it is protected by the first amendment, but that preventing corruption or its appearance in the political system is so important that first amendment rights can be abridged to ensure it.
-No other justification--not a more informed electorate, or more competitive elections, or anything else--is an important enough concern that we should limit speech.
+No other justification--not a more informed electorate, or more competitive elections, or anything else--is an important enough concern that we should limit political speech in the form of campaign donations.
 If there is no link between campaign contribution limits and corruption, then there is no reason to abridge US citizens’ first amendment rights by limiting campaign donations.

### 2018-06-15 Paper.Rmd
Stars and bars

@@
 output: pdf_document
+header-includes:
+- \usepackage{pdflscape}
+- \newcommand{\blandscape}{\begin{landscape}}
+- \newcommand{\elandscape}{\end{landscape}}
 ---
@@
   dep.var.labels = c("Corruption Convictions Index"),
-  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
+  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"),
+  font.size = "small",
+  header=FALSE,
+  column.sep.width = "-15pt",
+  digits = 2, digits.extra = 2)
 ```
-
+\newpage
 The second set of models (below) also fails to find a relationship between state-level campaign contribution limits and media mentions of corruption as measured by the Corruption Reflections Index, with one exception: The presence of limits on what an individual can give to a party is associated with a 0.087 point decline in the Corruption Reflection Index.
@@
   dep.var.labels = c("Corruption Reflections Index"),
-  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
+  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"),
+  font.size = "small",
+  header=FALSE,
+  column.sep.width = "-15pt",
+  digits = 2, digits.extra = 2)
 ```
@@
 As in the models above, the only correlation significant at the p<0.05 level is the presence of limits on what an individual can give to a party; again, the presence of limits in what an individual can give to a party is associated with a decline in the Corruption Reflections Index.
+\newpage
 
@@
 
-```{r stargazer controlled panel latex, results="asis", eval=TRUE}
+```{r 3 stargazer controlled panel latex, results="asis", eval=TRUE}
 stargazer(CCIcontrol01,CCIcontrol02,CRIcontrol01,CRIcontrol02,
@@
   dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
-  covariate.labels=c("Divided government", "Binding one-term limit"," Binding two-term limit","Real per capita income (thousands)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (thousands)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)","Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)")
-  )
+  covariate.labels=c("Divided government", "Binding one-term limit"," Binding two-term limit","Real per capita income (thousands)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (thousands)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)","Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"),
+  font.size = "small",
+  header=FALSE,
+  column.sep.width = "-15pt",
+  no.space = T,
+  digits = 2, digits.extra = 2)
 ```
@@
 
+\newpage
+\blandscape
 ```{r stargazer DiD latex, results="asis", eval=TRUE}
@@
                      "PAC limits removed","PAC limits imposed","PAC limit amount","PAC limits removed*amount","PAC limits imposed*amount",
-                     "Individual-to-party limits removed","Individual-to-party limits imposed","Individual-to-party limit amount","Individual-to-party limits removed*amount","Individual-to-party limits imposed*amount"))
+                     "Individual-to-party limits removed","Individual-to-party limits imposed","Individual-to-party limit amount","Individual-to-party limits removed*amount","Individual-to-party limits imposed*amount"),
+  font.size = "small", 
+  header = FALSE,
+  column.sep.width = "-15pt",
+  digits = 2, digits.extra = 2,
+  no.space = TRUE)
 
 ```
+\elandscape
 

### 2018-06-26 Paper.Rmd
Paper edits. Remaining: Chart details, page order, revisit Milyo.

@@
 - \newcommand{\elandscape}{\end{landscape}}
+- \usepackage{setspace}
+- \doublespacing
 ---
@@
 Supreme Court has frustrated efforts at campaign finance reform by maintaining that nearly all limits on political spending violate the first amendment’s protection of free speech.
-The Court makes only two exceptions: The state has a compelling enough interesting in preventing “corruption of the appearance of corruption” to limit political donations.
-But do campaign finance laws actually prevent corruption or its appearance?
+In its 1976 _Buckley v.
+Valeo_ decision, the Court laid out only two justifications for limiting political speech in the form of campaign donations: To prevent corruption or the appearance of corruption.
+But do campaign finance limits actually prevent corruption or its appearance?
 Using state-level data from 1990-2012 on contribution limits, corruption arrests, and media mentions of corruption, this paper employs a linear panel regression and a difference-in-differences analysis to test whether campaign contribution limits are associated with lower levels of corruption convictions or media mentions of corruption.
-These methods find no relationship between the presence or level of campaign finance laws and quid pro quo corruption, suggesting that would-be reformers must keep looking for evidence to support their efforts.
+These methods find no relationship between the presence or level of campaign finance laws and quid pro quo corruption.
 As current challenges to contribution limits wind their way through federal courts, the answer to this question will inform the Supreme Court’s decision to uphold or strike down remaining limits on political campaign contributions.
@@
 ##Introduction
-<!--Shorten?-->
-In 1976, the Supreme Court ruled in Buckley v.
-Valeo that political campaign contributions are the equivalent of free speech, and therefore protected by the first amendment.
-At the same time, the Court laid out one mechanism and one justification for limiting those contributions.
-First, it argued that more money spent doesn’t amount of “more” speech, allowing for campaign contribution dollar amount limits.
+In 1976, the Supreme Court ruled in _Buckley v.
+Valeo_ that political campaign contributions are the equivalent of free speech, and therefore protected by the first amendment.
+At the same time, the Court laid out one mechanism and two permissible reasons for limiting those contributions.
+First, it argued that more money spent doesn’t amount of “more” speech, allowing for the use of campaign contribution dollar amount limits.
 Donating one dollar or $5,000 to a political campaign amounts to a speech act, the Court held, and so it is permissible to impose limits on the amount of contributions as long as contributions are not prevented.
-Second, having laid out the mechanism by which money in politics might be limited, the court laid out the only justification for limiting contributions that it would accept moving forward: To prevent corruption or the appearance thereof.
-As Kang (2012) argues, the holdings in Buckley v.
-Valeo provided “the basic framework of contribution limits and disclosure requirements” for the following four decades.
-Since Buckley v.
-Valeo, Congress has passed only one campaign finance law, the Bipartisan Campaign Reform Act of 2002.
+Second, having laid out this mechanism by which money in politics might be limited, the court laid out only two constitutionally permissible reasons for limiting contributions: To prevent corruption or the appearance thereof.
+As Kang (2012) argues, the holdings in _Buckley v.
+Valeo_ provided “the basic framework of contribution limits and disclosure requirements” for the following four decades.
+Since _Buckley v.
+Valeo_, Congress has passed only one campaign finance law, the Bipartisan Campaign Reform Act of 2002.
 Better know as McCain-Feingold, the bill took aim at unlimited “soft money” contributions to political parties and expanded the Federal Election Commission’s disclosure requirements to what it called “electioneering communications,” political ads not paid for by campaigns themselves.
 
-Apart from McCain-Feingold, for forty years all changes in the landscape of campaign finance have come from the courts, the majority being decided upon how to balance questions of free political speech versus corruption.
-Those rulings have often been driven by the question of corporations’ participation in the political process.
+Apart from McCain-Feingold, for forty years all changes in the landscape of campaign finance have come from the courts, which have worked to balance questions of corruption with those of free speech.
+In 1981, the Court struck down contribution limits related to ballot measures (_Citizens against Rent Control v.
+City of Berkeley-).
+Just before the passage of McCain-Feingold, the courts considered state-level limits, allowing low limits in Missouri (_Nixon v.
+Shrink Missouri_, 2000), though it would later finding Vermont's to be low eonugh that they had a meaningful impact on political speech (_Randall v.
+Sorrell_, 2006).
+
+<!--Those rulings have often been driven by the question of corporations’ participation in the political process.
 In 1978, the Court extended free speech protections to corporations (First National Bank of Boston v.
 Bellotti).
-In 1986, it  and struck down efforts to restrict their expenditures to FEC-registered Political Action Committees (FEC v.
-Massachusetts Right to Life).
+
 Then in 1990, it upheld a ban on corporations using treasury funds to pay for issue advertisements, arguing for an extended definition of corruption, "the corrosive and distorting effects of immense aggregations of wealth that are accumulated with the help of the corporate form and that have little or no correlation to the public's support for the corporation's political ideas" (Austin v.
@@
 
-The passage of the McCain-Feingold in 2002 inspired a wave of challenges to campaign contributions and expenditures, driven mostly by conservative and religious groups.
+In 1986, it  and struck down efforts to restrict their expenditures to FEC-registered Political Action Committees (FEC v. Massachusetts Right to Life).
+
+-->
+The passage of the McCain-Feingold in 2002 inspired a wave of challenges to campaign contributions and expenditures, driven mostly by conservative and religious political groups.
 In 2007, the Court examined the McCain-Feingold ban on airing issue advertisements close to election.
-Banning such ads, the Court argued, would have a chilling effect on free speech, and it struck down the ban (FEC v.
-Wisconsin Right to Life).
-Then, in 2010, the Court issued what has become one of its most well-known rulings: In Citizens United v.
-FEC (2010), it struck down limits on independent expenditures by outside groups, including corporations and unions.
-One critical aspect of Citizens United is the establishment of the principle that, according to Justice Anthony Kennedy, “independent expenditures do not lead to, or create the appearance of, quid pro quo corruption.” The Court’s emphasis on quid pro quo corruption as the only justification for contribution limits extended the following year, as it struck down an Arizona effort to level the political playing field with matching state campaign funds (Arizona Free Enterprise Club v.
-Bennett, 2011).
+Banning such ads, the Court argued, would have a chilling effect on free speech, and it struck down the ban (_FEC v.
+Wisconsin Right to Life_).
+Then, in 2010, the Court issued what has become one of its most well-known rulings: In _Citizens United v.
+FEC_ (2010), it struck down limits on independent expenditures by outside groups, including corporations and unions.
+One critical aspect of _Citizens United_ is the establishment of the principle that, according to Justice Anthony Kennedy, “independent expenditures do not lead to, or create the appearance of, quid pro quo corruption.” The Court’s emphasis on quid pro quo corruption as the only justification for contribution limits extended the following year, as it struck down an Arizona effort to level the political playing field with matching state campaign funds (_Arizona Free Enterprise Club v.
+Bennett_, 2011).
 
@@
 The 1971 Federal Election Campaign Act placed a limit on the amount an individual could give to one campaign, in addition to two-year limits on the total amount an individual could give to political campaigns.
-In McCutcheon v.
-FEC (2014) James Bopp, one of the attorneys behind the Citizens United challenge, convinced the Court of the unconstitutionality of total individual limits.
-Another case, Holmes v.
-FEC (2017), targeted the distribution of individual campaign contribution across primary and general elections.
-In yet another, Lair v.
-Motl (2017), Bopp once again took aim at individual contribution limits, arguing that the state of Montana had not shown compelling evidence that campaign contribution limits decreased the risk of corruption.
+In _McCutcheon v.
+FEC_ (2014) James Bopp, one of the attorneys behind the Citizens United challenge, convinced the Court of the unconstitutionality of total individual limits.
+Another case, _Holmes v.
+FEC_ (2017), targeted the distribution of individual campaign contribution across primary and general elections.
+In yet another, _Lair v.
+Motl_ (2017), Bopp once again took aim at individual contribution limits, arguing that the state of Montana had not shown compelling evidence that campaign contribution limits decreased the risk of corruption.
 
-The Ninth Circuit Court of Appeals upheld Montana’s campaign contribution limits, but further challenges to contribution limits are likely.
+The Ninth Circuit Court of Appeals upheld Montana’s campaign contribution limits, and the Fifth Circuit similarly upheld limits in Austin, TX (_Zimmerman v.
+City of Austin_, 2018).
+But further challenges to contribution limits are likely.
 Bopp said that he planned to appeal the Ninth Circuit’s ruling.
@@
 Other scholars, however, are not so convinced.
-Wright (1990) finds that once lobbying efforts are factored in, the effects of contributions on voting outcomes washes out.
+Wright finds that once lobbying efforts are factored in, the effects of contributions on voting outcomes washes out (1990).
 And it is notoriously difficult to tease out whether political donations change legislators’ minds or instead flow to legislators with established, friendly positions (Ansolabehere et al 2003).
@@
 
-One fundamental limitation of these federal level studies on campaign contributions and corruption, however, is the absence of a counterfactual: Given that contribution limits have been in place since the 1970s, it is difficult to argue what might have happened in their absence.
+One fundamental limitation of these federal level studies on campaign contributions and corruption is the absence of a counterfactual.
+Given that contribution limits have been in place since the 1970s, it is difficult to argue what might have happened in their absence.
 Recent work on campaign finance has attempted to address this problem by focusing on the effects of differences in campaign finance laws at the state level.
-Variation across states and over time allows room for studying the causes and consequences of campaign finance limits.
+Variation across states and over time allows room for studying the causes and consequences of campaign finance limits, separate from the question of corruption.
 Studies suggest that campaign finance limits are associated with less electoral competition (Gross et al 2002, Lott 2006), but that disclosure rules and some organizational limits are associated with greater levels of government trust (Primo and Milyo 2006) and may increase the return on campaign expenditures (Stratmann 2006).
@@
 
-A largely separate body of work has examined the causes and consequences of corruption at the state level.
+A largely separate body of work has examined the causes and consequences of corruption at the state level, separate from campaign finance.
 Most use the Department of Justice’s Annual Public Integrity Report, which correlate highly with state level perceptions of corruption (Walker and Calcagno 2011, Glaeser and Saks 2006, Liu & Mikesell 2014).
@@
 They have also shown the absence of a link between state ethics commissions and reduced corruption (Crider and Milyo 2013).
-Researchers have also developed alternative measures of state level corruption, including surveys of state reporters (Boylan and Long 2003) and the recently available Transactional Records Access Clearinghouse (TRAC) database of political corruption (Cordis & Milyo 2016).
 
-Very little work, however, has connected the literature on state-level campaign finance regulations to measures of political corruption--the one question of import to the Supreme Court as it considers the constitutionality of contribution limits.
-The exception to this is one 2013 working paper by Cordis and Milyo.
+In response to criticisms of corruption convictions as a proper measure of corruption, researchers have also developed alternative measures of state level corruption.
+Boylan and Long make use of surveys of state reporters (2003).
+Cordis and Milyo deploy the recently available Transactional Records Access Clearinghouse (TRAC) database of political corruption (2016).
+Dincer and Jonhston introduce a Corruption Reflections Index, which tracks mentions of corruption in Associated Press reports (2016).
+
+A smaller number of scholars have begun connecting these bodies of work to examine the impact of state-level campaign finance regulations on measures of quid pro quo corruption--one of only two questions of import to the Supreme Court as it considers the constitutionality of contribution limits.
+The exception to this is a 2013 working paper by Cordis and Milyo.
 In line with Persily and Lammie (2004), Milyo argues that campaign reform efforts have little effect on public perceptions of corruption.
@@
 <!--Add in summary statistics?-->
-This paper builds upon the growing body of state-level political science research to ask the question: Are campaign contribution limits at the state level associated with lower levels of corruption?
-Given open debate about the proper measure of state-level corruption, this paper uses two.
+In this paper, I build upon the growing body of state-level political science research to ask whether campaign contribution limits at the state level associated with lower levels of corruption.
+Given open debate about the proper measure of state-level corruption, I use two measures.
 The first, a Corruptions Convictions Index, is the traditional measure of state level corruption, built from Department of Justice convictions data.
@@
 I combine these measures with a third dataset from Michael Barber’s 2016 work on campaign contribution limits and political polarization; and a fourth dataset from James Alt and David Dryer Lassen, to provide controls for the full model (Alt and Lassen 2012).
-
 Barber’s dataset is a panel of contribution limits from 1990-2012 for the lower house of every state legislature.
@@
 The second dataset comes from the Department of Justice’s “Report to Congress on the Activities and Operations of the Public Integrity Section” by way of the Institute for Corruption Studies.[^Koch]  Since 1976, the FBI has tracked political corruption at the state level, and the Corruption Convictions Index (CCI) used here includes the number of corruption convictions in a year normalized by the population in each state.
-This measure of corruption is widely used in academic research.
+This measure of corruption is widely used in academic research, though not without criticism.
 
@@
 The Corruption Convictions Index suffers from a number of issues, as outlined by Dincer and Johnston in their introduction to the Corruption Reflections Index.
-They argue that the CCI includes only federal data; the resources available to prosecutors varies from state to state; US Attorneys are political appointees; and the measure records only convictions, which is at best a reflection of underlying corruption.
+They argue that the CCI includes only federal data; that the resources available to prosecutors varies from state to state; that US Attorneys are political appointees; and that the measure records only convictions, which is at best a reflection of underlying corruption.
 
-The Corruption Reflections Index, too, has its limits: It relies on a single news source, the Associated Press.
+The Corruption Reflections Index, too, has its flaws: It relies on a single news source, the Associated Press.
 Similar to federal prosecutors’ offices, the resources available to each AP office vary.
@@
 The Corruption Reflections Index also seems to assume in its name that media reports of corruption are a mere reflection of corruption, rather than an endogenous variable in the ecosystem that enables corrupt behavior.
-Previous work, in contrast, has argued that media have a clear bias and play an important role in shaping public perceptions of corruption (Sorauf 1987; Ansolabehere, Snowberg and Snyder 2005).
+Previous work, in contrast, has argued that media have a clear bias and play an important role in shaping public perceptions of corruption, rather than just reflecting it (Sorauf 1987; Ansolabehere, Snowberg and Snyder 2005).
 
@@
 
-I include three independent variables in both sets of models: Individual contribution limits, individual-to-party contribution limits, and PAC contribution limits.
+I include three predictor variables in both sets of models: Individual contribution limits, individual-to-party contribution limits, and PAC contribution limits.
 For each of these independent variables, I construct two variables to use in the model.
@@
 If the model above fails to show an initial correlation, this may be due to the confounding effect of absent variables.
-In order to test that, I build a model of political corruption using control variables previously demonstrated to be correlated with corruption arrests, resulting in a dataset covering 1990-2004, the period of overlap between Barber's and Alt and Lassen's data.
+In order to test that, I build a model of political corruption using control variables previously demonstrated to be correlated with corruption arrests, resulting in a dataset covering 1990-2004, the period of overlap amogn the datasets listed above.
 These include controlling for the size and education levels of the population, the ideology of a population, income levels and inequality, education levels, the number and relative income of government employees, and urbanization.
@@
 ### Modeling campaign limits and corruption arrests 
-The results of the initial panel regression reveal no correlation between state-level campaign contribution limits and corruption, with one exception: There is a statistically significant relationship between the presence of individual-to-party limits and the Corruption Reflections Index.
+The results of the initial panel regressions reveal no correlation between state-level campaign contribution limits and corruption, with one exception: There is a statistically significant relationship between the presence of individual-to-party limits and the Corruption Reflections Index.
 
-The first set of models (below) measures the association of various campaign contribution limits with the Corruption Convictions Index.
+The first set of models (Table I) measures the association of various campaign contribution limits with the Corruption Convictions Index.
 The sign of each coefficient is negative, indicating that the presence of limits is associated with lower corruption levels, but that where limits exist, higher (weaker) donation limits are associated with lower levels of corruption.
@@
 
+The second set of models (Table II) also fails to find a relationship between state-level campaign contribution limits and media mentions of corruption as measured by the Corruption Reflections Index, with one exception: The presence of limits on what an individual can give to a party is associated with a 0.10 point decline in the Corruption Reflection Index.
+The Corruption Reflections Index operates on a scale of zero to one (with a few outlying exceptions), meaning that the presence of individual-to-party limits is associated with a 10% decrease in the index.
+
+The third set of models (Table 3) incorporates a number of control variables in order to isolate the effect of campaign finance laws on corruption arrest levels.
+As in the models above, the only correlation significant at the p<0.05 level is the presence of limits on what an individual can give to a party.
+As above, the presence of limits in what an individual can give to a party is associated with a decline in the Corruption Reflections Index.
+
+### Modeling changes in campaign limits and corruption arrests
+
+The final set of models (Table 4) displays results from multiple difference-in-difference models designed to isolate the effect of changes in campaign finance laws on corruption arrests.
+None of the models find correlation between campagin finance limits and either corruption convictions or corruption reflections.
+
+\newpage 
 ```{r stargzer CCI html}
@@
 ```
-\newpage
-The second set of models (below) also fails to find a relationship between state-level campaign contribution limits and media mentions of corruption as measured by the Corruption Reflections Index, with one exception: The presence of limits on what an individual can give to a party is associated with a 0.087 point decline in the Corruption Reflection Index.
-The Corruption Reflections Index operates on a scale of zero to one (with a few outlying exceptions), meaning that the presence of individual-to-party limits is associated with an 8.7% point decrease in the index.
 
@@
 stargazer(CRIreg1, CRIreg2, CRIreg3, CRIreg5,
+          type="latex",
   title = "Are campaign limits and corruption reflections correlated?",
@@
 ```
-
-The third set of models incorporates a number of control variables in order to isolate the effect of campaign finance laws on corruption arrest levels.
-As in the models above, the only correlation significant at the p<0.05 level is the presence of limits on what an individual can give to a party; again, the presence of limits in what an individual can give to a party is associated with a decline in the Corruption Reflections Index.
-\newpage
 
@@
 ```
-
-### Modeling changes in campaign limits and corruption arrests
-
-The final set of models is a set of difference-in-difference models designed to isolate the effect of changes in campaign finance laws on corruption arrests.
-None of the models find correlation between campagin finance limits and either corruption convictions or corruption reflections.
 
@@
 ##Discussion
-How might we interpret these results?
-The relationship between campaign finance laws and the Corruption Convictions Index is most clear: None of these methods reveal any correlation between state level campaign finance laws and levels of corruption as measured by corruptions convictions, even controlling for variation in enforcement across the states.
+At least one group of models allows for a straightforward interpretation.
+The panel models examining the relationship between state-level campaign finance laws and the Corruption Convictions Index fail to show any correlation between state level campaign finance laws and levels of corruption as measured by corruptions convictions, even controlling for variation in enforcement across the states.
 
-Interpreting the results for the Corruption Reflections Index must wrestle with one awkward result: The pair of stars that suggest the presence of individual-to-party limits is associated with a decrease in the Corruption Reflections Index.
+The results for the models examining the relationship between campaign finance limits and the Corruption Reflections Index are less clear.
+The pair of stars that suggest the presence of individual-to-party limits is associated with a decrease in the Corruption Reflections Index.
 There is a less than 1% probability that the results are due to chance.
-How could this be, given that (a) the presence of individual-to-party limits has no association with a change the Corruption Convictions Index; (b) none of the other contribution limits are associated with a change in the Corruption Reflections Index; and (c) there is no correlation between the level of the individual-to-party limit and the Corruption Reflections Index?
+How could this be, given that (a) the presence of individual-to-party limits has no association with a change the Corruption Convictions Index; (b) none of the other contribution limits are associated with a change in the Corruption Reflections Index; and (c) there is no correlation between the dollar amount of the individual-to-party limit and the Corruption Reflections Index?
 In practice, this would mean that states with individual-to-party limits also see lower levels of Associated Press reporting on corruption, but that once limits of any kind are imposed, the level of limit doesn’t matter.
 It would also mean that only individual-to-party limits matter, not individual-to-candidate or PAC-to-candidate limits.
-Lastly, it would imply that the presence of such limits has an effect on reporting about corruption, but not corruption convictions.
+Lastly, it would imply that the presence of such limits has an effect on reporting about corruption, but not on corruption convictions.
 
 There is limited theoretical explanation for this outcome.
-It could be that AP reporters are somehow more likely to report on conviction allegations against political parties than against individual candidates or corporations, even where those allegations don’t result in greater levels of convictions, and only in states where the absence of contribution limits allows for a clean, “no limits on contributions” narrative.
+It could be that AP reporters are somehow more likely to report on conviction allegations against political parties than against individual candidates or PACs, even where those allegations don’t result in greater levels of convictions, and only in states where the absence of contribution limits allows for a clean, “no limits on contributions” narrative.
 It is more likely, however, that these results call into question the robustness of Dincer and Johnston’s Corruption Reflections Index.
@@
 How could this be?
-One explanation is that the measures of corruption used here fail to capture most corruption, which is never prosecuted; this explanation, however, would rest on the assumption that corruption is _unequally_ captured across states over time.
-A second explanation is that corruption occurs regardless of campaign finance laws: Those politicians likely to engage in corrupt behavior will do so outside of the campaign finance regime, where their transactions would be most visible.
-A third explanation is the simplest one: Politics is simply less corrupt than is popularly believed.
+One explanation is that the measures of corruption used here fail to capture most corruption, which is never prosecuted.
+This explanation, however, would rest on the assumption that corruption is unequally captured across states over time.
+A second explanation is that corruption occurs regardless of campaign finance laws: Politicians likely to engage in corrupt behavior will do so outside of the campaign finance regime, where their transactions would be most visible.
 
-The legal implications of the second and third interpretations are clear and wide-reaching.
+The legal implications of the second interpretation are clear and material.
 The Supreme Court presently equates political donations with political speech, meaning that it is protected by the first amendment, but that preventing corruption or its appearance in the political system is so important that first amendment rights can be abridged to ensure it.
-No other justification--not a more informed electorate, or more competitive elections, or anything else--is an important enough concern that we should limit political speech in the form of campaign donations.
-If there is no link between campaign contribution limits and corruption, then there is no reason to abridge US citizens’ first amendment rights by limiting campaign donations.
+No other justification--including creating a more informed electorate, or stimulating more competitive elections, or equiality of financial participation in elections--is an important enough concern that we should limit political speech in the form of campaign donations.
+If there is no link between campaign contribution limits and corruption,  the Court may conclude that there is no reason to abridge US citizens’ first amendment rights by limiting campaign donations.
 
@@
 Further research could more fully explore these relationships, including the manner in which public perceptions of corruption provide enabling or constraining environments for corruption itself.
-Given the importance of these limitations, all that can be concluded from the analysis above is that no link between contribution limits and corruption has been demonstrated with this data; not that no link exists.
+Given the importance of these limitations, all that can be concluded from the analysis above is that no link between contribution limits and corruption has been demonstrated with this data, not that no link exists.
 
-The anti-reform/pro-free-speech interpretation must also more fully take into account the second half of the court’s reasoning for limiting free speech, the “appearance of corruption.” Cordis and Milyo’s working paper on confidence and trust in state government is an important step in that direction, though they acknowledges that “survey measures that relate to opinion on the integrity of democracy are likely to reflect a much more expansive view of ‘corruption’ than what any Court would consider appropriate (2012).
-Dincer and Johnston’s surveys of state reporters is another step, but is limited by its design: Though a clever proxy, state reporters’ perceptions are just a proxy, not a direct measure, of public perceptions of corruption (2017).
+The anti-reform/pro-speech interpretation must also more fully take into account the second half of the court’s reasoning for limiting free speech, the “appearance of corruption.” Cordis and Milyo’s working paper on confidence and trust in state government is an important step in that direction, though they acknowledges that “survey measures that relate to opinion on the integrity of democracy are likely to reflect a much more expansive view of ‘corruption’ than what any Court would consider appropriate (2012).
+Dincer and Johnston’s surveys of state reporters is another step, but is limited by its design: State reporters’ perceptions are just a proxy, not a direct measure, of public perceptions of corruption (2017).
 
-The second, pro-reform interpretation of these results would reiterate and add to these limitations.
-Using corruption convictions as a measure is inherently flawed, as effectively corrupt officials would never be arrested.
+The second, pro-reform interpretation of these results would highlight further issues.
+Using corruption convictions as a measure may be inherently flawed, as effectively corrupt officials would never be arrested.
 The Corruption Reflections Index, likewise, sits uncomfortably between measuring actual corruption and its appearance, saying nothing conclusive about either.
 Furthermore, this design does not speak to causality: It could very well be that in states with high levels of corruption, the public agitates for campaign contribution limits.
-Further research could examine this hypothesis by looking at changes in corruption and perception of corruption following the imposition and removal of state-level limits.
-Lastly, it may be the case that contribution limits are more or less effective under certain circumstances; further research could control for party control, prosecutorial resources, or other factors that might affect the effectiveness of contribution limits or measures of corruption.
 
 If Jim Bopp and other conservative legal scholars have their way, the Supreme Court will soon take a closer look at the logic laid out by their predecessors in 1976 in support of campaign contribution limits.
-Signs suggest that commitment to the Buckley v.
-Valeo structure are weakening, and not in the way that liberal reformers hope.
+Justice Thomas's comments in _McCutcheon v.
+FEC_ suggest that commitment to the Buckley v.
+Valeo structure is weakening, and not in the way that liberal reformers might hope.
 Despite effort, scholars have failed to provide compelling evidence of a link between campaign contribution limits and corruption as defined by the Court.
 The measures of corruption that academics have used to date have serious limitations.
-Yet if the Court decides the burden of proof is on those looking to restrict political spending on narrow corruption grounds, reform advocates worried about money in politics have a steep empirical hill to climb, and likely only a few years to do it.
+Yet if the Court decides the burden of proof is on those looking to restrict political spending on narrow corruption grounds, reform advocates worried about money in politics have a steep empirical hill to climb, and likely only a few short years to do it.
 
@@
 ##References 
-###Add new authors (see Google doc) and data. R packages?
+<!--Add new authors (see Google doc) and data. R packages?-->
 Ansolabehere, Stephen, John M de Figueiredo, and James M Snyder Jr. 2003. “Why is there so Little Money in US Politics?” Journal of Economic Perspectives. 17(1): 105–130.

### 2018-07-02 Paper.Rmd
Spellchecking

@@
 At the same time, the Court laid out one mechanism and two permissible reasons for limiting those contributions.
-First, it argued that more money spent doesn’t amount of “more” speech, allowing for the use of campaign contribution dollar amount limits.
+First, it argued that more money spent does not amount of “more” speech, allowing for the use of campaign contribution dollar amount limits.
 Donating one dollar or $5,000 to a political campaign amounts to a speech act, the Court held, and so it is permissible to impose limits on the amount of contributions as long as contributions are not prevented.
@@
 Just before the passage of McCain-Feingold, the courts considered state-level limits, allowing low limits in Missouri (_Nixon v.
-Shrink Missouri_, 2000), though it would later finding Vermont's to be low eonugh that they had a meaningful impact on political speech (_Randall v.
+Shrink Missouri_, 2000), though it would later finding Vermont's to be low enough that they had a meaningful impact on political speech (_Randall v.
 Sorrell_, 2006).
@@
 
-One fundamental limitation of these federal level studies on campaign contributions and corruption is the absence of a counterfactual.
+One fundamental limitation of these federal level studies on campaign contributions and corruption is the absence of a counter-factual.
 Given that contribution limits have been in place since the 1970s, it is difficult to argue what might have happened in their absence.
@@
 The second, the Corruptions Reflection Index, is a new measure put forward by Dincer and Johnston (2016).
-I combine these measures with a third dataset from Michael Barber’s 2016 work on campaign contribution limits and political polarization; and a fourth dataset from James Alt and David Dryer Lassen, to provide controls for the full model (Alt and Lassen 2012).
-Barber’s dataset is a panel of contribution limits from 1990-2012 for the lower house of every state legislature.
-Barber compiled this dataset from the FEC, Westlaw, and the Nation Council of State Legislatures.
+I combine these measures with a third data set from Michael Barber’s 2016 work on campaign contribution limits and political polarization; and a fourth data set from James Alt and David Dryer Lassen, to provide controls for the full model (Alt and Lassen 2012).
+Barber’s data set is a panel of contribution limits from 1990-2012 for the lower house of every state legislature.
+Barber compiled this data set from the FEC, Westlaw, and the Nation Council of State Legislatures.
 Each dollar amount is inflation indexed to 2010 dollar amounts, and bi-annualized.
 There are three different types of limits in the Barber database: Individual contribution limits, individual-to-party limits, and PAC limits.
-Barber utilized individual and PAC contributions in his analysis of polarization, leaving out individual-to-party limits given that party contributions typically make up less than 10% of total political fundraising; I include it this analysis to determine whether parties, rather than PACs or individuals, might be the locus of corruption as measured by our other two datasets (Barber 2016).
+Barber utilized individual and PAC contributions in his analysis of polarization, leaving out individual-to-party limits given that party contributions typically make up less than 10% of total political fundraising; I include it this analysis to determine whether parties, rather than PACs or individuals, might be the locus of corruption as measured by our other two data sets (Barber 2016).
 
-The second dataset comes from the Department of Justice’s “Report to Congress on the Activities and Operations of the Public Integrity Section” by way of the Institute for Corruption Studies.[^Koch]  Since 1976, the FBI has tracked political corruption at the state level, and the Corruption Convictions Index (CCI) used here includes the number of corruption convictions in a year normalized by the population in each state.
+The second data set comes from the Department of Justice’s “Report to Congress on the Activities and Operations of the Public Integrity Section” by way of the Institute for Corruption Studies.[^Koch]  Since 1976, the FBI has tracked political corruption at the state level, and the Corruption Convictions Index (CCI) used here includes the number of corruption convictions in a year normalized by the population in each state.
 This measure of corruption is widely used in academic research, though not without criticism.
 
-The third dataset is the Institute for Corruption Studies’ Corruption Reflections Index (CRI), put together by Dincer and Johnston for their 2016 article on state-level corruption, and which they create in response to the limitations of the Corruption Convictions.
+The third data set is the Institute for Corruption Studies’ Corruption Reflections Index (CRI), put together by Dincer and Johnston for their 2016 article on state-level corruption, and which they create in response to the limitations of the Corruption Convictions.
 The Corruption Reflections Index represents the fraction of Associated Press stories about politics in a particular state that mention political corruption (Dincer and Johnston 2016).
 
-The fourth dataset provides controls for the panel model.
+The fourth data set provides controls for the panel model.
 In their 2012 work examining variation in prosecutorial resources, Alt and Lassen follow Glaeser and Saks (2006) in controlling for income and education levels, size of government, legislature control, and urbanization.
-Alt and Lassen's dataset runs from 1976-2004.
+Alt and Lassen's data set runs from 1976-2004.
 When included in the second and third models, this limits the analysis to the years from 1990-2004.
 
-This analysis has its limitations, beginning with the datasets themselves.
+This analysis has its limitations, beginning with the data sets themselves.
 Barber’s state campaign contributions data lacks information about upper houses of state legislatures, which are included in both the CCI and CRI.
@@
 Similar to federal prosecutors’ offices, the resources available to each AP office vary.
-It also demonstrates high variation in the data; Utah, for example, has a mean CRI score of 0.46 and standard deviation of 0.38, in a dataset with an overall mean of 0.28 and standard deviation of 0.19.
+It also demonstrates high variation in the data; Utah, for example, has a mean CRI score of 0.46 and standard deviation of 0.38, in a data set with an overall mean of 0.28 and standard deviation of 0.19.
 The Corruption Reflections Index also seems to assume in its name that media reports of corruption are a mere reflection of corruption, rather than an endogenous variable in the ecosystem that enables corrupt behavior.
@@
 Most broadly, this analysis does not directly address the “appearance of corruption,” the second of the Supreme Court’s reasons for allowing campaign contribution limits; to do so effectively would require time series, state-level data specifically about quid pro quo corruption.
-It is also the case that this analysis looks to the states intentionally in order to address the issue of the counterfactual inherent in looking at federal data, it may not be the case that statewide results are generalizable to, or distinct from, what is occurring at the federal level.
-Finally, the period in question (1990-2004) is short enough that there may be some factor that influences corruption arrest across a meaningful portion of the dataset.
+It is also the case that this analysis looks to the states intentionally in order to address the issue of the counter-factual inherent in looking at federal data, it may not be the case that statewide results are generalizable to, or distinct from, what is occurring at the federal level.
+Finally, the period in question (1990-2004) is short enough that there may be some factor that influences corruption arrest across a meaningful portion of the data set.
 
@@
 ### Model I: Panel Regression
-Having constructed a full 1990-2012 panel dataset from these three datasets, I then run a set of time series regressions testing the relationship between contribution limits and both dependent variables, the Corruption Convictions Index and the Corruption Reflections Index.
+Having constructed a full 1990-2012 panel data set from these three data sets, I then run a set of time series regressions testing the relationship between contribution limits and both dependent variables, the Corruption Convictions Index and the Corruption Reflections Index.
 
@@
 If the model above fails to show an initial correlation, this may be due to the confounding effect of absent variables.
-In order to test that, I build a model of political corruption using control variables previously demonstrated to be correlated with corruption arrests, resulting in a dataset covering 1990-2004, the period of overlap amogn the datasets listed above.
+In order to test that, I build a model of political corruption using control variables previously demonstrated to be correlated with corruption arrests, resulting in a data set covering 1990-2004, the period of overlap among the data sets listed above.
 These include controlling for the size and education levels of the population, the ideology of a population, income levels and inequality, education levels, the number and relative income of government employees, and urbanization.
@@
 The final set of models (Table 4) displays results from multiple difference-in-difference models designed to isolate the effect of changes in campaign finance laws on corruption arrests.
-None of the models find correlation between campagin finance limits and either corruption convictions or corruption reflections.
+None of the models find correlation between campaign finance limits and either corruption convictions or corruption reflections.
 
@@
 How could this be, given that (a) the presence of individual-to-party limits has no association with a change the Corruption Convictions Index; (b) none of the other contribution limits are associated with a change in the Corruption Reflections Index; and (c) there is no correlation between the dollar amount of the individual-to-party limit and the Corruption Reflections Index?
-In practice, this would mean that states with individual-to-party limits also see lower levels of Associated Press reporting on corruption, but that once limits of any kind are imposed, the level of limit doesn’t matter.
+In practice, this would mean that states with individual-to-party limits also see lower levels of Associated Press reporting on corruption, but that once limits of any kind are imposed, the level of limit does not matter.
 It would also mean that only individual-to-party limits matter, not individual-to-candidate or PAC-to-candidate limits.
@@
 The Supreme Court presently equates political donations with political speech, meaning that it is protected by the first amendment, but that preventing corruption or its appearance in the political system is so important that first amendment rights can be abridged to ensure it.
-No other justification--including creating a more informed electorate, or stimulating more competitive elections, or equiality of financial participation in elections--is an important enough concern that we should limit political speech in the form of campaign donations.
+No other justification--including creating a more informed electorate, or stimulating more competitive elections, or equality of financial participation in elections--is an important enough concern that we should limit political speech in the form of campaign donations.
 If there is no link between campaign contribution limits and corruption,  the Court may conclude that there is no reason to abridge US citizens’ first amendment rights by limiting campaign donations.

### 2018-10-17 Paper.Rmd
A couple of notes based on Lentz's suggestions

@@
 AltBarber <- inner_join(BarberICC, AltLassen)
+```
+
+```{r panel effects mmodeling, eval=T}
+# Maybe helpful https://onlinecourses.science.psu.edu/stat502/node/162/
+# Erin's suggestion https://www.princeton.edu/~otorres/Panel101R.pdf 
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC))
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways"))
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="within"))
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="random")) #FAIL 
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC), model="pooling")
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC), model="within")
 ```

### 2018-10-18 Paper.Rmd
More testing with Erin's suggestions

--- 2018-07-02 Paper.Rmd
@@
 AltBarber <- inner_join(BarberICC, AltLassen)
+```
+
+```{r panel effects mmodeling, eval=T}
+# Maybe helpful https://onlinecourses.science.psu.edu/stat502/node/162/
+# Erin's suggestion https://www.princeton.edu/~otorres/Panel101R.pdf 
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC))
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways"))
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="within", effect="twoways"))
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="within"))
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="random")) #FAIL 
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC), model="pooling")
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC), model="within")
 ```

### 2018-11-27 Paper.Rmd
stuff

--- 2018-07-02 Paper.Rmd
@@
 ```{r setup, include=FALSE}
+# This is all necessary setup stuff, including packages and for Markdown
 knitr::opts_chunk$set(echo = FALSE, eval=FALSE, cache = TRUE, message=FALSE, warning=FALSE)
@@
 AltBarber <- inner_join(BarberICC, AltLassen)
+```
+
+```{r panel effects modeling, eval=F}
+# Maybe helpful? https://onlinecourses.science.psu.edu/stat502/node/162/
+# Erin's suggestion https://www.princeton.edu/~otorres/Panel101R.pdf
+# On robust standard errors https://stats.stackexchange.com/questions/117052/replicating-statas-robust-option-in-r
+# And https://cran.r-project.org/web/packages/sandwich/vignettes/sandwich.pdf
+# And https://www.brodrigues.co/blog/2018-07-08-rob_stderr/, 
+# Pretty good explanation here https://www.methodsconsultants.com/tutorial/introduction-to-random-effects-models-including-hlm/
+# Go through this? https://github.com/tyleransom/EconometricsLabs/blob/master/tidyRcheatsheet.pdf
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC))
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways"))
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="within", effect="twoways"))
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="within"))
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="random")) #FAIL 
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC), model="pooling")
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC), model="within")
 ```
@@
 I combine these measures with a third data set from Michael Barber’s 2016 work on campaign contribution limits and political polarization; and a fourth data set from James Alt and David Dryer Lassen, to provide controls for the full model (Alt and Lassen 2012).
+
 Barber’s data set is a panel of contribution limits from 1990-2012 for the lower house of every state legislature.
@@
 
-If the model above fails to show an initial correlation, this may be due to the confounding effect of absent variables.
+As demonstrated below, this model fails to uncover any initial correlation between changes in campaign finance law and CCI or CRI scores.
+This may be due to the confounding effect of absent variables.
 In order to test that, I build a model of political corruption using control variables previously demonstrated to be correlated with corruption arrests, resulting in a data set covering 1990-2004, the period of overlap among the data sets listed above.
@@
 <!--Add specification, formulas?-->
-Even if the panel models above fail to capture correlation between state level campaign finance laws and corruption arrests, it could be the case that changes in campaign finance laws, rather than relative campaign finance limits, could be correlated with decreases in corruption.
+Even if the panel models above fail to capture correlation between state level campaign finance laws and corruption arrests, it could be the case that changes in campaign finance laws, rather than relative campaign finance limits, are correlated with decreases in corruption.
 A difference-in-difference regression can help identify this by comparing the state-years in which campaign finance laws changed to state-years where they remained constant.
@@
 The second set of models (Table II) also fails to find a relationship between state-level campaign contribution limits and media mentions of corruption as measured by the Corruption Reflections Index, with one exception: The presence of limits on what an individual can give to a party is associated with a 0.10 point decline in the Corruption Reflection Index.
-The Corruption Reflections Index operates on a scale of zero to one (with a few outlying exceptions), meaning that the presence of individual-to-party limits is associated with a 10% decrease in the index.
+The Corruption Reflections Index operates on a scale of zero to one (with a few outlying exceptions), indicating that the presence of individual-to-party limits is associated with a 10% decrease in the index.
 

### 2018-12-03 Paper.Rmd
blarg
Adding in Lentz's suggestions; Highlighting next changes.

@@
 Since the 1970s, the U.S.
-Supreme Court has frustrated efforts at campaign finance reform by maintaining that nearly all limits on political spending violate the first amendment’s protection of free speech.
+Supreme Court has maintained that nearly all limits on political spending violate the first amendment’s protection of free speech.
 In its 1976 _Buckley v.
-Valeo_ decision, the Court laid out only two justifications for limiting political speech in the form of campaign donations: To prevent corruption or the appearance of corruption.
+Valeo_ decision, the Court laid out only two admissible justifications for limiting campaign donations: To prevent corruption or the appearance of corruption.
 But do campaign finance limits actually prevent corruption or its appearance?
-Using state-level data from 1990-2012 on contribution limits, corruption arrests, and media mentions of corruption, this paper employs a linear panel regression and a difference-in-differences analysis to test whether campaign contribution limits are associated with lower levels of corruption convictions or media mentions of corruption.
+As current challenges to contribution limits wind their way through federal courts, the answer to this question will inform the Supreme Court’s decision to uphold or strike down remaining limits on political campaign contributions.
+Using state-level data from 1990-2012 on contribution limits, corruption arrests, and media mentions of corruption, this paper employs linear panel regression and difference-in-differences analyses to test whether campaign contribution limits are associated with lower levels of corruption convictions or media mentions of corruption.
 These methods find no relationship between the presence or level of campaign finance laws and quid pro quo corruption.
-As current challenges to contribution limits wind their way through federal courts, the answer to this question will inform the Supreme Court’s decision to uphold or strike down remaining limits on political campaign contributions.
 
@@
 
-```{r panel effects modeling, eval=F}
-# Maybe helpful? https://onlinecourses.science.psu.edu/stat502/node/162/
-# Erin's suggestion https://www.princeton.edu/~otorres/Panel101R.pdf
-# On robust standard errors https://stats.stackexchange.com/questions/117052/replicating-statas-robust-option-in-r
-# And https://cran.r-project.org/web/packages/sandwich/vignettes/sandwich.pdf
-# And https://www.brodrigues.co/blog/2018-07-08-rob_stderr/, 
-# Pretty good explanation here https://www.methodsconsultants.com/tutorial/introduction-to-random-effects-models-including-hlm/
-# Go through this? https://github.com/tyleransom/EconometricsLabs/blob/master/tidyRcheatsheet.pdf
-summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC))
-summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways"))
-summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="within", effect="twoways"))
-summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="within"))
-summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="random")) #FAIL 
-summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC), model="pooling")
-summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC), model="within")
-```
-
 ```{r panel modeling, eval=T}
@@
 CRIreg5 <- plm(CRI ~ ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = BarberICC, index = c("st","year"), effect="twoways")
+```
+
+```{r post-Lentz panel effects modeling, eval=F}
+# Maybe helpful? https://onlinecourses.science.psu.edu/stat502/node/162/
+# Erin's suggestion https://www.princeton.edu/~otorres/Panel101R.pdf
+# On robust standard errors https://stats.stackexchange.com/questions/117052/replicating-statas-robust-option-in-r
+# And https://cran.r-project.org/web/packages/sandwich/vignettes/sandwich.pdf
+# And https://www.brodrigues.co/blog/2018-07-08-rob_stderr/, 
+# Pretty good explanation here https://www.methodsconsultants.com/tutorial/introduction-to-random-effects-models-including-hlm/
+# Go through this? https://github.com/tyleransom/EconometricsLabs/blob/master/tidyRcheatsheet.pdf
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC))
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways"))
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="within", effect="twoways"))
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="within"))
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="random")) #FAIL 
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC), model="pooling")
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC), model="within")
+
+#From Erin: 
+# •	Based on the results in Table 3, it appears that neither fixed effects or random effects were included in the panel estimation results.
+If that is correct, I’d argue including one of them could materially change the results.
+# o	I’m not sure which would be better: state fixed effects would limit the interpretation of results to effects within states, as opposed to across states but fixed effects are not a good idea when the error terms of each state are correlated (use a Hausman to check).
+Random effects assume no omitted variables, which can be a strong assumption.
+# o	This might be a useful resource: https://www.princeton.edu/~otorres/Panel101.pdf
+# o	Explain your treatment of standard errors (e.g., are you using robust se?).
+
 ```
@@
 
+```{r post-Lentz DID effects modeling, eval=F}
+# From Erin: 
+# •	Again, writing out a model for the D-in-D in Table 4 might help readers to understand what is being isolated. Right now, I’m not sure I fully follow the estimation choices.
+# o	At a minimum, the state-level control variables changed during this time (and hence wouldn’t get differenced out), and ought to be included.
+# o	Column 1 (and 2): the large standard errors on individual limits removed and imposed suggest multicollinearity and needs to be investigated. 
+```
+
 \newpage 
@@
 
-Apart from McCain-Feingold, for forty years all changes in the landscape of campaign finance have come from the courts, which have worked to balance questions of corruption with those of free speech.
+Apart from McCain-Feingold, for forty years all changes in the landscape of campaign finance have come from the Supreme Court and appellate courts, which have worked to balance questions of corruption with those of free speech.
 In 1981, the Court struck down contribution limits related to ballot measures (_Citizens against Rent Control v.
@@
 In 1986, it  and struck down efforts to restrict their expenditures to FEC-registered Political Action Committees (FEC v. Massachusetts Right to Life). 
-
 -->
@@
 ##Prior Work 
-<!--Add in more references--> 
 Since the Buckley v.
@@
 
-##Design and Data 
-<!--Add in summary statistics?-->
+##Data and Design  
 In this paper, I build upon the growing body of state-level political science research to ask whether campaign contribution limits at the state level associated with lower levels of corruption.
@@
 
+<!--Add in summary statistics here-->
+
 The second data set comes from the Department of Justice’s “Report to Congress on the Activities and Operations of the Public Integrity Section” by way of the Institute for Corruption Studies.[^Koch]  Since 1976, the FBI has tracked political corruption at the state level, and the Corruption Convictions Index (CCI) used here includes the number of corruption convictions in a year normalized by the population in each state.
@@
 
+<!--Add in summary statistics here-->
+<!--Test whether these are correlated?-->
+
 The fourth data set provides controls for the panel model.
@@
 When included in the second and third models, this limits the analysis to the years from 1990-2004.
+
+<!--Describe controls here, then add a table with summary statistics for everything-->
 
@@
 It is also the case that this analysis looks to the states intentionally in order to address the issue of the counter-factual inherent in looking at federal data, it may not be the case that statewide results are generalizable to, or distinct from, what is occurring at the federal level.
+Third, it is also the case that campaign finance laws may not be equally enforced across states, even though the enforcement measures used here are from federal rather than state authorities.
 Finally, the period in question (1990-2004) is short enough that there may be some factor that influences corruption arrest across a meaningful portion of the data set.
@@
 
-<!--
-Corruption Convictions Index versus campaign contribution limits in a given state-year:
+<!--Edit specifications--> 
+####Corruption Convictions Index versus campaign contribution limits in a given state-year:
 
@@
 
-Corruption Reflections Index versus campaign contributions in a given state-year:
+####Corruption Reflections Index versus campaign contributions in a given state-year:
 
 $Reflections = \alpha + \beta_{indiv.dummy} + \beta_{indiv.dummy}*\beta_{indiv.limit} + \beta_{pac.dummy} + \beta_{pac.dummy}*\beta_{pac.limit} + \beta_{indiv-to-party.dummy} + \beta_{indiv-to-party.dummy}*\beta_{indiv-to-party.limit} + \epsilon$
--->
 
@@
 If tighter campaign finance laws are correlated with lower corruption levels, then a change in one year should lead to lower corruption convictions in the years following.
+
+<!--add something to show what change occurred-->
 
@@
 The Supreme Court presently equates political donations with political speech, meaning that it is protected by the first amendment, but that preventing corruption or its appearance in the political system is so important that first amendment rights can be abridged to ensure it.
-No other justification--including creating a more informed electorate, or stimulating more competitive elections, or equality of financial participation in elections--is an important enough concern that we should limit political speech in the form of campaign donations.
+For the Court, no other justification--including creating a more informed electorate, or stimulating more competitive elections, or equality of financial participation in elections--is an important enough concern that we should limit political speech in the form of campaign donations.
 If there is no link between campaign contribution limits and corruption,  the Court may conclude that there is no reason to abridge US citizens’ first amendment rights by limiting campaign donations.
@@
 FEC_ suggest that commitment to the Buckley v.
-Valeo structure is weakening, and not in the way that liberal reformers might hope.
+Valeo structure is weakening, and not in the way that campaign finance reformers might hope.
 Despite effort, scholars have failed to provide compelling evidence of a link between campaign contribution limits and corruption as defined by the Court.

### 2018-12-11 Paper 2019.Rmd
Should probably have started a new paper here. Nuts.

--- 2018-12-03 Paper.Rmd
@@
 title: | 
+  | UNDER CONSTRUCTION 
   | Campaign Contribution Limits and Corruption: 
@@
 library(knitr) # Because Matt Worthington said so 
-
+library(summarytools) # For summary statistics 
 ```
@@
 
-<!--Add in summary statistics here-->
+<!--Add in summary statistics here. 
+Plot of something over time?
+Histograms?
+-->
+```{r Barber summary, eval=TRUE}
+descr(Barber)
+# Barber histograms 
+ind_limits_2010.plot <- ggplot(Barber, aes(ind_limits_2010)) + geom_density() + theme_minimal()
+ind_limits_2010.plot
+ind2pty_limits_2010.plot <- ggplot(Barber, aes(ind2pty_limits_2010)) + geom_density() + theme_minimal()
+ind_limits_2010.plot
+pac_limits_2010.plot <- ggplot(Barber, aes(pac_limits_2010)) + geom_density() + theme_minimal()
+```
 
@@
 
+```{r CCI summary, eval=TRUE}
+descr(convictions)
+# Barber histograms 
+convictions.plot <- ggplot(convictions, aes(CCI)) + geom_density() + theme_minimal()
+convictions.plot
+```
+
 The third data set is the Institute for Corruption Studies’ Corruption Reflections Index (CRI), put together by Dincer and Johnston for their 2016 article on state-level corruption, and which they create in response to the limitations of the Corruption Convictions.
@@
 
-<!--Add in summary statistics here-->
+```{r CRI summary, eval=TRUE}
+descr(reflections)
+# Barber histograms 
+reflections.plot <- ggplot(reflections, aes(CRI)) + geom_density() + theme_minimal()
+reflections.plot
+```
+
 <!--Test whether these are correlated?-->

### 2018-12-13 Paper 2019.Rmd
Adding notes from conversation with Erin

@@
 
+\newpage 
+##Introduction
+In 1976, the Supreme Court ruled in _Buckley v.
+Valeo_ that political campaign contributions are the equivalent of free speech, and therefore protected by the first amendment.
+At the same time, the Court laid out one mechanism and two permissible reasons for limiting those contributions.
+First, it argued that more money spent does not amount of “more” speech, allowing for the use of campaign contribution dollar amount limits.
+Donating one dollar or $5,000 to a political campaign amounts to a speech act, the Court held, and so it is permissible to impose limits on the amount of contributions as long as contributions are not prevented.
+Second, having laid out this mechanism by which money in politics might be limited, the court laid out only two constitutionally permissible reasons for limiting contributions: To prevent corruption or the appearance thereof.
+As Kang (2012) argues, the holdings in _Buckley v.
+Valeo_ provided “the basic framework of contribution limits and disclosure requirements” for the following four decades.
+Since _Buckley v.
+Valeo_, Congress has passed only one campaign finance law, the Bipartisan Campaign Reform Act of 2002.
+Better know as McCain-Feingold, the bill took aim at unlimited “soft money” contributions to political parties and expanded the Federal Election Commission’s disclosure requirements to what it called “electioneering communications,” political ads not paid for by campaigns themselves.
+
+Apart from McCain-Feingold, for forty years all changes in the landscape of campaign finance have come from the Supreme Court and appellate courts, which have worked to balance questions of corruption with those of free speech.
+In 1981, the Court struck down contribution limits related to ballot measures (_Citizens against Rent Control v.
+City of Berkeley-).
+Just before the passage of McCain-Feingold, the courts considered state-level limits, allowing low limits in Missouri (_Nixon v.
+Shrink Missouri_, 2000), though it would later finding Vermont's to be low enough that they had a meaningful impact on political speech (_Randall v.
+Sorrell_, 2006).
+
+<!--Those rulings have often been driven by the question of corporations’ participation in the political process.
+In 1978, the Court extended free speech protections to corporations (First National Bank of Boston v.
+Bellotti).
+
+Then in 1990, it upheld a ban on corporations using treasury funds to pay for issue advertisements, arguing for an extended definition of corruption, "the corrosive and distorting effects of immense aggregations of wealth that are accumulated with the help of the corporate form and that have little or no correlation to the public's support for the corporation's political ideas" (Austin v.
+Michigan State Chamber of Commerce, later overturned).
+
+In 1986, it  and struck down efforts to restrict their expenditures to FEC-registered Political Action Committees (FEC v. Massachusetts Right to Life). 
+-->
+The passage of the McCain-Feingold in 2002 inspired a wave of challenges to campaign contributions and expenditures, driven mostly by conservative and religious political groups.
+In 2007, the Court examined the McCain-Feingold ban on airing issue advertisements close to election.
+Banning such ads, the Court argued, would have a chilling effect on free speech, and it struck down the ban (_FEC v.
+Wisconsin Right to Life_).
+Then, in 2010, the Court issued what has become one of its most well-known rulings: In _Citizens United v.
+FEC_ (2010), it struck down limits on independent expenditures by outside groups, including corporations and unions.
+One critical aspect of _Citizens United_ is the establishment of the principle that, according to Justice Anthony Kennedy, “independent expenditures do not lead to, or create the appearance of, quid pro quo corruption.” The Court’s emphasis on quid pro quo corruption as the only justification for contribution limits extended the following year, as it struck down an Arizona effort to level the political playing field with matching state campaign funds (_Arizona Free Enterprise Club v.
+Bennett_, 2011).
+
+Since 2011, the network of conservative legal groups behind Citizens United has continued to take aim at contribution limits as an unnecessary restriction of political speech, with a focus on individual contribution limits.
+The 1971 Federal Election Campaign Act placed a limit on the amount an individual could give to one campaign, in addition to two-year limits on the total amount an individual could give to political campaigns.
+In _McCutcheon v.
+FEC_ (2014) James Bopp, one of the attorneys behind the Citizens United challenge, convinced the Court of the unconstitutionality of total individual limits.
+Another case, _Holmes v.
+FEC_ (2017), targeted the distribution of individual campaign contribution across primary and general elections.
+In yet another, _Lair v.
+Motl_ (2017), Bopp once again took aim at individual contribution limits, arguing that the state of Montana had not shown compelling evidence that campaign contribution limits decreased the risk of corruption.
+
+The Ninth Circuit Court of Appeals upheld Montana’s campaign contribution limits, and the Fifth Circuit similarly upheld limits in Austin, TX (_Zimmerman v.
+City of Austin_, 2018).
+But further challenges to contribution limits are likely.
+Bopp said that he planned to appeal the Ninth Circuit’s ruling.
+Even if that fails, Bopp and other conservative groups plan to carry on.
+“I handle a lot of cases,” he said after the 2014 McCutcheon ruling, “and I‘m not done yet.” Supreme Court Justice Clarence Thomas laid the groundwork for future challenges in his commentary on the McCutcheon decision by arguing that more dollars did, in fact, equate to more speech.
+Once established, that principle supports the argument that campaign contribution dollar amount limits are a potentially unconstitutional restriction on speech (Hurley & Debenedetti 2014, Zall 2017).
+
+##Prior Work 
+Since the Buckley v.
+Valeo decision, a wave of scholarship has taken advantage of the campaign contribution data collected by the Federal Election Commission to examine the causes and consequences of political campaign contributions, including whether contributions buy access (not to a meaningful degree, find Welch 1982 and Langbein 1986) and the effectiveness of contributions relative to lobbying efforts (yes, according to Wright 1990).
+Since the 2010 Citizens United and speechnow.org decisions, another arm of scholarship has examined the flows of money to groups engaging in independent expenditures (Spencer and Wood 2014, Werner and Coleman 2014).
+
+But lobbying, money for access, and independent expenditures all fall outside of the narrow definition of quid pro corruption that the Supreme Court considers a compelling enough state interest to justify campaign contribution limits.
+The scholarly research on corruption thus narrowly defined is mixed and heated.
+Stratmann finds evidence that donations determined votes in at least one instance (1991); he also finds that the timing of political action committees (PAC) donations suggests that corporations believe those donations do affect legislators’ votes (1998).
+Reacting to the absence of evidence that donations lead to favorable final votes on bills, Hall and Wayman (1990) look for and find a positive relationship between political donations and the amount of attention that legislators give to a particular issue.
+Other scholars, however, are not so convinced.
+Wright finds that once lobbying efforts are factored in, the effects of contributions on voting outcomes washes out (1990).
+And it is notoriously difficult to tease out whether political donations change legislators’ minds or instead flow to legislators with established, friendly positions (Ansolabehere et al 2003).
+
+As mentioned above, the Court is also interested in the appearance of corruption.
+On this score, results are more consonant: There seems to be little association between campaign spending and public trust in government (Primo 2002).
+Other factors, including media coverage of campaign finance law and the professionalization of legislatures, are more predictive of public perceptions of corruptions (Rosenson 2009).
+And while the public does seem to report viewing campaign finance as a contributor to corruption, there is not evidence that reform efforts will have an effect on those views (Persily & Lammie 2004).
+
+One fundamental limitation of these federal level studies on campaign contributions and corruption is the absence of a counter-factual.
+Given that contribution limits have been in place since the 1970s, it is difficult to argue what might have happened in their absence.
+Recent work on campaign finance has attempted to address this problem by focusing on the effects of differences in campaign finance laws at the state level.
+Variation across states and over time allows room for studying the causes and consequences of campaign finance limits, separate from the question of corruption.
+Studies suggest that campaign finance limits are associated with less electoral competition (Gross et al 2002, Lott 2006), but that disclosure rules and some organizational limits are associated with greater levels of government trust (Primo and Milyo 2006) and may increase the return on campaign expenditures (Stratmann 2006).
+As mentioned, Michael Barber’s 2016 work finds that lower limits on PAC donations relative to individual donations are associated with higher polarization.
+
+A largely separate body of work has examined the causes and consequences of corruption at the state level, separate from campaign finance.
+Most use the Department of Justice’s Annual Public Integrity Report, which correlate highly with state level perceptions of corruption (Walker and Calcagno 2011, Glaeser and Saks 2006, Liu & Mikesell 2014).
+Using that data, researchers have found evidence that political corruption leads to inflated state budgets and that the presence of casinos and subsequent corruption (Liu & Mikesell 2014, Walker & Calcagno 2013).
+They have also shown the absence of a link between state ethics commissions and reduced corruption (Crider and Milyo 2013).
+
+In response to criticisms of corruption convictions as a proper measure of corruption, researchers have also developed alternative measures of state level corruption.
+Boylan and Long make use of surveys of state reporters (2003).
+Cordis and Milyo deploy the recently available Transactional Records Access Clearinghouse (TRAC) database of political corruption (2016).
+Dincer and Jonhston introduce a Corruption Reflections Index, which tracks mentions of corruption in Associated Press reports (2016).
+
+A smaller number of scholars have begun connecting these bodies of work to examine the impact of state-level campaign finance regulations on measures of quid pro quo corruption--one of only two questions of import to the Supreme Court as it considers the constitutionality of contribution limits.
+The exception to this is a 2013 working paper by Cordis and Milyo.
+In line with Persily and Lammie (2004), Milyo argues that campaign reform efforts have little effect on public perceptions of corruption.
+This paper seeks to address this gap, putting state level campaign finance data in direct conversation with state level corruption data.
+
+##Data and Design  
+In this paper, I build upon the growing body of state-level political science research to ask whether campaign contribution limits at the state level associated with lower levels of corruption.
+Given open debate about the proper measure of state-level corruption, I use two measures.
+The first, a Corruptions Convictions Index, is the traditional measure of state level corruption, built from Department of Justice convictions data.
+The second, the Corruptions Reflection Index, is a new measure put forward by Dincer and Johnston (2016).
+I combine these measures with a third data set from Michael Barber’s 2016 work on campaign contribution limits and political polarization; and a fourth data set from James Alt and David Dryer Lassen, to provide controls for the full model (Alt and Lassen 2012).
+
+Barber’s data set is a panel of contribution limits from 1990-2012 for the lower house of every state legislature.
+Barber compiled this data set from the FEC, Westlaw, and the Nation Council of State Legislatures.
+Each dollar amount is inflation indexed to 2010 dollar amounts, and bi-annualized.
+There are three different types of limits in the Barber database: Individual contribution limits, individual-to-party limits, and PAC limits.
+Barber utilized individual and PAC contributions in his analysis of polarization, leaving out individual-to-party limits given that party contributions typically make up less than 10% of total political fundraising; I include it this analysis to determine whether parties, rather than PACs or individuals, might be the locus of corruption as measured by our other two data sets (Barber 2016).
+
+<!--Add in summary statistics here. 
+Plot of something over time? Histograms? Correlations? 
+-->
+```{r Barber summary, eval=TRUE}
+descr(Barber)
+# Barber histograms 
+ind_limits_2010.plot <- ggplot(Barber, aes(ind_limits_2010)) + geom_density() + theme_minimal()
+ind_limits_2010.plot
+ind2pty_limits_2010.plot <- ggplot(Barber, aes(ind2pty_limits_2010)) + geom_density() + theme_minimal()
+ind_limits_2010.plot
+pac_limits_2010.plot <- ggplot(Barber, aes(pac_limits_2010)) + geom_density() + theme_minimal()
+
+# Correlation matrix? 
+pairs(Barber[3:7])
+# Doesn't make sense, because of use of 99,999s. 
+```
+
+The second data set comes from the Department of Justice’s “Report to Congress on the Activities and Operations of the Public Integrity Section” by way of the Institute for Corruption Studies.[^Koch]  Since 1976, the FBI has tracked political corruption at the state level, and the Corruption Convictions Index (CCI) used here includes the number of corruption convictions in a year normalized by the population in each state.
+This measure of corruption is widely used in academic research, though not without criticism.
+
+<!--clean these up-->
+
+```{r CCI summary, eval=TRUE}
+descr(convictions)
+# Barber histograms 
+convictions.plot <- ggplot(convictions, aes(CCI)) + geom_density() + theme_minimal()
+convictions.plot
+```
+
+The third data set is the Institute for Corruption Studies’ Corruption Reflections Index (CRI), put together by Dincer and Johnston for their 2016 article on state-level corruption, and which they create in response to the limitations of the Corruption Convictions.
+The Corruption Reflections Index represents the fraction of Associated Press stories about politics in a particular state that mention political corruption (Dincer and Johnston 2016).
+
+<!--clean these up-->
+
+```{r CRI summary, eval=TRUE}
+descr(reflections)
+# Barber histograms 
+reflections.plot <- ggplot(reflections, aes(CRI)) + geom_density() + theme_minimal()
+reflections.plot
+```
+
+<!--Test whether these are correlated?-->
+
+```{r CCI and CRI correlations }
+ggplot(BarberICC, aes(CCI,CRI)) + geom_point() + theme_minimal() + geom_abline()
+```
+
+The fourth data set provides controls for the panel model.
+In their 2012 work examining variation in prosecutorial resources, Alt and Lassen follow Glaeser and Saks (2006) in controlling for income and education levels, size of government, legislature control, and urbanization (see Appendix A).
+Alt and Lassen's data set runs from 1976-2004.
+When included in the second and third models, this limits the analysis to the years from 1990-2004.
+
+This analysis has its limitations, beginning with the data sets themselves.
+Barber’s state campaign contributions data lacks information about upper houses of state legislatures, which are included in both the CCI and CRI.
+The Corruption Convictions Index suffers from a number of issues, as outlined by Dincer and Johnston in their introduction to the Corruption Reflections Index.
+They argue that the CCI includes only federal data; that the resources available to prosecutors varies from state to state; that US Attorneys are political appointees; and that the measure records only convictions, which is at best a reflection of underlying corruption.
+
+The Corruption Reflections Index, too, has its flaws: It relies on a single news source, the Associated Press.
+Similar to federal prosecutors’ offices, the resources available to each AP office vary.
+It also demonstrates high variation in the data; Utah, for example, has a mean CRI score of 0.46 and standard deviation of 0.38, in a data set with an overall mean of 0.28 and standard deviation of 0.19.
+The Corruption Reflections Index also seems to assume in its name that media reports of corruption are a mere reflection of corruption, rather than an endogenous variable in the ecosystem that enables corrupt behavior.
+Previous work, in contrast, has argued that media have a clear bias and play an important role in shaping public perceptions of corruption, rather than just reflecting it (Sorauf 1987; Ansolabehere, Snowberg and Snyder 2005).
+
+Most broadly, this analysis does not directly address the “appearance of corruption,” the second of the Supreme Court’s reasons for allowing campaign contribution limits; to do so effectively would require time series, state-level data specifically about quid pro quo corruption.
+It is also the case that this analysis looks to the states intentionally in order to address the issue of the counter-factual inherent in looking at federal data, it may not be the case that statewide results are generalizable to, or distinct from, what is occurring at the federal level.
+Third, it is also the case that campaign finance laws may not be equally enforced across states, even though the enforcement measures used here are from federal rather than state authorities.
+Finally, the period in question (1990-2004) is short enough that there may be some factor that influences corruption arrest across a meaningful portion of the data set.
+
+[^Koch]: N.B.
+According to one of the researchers’ [curricula vitae](https://about.illinoisstate.edu/odincer/Documents/CVDincerApril2016.docx), the Institute for Corruption Studies is funded in part by a grant from the Charles Koch Research Foundation.
+Organizations funded by Charles and David Koch are also funders of legal groups driving legal battles mentioned in the introduction, according to a [report](https://www.publicintegrity.org/2017/11/15/21279/kochs-key-among-small-group-quietly-funding-legal-assault-campaign-finance) by the Center for Public Integrity.
+
+##Methods
+### Model I: Panel Regression
+Having constructed a full 1990-2012 panel data set from these three data sets, I then run a set of time series regressions testing the relationship between contribution limits and both dependent variables, the Corruption Convictions Index and the Corruption Reflections Index.
+
+I include three predictor variables in both sets of models: Individual contribution limits, individual-to-party contribution limits, and PAC contribution limits.
+For each of these independent variables, I construct two variables to use in the model.
+The first is a dummy variable indicating whether there are contribution limits in that state in that year, coded as “0” if there are no limits and “1” if there are.
+The second is a continuous variable indicating the dollar amount of the limit in the state in that year.
+By interacting these two variables, I test two separate associations.
+The dummy variable tests whether there is a difference in the CCI and CRI in states with limits versus states without limits.
+The continuous variable tests whether higher or lower limits are associated with higher or lower CCI and CRI scores, within the group of states that have limits in a given year.
+After performing this transformation on all three independent variables, I test two initial sets of models: (1) Corruption Convictions Index versus campaign contribution limits in a given state-year, and (2) Corruption Reflections Index versus campaign contributions in a given state-year.
+
+<!--Edit specifications--> 
+####Corruption Convictions Index versus campaign contribution limits in a given state-year:
+
+$Convictions = \alpha + \beta_{indiv.dummy} + \beta_{indiv.dummy}*\beta_{indiv.limit} + \beta_{pac.dummy} + \beta_{pac.dummy}*\beta_{pac.limit} + \beta_{indiv-to-party.dummy} + \beta_{indiv-to-party.dummy}*\beta_{indiv-to-party.limit} + \epsilon$
+
+####Corruption Reflections Index versus campaign contributions in a given state-year:
+
+$Reflections = \alpha + \beta_{indiv.dummy} + \beta_{indiv.dummy}*\beta_{indiv.limit} + \beta_{pac.dummy} + \beta_{pac.dummy}*\beta_{pac.limit} + \beta_{indiv-to-party.dummy} + \beta_{indiv-to-party.dummy}*\beta_{indiv-to-party.limit} + \epsilon$
+
+As demonstrated below, this model fails to uncover any initial correlation between changes in campaign finance law and CCI or CRI scores.
+This may be due to the confounding effect of absent variables.
+In order to test that, I build a model of political corruption using control variables previously demonstrated to be correlated with corruption arrests, resulting in a data set covering 1990-2004, the period of overlap among the data sets listed above.
+These include controlling for the size and education levels of the population, the ideology of a population, income levels and inequality, education levels, the number and relative income of government employees, and urbanization.
+Building a model of corruption that includes variables previously demonstrated to be correlated with corruption levels, then adding in campaign finance data, can better identify the association of campaign finance laws with corruption levels.
+
 ```{r panel modeling, eval=T}
@@
 ```{r post-Lentz panel effects modeling, eval=F}
+# Include lagged dependent variables here. 
+# Erin's question: Are these "pooled"? 
+# Her effort to understand: Write out the formulas. 
 # Maybe helpful? https://onlinecourses.science.psu.edu/stat502/node/162/
@@
 
+### Model II: Difference-in-Difference Model
+<!--Add specification, formulas?-->
+Even if the panel models above fail to capture correlation between state level campaign finance laws and corruption arrests, it could be the case that changes in campaign finance laws, rather than relative campaign finance limits, are correlated with decreases in corruption.
+A difference-in-difference regression can help identify this by comparing the state-years in which campaign finance laws changed to state-years where they remained constant.
+If tighter campaign finance laws are correlated with lower corruption levels, then a change in one year should lead to lower corruption convictions in the years following.
+
+<!--add something to show what change occurred-->
+
 ```{r DiD wrangling, eval=T}
@@
 CCIDID01 <- lm(CCI ~ ind_dummy_f*ind_d, data = DiDsmall)
+# Erin: What this doesn't have is an average treatment effect. So add the interaction of the dummy variable of the change having happened and the law occurring. Time dummy, maybe? 
 CCIDID02 <- lm(CCI ~ pac_dummy_f*pac_d, data = DiDsmall)
@@
 # o	Column 1 (and 2): the large standard errors on individual limits removed and imposed suggest multicollinearity and needs to be investigated. 
+# Are presence of campaign finance laws in a state year associated with a different level of corruption? No, according to that panel model. 
+# Consider adding state fixed effects to the DiD model, for robustness. 
 ```
-
-\newpage 
-##Introduction
-In 1976, the Supreme Court ruled in _Buckley v.
-Valeo_ that political campaign contributions are the equivalent of free speech, and therefore protected by the first amendment.
-At the same time, the Court laid out one mechanism and two permissible reasons for limiting those contributions.
-First, it argued that more money spent does not amount of “more” speech, allowing for the use of campaign contribution dollar amount limits.
-Donating one dollar or $5,000 to a political campaign amounts to a speech act, the Court held, and so it is permissible to impose limits on the amount of contributions as long as contributions are not prevented.
-Second, having laid out this mechanism by which money in politics might be limited, the court laid out only two constitutionally permissible reasons for limiting contributions: To prevent corruption or the appearance thereof.
-As Kang (2012) argues, the holdings in _Buckley v.
-Valeo_ provided “the basic framework of contribution limits and disclosure requirements” for the following four decades.
-Since _Buckley v.
-Valeo_, Congress has passed only one campaign finance law, the Bipartisan Campaign Reform Act of 2002.
-Better know as McCain-Feingold, the bill took aim at unlimited “soft money” contributions to political parties and expanded the Federal Election Commission’s disclosure requirements to what it called “electioneering communications,” political ads not paid for by campaigns themselves.
-
-Apart from McCain-Feingold, for forty years all changes in the landscape of campaign finance have come from the Supreme Court and appellate courts, which have worked to balance questions of corruption with those of free speech.
-In 1981, the Court struck down contribution limits related to ballot measures (_Citizens against Rent Control v.
-City of Berkeley-).
-Just before the passage of McCain-Feingold, the courts considered state-level limits, allowing low limits in Missouri (_Nixon v.
-Shrink Missouri_, 2000), though it would later finding Vermont's to be low enough that they had a meaningful impact on political speech (_Randall v.
-Sorrell_, 2006).
-
-<!--Those rulings have often been driven by the question of corporations’ participation in the political process.
-In 1978, the Court extended free speech protections to corporations (First National Bank of Boston v.
-Bellotti).
-
-Then in 1990, it upheld a ban on corporations using treasury funds to pay for issue advertisements, arguing for an extended definition of corruption, "the corrosive and distorting effects of immense aggregations of wealth that are accumulated with the help of the corporate form and that have little or no correlation to the public's support for the corporation's political ideas" (Austin v.
-Michigan State Chamber of Commerce, later overturned).
-
-In 1986, it  and struck down efforts to restrict their expenditures to FEC-registered Political Action Committees (FEC v. Massachusetts Right to Life). 
--->
-The passage of the McCain-Feingold in 2002 inspired a wave of challenges to campaign contributions and expenditures, driven mostly by conservative and religious political groups.
-In 2007, the Court examined the McCain-Feingold ban on airing issue advertisements close to election.
-Banning such ads, the Court argued, would have a chilling effect on free speech, and it struck down the ban (_FEC v.
-Wisconsin Right to Life_).
-Then, in 2010, the Court issued what has become one of its most well-known rulings: In _Citizens United v.
-FEC_ (2010), it struck down limits on independent expenditures by outside groups, including corporations and unions.
-One critical aspect of _Citizens United_ is the establishment of the principle that, according to Justice Anthony Kennedy, “independent expenditures do not lead to, or create the appearance of, quid pro quo corruption.” The Court’s emphasis on quid pro quo corruption as the only justification for contribution limits extended the following year, as it struck down an Arizona effort to level the political playing field with matching state campaign funds (_Arizona Free Enterprise Club v.
-Bennett_, 2011).
-
-Since 2011, the network of conservative legal groups behind Citizens United has continued to take aim at contribution limits as an unnecessary restriction of political speech, with a focus on individual contribution limits.
-The 1971 Federal Election Campaign Act placed a limit on the amount an individual could give to one campaign, in addition to two-year limits on the total amount an individual could give to political campaigns.
-In _McCutcheon v.
-FEC_ (2014) James Bopp, one of the attorneys behind the Citizens United challenge, convinced the Court of the unconstitutionality of total individual limits.
-Another case, _Holmes v.
-FEC_ (2017), targeted the distribution of individual campaign contribution across primary and general elections.
-In yet another, _Lair v.
-Motl_ (2017), Bopp once again took aim at individual contribution limits, arguing that the state of Montana had not shown compelling evidence that campaign contribution limits decreased the risk of corruption.
-
-The Ninth Circuit Court of Appeals upheld Montana’s campaign contribution limits, and the Fifth Circuit similarly upheld limits in Austin, TX (_Zimmerman v.
-City of Austin_, 2018).
-But further challenges to contribution limits are likely.
-Bopp said that he planned to appeal the Ninth Circuit’s ruling.
-Even if that fails, Bopp and other conservative groups plan to carry on.
-“I handle a lot of cases,” he said after the 2014 McCutcheon ruling, “and I‘m not done yet.” Supreme Court Justice Clarence Thomas laid the groundwork for future challenges in his commentary on the McCutcheon decision by arguing that more dollars did, in fact, equate to more speech.
-Once established, that principle supports the argument that campaign contribution dollar amount limits are a potentially unconstitutional restriction on speech (Hurley & Debenedetti 2014, Zall 2017).
-
-##Prior Work 
-Since the Buckley v.
-Valeo decision, a wave of scholarship has taken advantage of the campaign contribution data collected by the Federal Election Commission to examine the causes and consequences of political campaign contributions, including whether contributions buy access (not to a meaningful degree, find Welch 1982 and Langbein 1986) and the effectiveness of contributions relative to lobbying efforts (yes, according to Wright 1990).
-Since the 2010 Citizens United and speechnow.org decisions, another arm of scholarship has examined the flows of money to groups engaging in independent expenditures (Spencer and Wood 2014, Werner and Coleman 2014).
-
-But lobbying, money for access, and independent expenditures all fall outside of the narrow definition of quid pro corruption that the Supreme Court considers a compelling enough state interest to justify campaign contribution limits.
-The scholarly research on corruption thus narrowly defined is mixed and heated.
-Stratmann finds evidence that donations determined votes in at least one instance (1991); he also finds that the timing of political action committees (PAC) donations suggests that corporations believe those donations do affect legislators’ votes (1998).
-Reacting to the absence of evidence that donations lead to favorable final votes on bills, Hall and Wayman (1990) look for and find a positive relationship between political donations and the amount of attention that legislators give to a particular issue.
-Other scholars, however, are not so convinced.
-Wright finds that once lobbying efforts are factored in, the effects of contributions on voting outcomes washes out (1990).
-And it is notoriously difficult to tease out whether political donations change legislators’ minds or instead flow to legislators with established, friendly positions (Ansolabehere et al 2003).
-
-As mentioned above, the Court is also interested in the appearance of corruption.
-On this score, results are more consonant: There seems to be little association between campaign spending and public trust in government (Primo 2002).
-Other factors, including media coverage of campaign finance law and the professionalization of legislatures, are more predictive of public perceptions of corruptions (Rosenson 2009).
-And while the public does seem to report viewing campaign finance as a contributor to corruption, there is not evidence that reform efforts will have an effect on those views (Persily & Lammie 2004).
-
-One fundamental limitation of these federal level studies on campaign contributions and corruption is the absence of a counter-factual.
-Given that contribution limits have been in place since the 1970s, it is difficult to argue what might have happened in their absence.
-Recent work on campaign finance has attempted to address this problem by focusing on the effects of differences in campaign finance laws at the state level.
-Variation across states and over time allows room for studying the causes and consequences of campaign finance limits, separate from the question of corruption.
-Studies suggest that campaign finance limits are associated with less electoral competition (Gross et al 2002, Lott 2006), but that disclosure rules and some organizational limits are associated with greater levels of government trust (Primo and Milyo 2006) and may increase the return on campaign expenditures (Stratmann 2006).
-As mentioned, Michael Barber’s 2016 work finds that lower limits on PAC donations relative to individual donations are associated with higher polarization.
-
-A largely separate body of work has examined the causes and consequences of corruption at the state level, separate from campaign finance.
-Most use the Department of Justice’s Annual Public Integrity Report, which correlate highly with state level perceptions of corruption (Walker and Calcagno 2011, Glaeser and Saks 2006, Liu & Mikesell 2014).
-Using that data, researchers have found evidence that political corruption leads to inflated state budgets and that the presence of casinos and subsequent corruption (Liu & Mikesell 2014, Walker & Calcagno 2013).
-They have also shown the absence of a link between state ethics commissions and reduced corruption (Crider and Milyo 2013).
-
-In response to criticisms of corruption convictions as a proper measure of corruption, researchers have also developed alternative measures of state level corruption.
-Boylan and Long make use of surveys of state reporters (2003).
-Cordis and Milyo deploy the recently available Transactional Records Access Clearinghouse (TRAC) database of political corruption (2016).
-Dincer and Jonhston introduce a Corruption Reflections Index, which tracks mentions of corruption in Associated Press reports (2016).
-
-A smaller number of scholars have begun connecting these bodies of work to examine the impact of state-level campaign finance regulations on measures of quid pro quo corruption--one of only two questions of import to the Supreme Court as it considers the constitutionality of contribution limits.
-The exception to this is a 2013 working paper by Cordis and Milyo.
-In line with Persily and Lammie (2004), Milyo argues that campaign reform efforts have little effect on public perceptions of corruption.
-This paper seeks to address this gap, putting state level campaign finance data in direct conversation with state level corruption data.
-
-##Data and Design  
-In this paper, I build upon the growing body of state-level political science research to ask whether campaign contribution limits at the state level associated with lower levels of corruption.
-Given open debate about the proper measure of state-level corruption, I use two measures.
-The first, a Corruptions Convictions Index, is the traditional measure of state level corruption, built from Department of Justice convictions data.
-The second, the Corruptions Reflection Index, is a new measure put forward by Dincer and Johnston (2016).
-I combine these measures with a third data set from Michael Barber’s 2016 work on campaign contribution limits and political polarization; and a fourth data set from James Alt and David Dryer Lassen, to provide controls for the full model (Alt and Lassen 2012).
-
-Barber’s data set is a panel of contribution limits from 1990-2012 for the lower house of every state legislature.
-Barber compiled this data set from the FEC, Westlaw, and the Nation Council of State Legislatures.
-Each dollar amount is inflation indexed to 2010 dollar amounts, and bi-annualized.
-There are three different types of limits in the Barber database: Individual contribution limits, individual-to-party limits, and PAC limits.
-Barber utilized individual and PAC contributions in his analysis of polarization, leaving out individual-to-party limits given that party contributions typically make up less than 10% of total political fundraising; I include it this analysis to determine whether parties, rather than PACs or individuals, might be the locus of corruption as measured by our other two data sets (Barber 2016).
-
-<!--Add in summary statistics here. 
-Plot of something over time?
-Histograms?
--->
-```{r Barber summary, eval=TRUE}
-descr(Barber)
-# Barber histograms 
-ind_limits_2010.plot <- ggplot(Barber, aes(ind_limits_2010)) + geom_density() + theme_minimal()
-ind_limits_2010.plot
-ind2pty_limits_2010.plot <- ggplot(Barber, aes(ind2pty_limits_2010)) + geom_density() + theme_minimal()
-ind_limits_2010.plot
-pac_limits_2010.plot <- ggplot(Barber, aes(pac_limits_2010)) + geom_density() + theme_minimal()
-```
-
-The second data set comes from the Department of Justice’s “Report to Congress on the Activities and Operations of the Public Integrity Section” by way of the Institute for Corruption Studies.[^Koch]  Since 1976, the FBI has tracked political corruption at the state level, and the Corruption Convictions Index (CCI) used here includes the number of corruption convictions in a year normalized by the population in each state.
-This measure of corruption is widely used in academic research, though not without criticism.
-
-```{r CCI summary, eval=TRUE}
-descr(convictions)
-# Barber histograms 
-convictions.plot <- ggplot(convictions, aes(CCI)) + geom_density() + theme_minimal()
-convictions.plot
-```
-
-The third data set is the Institute for Corruption Studies’ Corruption Reflections Index (CRI), put together by Dincer and Johnston for their 2016 article on state-level corruption, and which they create in response to the limitations of the Corruption Convictions.
-The Corruption Reflections Index represents the fraction of Associated Press stories about politics in a particular state that mention political corruption (Dincer and Johnston 2016).
-
-```{r CRI summary, eval=TRUE}
-descr(reflections)
-# Barber histograms 
-reflections.plot <- ggplot(reflections, aes(CRI)) + geom_density() + theme_minimal()
-reflections.plot
-```
-
-<!--Test whether these are correlated?-->
-
-The fourth data set provides controls for the panel model.
-In their 2012 work examining variation in prosecutorial resources, Alt and Lassen follow Glaeser and Saks (2006) in controlling for income and education levels, size of government, legislature control, and urbanization.
-Alt and Lassen's data set runs from 1976-2004.
-When included in the second and third models, this limits the analysis to the years from 1990-2004.
-
-<!--Describe controls here, then add a table with summary statistics for everything-->
-
-This analysis has its limitations, beginning with the data sets themselves.
-Barber’s state campaign contributions data lacks information about upper houses of state legislatures, which are included in both the CCI and CRI.
-The Corruption Convictions Index suffers from a number of issues, as outlined by Dincer and Johnston in their introduction to the Corruption Reflections Index.
-They argue that the CCI includes only federal data; that the resources available to prosecutors varies from state to state; that US Attorneys are political appointees; and that the measure records only convictions, which is at best a reflection of underlying corruption.
-
-The Corruption Reflections Index, too, has its flaws: It relies on a single news source, the Associated Press.
-Similar to federal prosecutors’ offices, the resources available to each AP office vary.
-It also demonstrates high variation in the data; Utah, for example, has a mean CRI score of 0.46 and standard deviation of 0.38, in a data set with an overall mean of 0.28 and standard deviation of 0.19.
-The Corruption Reflections Index also seems to assume in its name that media reports of corruption are a mere reflection of corruption, rather than an endogenous variable in the ecosystem that enables corrupt behavior.
-Previous work, in contrast, has argued that media have a clear bias and play an important role in shaping public perceptions of corruption, rather than just reflecting it (Sorauf 1987; Ansolabehere, Snowberg and Snyder 2005).
-
-Most broadly, this analysis does not directly address the “appearance of corruption,” the second of the Supreme Court’s reasons for allowing campaign contribution limits; to do so effectively would require time series, state-level data specifically about quid pro quo corruption.
-It is also the case that this analysis looks to the states intentionally in order to address the issue of the counter-factual inherent in looking at federal data, it may not be the case that statewide results are generalizable to, or distinct from, what is occurring at the federal level.
-Third, it is also the case that campaign finance laws may not be equally enforced across states, even though the enforcement measures used here are from federal rather than state authorities.
-Finally, the period in question (1990-2004) is short enough that there may be some factor that influences corruption arrest across a meaningful portion of the data set.
-
-[^Koch]: N.B.
-According to one of the researchers’ [curricula vitae](https://about.illinoisstate.edu/odincer/Documents/CVDincerApril2016.docx), the Institute for Corruption Studies is funded in part by a grant from the Charles Koch Research Foundation.
-Organizations funded by Charles and David Koch are also funders of legal groups driving legal battles mentioned in the introduction, according to a [report](https://www.publicintegrity.org/2017/11/15/21279/kochs-key-among-small-group-quietly-funding-legal-assault-campaign-finance) by the Center for Public Integrity.
-
-##Methods
-### Model I: Panel Regression
-Having constructed a full 1990-2012 panel data set from these three data sets, I then run a set of time series regressions testing the relationship between contribution limits and both dependent variables, the Corruption Convictions Index and the Corruption Reflections Index.
-
-I include three predictor variables in both sets of models: Individual contribution limits, individual-to-party contribution limits, and PAC contribution limits.
-For each of these independent variables, I construct two variables to use in the model.
-The first is a dummy variable indicating whether there are contribution limits in that state in that year, coded as “0” if there are no limits and “1” if there are.
-The second is a continuous variable indicating the dollar amount of the limit in the state in that year.
-By interacting these two variables, I test two separate associations.
-The dummy variable tests whether there is a difference in the CCI and CRI in states with limits versus states without limits.
-The continuous variable tests whether higher or lower limits are associated with higher or lower CCI and CRI scores, within the group of states that have limits in a given year.
-After performing this transformation on all three independent variables, I test two initial sets of models: (1) Corruption Convictions Index versus campaign contribution limits in a given state-year, and (2) Corruption Reflections Index versus campaign contributions in a given state-year.
-
-<!--Edit specifications--> 
-####Corruption Convictions Index versus campaign contribution limits in a given state-year:
-
-$Convictions = \alpha + \beta_{indiv.dummy} + \beta_{indiv.dummy}*\beta_{indiv.limit} + \beta_{pac.dummy} + \beta_{pac.dummy}*\beta_{pac.limit} + \beta_{indiv-to-party.dummy} + \beta_{indiv-to-party.dummy}*\beta_{indiv-to-party.limit} + \epsilon$
-
-####Corruption Reflections Index versus campaign contributions in a given state-year:
-
-$Reflections = \alpha + \beta_{indiv.dummy} + \beta_{indiv.dummy}*\beta_{indiv.limit} + \beta_{pac.dummy} + \beta_{pac.dummy}*\beta_{pac.limit} + \beta_{indiv-to-party.dummy} + \beta_{indiv-to-party.dummy}*\beta_{indiv-to-party.limit} + \epsilon$
-
-As demonstrated below, this model fails to uncover any initial correlation between changes in campaign finance law and CCI or CRI scores.
-This may be due to the confounding effect of absent variables.
-In order to test that, I build a model of political corruption using control variables previously demonstrated to be correlated with corruption arrests, resulting in a data set covering 1990-2004, the period of overlap among the data sets listed above.
-These include controlling for the size and education levels of the population, the ideology of a population, income levels and inequality, education levels, the number and relative income of government employees, and urbanization.
-Building a model of corruption that includes variables previously demonstrated to be correlated with corruption levels, then adding in campaign finance data, can better identify the association of campaign finance laws with corruption levels.
-
-### Model II: Difference-in-Difference Model
-<!--Add specification, formulas?-->
-Even if the panel models above fail to capture correlation between state level campaign finance laws and corruption arrests, it could be the case that changes in campaign finance laws, rather than relative campaign finance limits, are correlated with decreases in corruption.
-A difference-in-difference regression can help identify this by comparing the state-years in which campaign finance laws changed to state-years where they remained constant.
-If tighter campaign finance laws are correlated with lower corruption levels, then a change in one year should lead to lower corruption convictions in the years following.
-
-<!--add something to show what change occurred-->
 
@@
 \newpage
+##Appendix A: Descriptions of Control Variables
+In their 2006 paper "Corruption in America," Glaeser and Saks make use of the following control variables, which we have included here:
+
+\newpage
 ##References 

### 2018-12-18 Paper 2019.Rmd
Modeling!

@@
 
-```{r panel modeling, eval=T}
-## CCI 
-# Individual limits and corruption
-CCIreg1  <- plm(CCI ~ ind_limits_2010*ind_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
-# No signifigance
-
-# Individual-to-party limits and corruption
-CCIreg2  <- plm(CCI ~ ind2pty_limits_2010*ind2pty_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
-# No Signifigance
-
-# PAC Limits and corruption
-CCIreg3  <- plm(CCI ~ pac_limits_2010*pac_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
-# No Signifigance
-
-# Total Limits and corruption
-CCIreg4  <- plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
-# One star. Hmm...
-
-# Everybody? 
-CCIreg5 <- plm(CCI ~ ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = BarberICC, index = c("st","year"), effect="twoways")
-
-## CRI
-CRIreg1  <- plm(CRI ~ ind_limits_2010*ind_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
-# No signifigance
-
-# Individual-to-party limits and reflection
-CRIreg2  <- plm(CRI ~ ind2pty_limits_2010*ind2pty_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
-# One star. Hmm...
-
-# PAC Limits and reflection
-CRIreg3  <- plm(CRI ~ pac_limits_2010*pac_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
-# No Signifigance
-
-# All Limits and reflection
-CRIreg4  <- plm(CRI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
-# No Signifigance
-
-# Everybody? 
-CRIreg5 <- plm(CRI ~ ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = BarberICC, index = c("st","year"), effect="twoways")
-```
-
-```{r post-Lentz panel effects modeling, eval=F}
-# Include lagged dependent variables here. 
-# Erin's question: Are these "pooled"? 
-# Her effort to understand: Write out the formulas. 
-# Maybe helpful? https://onlinecourses.science.psu.edu/stat502/node/162/
-# Erin's suggestion https://www.princeton.edu/~otorres/Panel101R.pdf
-# On robust standard errors https://stats.stackexchange.com/questions/117052/replicating-statas-robust-option-in-r
-# And https://cran.r-project.org/web/packages/sandwich/vignettes/sandwich.pdf
-# And https://www.brodrigues.co/blog/2018-07-08-rob_stderr/, 
-# Pretty good explanation here https://www.methodsconsultants.com/tutorial/introduction-to-random-effects-models-including-hlm/
-# Go through this? https://github.com/tyleransom/EconometricsLabs/blob/master/tidyRcheatsheet.pdf
-summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC))
-summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways"))
-summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="within", effect="twoways"))
-summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="within"))
-summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="random")) #FAIL 
-summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC), model="pooling")
-summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC), model="within")
-
-#From Erin: 
-# •	Based on the results in Table 3, it appears that neither fixed effects or random effects were included in the panel estimation results.
-If that is correct, I’d argue including one of them could materially change the results.
-# o	I’m not sure which would be better: state fixed effects would limit the interpretation of results to effects within states, as opposed to across states but fixed effects are not a good idea when the error terms of each state are correlated (use a Hausman to check).
-Random effects assume no omitted variables, which can be a strong assumption.
-# o	This might be a useful resource: https://www.princeton.edu/~otorres/Panel101.pdf
-# o	Explain your treatment of standard errors (e.g., are you using robust se?).
-
-```
-
-```{r (old) controlled panel modeling}
-#Next: Panel model of corruption against unemployment and high school? 
-testmodel01 <- plm(CCI ~ rpcinc_annual_new + unemp + high_school + logNumpop + citi6006 + grelimp, data = AltBarber, index = c("st","year"), effect="twoways")
-
-testmodel02 <- plm(CCI ~ jdiv + bindingonetermlimit + bindingtwotermlimit + rpcinc_annual_new + eousa + unemp + citi6006 + high_school + rgenrevpc + logNumpop + eopop + men_ineqincwag + grelimp + fedrepcons + urbanization_2 + logpop + inspop, data = AltBarber, index = c("st","year"), effect="twoways")
-
-testmodel03 <- plm(CCI ~ jdiv + bindingonetermlimit + bindingtwotermlimit + rpcinc_annual_new + eousa + unemp + citi6006 + high_school + rgenrevpc + logNumpop + eopop + men_ineqincwag + grelimp + fedrepcons + urbanization_2 + logpop + inspop + ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = AltBarber, index = c("st","year"), effect="twoways")
-
-testmodel05 <- plm(CCI ~ jdiv + bindingonetermlimit + bindingtwotermlimit + rpcinc_annual_new + eousa + unemp + citi6006 + high_school + rgenrevpc + logNumpop + eopop + men_ineqincwag + grelimp + urbanization_2 + logpop + inspop, data = AltBarber, index = c("st","year"), effect="twoways")
-```
-
-```{r controlled panel modeling, eval=T}
-
-CCIcontrol01 <- plm(CCI ~ jdiv  # Divided government 
+```{r modeling of CCI base model effects, eval=F}
+# Base model with no fixed or random effects 
+ cci.base.pooled <- plm(CCI ~ jdiv  # Divided government 
                    + bindingonetermlimit # Binding one-term limit 
@@
                    data = AltBarber, 
-                   index = c("st","year"), 
-                   effect="twoways")
+                   model="pooling")
 
-CCIcontrol02 <- plm(CCI ~ jdiv  # Divided government 
-                   + bindingonetermlimit # Binding one-term limit 
-                   + bindingtwotermlimit # Binding two-term limit 
-                   + rpcinc_annual_new # Real per capita income ($1000)
-                   + eopop # AUSAs per million population
-                   + unemp # Unemployment 
-                   + citi6006 # Citizen ideology measure 
-                   + high_school + # Percent high school graduates
-                   + rgenrevpc # Real per capita gov revenues ($1000)
-                   + men_ineqincwag # Inequality: Male wages
-                   + grelimp # Relative government wages
-                   + urbanization_2 # Urbanization 
-                   + logpop # Log of population (millions)
-                   + ind_limits_2010*ind_limits_dummy 
-                   + ind2pty_limits_2010*ind2pty_limits_dummy 
-                   + pac_limits_2010*pac_limits_dummy, 
-                   data = AltBarber, 
-                   index = c("st","year"), 
-                   effect="twoways")
-
-CRIcontrol01 <- plm(CRI ~ jdiv  # Divided government 
+# Base model with fixed effects (NB: effect="individual" is redundant here)
+cci.base.fixed <- plm(CCI ~ jdiv  # Divided government 
                    + bindingonetermlimit # Binding one-term limit 
@@
                    data = AltBarber, 
-                   index = c("st","year"), 
-                   effect="twoways")
+                   model="within")
 
-CRIcontrol02 <- plm(CRI ~ jdiv  # Divided government 
+# Base model with random effects 
+cci.base.random <- plm(CCI ~ jdiv  # Divided government 
                    + bindingonetermlimit # Binding one-term limit 
@@
                    + urbanization_2 # Urbanization 
-                   + logpop # Log of population (millions)
-                   + ind_limits_2010*ind_limits_dummy 
+                   + logpop, # Log of population (millions)
+                   data = AltBarber, 
+                   model="random")
+
+#Base model with fixed effects and time fixed effects 
+cci.base.fixed.time <- plm(CCI ~ jdiv  # Divided government 
+                   + bindingonetermlimit # Binding one-term limit 
+                   + bindingtwotermlimit # Binding two-term limit 
+                   + rpcinc_annual_new # Real per capita income ($1000)
+                   + eopop # AUSAs per million population
+                   + unemp # Unemployment 
+                   + citi6006 # Citizen ideology measure 
+                   + high_school + # Percent high school graduates
+                   + rgenrevpc # Real per capita gov revenues ($1000)
+                   + men_ineqincwag # Inequality: Male wages
+                   + grelimp # Relative government wages
+                   + urbanization_2 # Urbanization 
+                   + logpop, # Log of population (millions)
+                   data = AltBarber, 
+                   model="within", 
+                   effect = "twoways")
+
+# Base model with random effects doesn't work: 
+# Error in solve.default(crossprod(ZBmu)) : 
+  # system is computationally singular: reciprocal condition number = 1.96767e-18
+
+# Hausman for base model 
+phtest(cci.base.pooled, cci.base.fixed, cci.base.random, cci.base.fixed.time)
+```
+
+```{r output of CCI base model effects, eval=F}
+stargazer(cci.base.pooled, 
+          cci.base.fixed, 
+          cci.base.random, 
+          cci.base.fixed.time, 
+          type="text",
+          add.lines = list(c("Effects", "Pooled", "Fixed", "Random", "Two-Way"))
+          )
+```
+
+```{r modeling of CRI base model effects, eval=F}
+# Base model with no fixed or random effects 
+ cri.base.pooled <- plm(CRI ~ jdiv  # Divided government 
+                   + bindingonetermlimit # Binding one-term limit 
+                   + bindingtwotermlimit # Binding two-term limit 
+                   + rpcinc_annual_new # Real per capita income ($1000)
+                   + eopop # AUSAs per million population
+                   + unemp # Unemployment 
+                   + citi6006 # Citizen ideology measure 
+                   + high_school + # Percent high school graduates
+                   + rgenrevpc # Real per capita gov revenues ($1000)
+                   + men_ineqincwag # Inequality: Male wages
+                   + grelimp # Relative government wages
+                   + urbanization_2 # Urbanization 
+                   + logpop, # Log of population (millions)
+                   data = AltBarber, 
+                   model="pooling")
+
+# Base model with fixed effects (NB: effect="individual" is redundant here)
+cri.base.fixed <- plm(CRI ~ jdiv  # Divided government 
+                   + bindingonetermlimit # Binding one-term limit 
+                   + bindingtwotermlimit # Binding two-term limit 
+                   + rpcinc_annual_new # Real per capita income ($1000)
+                   + eopop # AUSAs per million population
+                   + unemp # Unemployment 
+                   + citi6006 # Citizen ideology measure 
+                   + high_school + # Percent high school graduates
+                   + rgenrevpc # Real per capita gov revenues ($1000)
+                   + men_ineqincwag # Inequality: Male wages
+                   + grelimp # Relative government wages
+                   + urbanization_2 # Urbanization 
+                   + logpop, # Log of population (millions)
+                   data = AltBarber, 
+                   model="within")
+
+# Base model with random effects 
+cri.base.random <- plm(CRI ~ jdiv  # Divided government 
+                   + bindingonetermlimit # Binding one-term limit 
+                   + bindingtwotermlimit # Binding two-term limit 
+                   + rpcinc_annual_new # Real per capita income ($1000)
+                   + eopop # AUSAs per million population
+                   + unemp # Unemployment 
+                   + citi6006 # Citizen ideology measure 
+                   + high_school + # Percent high school graduates
+                   + rgenrevpc # Real per capita gov revenues ($1000)
+                   + men_ineqincwag # Inequality: Male wages
+                   + grelimp # Relative government wages
+                   + urbanization_2 # Urbanization 
+                   + logpop, # Log of population (millions)
+                   data = AltBarber, 
+                   model="random")
+
+#Base model with fixed effects and time fixed effects 
+cri.base.fixed.time <- plm(CRI ~ jdiv  # Divided government 
+                   + bindingonetermlimit # Binding one-term limit 
+                   + bindingtwotermlimit # Binding two-term limit 
+                   + rpcinc_annual_new # Real per capita income ($1000)
+                   + eopop # AUSAs per million population
+                   + unemp # Unemployment 
+                   + citi6006 # Citizen ideology measure 
+                   + high_school + # Percent high school graduates
+                   + rgenrevpc # Real per capita gov revenues ($1000)
+                   + men_ineqincwag # Inequality: Male wages
+                   + grelimp # Relative government wages
+                   + urbanization_2 # Urbanization 
+                   + logpop, # Log of population (millions)
+                   data = AltBarber, 
+                   model="within", 
+                   effect = "twoways")
+
+# Hausman for base model 
+phtest(cri.base.pooled, cri.base.fixed, cri.base.random, cri.base.fixed.time)
+```
+
+```{r output of CRI base model effects, eval=F}
+stargazer(cri.base.pooled, 
+          cri.base.fixed, 
+          cri.base.random, 
+          cri.base.fixed.time, 
+          type="text",
+          add.lines = list(c("Effects", "Pooled", "Fixed", "Random", "Two-Way"))
+          )
+```
+
+```{r modeling of CCI with campaign finance variables, eval=F}
+# Base model with no fixed or random effects 
+ cci.limits.pooled <- plm(CCI 
+                   ~ ind_limits_2010*ind_limits_dummy 
                    + ind2pty_limits_2010*ind2pty_limits_dummy 
-                   + pac_limits_2010*pac_limits_dummy, 
+                   + pac_limits_2010*pac_limits_dummy
+                   + jdiv  # Divided government 
+                   + bindingonetermlimit # Binding one-term limit 
+                   + bindingtwotermlimit # Binding two-term limit 
+                   + rpcinc_annual_new # Real per capita income ($1000)
+                   + eopop # AUSAs per million population
+                   + unemp # Unemployment 
+                   + citi6006 # Citizen ideology measure 
+                   + high_school + # Percent high school graduates
+                   + rgenrevpc # Real per capita gov revenues ($1000)
+                   + men_ineqincwag # Inequality: Male wages
+                   + grelimp # Relative government wages
+                   + urbanization_2 # Urbanization 
+                   + logpop, # Log of population (millions)
                    data = AltBarber, 
-                   index = c("st","year"), 
-                   effect="twoways")
+                   model="pooling")
+
+# Base model with fixed effects (NB: effect="individual" is redundant here)
+cci.limits.fixed <- plm(CCI 
+                   ~ ind_limits_2010*ind_limits_dummy 
+                   + ind2pty_limits_2010*ind2pty_limits_dummy 
+                   + pac_limits_2010*pac_limits_dummy
+                   + jdiv  # Divided government 
+                   + bindingonetermlimit # Binding one-term limit 
+                   + bindingtwotermlimit # Binding two-term limit 
+                   + rpcinc_annual_new # Real per capita income ($1000)
+                   + eopop # AUSAs per million population
+                   + unemp # Unemployment 
+                   + citi6006 # Citizen ideology measure 
+                   + high_school + # Percent high school graduates
+                   + rgenrevpc # Real per capita gov revenues ($1000)
+                   + men_ineqincwag # Inequality: Male wages
+                   + grelimp # Relative government wages
+                   + urbanization_2 # Urbanization 
+                   + logpop, # Log of population (millions)
+                   data = AltBarber, 
+                   model="within")
+
+# Base model with random effects (failed)  
+# cci.limits.random <- plm(CCI 
+#                    ~ ind_limits_2010*ind_limits_dummy 
+#                    + ind2pty_limits_2010*ind2pty_limits_dummy 
+#                    + pac_limits_2010*pac_limits_dummy
+#                    + jdiv  # Divided government 
+#                    + bindingonetermlimit # Binding one-term limit 
+#                    + bindingtwotermlimit # Binding two-term limit 
+#                    + rpcinc_annual_new # Real per capita income ($1000)
+#                    + eopop # AUSAs per million population
+#                    + unemp # Unemployment 
+#                    + citi6006 # Citizen ideology measure 
+#                    + high_school + # Percent high school graduates
+#                    + rgenrevpc # Real per capita gov revenues ($1000)
+#                    + men_ineqincwag # Inequality: Male wages
+#                    + grelimp # Relative government wages
+#                    + urbanization_2 # Urbanization 
+#                    + logpop, # Log of population (millions)
+#                    data = AltBarber, 
+#                    model="random")
+
+#Base model with fixed effects and time fixed effects 
+cci.limits.fixed.time <- plm(CCI 
+                   ~ ind_limits_2010*ind_limits_dummy 
+                   + ind2pty_limits_2010*ind2pty_limits_dummy 
+                   + pac_limits_2010*pac_limits_dummy
+                   + jdiv  # Divided government 
+                   + bindingonetermlimit # Binding one-term limit 
+                   + bindingtwotermlimit # Binding two-term limit 
+                   + rpcinc_annual_new # Real per capita income ($1000)
+                   + eopop # AUSAs per million population
+                   + unemp # Unemployment 
+                   + citi6006 # Citizen ideology measure 
+                   + high_school + # Percent high school graduates
+                   + rgenrevpc # Real per capita gov revenues ($1000)
+                   + men_ineqincwag # Inequality: Male wages
+                   + grelimp # Relative government wages
+                   + urbanization_2 # Urbanization 
+                   + logpop, # Log of population (millions)
+                   data = AltBarber, 
+                   model="within", 
+                   effect = "twoways")
+
+# Hausman for base model 
+phtest(cci.limits.pooled, cci.limits.fixed, cci.limits.random, cci.limits.fixed.time)
+```
+
+```{r output of CCI with campaign finance variables, eval=F}
+stargazer(cci.limits.pooled, 
+          cci.limits.fixed, 
+          cci.limits.fixed.time, 
+          type="text",
+          add.lines = list(c("Effects", "Pooled", "Fixed", "Two-Way"))
+          )
+```
+
+```{r modeling of CRI with campaign finance variables, eval=F}
+# Base model with no fixed or random effects 
+cri.limits.pooled <- plm(CRI 
+                   ~ ind_limits_2010*ind_limits_dummy 
+                   + ind2pty_limits_2010*ind2pty_limits_dummy 
+                   + pac_limits_2010*pac_limits_dummy
+                   + jdiv  # Divided government 
+                   + bindingonetermlimit # Binding one-term limit 
+                   + bindingtwotermlimit # Binding two-term limit 
+                   + rpcinc_annual_new # Real per capita income ($1000)
+                   + eopop # AUSAs per million population
+                   + unemp # Unemployment 
+                   + citi6006 # Citizen ideology measure 
+                   + high_school + # Percent high school graduates
+                   + rgenrevpc # Real per capita gov revenues ($1000)
+                   + men_ineqincwag # Inequality: Male wages
+                   + grelimp # Relative government wages
+                   + urbanization_2 # Urbanization 
+                   + logpop, # Log of population (millions)
+                   data = AltBarber, 
+                   model="pooling")
+
+# Base model with fixed effects (NB: effect="individual" is redundant here)
+cri.limits.fixed <- plm(CRI 
+                   ~ ind_limits_2010*ind_limits_dummy 
+                   + ind2pty_limits_2010*ind2pty_limits_dummy 
+                   + pac_limits_2010*pac_limits_dummy
+                   + jdiv  # Divided government 
+                   + bindingonetermlimit # Binding one-term limit 
+                   + bindingtwotermlimit # Binding two-term limit 
+                   + rpcinc_annual_new # Real per capita income ($1000)
+                   + eopop # AUSAs per million population
+                   + unemp # Unemployment 
+                   + citi6006 # Citizen ideology measure 
+                   + high_school + # Percent high school graduates
+                   + rgenrevpc # Real per capita gov revenues ($1000)
+                   + men_ineqincwag # Inequality: Male wages
+                   + grelimp # Relative government wages
+                   + urbanization_2 # Urbanization 
+                   + logpop, # Log of population (millions)
+                   data = AltBarber, 
+                   model="within")
+
+# Base model with random effects (failed)  
+cri.limits.random <- plm(CRI
+                   ~ ind_limits_2010*ind_limits_dummy
+                   + ind2pty_limits_2010*ind2pty_limits_dummy
+                   + pac_limits_2010*pac_limits_dummy
+                   + jdiv  # Divided government
+                   + bindingonetermlimit # Binding one-term limit
+                   + bindingtwotermlimit # Binding two-term limit
+                   + rpcinc_annual_new # Real per capita income ($1000)
+                   + eopop # AUSAs per million population
+                   + unemp # Unemployment
+                   + citi6006 # Citizen ideology measure
+                   + high_school + # Percent high school graduates
+                   + rgenrevpc # Real per capita gov revenues ($1000)
+                   + men_ineqincwag # Inequality: Male wages
+                   + grelimp # Relative government wages
+                   + urbanization_2 # Urbanization
+                   + logpop, # Log of population (millions)
+                   data = AltBarber,
+                   model="random")
+
+#Base model with fixed effects and time fixed effects 
+cri.limits.fixed.time <- plm(CRI 
+                   ~ ind_limits_2010*ind_limits_dummy 
+                   + ind2pty_limits_2010*ind2pty_limits_dummy 
+                   + pac_limits_2010*pac_limits_dummy
+                   + jdiv  # Divided government 
+                   + bindingonetermlimit # Binding one-term limit 
+                   + bindingtwotermlimit # Binding two-term limit 
+                   + rpcinc_annual_new # Real per capita income ($1000)
+                   + eopop # AUSAs per million population
+                   + unemp # Unemployment 
+                   + citi6006 # Citizen ideology measure 
+                   + high_school + # Percent high school graduates
+                   + rgenrevpc # Real per capita gov revenues ($1000)
+                   + men_ineqincwag # Inequality: Male wages
+                   + grelimp # Relative government wages
+                   + urbanization_2 # Urbanization 
+                   + logpop, # Log of population (millions)
+                   data = AltBarber, 
+                   model="within", 
+                   effect = "twoways")
+
+# Base model with random effects doesn't work: 
+# Error in solve.default(crossprod(ZBmu)) : 
+  # system is computationally singular: reciprocal condition number = 1.96767e-18
+
+# Hausman for base model 
+phtest(cri.limits.pooled, cri.limits.fixed, cri.limits.random, cri.limits.fixed.time)
+```
+
+```{r output of CRI with campaign finance variables, eval=F}
+stargazer(cri.limits.pooled, 
+          cri.limits.fixed, 
+          cri.limits.random,
+          cri.limits.fixed.time, 
+          type="text",
+          add.lines = list(c("Effects", "Pooled", "Fixed", "Random", "Two-Way"))
+          )
+```
+
+```{r output to table?}
 
@@
 
-The first set of models (Table I) measures the association of various campaign contribution limits with the Corruption Convictions Index.
+The first set of models (Table 1) measures the association of various campaign contribution limits with the Corruption Convictions Index.
 The sign of each coefficient is negative, indicating that the presence of limits is associated with lower corruption levels, but that where limits exist, higher (weaker) donation limits are associated with lower levels of corruption.
@@
 
-The second set of models (Table II) also fails to find a relationship between state-level campaign contribution limits and media mentions of corruption as measured by the Corruption Reflections Index, with one exception: The presence of limits on what an individual can give to a party is associated with a 0.10 point decline in the Corruption Reflection Index.
+The second set of models (Table 2) also fails to find a relationship between state-level campaign contribution limits and media mentions of corruption as measured by the Corruption Reflections Index, with one exception: The presence of limits on what an individual can give to a party is associated with a 0.10 point decline in the Corruption Reflection Index.
 The Corruption Reflections Index operates on a scale of zero to one (with a few outlying exceptions), indicating that the presence of individual-to-party limits is associated with a 10% decrease in the index.
@@
 
-```{r stargazer CRI html}
+```{r stargazer CRI html, eval=F}
 stargazer(CRIreg1, CRIreg2, CRIreg3, CRIreg5,
@@
 
-```{r stargazer controlled panel}
+```{r stargazer controlled panel, eval=F}
 stargazer(CCIcontrol01,CCIcontrol02,CRIcontrol01,CRIcontrol02,
@@
 Retrieved November 22, 2017, from https://publicpolicylegal.com/2017/10/24/ninth-circuit-tees-up-latest-challenge-to-citizens-united-and-mccutcheon/
+
+<!-- Old code
+```{r panel modeling, eval=F}
+## CCI 
+# Individual limits and corruption
+CCIreg1  <- plm(CCI ~ ind_limits_2010*ind_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
+# No signifigance
+
+# Individual-to-party limits and corruption
+CCIreg2  <- plm(CCI ~ ind2pty_limits_2010*ind2pty_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
+# No Signifigance
+
+# PAC Limits and corruption
+CCIreg3  <- plm(CCI ~ pac_limits_2010*pac_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
+# No Signifigance
+
+# Total Limits and corruption
+CCIreg4  <- plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
+# One star. Hmm...
+
+# Everybody? 
+CCIreg5 <- plm(CCI ~ ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = BarberICC, index = c("st","year"), effect="twoways")
+
+## CRI
+CRIreg1  <- plm(CRI ~ ind_limits_2010*ind_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
+# No signifigance
+
+# Individual-to-party limits and reflection
+CRIreg2  <- plm(CRI ~ ind2pty_limits_2010*ind2pty_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
+# One star. Hmm...
+
+# PAC Limits and reflection
+CRIreg3  <- plm(CRI ~ pac_limits_2010*pac_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
+# No Signifigance
+
+# All Limits and reflection
+CRIreg4  <- plm(CRI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
+# No Signifigance
+
+# Everybody? 
+CRIreg5 <- plm(CRI ~ ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = BarberICC, index = c("st","year"), effect="twoways")
+```
+
+```{r (old) controlled panel modeling, eval=F}
+#Next: Panel model of corruption against unemployment and high school? 
+testmodel01 <- plm(CCI ~ rpcinc_annual_new + unemp + high_school + logNumpop + citi6006 + grelimp, data = AltBarber, index = c("st","year"), effect="twoways")
+
+testmodel02 <- plm(CCI ~ jdiv + bindingonetermlimit + bindingtwotermlimit + rpcinc_annual_new + eousa + unemp + citi6006 + high_school + rgenrevpc + logNumpop + eopop + men_ineqincwag + grelimp + fedrepcons + urbanization_2 + logpop + inspop, data = AltBarber, index = c("st","year"), effect="twoways")
+
+testmodel03 <- plm(CCI ~ jdiv + bindingonetermlimit + bindingtwotermlimit + rpcinc_annual_new + eousa + unemp + citi6006 + high_school + rgenrevpc + logNumpop + eopop + men_ineqincwag + grelimp + fedrepcons + urbanization_2 + logpop + inspop + ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = AltBarber, index = c("st","year"), effect="twoways")
+
+testmodel05 <- plm(CCI ~ jdiv + bindingonetermlimit + bindingtwotermlimit + rpcinc_annual_new + eousa + unemp + citi6006 + high_school + rgenrevpc + logNumpop + eopop + men_ineqincwag + grelimp + urbanization_2 + logpop + inspop, data = AltBarber, index = c("st","year"), effect="twoways")
+```
+
+```{r controlled panel modeling, eval=F}
+
+CCIcontrol01 <- plm(CCI ~ jdiv  # Divided government 
+                   + bindingonetermlimit # Binding one-term limit 
+                   + bindingtwotermlimit # Binding two-term limit 
+                   + rpcinc_annual_new # Real per capita income ($1000)
+                   + eopop # AUSAs per million population
+                   + unemp # Unemployment 
+                   + citi6006 # Citizen ideology measure 
+                   + high_school + # Percent high school graduates
+                   + rgenrevpc # Real per capita gov revenues ($1000)
+                   + men_ineqincwag # Inequality: Male wages
+                   + grelimp # Relative government wages
+                   + urbanization_2 # Urbanization 
+                   + logpop, # Log of population (millions)
+                   data = AltBarber, 
+                   index = c("st","year"), 
+                   effect="twoways")
+
+CCIcontrol02 <- plm(CCI ~ jdiv  # Divided government 
+                   + bindingonetermlimit # Binding one-term limit 
+                   + bindingtwotermlimit # Binding two-term limit 
+                   + rpcinc_annual_new # Real per capita income ($1000)
+                   + eopop # AUSAs per million population
+                   + unemp # Unemployment 
+                   + citi6006 # Citizen ideology measure 
+                   + high_school + # Percent high school graduates
+                   + rgenrevpc # Real per capita gov revenues ($1000)
+                   + men_ineqincwag # Inequality: Male wages
+                   + grelimp # Relative government wages
+                   + urbanization_2 # Urbanization 
+                   + logpop # Log of population (millions)
+                   + ind_limits_2010*ind_limits_dummy 
+                   + ind2pty_limits_2010*ind2pty_limits_dummy 
+                   + pac_limits_2010*pac_limits_dummy, 
+                   data = AltBarber, 
+                   index = c("st","year"), 
+                   effect="twoways")
+
+CRIcontrol01 <- plm(CRI ~ jdiv  # Divided government 
+                   + bindingonetermlimit # Binding one-term limit 
+                   + bindingtwotermlimit # Binding two-term limit 
+                   + rpcinc_annual_new # Real per capita income ($1000)
+                   + eopop # AUSAs per million population
+                   + unemp # Unemployment 
+                   + citi6006 # Citizen ideology measure 
+                   + high_school + # Percent high school graduates
+                   + rgenrevpc # Real per capita gov revenues ($1000)
+                   + men_ineqincwag # Inequality: Male wages
+                   + grelimp # Relative government wages
+                   + urbanization_2 # Urbanization 
+                   + logpop, # Log of population (millions)
+                   data = AltBarber, 
+                   index = c("st","year"), 
+                   effect="twoways")
+
+CRIcontrol02 <- plm(CRI ~ jdiv  # Divided government 
+                   + bindingonetermlimit # Binding one-term limit 
+                   + bindingtwotermlimit # Binding two-term limit 
+                   + rpcinc_annual_new # Real per capita income ($1000)
+                   + eopop # AUSAs per million population
+                   + unemp # Unemployment 
+                   + citi6006 # Citizen ideology measure 
+                   + high_school + # Percent high school graduates
+                   + rgenrevpc # Real per capita gov revenues ($1000)
+                   + men_ineqincwag # Inequality: Male wages
+                   + grelimp # Relative government wages
+                   + urbanization_2 # Urbanization 
+                   + logpop # Log of population (millions)
+                   + ind_limits_2010*ind_limits_dummy 
+                   + ind2pty_limits_2010*ind2pty_limits_dummy 
+                   + pac_limits_2010*pac_limits_dummy, 
+                   data = AltBarber, 
+                   index = c("st","year"), 
+                   effect="twoways")
+
+```
+
+```{r post-Lentz panel effects modeling 1, eval=F}
+# Include lagged dependent variables here. 
+# Erin's question: Are these "pooled"? 
+# Her effort to understand: Write out the formulas. 
+# Maybe helpful? https://onlinecourses.science.psu.edu/stat502/node/162/
+# Erin's suggestion https://www.princeton.edu/~otorres/Panel101R.pdf
+# On robust standard errors https://stats.stackexchange.com/questions/117052/replicating-statas-robust-option-in-r
+# And https://cran.r-project.org/web/packages/sandwich/vignettes/sandwich.pdf
+# And https://www.brodrigues.co/blog/2018-07-08-rob_stderr/, 
+# Pretty good explanation here https://www.methodsconsultants.com/tutorial/introduction-to-random-effects-models-including-hlm/
+# Go through this? https://github.com/tyleransom/EconometricsLabs/blob/master/tidyRcheatsheet.pdf
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC))
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways"))
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="within", effect="twoways"))
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="within"))
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="random")) #FAIL 
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC), model="pooling")
+summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC), model="within")
+
+#From Erin: 
+# •	Based on the results in Table 3, it appears that neither fixed effects or random effects were included in the panel estimation results.
+If that is correct, I’d argue including one of them could materially change the results.
+# o	I’m not sure which would be better: state fixed effects would limit the interpretation of results to effects within states, as opposed to across states but fixed effects are not a good idea when the error terms of each state are correlated (use a Hausman to check).
+Random effects assume no omitted variables, which can be a strong assumption.
+# o	This might be a useful resource: https://www.princeton.edu/~otorres/Panel101.pdf
+# o	Explain your treatment of standard errors (e.g., are you using robust se?).
+
+```
+old code -->

### 2018-12-18 Paper 2019.Rmd
Panel tables to pull from. Does any of this go in the paper? Appendices?

@@
 
-```{r output to table?}
-
-```
-
+```{r CCI output to table}
+stargazer(cci.base.pooled, 
+          cci.limits.pooled, 
+          cci.limits.fixed,
+          cci.limits.fixed.time, 
+          type="text",
+          title = "Are the presence or amounts of campaign limits correlated with corruption convictions?",
+          out="collateral/CCI.htm",
+          dep.var.labels = "Corruption Convictions Index",
+          covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)","Divided government","Binding one-term limit","Binding two-term limit","Real per capita income ($1000)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues ($1000)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)"),
+          add.lines = list(c("Effects","Pooled","Pooled","Fixed","Two-Way"))
+          )
+```
+
+```{r CRI output to table}
+stargazer(cri.base.pooled, 
+          cri.limits.pooled, 
+          cri.limits.fixed,
+          cri.limits.fixed.time, 
+          type="text",
+          title = "Are the presence or amounts of campaign limits correlated with the Corruption Reflections Index?",
+          out="collateral/CRI.htm",
+          dep.var.labels = "Corruption Convictions Index",
+          covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)","Divided government","Binding one-term limit","Binding two-term limit","Real per capita income ($1000)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues ($1000)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)"),
+          add.lines = list(c("Effects","Pooled","Pooled","Fixed","Two-Way"))
+          )
+```
 ### Model II: Difference-in-Difference Model
@@
 None of the models find correlation between campaign finance limits and either corruption convictions or corruption reflections.
-
-\newpage 
-```{r stargzer CCI html}
-stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,
-  type="text", 
-  title = "Are campaign limits and corruption convictions correlated?",
-  out="collateral/CCI.htm",
-  dep.var.labels = c("Corruption Convictions Index"),
-  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
-```
-
-```{r stargazer CCI latex, results="asis", eval=TRUE}
-stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,
-  type="latex", 
-  title = "Are campaign limits and corruption convictions correlated?",
-  dep.var.labels = c("Corruption Convictions Index"),
-  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"),
-  font.size = "small",
-  header=FALSE,
-  column.sep.width = "-15pt",
-  digits = 2, digits.extra = 2)
-```
-
-```{r stargazer CRI html, eval=F}
-stargazer(CRIreg1, CRIreg2, CRIreg3, CRIreg5,
-  type="text", 
-  title = "Are campaign limits and corruption reflections correlated?",
-  out="collateral/CRI.htm",
-  dep.var.labels = c("Corruption Reflections Index"),
-  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
-```
-
-```{r stargazer CRI latex, results="asis", eval=TRUE}
-stargazer(CRIreg1, CRIreg2, CRIreg3, CRIreg5,
-          type="latex",
-  title = "Are campaign limits and corruption reflections correlated?",
-  dep.var.labels = c("Corruption Reflections Index"),
-  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"),
-  font.size = "small",
-  header=FALSE,
-  column.sep.width = "-15pt",
-  digits = 2, digits.extra = 2)
-```
-
-```{r stargazer controlled panel, eval=F}
-stargazer(CCIcontrol01,CCIcontrol02,CRIcontrol01,CRIcontrol02,
-  type="text", 
-  title = "Are campaign limits and correlated with corruption convictions or reflections?",
-  out="collateral/CCICRIcontrol.htm",
-  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
-  covariate.labels=c("Divided government", "Binding one-term limit"," Binding two-term limit","Real per capita income ($1000)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues ($1000)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)","Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)")
-  )
-```
-
-```{r 3 stargazer controlled panel latex, results="asis", eval=TRUE}
-stargazer(CCIcontrol01,CCIcontrol02,CRIcontrol01,CRIcontrol02,
-  title = "Are campaign limits and correlated with corruption convictions or reflections?",
-  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
-  covariate.labels=c("Divided government", "Binding one-term limit"," Binding two-term limit","Real per capita income (thousands)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (thousands)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)","Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"),
-  font.size = "small",
-  header=FALSE,
-  column.sep.width = "-15pt",
-  no.space = T,
-  digits = 2, digits.extra = 2)
-```
-
-```{r stargazer DiD}
-stargazer(CCIDID01, CCIDID02, CCIDID03, CRIDID01, CRIDID02, CRIDID03,
-  type="text", 
-  title = "Do changes in limits lead to lower levels of corruption?",
-  out="collateral/DiD.htm",
-  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
-  covariate.labels=c("Individual limits removed","Individual limits imposed","Individual limit amount","Individual limits removed*amount","Individual limits imposed*amount",
-                     "PAC limits removed","PAC limits imposed","PAC limit amount","PAC limits removed*amount","PAC limits imposed*amount",
-                     "Individual-to-party limits removed","Individual-to-party limits imposed","Individual-to-party limit amount","Individual-to-party limits removed*amount","Individual-to-party limits imposed*amount"))
-
-```
-
-\newpage
-\blandscape
-```{r stargazer DiD latex, results="asis", eval=TRUE}
-stargazer(CCIDID01, CCIDID02, CCIDID03, CRIDID01, CRIDID02, CRIDID03,
-  title = "Do changes in limits lead to lower levels of corruption?",
-  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
-  covariate.labels=c("Individual limits removed","Individual limits imposed","Individual limit amount","Individual limits removed*amount","Individual limits imposed*amount",
-                     "PAC limits removed","PAC limits imposed","PAC limit amount","PAC limits removed*amount","PAC limits imposed*amount",
-                     "Individual-to-party limits removed","Individual-to-party limits imposed","Individual-to-party limit amount","Individual-to-party limits removed*amount","Individual-to-party limits imposed*amount"),
-  font.size = "small", 
-  header = FALSE,
-  column.sep.width = "-15pt",
-  digits = 2, digits.extra = 2,
-  no.space = TRUE)
-
-```
-\elandscape
 
@@
 ```
+
+```{r stargzer CCI html}
+stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,
+  type="text", 
+  title = "Are campaign limits and corruption convictions correlated?",
+  out="collateral/CCI.htm",
+  dep.var.labels = c("Corruption Convictions Index"),
+  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
+```
+
+```{r stargazer CCI latex, results="asis", eval=TRUE}
+stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,
+  type="latex", 
+  title = "Are campaign limits and corruption convictions correlated?",
+  dep.var.labels = c("Corruption Convictions Index"),
+  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"),
+  font.size = "small",
+  header=FALSE,
+  column.sep.width = "-15pt",
+  digits = 2, digits.extra = 2)
+```
+
+```{r stargazer CRI html, eval=F}
+stargazer(CRIreg1, CRIreg2, CRIreg3, CRIreg5,
+  type="text", 
+  title = "Are campaign limits and corruption reflections correlated?",
+  out="collateral/CRI.htm",
+  dep.var.labels = c("Corruption Reflections Index"),
+  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
+```
+
+```{r stargazer CRI latex, results="asis", eval=TRUE}
+stargazer(CRIreg1, CRIreg2, CRIreg3, CRIreg5,
+          type="latex",
+  title = "Are campaign limits and corruption reflections correlated?",
+  dep.var.labels = c("Corruption Reflections Index"),
+  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"),
+  font.size = "small",
+  header=FALSE,
+  column.sep.width = "-15pt",
+  digits = 2, digits.extra = 2)
+```
+
+```{r stargazer controlled panel, eval=F}
+stargazer(CCIcontrol01,CCIcontrol02,CRIcontrol01,CRIcontrol02,
+  type="text", 
+  title = "Are campaign limits and correlated with corruption convictions or reflections?",
+  out="collateral/CCICRIcontrol.htm",
+  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
+  covariate.labels=c("Divided government", "Binding one-term limit"," Binding two-term limit","Real per capita income ($1000)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues ($1000)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)","Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)")
+  )
+```
+
+```{r 3 stargazer controlled panel latex, results="asis", eval=TRUE}
+stargazer(CCIcontrol01,CCIcontrol02,CRIcontrol01,CRIcontrol02,
+  title = "Are campaign limits and correlated with corruption convictions or reflections?",
+  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
+  covariate.labels=c("Divided government", "Binding one-term limit"," Binding two-term limit","Real per capita income (thousands)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (thousands)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)","Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"),
+  font.size = "small",
+  header=FALSE,
+  column.sep.width = "-15pt",
+  no.space = T,
+  digits = 2, digits.extra = 2)
+```
+
+```{r stargazer DiD}
+stargazer(CCIDID01, CCIDID02, CCIDID03, CRIDID01, CRIDID02, CRIDID03,
+  type="text", 
+  title = "Do changes in limits lead to lower levels of corruption?",
+  out="collateral/DiD.htm",
+  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
+  covariate.labels=c("Individual limits removed","Individual limits imposed","Individual limit amount","Individual limits removed*amount","Individual limits imposed*amount",
+                     "PAC limits removed","PAC limits imposed","PAC limit amount","PAC limits removed*amount","PAC limits imposed*amount",
+                     "Individual-to-party limits removed","Individual-to-party limits imposed","Individual-to-party limit amount","Individual-to-party limits removed*amount","Individual-to-party limits imposed*amount"))
+
+```
+
+\blandscape
+```{r stargazer DiD latex, results="asis", eval=TRUE}
+stargazer(CCIDID01, CCIDID02, CCIDID03, CRIDID01, CRIDID02, CRIDID03,
+  title = "Do changes in limits lead to lower levels of corruption?",
+  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
+  covariate.labels=c("Individual limits removed","Individual limits imposed","Individual limit amount","Individual limits removed*amount","Individual limits imposed*amount",
+                     "PAC limits removed","PAC limits imposed","PAC limit amount","PAC limits removed*amount","PAC limits imposed*amount",
+                     "Individual-to-party limits removed","Individual-to-party limits imposed","Individual-to-party limit amount","Individual-to-party limits removed*amount","Individual-to-party limits imposed*amount"),
+  font.size = "small", 
+  header = FALSE,
+  column.sep.width = "-15pt",
+  digits = 2, digits.extra = 2,
+  no.space = TRUE)
+
+```
+\elandscape
+
 old code -->

### 2018-12-18 Paper 2019.Rmd
Trying to understand gitignore again

@@
 ```
+
 ### Model II: Difference-in-Difference Model
@@
 <!-- Old code
-```{r panel modeling, eval=F}
+```{r panel modeling}
 ## CCI 
@@
 
-```{r (old) controlled panel modeling, eval=F}
+```{r (old) controlled panel modeling}
 #Next: Panel model of corruption against unemployment and high school? 
@@
 
-```{r controlled panel modeling, eval=F}
+```{r controlled panel modeling}
 
@@
 
-```{r post-Lentz panel effects modeling 1, eval=F}
+```{r post-Lentz panel effects modeling 1}
 # Include lagged dependent variables here. 
@@
 
-```{r stargazer CCI latex, results="asis", eval=TRUE}
+```{r stargazer CCI latex, results="asis"}
 stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,
@@
 
-```{r stargazer CRI latex, results="asis", eval=TRUE}
+```{r stargazer CRI latex, results="asis"}
 stargazer(CRIreg1, CRIreg2, CRIreg3, CRIreg5,
@@
 
-```{r stargazer controlled panel, eval=F}
+```{r stargazer controlled panel}
 stargazer(CCIcontrol01,CCIcontrol02,CRIcontrol01,CRIcontrol02,
@@
 
-```{r 3 stargazer controlled panel latex, results="asis", eval=TRUE}
+```{r 3 stargazer controlled panel latex, results="asis"}
 stargazer(CCIcontrol01,CCIcontrol02,CRIcontrol01,CRIcontrol02,
@@
 \blandscape
-```{r stargazer DiD latex, results="asis", eval=TRUE}
+```{r stargazer DiD latex, results="asis"}
 stargazer(CCIDID01, CCIDID02, CCIDID03, CRIDID01, CRIDID02, CRIDID03,

### 2018-12-18 Paper 2019.Rmd
Running out of steam, time to go climb

@@
 title: | 
-  | UNDER CONSTRUCTION 
+  | [UNDER CONSTRUCTION]
   | Campaign Contribution Limits and Corruption: 
@@
 Sorrell_, 2006).
-
 <!--Those rulings have often been driven by the question of corporations’ participation in the political process.
@@
 
-<!--Add in summary statistics here. 
-Plot of something over time? Histograms? Correlations? 
--->
-```{r Barber summary, eval=TRUE}
+*Add Barber Summary*
+*Test Barber correlations?* Maybe not necessary 
+<!--Add in summary statistics here. Plot of something over time? Histograms? Correlations? -->
+```{r Barber summary}
 descr(Barber)
@@
 
+*Add CCI summary* 
 <!--clean these up--> 
-
-```{r CCI summary, eval=TRUE}
+```{r CCI summary}
 descr(convictions)
@@
 <!--clean these up--> 
-
-```{r CRI summary, eval=TRUE}
+*Add CRI summary* 
+```{r CRI summary}
 descr(reflections)
@@
 <!--Test whether these are correlated?--> 
-
-```{r CCI and CRI correlations }
+*Test CRI and CCI correlations?* 
+```{r CCI and CRI correlations}
 ggplot(BarberICC, aes(CCI,CRI)) + geom_point() + theme_minimal() + geom_abline()
@@
 ####Corruption Convictions Index versus campaign contribution limits in a given state-year: 
+*Edit these*
 
@@
 ####Corruption Reflections Index versus campaign contributions in a given state-year: 
-
+*Edit these* 
 $Reflections = \alpha + \beta_{indiv.dummy} + \beta_{indiv.dummy}*\beta_{indiv.limit} + \beta_{pac.dummy} + \beta_{pac.dummy}*\beta_{pac.limit} + \beta_{indiv-to-party.dummy} + \beta_{indiv-to-party.dummy}*\beta_{indiv-to-party.limit} + \epsilon$
@@
 These include controlling for the size and education levels of the population, the ideology of a population, income levels and inequality, education levels, the number and relative income of government employees, and urbanization.
-Building a model of corruption that includes variables previously demonstrated to be correlated with corruption levels, then adding in campaign finance data, can better identify the association of campaign finance laws with corruption levels.
-
-```{r modeling of CCI base model effects, eval=F}
-# Base model with no fixed or random effects 
+Building a model of corruption that includes variables previously demonstrated to be correlated with corruption levels, then adding in campaign finance data, I can better identify the association of campaign finance laws with corruption levels.
+
+```{r modeling of initial correlations (with fixed effects), eval=T}
+## CCI 
+# Individual limits and corruption
+CCIreg1  <- plm(CCI ~ ind_limits_2010*ind_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
+# No signifigance
+
+# Individual-to-party limits and corruption
+CCIreg2  <- plm(CCI ~ ind2pty_limits_2010*ind2pty_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
+# No Signifigance
+
+# PAC Limits and corruption
+CCIreg3  <- plm(CCI ~ pac_limits_2010*pac_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
+# No Signifigance
+
+# Total Limits and corruption
+CCIreg4  <- plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
+# One star. Hmm...
+
+# Everybody? 
+CCIreg5 <- plm(CCI ~ ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = BarberICC, index = c("st","year"), effect="twoways")
+
+## CRI
+CRIreg1  <- plm(CRI ~ ind_limits_2010*ind_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
+# No signifigance
+
+# Individual-to-party limits and reflection
+CRIreg2  <- plm(CRI ~ ind2pty_limits_2010*ind2pty_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
+# One star. Hmm...
+
+# PAC Limits and reflection
+CRIreg3  <- plm(CRI ~ pac_limits_2010*pac_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
+# No Signifigance
+
+# All Limits and reflection
+CRIreg4  <- plm(CRI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
+# No Signifigance
+
+# Everybody? 
+CRIreg5 <- plm(CRI ~ ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = BarberICC, index = c("st","year"), effect="twoways")
+```
+
+```{r output of initial correlations (with fixed effects), include=F}
+stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,CRIreg1, CRIreg2, CRIreg3, CRIreg5,
+  type="text", 
+  title = "Appendix A: Are campaign limits correlated with corruption convictions or reflections?",
+  out="collateral/AppendixA.htm",
+  dep.var.labels = c("Corruption Convictions Index","Corruption Reflections Index"),
+  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"),
+  add.lines = list(c("Effects","Two-Way","Two-Way","Two-Way","Two-Way","Two-Way","Two-Way","Two-Way","Two-Way"))
+  )
+```
+
+```{r modeling of CCI base model effects, eval=T}
+# Base model with no Two-Way or random effects 
  cci.base.pooled <- plm(CCI ~ jdiv  # Divided government 
@@
   # system is computationally singular: reciprocal condition number = 1.96767e-18
-
-# Hausman for base model 
+```
+
+```{r Hausman for CCI base model, eval=F}
 phtest(cci.base.pooled, cci.base.fixed, cci.base.random, cci.base.fixed.time)
-```
-
-```{r output of CCI base model effects, eval=F}
+
+```
+
+```{r output of CCI base model effects}
 stargazer(cci.base.pooled, 
@@
 
-```{r modeling of CRI base model effects, eval=F}
+```{r modeling of CRI base model effects, eval=T}
 # Base model with no fixed or random effects 
@@
                    effect = "twoways")
-
-# Hausman for base model 
+```
+
+```{r Hausman for CRI base model, eval=F}
 phtest(cri.base.pooled, cri.base.fixed, cri.base.random, cri.base.fixed.time)
@@
 
-```{r output of CRI base model effects, eval=F}
+```{r output of CRI base model effects}
 stargazer(cri.base.pooled, 
@@
 
-```{r modeling of CCI with campaign finance variables, eval=F}
+```{r modeling of CCI with campaign finance variables, eval=T}
 # Base model with no fixed or random effects 
@@
 
-# Hausman for base model 
+```
+
+```{r Hausman test for CCI with campaign finance variables, eval=F}
 phtest(cci.limits.pooled, cci.limits.fixed, cci.limits.random, cci.limits.fixed.time)
@@
 
-```{r output of CCI with campaign finance variables, eval=F}
+```{r output of CCI with campaign finance variables}
 stargazer(cci.limits.pooled, 
@@
 
-```{r modeling of CRI with campaign finance variables, eval=F}
+```{r modeling of CRI with campaign finance variables, eval=T}
 # Base model with no fixed or random effects 
@@
                    effect = "twoways")
-
-# Base model with random effects doesn't work: 
-# Error in solve.default(crossprod(ZBmu)) : 
-  # system is computationally singular: reciprocal condition number = 1.96767e-18
-
-# Hausman for base model 
+```
+
+```{r Hausman test for CRI with campaign finance variables, eval=F}
 phtest(cri.limits.pooled, cri.limits.fixed, cri.limits.random, cri.limits.fixed.time)
@@
 
-```{r output of CRI with campaign finance variables, eval=F}
+```{r output of CRI with campaign finance variables}
 stargazer(cri.limits.pooled, 
@@
           type="text",
-          title = "Are the presence or amounts of campaign limits correlated with corruption convictions?",
+          title = "Table 1: Are the presence or amounts of campaign limits correlated with corruption convictions?",
           out="collateral/CCI.htm",
@@
           type="text",
-          title = "Are the presence or amounts of campaign limits correlated with the Corruption Reflections Index?",
+          title = "Table 2: Are the presence or amounts of campaign limits correlated with the Corruption Reflections Index?",
           out="collateral/CRI.htm",
@@
 ### Modeling campaign limits and corruption arrests 
-The results of the initial panel regressions reveal no correlation between state-level campaign contribution limits and corruption, with one exception: There is a statistically significant relationship between the presence of individual-to-party limits and the Corruption Reflections Index.
-
-The first set of models (Table 1) measures the association of various campaign contribution limits with the Corruption Convictions Index.
+*(rework based on which tables you'll show)*
+The results of the panel regressions reveal no correlation between state-level campaign contribution limits and corruption, with one exception: There is a statistically significant relationship between the presence of individual-to-party limits and the Corruption Reflections Index.
+
+The first set of models (Table X) measures the association of various campaign contribution limits with the Corruption Convictions Index.
 The sign of each coefficient is negative, indicating that the presence of limits is associated with lower corruption levels, but that where limits exist, higher (weaker) donation limits are associated with lower levels of corruption.
@@
 
-The second set of models (Table 2) also fails to find a relationship between state-level campaign contribution limits and media mentions of corruption as measured by the Corruption Reflections Index, with one exception: The presence of limits on what an individual can give to a party is associated with a 0.10 point decline in the Corruption Reflection Index.
+The second set of models (Table X) also fails to find a relationship between state-level campaign contribution limits and media mentions of corruption as measured by the Corruption Reflections Index, with one exception: The presence of limits on what an individual can give to a party is associated with a 0.10 point decline in the Corruption Reflection Index.
 The Corruption Reflections Index operates on a scale of zero to one (with a few outlying exceptions), indicating that the presence of individual-to-party limits is associated with a 10% decrease in the index.
 
-The third set of models (Table 3) incorporates a number of control variables in order to isolate the effect of campaign finance laws on corruption arrest levels.
+The third set of models (Table X) incorporates a number of control variables in order to isolate the effect of campaign finance laws on corruption arrest levels.
 As in the models above, the only correlation significant at the p<0.05 level is the presence of limits on what an individual can give to a party.
@@
 
-The final set of models (Table 4) displays results from multiple difference-in-difference models designed to isolate the effect of changes in campaign finance laws on corruption arrests.
+The final set of models (Table X) displays results from multiple difference-in-difference models designed to isolate the effect of changes in campaign finance laws on corruption arrests.
 None of the models find correlation between campaign finance limits and either corruption convictions or corruption reflections.
 
-##Discussion
+## Discussion
 At least one group of models allows for a straightforward interpretation.
@@
 
-##Conclusion
+## Conclusion
 There at least two distinct and opposing ways to explain these results, viewpoints that will come into direct and public conflict if the Court chooses to hear a first amendment challenge to campaign contribution limits.
@@
 \newpage
-##Appendix A: Descriptions of Control Variables
+
+\newpage
+\blandscape
+
+## Appendix A: Initital modeling of independent and dependent variables
+
+*Clean up*
+
+```{r output of initial correlations, results="asis", eval=T}
+stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,CRIreg1, CRIreg2, CRIreg3, CRIreg5,
+  title = "Appendix A: Are campaign limits correlated with corruption convictions or reflections?",
+  type="latex",
+  dep.var.labels = c("Corruption Convictions Index","Corruption Reflections Index"),
+  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"),
+  add.lines = list(c("Effects","Two-Way","Two-Way","Two-Way","Two-Way","Two-Way","Two-Way","Two-Way","Two-Way")),
+  font.size = "small",
+  header = FALSE,
+  column.sep.width = "-5pt",
+  digits = 2, digits.extra = 0,
+  no.space = TRUE, 
+  omit.stat = "f"
+  )
+```
+\elandscape
+
+\newpage
+##Appendix B: Descriptions of Control Variables
 In their 2006 paper "Corruption in America," Glaeser and Saks make use of the following control variables, which we have included here:
@@
 <!-- Old code
-```{r panel modeling}
-## CCI 
-# Individual limits and corruption
-CCIreg1  <- plm(CCI ~ ind_limits_2010*ind_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
-# No signifigance
-
-# Individual-to-party limits and corruption
-CCIreg2  <- plm(CCI ~ ind2pty_limits_2010*ind2pty_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
-# No Signifigance
-
-# PAC Limits and corruption
-CCIreg3  <- plm(CCI ~ pac_limits_2010*pac_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
-# No Signifigance
-
-# Total Limits and corruption
-CCIreg4  <- plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
-# One star. Hmm...
-
-# Everybody? 
-CCIreg5 <- plm(CCI ~ ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = BarberICC, index = c("st","year"), effect="twoways")
-
-## CRI
-CRIreg1  <- plm(CRI ~ ind_limits_2010*ind_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
-# No signifigance
-
-# Individual-to-party limits and reflection
-CRIreg2  <- plm(CRI ~ ind2pty_limits_2010*ind2pty_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
-# One star. Hmm...
-
-# PAC Limits and reflection
-CRIreg3  <- plm(CRI ~ pac_limits_2010*pac_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
-# No Signifigance
-
-# All Limits and reflection
-CRIreg4  <- plm(CRI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
-# No Signifigance
-
-# Everybody? 
-CRIreg5 <- plm(CRI ~ ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = BarberICC, index = c("st","year"), effect="twoways")
-```
 
@@
 
-```{r stargzer CCI html}
-stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,
-  type="text", 
-  title = "Are campaign limits and corruption convictions correlated?",
-  out="collateral/CCI.htm",
-  dep.var.labels = c("Corruption Convictions Index"),
-  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
-```
-
 ```{r stargazer CCI latex, results="asis"}
@@
 
-```{r stargazer CRI html, eval=F}
+```{r stargzer CCI html}
+stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,
+  type="text", 
+  title = "Are campaign limits and corruption convictions correlated?",
+  out="collateral/CCI.htm",
+  dep.var.labels = c("Corruption Convictions Index"),
+  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
+```
+
+```{r stargazer CRI html}
 stargazer(CRIreg1, CRIreg2, CRIreg3, CRIreg5,

### 2018-12-19 Paper 2019.Rmd
Adding old paper for history

@@
 descr(convictions)
-# Barber histograms 
 convictions.plot <- ggplot(convictions, aes(CCI)) + geom_density() + theme_minimal()
 convictions.plot
+# FAIL convictions.time <- ggplot(convictions, aes(Year,CCI)) + stat_summary(fun.y = sum) + theme_minimal()
 ```

### 2019-01-02 Paper 2019.Rmd
Progress on summary statistics

--- 2018-12-18 Paper 2019.Rmd
@@
 library(summarytools) # For summary statistics 
+library(psych) # Also for summary statistics
 ```
@@
 I combine these measures with a third data set from Michael Barber’s 2016 work on campaign contribution limits and political polarization; and a fourth data set from James Alt and David Dryer Lassen, to provide controls for the full model (Alt and Lassen 2012).
-
 Barber’s data set is a panel of contribution limits from 1990-2012 for the lower house of every state legislature.
@@
 
-*Add Barber Summary*
-*Test Barber correlations?* Maybe not necessary 
-<!--Add in summary statistics here. Plot of something over time? Histograms? Correlations? -->
-```{r Barber summary}
-descr(Barber)
-# Barber histograms 
-ind_limits_2010.plot <- ggplot(Barber, aes(ind_limits_2010)) + geom_density() + theme_minimal()
-ind_limits_2010.plot
-ind2pty_limits_2010.plot <- ggplot(Barber, aes(ind2pty_limits_2010)) + geom_density() + theme_minimal()
-ind_limits_2010.plot
-pac_limits_2010.plot <- ggplot(Barber, aes(pac_limits_2010)) + geom_density() + theme_minimal()
-
-# Correlation matrix? 
-pairs(Barber[3:7])
-# Doesn't make sense, because of use of 99,999s. 
+#### Insert Barber Summary Statistics Here. 
+```{r Barber summary, eval=F}
+# This is a summary it, but includes all the 99999s and doesn't have skew in it. 
+stargazer(as.data.frame(subset(Barber[,3:6])), type="text", digits=0)
+
+# This replaces all the 99999s. 
+BarberNAs <- Barber %>% dplyr::na_if(99999)
+
+# These are (highly skewed) histograms of the remaining values 
+ind_limits_2010.plot <- ggplot(BarberNAs, aes(ind_limits_2010)) + geom_density() + theme_minimal()
+ind2pty_limits_2010.plot <- ggplot(BarberNAs, aes(ind2pty_limits_2010)) + geom_density() + theme_minimal()
+pac_limits_2010.plot <- ggplot(BarberNAs, aes(pac_limits_2010)) + geom_density() + theme_minimal()
+
+# How about correlations? Unclear what this shows us. 
+pairs(BarberNAs[3:6])
+
+# This is a summary table for all the non-99999 values. 
+stargazer(as.data.frame(subset(BarberNAs[,3:6])), type="text", digits=0, title="Descriptive Statistics (n=1150 state-years)", covariate.labels = c("Individual Limits","Individual-to-Party Limits","Party Limits", "PAC Limits"))
+# How do I get this printed?
+
+# An alternative, perhaps to combine if I can figure out how to print: 
+# psych::describe(subset(BarberNAs[,3:6]))
 ```
@@
 This measure of corruption is widely used in academic research, though not without criticism.
-
-*Add CCI summary* 
-<!--clean these up--> 
-```{r CCI summary}
-descr(convictions)
-# Barber histograms 
-convictions.plot <- ggplot(convictions, aes(CCI)) + geom_density() + theme_minimal()
-convictions.plot
-```
+Descriptive statistics for corruption convictions are included below.
 
@@
 
-<!--clean these up--> 
-*Add CRI summary* 
-```{r CRI summary}
-descr(reflections)
-# Barber histograms 
-reflections.plot <- ggplot(reflections, aes(CRI)) + geom_density() + theme_minimal()
-reflections.plot
-```
-
-<!--Test whether these are correlated?--> 
-*Test CRI and CCI correlations?* 
-```{r CCI and CRI correlations}
-ggplot(BarberICC, aes(CCI,CRI)) + geom_point() + theme_minimal() + geom_abline()
+#### Insert CRI and CCI Summary Statistics Here  
+```{r CRI summary, eval=F}
+stargazer(as.data.frame(subset(corruption[,c(3,6)])), type="text", digits=2, title="Descriptive Statistics of Corruption and Reflections", covariate.labels = c("Corruption Convictions Index (CCI)","Corruption Reflections Index (CRI)"))
+
+# Next: How to demonstrate skew? # Test whether these are correlated? 
+# ggplot(BarberICC, aes(CCI,CRI)) + geom_point() + theme_minimal() + geom_abline()
 ```
@@
 
-##Methods
+## Methods
 ### Model I: Panel Regression
@@
 After performing this transformation on all three independent variables, I test two initial sets of models: (1) Corruption Convictions Index versus campaign contribution limits in a given state-year, and (2) Corruption Reflections Index versus campaign contributions in a given state-year.
-
-<!--Edit specifications--> 
-####Corruption Convictions Index versus campaign contribution limits in a given state-year: 
-*Edit these*
-
-$Convictions = \alpha + \beta_{indiv.dummy} + \beta_{indiv.dummy}*\beta_{indiv.limit} + \beta_{pac.dummy} + \beta_{pac.dummy}*\beta_{pac.limit} + \beta_{indiv-to-party.dummy} + \beta_{indiv-to-party.dummy}*\beta_{indiv-to-party.limit} + \epsilon$
-
-####Corruption Reflections Index versus campaign contributions in a given state-year: 
-*Edit these* 
-$Reflections = \alpha + \beta_{indiv.dummy} + \beta_{indiv.dummy}*\beta_{indiv.limit} + \beta_{pac.dummy} + \beta_{pac.dummy}*\beta_{pac.limit} + \beta_{indiv-to-party.dummy} + \beta_{indiv-to-party.dummy}*\beta_{indiv-to-party.limit} + \epsilon$
+The models are are as follows:
+
+#### Corruption Convictions Index versus campaign contribution limits in a given state-year: 
+$Convictions = \alpha_{state} + \beta_{1}{indiv.dummy} + \beta_{2}{indiv.dummy}*{indiv.limit} + \beta_{3}{pac.dummy} + \beta_{4}{pac.dummy}*{pac.limit} + \beta_{5}{indiv-to-party.dummy} + \beta_{6}{indiv-to-party.dummy}*{indiv-to-party.limit} + Controls + \epsilon$
+
+#### Corruption Reflections Index versus campaign contributions in a given state-year: 
+$Reflections = \alpha_{state} + \beta_{1}{indiv.dummy} + \beta_{2}{indiv.dummy}*{indiv.limit} + \beta_{3}{pac.dummy} + \beta_{4}{pac.dummy}*{pac.limit} + \beta_{5}{indiv-to-party.dummy} + \beta_{6}{indiv-to-party.dummy}*{indiv-to-party.limit} + Controls + \epsilon$
 
@@
 *Clean up*
-
 ```{r output of initial correlations, results="asis", eval=T}
@@
 \newpage
-##Appendix B: Descriptions of Control Variables
+##Appendix B: Descriptions and Descriptive Statistics of Control Variables
 In their 2006 paper "Corruption in America," Glaeser and Saks make use of the following control variables, which we have included here:
+
+* Divided government
+* Binding one-term limit
+* Binding two-term limit
+* Real per capita income ($1000)
+* AUSAs per million population
+* Unemployment
+* Citizen ideology measure
+* Percent high school graduates
+* Real per capita gov revenues ($1000)
+* Inequality: Male wages
+* Relative government wages
+* Urbanization
+* Log of population (millions)
+
+#### Include Descriptive Statistics Here
+```{r Alt and Lassen summary, eval=F}
+stargazer(as.data.frame(subset(AltLassen[,c("jdiv","bindingonetermlimit","bindingtwotermlimit","rpcinc_annual_new","eopop","unemp","citi6006","high_school","rgenrevpc","men_ineqincwag","grelimp","urbanization_2","logpop")])), type="text", digits=2, title="Descriptive Statistics of Control Variables", covariate.labels = c("Divided government","Binding one-term limit","Binding two-term limit","Real per capita income ($1000)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues ($1000)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)"))
+```
 

### 2019-01-03 Paper 2019.Rmd
Getting summaries printed, with thanks to Matt Worthington

@@
 library(stargazer) # For regression outputs #fail 
-library(texreg) # For regression outputs #fail 
-library(kableExtra) # For regression outputs 
-library(broom) # Because Matt Worthington said so 
 library(knitr) # Because Matt Worthington said so 
-library(summarytools) # For summary statistics 
-library(psych) # Also for summary statistics
+library (MASS) # For binomial regression 
+library(pglm) # For panel + binomial 
+# library(psych) # Also for summary statistics
+# library(texreg) # For regression outputs #fail 
+# library(kableExtra) # For regression outputs 
+# library(broom) # Because Matt Worthington said so 
+# library(summarytools) # For summary statistics 
 ```
@@
 
-#### Insert Barber Summary Statistics Here. 
-```{r Barber summary, eval=F}
+```{r Barber summary, eval=T}
 # This is a summary it, but includes all the 99999s and doesn't have skew in it. 
-stargazer(as.data.frame(subset(Barber[,3:6])), type="text", digits=0)
+# stargazer(as.data.frame(subset(Barber[,3:6])), type="text", digits=0)
 
@@
 # How about correlations? Unclear what this shows us. 
-pairs(BarberNAs[3:6])
-
-# This is a summary table for all the non-99999 values. 
-stargazer(as.data.frame(subset(BarberNAs[,3:6])), type="text", digits=0, title="Descriptive Statistics (n=1150 state-years)", covariate.labels = c("Individual Limits","Individual-to-Party Limits","Party Limits", "PAC Limits"))
-# How do I get this printed?
+# pairs(BarberNAs[3:6])
 
@@
 # psych::describe(subset(BarberNAs[,3:6]))
+
+# This is a summary table for all the state-years where limits exist:  
+# stargazer(as.data.frame(subset(BarberNAs[,3:6])), type="text", digits=0, title="Descriptive Statistics (n=1150 state-years)", covariate.labels = c("Individual Limits","Individual-to-Party Limits","Party Limits", "PAC Limits"))
+```
+
+```{r Barber summary statistics fail, results="asis", eval=TRUE}
+# This is what fails to knit (see error below)
+stargazer(as.data.frame(subset(BarberNAs[,3:6])), digits=0, type="latex", title="Descriptive Statistics for State Level Campaign Finance Limits (n=1150 state-years)", covariate.labels = c("Individual Limits","Individual-to-Party Limits","Party Limits", "PAC Limits"), header=F)
 ```
@@
 
-#### Insert CRI and CCI Summary Statistics Here  
-```{r CRI summary, eval=F}
-stargazer(as.data.frame(subset(corruption[,c(3,6)])), type="text", digits=2, title="Descriptive Statistics of Corruption and Reflections", covariate.labels = c("Corruption Convictions Index (CCI)","Corruption Reflections Index (CRI)"))
+```{r CRI summary, results="asis", eval=T}
+stargazer(as.data.frame(subset(corruption[,c(3,6)])), type="latex", digits=2, title="Descriptive Statistics for Corruption and Reflections", covariate.labels = c("Corruption Convictions Index (CCI)","Corruption Reflections Index (CRI)"), header=F)
 
@@
 
-```{r Hausman test for CRI with campaign finance variables, eval=F}
+```{r Hausman test for CRI with campaign finance variables}
 phtest(cri.limits.pooled, cri.limits.fixed, cri.limits.random, cri.limits.fixed.time)
@@
 ```
+
+```{r Empty, Binomial, and Poisson models}
+# First, trying to run the model above but with the pglm() package
+# pglm(formula, data, subset, na.action, effect = c("individual", "time", "twoways"), model = c("random", "pooling", "within", "between"), family, other = NULL, index = NULL, start = NULL, R = 20, ...)
+
+# Initial correlations of independent variables with CCI 
+pglm(CCI ~ ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = BarberICC, model = "within", index = c("st","year"), effect = "twoways", family = gaussian)
+# Return code 100: Initial value out of range. May have something to do with the interaction terms, because when I strip those out, the model at least returns something.
+
+# What about Cale's empty model? 
+cci.empty.pooling <- plm(CCI ~ st + year,
+                   data = AltBarber, 
+                   model="pooling")
+summary(cci.empty.pooling)
+
+cci.empty.within <- plm(CCI ~ st + year,
+                   data = AltBarber, 
+                   model="within")
+summary(cci.empty.within)
+
+# Verifying that I didn't screw up by not having st and year as variables in my preivous model 
+cci.base.fixed.time.redo <- plm(CCI ~ st + year 
+                   + jdiv  # Divided government
+                   + bindingonetermlimit # Binding one-term limit 
+                   + bindingtwotermlimit # Binding two-term limit 
+                   + rpcinc_annual_new # Real per capita income ($1000)
+                   + eopop # AUSAs per million population
+                   + unemp # Unemployment 
+                   + citi6006 # Citizen ideology measure 
+                   + high_school + # Percent high school graduates
+                   + rgenrevpc # Real per capita gov revenues ($1000)
+                   + men_ineqincwag # Inequality: Male wages
+                   + grelimp # Relative government wages
+                   + urbanization_2 # Urbanization 
+                   + logpop, # Log of population (millions)
+                   data = AltBarber, 
+                   model="within", 
+                   effect = "twoways")
+# stargazer(cci.base.fixed.time, cci.base.fixed.time.redo, type="text")
+```
+
+### Model II: Difference-in-Difference Model
+<!--Add specification, formulas?-->
+Even if the panel models above fail to capture correlation between state level campaign finance laws and corruption arrests, it could be the case that changes in campaign finance laws, rather than relative campaign finance limits, are correlated with decreases in corruption.
+A difference-in-difference regression can help identify this by comparing the state-years in which campaign finance laws changed to state-years where they remained constant.
+If tighter campaign finance laws are correlated with lower corruption levels, then a change in one year should lead to lower corruption convictions in the years following.
+
+<!--add something to show what change occurred-->
+
+```{r DiD wrangling, eval=T}
+BarberICC %>% arrange(year) %>% group_by(st) %>% mutate(
+  ind_d = (ind_limits_2010 - dplyr::lag(ind_limits_2010)),
+  ind_dummy_d = (ind_limits_dummy - dplyr::lag(ind_limits_dummy)),
+  pac_d = (pac_limits_2010 - dplyr::lag(pac_limits_2010)),
+  pac_dummy_d = (pac_limits_dummy - dplyr::lag(pac_limits_dummy)),
+  ind2pty_d = (ind2pty_limits_2010 - dplyr::lag(ind2pty_limits_2010)),
+  ind2pty_dummy_d = (ind2pty_limits_dummy - dplyr::lag(ind2pty_limits_dummy))
+  ) -> testframe
+
+testframe %>% dplyr::select(1:2,8,11,3:7,12:21) -> DiDsmall
+
+# Now I have what I think are three multi-level categorical independent variables. 
+# https://stats.idre.ucla.edu/r/modules/coding-for-categorical-variables-in-regression-models/
+#1. When limits were imposed (1) or went down, did corruption go down? 
+#2. When limits were removed (-1) or went up, did corruption go up?
+
+DiDsmall$ind_dummy_f <- factor(DiDsmall$ind_dummy_d)
+DiDsmall <- within(DiDsmall, ind_dummy_f <- relevel(ind_dummy_f, ref = "0"))
+DiDsmall$pac_dummy_f <- factor(DiDsmall$pac_dummy_d)
+DiDsmall <- within(DiDsmall, pac_dummy_f <- relevel(pac_dummy_f, ref = "0"))
+DiDsmall$ind2pty_dummy_f <- factor(DiDsmall$ind2pty_dummy_d)
+DiDsmall <- within(DiDsmall, ind2pty_dummy_f <- relevel(ind2pty_dummy_f, ref = "0"))
+```
+
+```{r DiD modeling, eval=T}
+#summary(lm(CCI ~ ind_dummy_f, data = DiDsmall))
+#summary(lm(CCI ~ pac_dummy_f, data = DiDsmall))
+#summary(lm(CCI ~ ind2pty_dummy_f, data = DiDsmall))
+#summary(lm(CRI ~ ind_dummy_f, data = DiDsmall))
+#summary(lm(CRI ~ pac_dummy_f, data = DiDsmall))
+#summary(lm(CRI ~ ind2pty_dummy_f, data = DiDsmall))
+# No effects
+
+CCIDID01 <- lm(CCI ~ ind_dummy_f*ind_d, data = DiDsmall)
+# Erin: What this doesn't have is an average treatment effect. So add the interaction of the dummy variable of the change having happened and the law occurring. Time dummy, maybe? 
+CCIDID02 <- lm(CCI ~ pac_dummy_f*pac_d, data = DiDsmall)
+CCIDID03 <- lm(CCI ~ ind2pty_dummy_f*ind2pty_d, data = DiDsmall)
+
+CRIDID01 <- lm(CRI ~ ind_dummy_f*ind_d, data = DiDsmall)
+CRIDID02 <- lm(CRI ~ pac_dummy_f*pac_d, data = DiDsmall)
+CRIDID03 <- lm(CRI ~ ind2pty_dummy_f*ind2pty_d, data = DiDsmall)
+# No effects 
+# Next: Lag?  
+```
+
+```{r post-Lentz DID effects modeling, eval=F}
+# From Erin: 
+# •	Again, writing out a model for the D-in-D in Table 4 might help readers to understand what is being isolated. Right now, I’m not sure I fully follow the estimation choices.
+# o	At a minimum, the state-level control variables changed during this time (and hence wouldn’t get differenced out), and ought to be included.
+# o	Column 1 (and 2): the large standard errors on individual limits removed and imposed suggest multicollinearity and needs to be investigated. 
+# Are presence of campaign finance laws in a state year associated with a different level of corruption? No, according to that panel model. 
+# Consider adding state fixed effects to the DiD model, for robustness. 
+```
+
+##Results 
+### Modeling campaign limits and corruption arrests 
+The results of the panel regressions reveal no correlation between state-level campaign contribution limits and corruption, with one exception: There is a statistically significant relationship between the presence of individual-to-party limits and the Corruption Reflections Index.
+
+The first set of models (Table X) measures the association of various campaign contribution limits with the Corruption Convictions Index.
+The sign of each coefficient is negative, indicating that the presence of limits is associated with lower corruption levels, but that where limits exist, higher (weaker) donation limits are associated with lower levels of corruption.
+None of those results are significant at the p<0.05 level, however, meaning that we cannot claim their effect is statistically distinguishable from zero.
+I interpret these results as showing no relationship between the presence or amount of state-level contribution limits and levels of corruption as measured by the Corruption Convictions Index.
+
+The second set of models (Table X) also fails to find a relationship between state-level campaign contribution limits and media mentions of corruption as measured by the Corruption Reflections Index, with one exception: The presence of limits on what an individual can give to a party is associated with a 0.10 point decline in the Corruption Reflection Index.
+The Corruption Reflections Index operates on a scale of zero to one (with a few outlying exceptions), indicating that the presence of individual-to-party limits is associated with a 10% decrease in the index.
+
+The third set of models (Table X) incorporates a number of control variables in order to isolate the effect of campaign finance laws on corruption arrest levels.
+As in the models above, the only correlation significant at the p<0.05 level is the presence of limits on what an individual can give to a party.
+As above, the presence of limits in what an individual can give to a party is associated with a decline in the Corruption Reflections Index.
+
+### Modeling changes in campaign limits and corruption arrests
+
+The final set of models (Table X) displays results from multiple difference-in-difference models designed to isolate the effect of changes in campaign finance laws on corruption arrests.
+None of the models find correlation between campaign finance limits and either corruption convictions or corruption reflections.
 
@@
 
-```{r CRI output to table}
+```{r CCI output to table latex, results="asis", eval=T}
+# Maaaaaybe figure out how to add back in those $ signs. 
+stargazer(cci.base.pooled, 
+          cci.limits.pooled, 
+          cci.limits.fixed,
+          cci.limits.fixed.time, 
+          type="latex",
+          title = "Are the presence or amounts of campaign limits correlated with corruption convictions?",
+          dep.var.labels = "Corruption Convictions Index",
+          covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)","Divided government","Binding one-term limit","Binding two-term limit","Real per capita income (1000s)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (1000s)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)"),
+  add.lines = list(c("Effects","Pooled","Pooled","Fixed","Two-Way")),     
+  header=FALSE, 
+  font.size = "small",
+  # column.sep.width = "-5pt",
+  digits = 2, digits.extra = 0,
+  no.space = TRUE,
+  omit.stat = "f"
+  )
+
+```
+
+```{r CRI output to table latex, results="asis", eval=T}
 stargazer(cri.base.pooled, 
@@
           cri.limits.fixed.time, 
-          type="text",
-          title = "Table 2: Are the presence or amounts of campaign limits correlated with the Corruption Reflections Index?",
-          out="collateral/CRI.htm",
+          type="latex",
+          title = "Are the presence or amounts of campaign limits correlated with the Corruption Reflections Index?",
           dep.var.labels = "Corruption Convictions Index",
-          covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)","Divided government","Binding one-term limit","Binding two-term limit","Real per capita income ($1000)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues ($1000)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)"),
-          add.lines = list(c("Effects","Pooled","Pooled","Fixed","Two-Way"))
+          covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)","Divided government","Binding one-term limit","Binding two-term limit","Real per capita income (1000s)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (1000s)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)"),
+          add.lines = list(c("Effects","Pooled","Pooled","Fixed","Two-Way")),
+  header=FALSE, 
+  font.size = "small",
+  # column.sep.width = "-5pt",
+  digits = 2, digits.extra = 0,
+  no.space = TRUE,
+  omit.stat = "f"
   )
 ```
-
-### Model II: Difference-in-Difference Model
-<!--Add specification, formulas?-->
-Even if the panel models above fail to capture correlation between state level campaign finance laws and corruption arrests, it could be the case that changes in campaign finance laws, rather than relative campaign finance limits, are correlated with decreases in corruption.
-A difference-in-difference regression can help identify this by comparing the state-years in which campaign finance laws changed to state-years where they remained constant.
-If tighter campaign finance laws are correlated with lower corruption levels, then a change in one year should lead to lower corruption convictions in the years following.
-
-<!--add something to show what change occurred-->
-
-```{r DiD wrangling, eval=T}
-BarberICC %>% arrange(year) %>% group_by(st) %>% mutate(
-  ind_d = (ind_limits_2010 - dplyr::lag(ind_limits_2010)),
-  ind_dummy_d = (ind_limits_dummy - dplyr::lag(ind_limits_dummy)),
-  pac_d = (pac_limits_2010 - dplyr::lag(pac_limits_2010)),
-  pac_dummy_d = (pac_limits_dummy - dplyr::lag(pac_limits_dummy)),
-  ind2pty_d = (ind2pty_limits_2010 - dplyr::lag(ind2pty_limits_2010)),
-  ind2pty_dummy_d = (ind2pty_limits_dummy - dplyr::lag(ind2pty_limits_dummy))
-  ) -> testframe
-
-testframe %>% dplyr::select(1:2,8,11,3:7,12:21) -> DiDsmall
-
-# Now I have what I think are three multi-level categorical independent variables. 
-# https://stats.idre.ucla.edu/r/modules/coding-for-categorical-variables-in-regression-models/
-#1. When limits were imposed (1) or went down, did corruption go down? 
-#2. When limits were removed (-1) or went up, did corruption go up?
-
-DiDsmall$ind_dummy_f <- factor(DiDsmall$ind_dummy_d)
-DiDsmall <- within(DiDsmall, ind_dummy_f <- relevel(ind_dummy_f, ref = "0"))
-DiDsmall$pac_dummy_f <- factor(DiDsmall$pac_dummy_d)
-DiDsmall <- within(DiDsmall, pac_dummy_f <- relevel(pac_dummy_f, ref = "0"))
-DiDsmall$ind2pty_dummy_f <- factor(DiDsmall$ind2pty_dummy_d)
-DiDsmall <- within(DiDsmall, ind2pty_dummy_f <- relevel(ind2pty_dummy_f, ref = "0"))
-```
-
-```{r DiD modeling, eval=T}
-#summary(lm(CCI ~ ind_dummy_f, data = DiDsmall))
-#summary(lm(CCI ~ pac_dummy_f, data = DiDsmall))
-#summary(lm(CCI ~ ind2pty_dummy_f, data = DiDsmall))
-#summary(lm(CRI ~ ind_dummy_f, data = DiDsmall))
-#summary(lm(CRI ~ pac_dummy_f, data = DiDsmall))
-#summary(lm(CRI ~ ind2pty_dummy_f, data = DiDsmall))
-# No effects
-
-CCIDID01 <- lm(CCI ~ ind_dummy_f*ind_d, data = DiDsmall)
-# Erin: What this doesn't have is an average treatment effect. So add the interaction of the dummy variable of the change having happened and the law occurring. Time dummy, maybe? 
-CCIDID02 <- lm(CCI ~ pac_dummy_f*pac_d, data = DiDsmall)
-CCIDID03 <- lm(CCI ~ ind2pty_dummy_f*ind2pty_d, data = DiDsmall)
-
-CRIDID01 <- lm(CRI ~ ind_dummy_f*ind_d, data = DiDsmall)
-CRIDID02 <- lm(CRI ~ pac_dummy_f*pac_d, data = DiDsmall)
-CRIDID03 <- lm(CRI ~ ind2pty_dummy_f*ind2pty_d, data = DiDsmall)
-# No effects 
-# Next: Lag?  
-```
-
-```{r post-Lentz DID effects modeling, eval=F}
-# From Erin: 
-# •	Again, writing out a model for the D-in-D in Table 4 might help readers to understand what is being isolated. Right now, I’m not sure I fully follow the estimation choices.
-# o	At a minimum, the state-level control variables changed during this time (and hence wouldn’t get differenced out), and ought to be included.
-# o	Column 1 (and 2): the large standard errors on individual limits removed and imposed suggest multicollinearity and needs to be investigated. 
-# Are presence of campaign finance laws in a state year associated with a different level of corruption? No, according to that panel model. 
-# Consider adding state fixed effects to the DiD model, for robustness. 
-```
-
-##Results 
-### Modeling campaign limits and corruption arrests 
-*(rework based on which tables you'll show)*
-The results of the panel regressions reveal no correlation between state-level campaign contribution limits and corruption, with one exception: There is a statistically significant relationship between the presence of individual-to-party limits and the Corruption Reflections Index.
-
-The first set of models (Table X) measures the association of various campaign contribution limits with the Corruption Convictions Index.
-The sign of each coefficient is negative, indicating that the presence of limits is associated with lower corruption levels, but that where limits exist, higher (weaker) donation limits are associated with lower levels of corruption.
-None of those results are significant at the p<0.05 level, however, meaning that we cannot claim their effect is statistically distinguishable from zero.
-I interpret these results as showing no relationship between the presence or amount of state-level contribution limits and levels of corruption as measured by the Corruption Convictions Index.
-
-The second set of models (Table X) also fails to find a relationship between state-level campaign contribution limits and media mentions of corruption as measured by the Corruption Reflections Index, with one exception: The presence of limits on what an individual can give to a party is associated with a 0.10 point decline in the Corruption Reflection Index.
-The Corruption Reflections Index operates on a scale of zero to one (with a few outlying exceptions), indicating that the presence of individual-to-party limits is associated with a 10% decrease in the index.
-
-The third set of models (Table X) incorporates a number of control variables in order to isolate the effect of campaign finance laws on corruption arrest levels.
-As in the models above, the only correlation significant at the p<0.05 level is the presence of limits on what an individual can give to a party.
-As above, the presence of limits in what an individual can give to a party is associated with a decline in the Corruption Reflections Index.
-
-### Modeling changes in campaign limits and corruption arrests
-
-The final set of models (Table X) displays results from multiple difference-in-difference models designed to isolate the effect of changes in campaign finance laws on corruption arrests.
-None of the models find correlation between campaign finance limits and either corruption convictions or corruption reflections.
 
@@
 ## Appendix A: Initital modeling of independent and dependent variables
-
-*Clean up*
 ```{r output of initial correlations, results="asis", eval=T}
 stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,CRIreg1, CRIreg2, CRIreg3, CRIreg5,
-  title = "Appendix A: Are campaign limits correlated with corruption convictions or reflections?",
+  title = "Are campaign limits correlated with corruption convictions or reflections?",
   type="latex",
@@
 
-#### Include Descriptive Statistics Here
-```{r Alt and Lassen summary, eval=F}
-stargazer(as.data.frame(subset(AltLassen[,c("jdiv","bindingonetermlimit","bindingtwotermlimit","rpcinc_annual_new","eopop","unemp","citi6006","high_school","rgenrevpc","men_ineqincwag","grelimp","urbanization_2","logpop")])), type="text", digits=2, title="Descriptive Statistics of Control Variables", covariate.labels = c("Divided government","Binding one-term limit","Binding two-term limit","Real per capita income ($1000)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues ($1000)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)"))
+```{r Alt and Lassen summary, results="asis", eval=T}
+stargazer(as.data.frame(subset(AltLassen[,c("jdiv","bindingonetermlimit","bindingtwotermlimit","rpcinc_annual_new","eopop","unemp","citi6006","high_school","rgenrevpc","men_ineqincwag","grelimp","urbanization_2","logpop")])),
+          type="latex", 
+          digits=2, 
+          title="Descriptive Statistics of Control Variables", 
+          covariate.labels = c("Divided government","Binding one-term limit","Binding two-term limit","Real per capita income (1000s)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (1000s)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)"),
+          header=FALSE,
+          font.size = "small",
+          column.sep.width = "-5pt",
+          # digits = 2, digits.extra = 0,
+          no.space = TRUE) 
 ```

### 2019-01-03 Paper 2019.Rmd
Minor cleanup

@@
 
-```{r Barber summary statistics fail, results="asis", eval=TRUE}
+```{r Barber summary statistics latex, results="asis", eval=TRUE}
 # This is what fails to knit (see error below)
@@
 
-```{r CRI summary, results="asis", eval=T}
+```{r CRI summary latex, results="asis", eval=T}
 stargazer(as.data.frame(subset(corruption[,c(3,6)])), type="latex", digits=2, title="Descriptive Statistics for Corruption and Reflections", covariate.labels = c("Corruption Convictions Index (CCI)","Corruption Reflections Index (CRI)"), header=F)
@@
 The fourth data set provides controls for the panel model.
-In their 2012 work examining variation in prosecutorial resources, Alt and Lassen follow Glaeser and Saks (2006) in controlling for income and education levels, size of government, legislature control, and urbanization (see Appendix A).
+In their 2012 work examining variation in prosecutorial resources, Alt and Lassen follow Glaeser and Saks (2006) in controlling for income and education levels, size of government, legislature control, and urbanization (see Appendix X).
 Alt and Lassen's data set runs from 1976-2004.
@@
 
-```{r Empty, Binomial, and Poisson models}
+```{r Empty, Binomial, and Poisson models FAIL}
 # First, trying to run the model above but with the pglm() package
@@
 None of the models find correlation between campaign finance limits and either corruption convictions or corruption reflections.
-
-```{r CCI output to table}
-stargazer(cci.base.pooled, 
-          cci.limits.pooled, 
-          cci.limits.fixed,
-          cci.limits.fixed.time, 
-          type="text",
-          title = "Table 1: Are the presence or amounts of campaign limits correlated with corruption convictions?",
-          out="collateral/CCI.htm",
-          dep.var.labels = "Corruption Convictions Index",
-          covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)","Divided government","Binding one-term limit","Binding two-term limit","Real per capita income ($1000)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues ($1000)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)"),
-          add.lines = list(c("Effects","Pooled","Pooled","Fixed","Two-Way"))
-          )
-```
 
@@
 \newpage
-
-\newpage
 \blandscape

### 2019-01-05 Paper 2019.Rmd
cleanup

@@
 title: | 
-  | [UNDER CONSTRUCTION]
   | Campaign Contribution Limits and Corruption: 
@@
 author: "Mark Hand"
-date: "5/23/2018"
+date: "01/06/2018"
 output: pdf_document
@@
 As current challenges to contribution limits wind their way through federal courts, the answer to this question will inform the Supreme Court’s decision to uphold or strike down remaining limits on political campaign contributions.
-Using state-level data from 1990-2012 on contribution limits, corruption arrests, and media mentions of corruption, this paper employs linear panel regression and difference-in-differences analyses to test whether campaign contribution limits are associated with lower levels of corruption convictions or media mentions of corruption.
-These methods find no relationship between the presence or level of campaign finance laws and quid pro quo corruption.
+Using state-level data from 1990-2012 on contribution limits, corruption arrests, and media mentions of corruption, this paper employs linear panel regression and first differences analyses to test whether campaign contribution limits are associated with lower levels of corruption convictions or media mentions of corruption.
+These methods find no relationship between the presence or level of campaign finance laws and quid pro quo corruption.[^SPSA]
+
+[^SPSA]: Working paper presented at the Annual Meeting of the Southern Political Science Association, January 2019.
 
@@
 \newpage
+
 ##Introduction
@@
 ## Methods
+
 ### Model I: Panel Regression
@@
 I include three predictor variables in both sets of models: Individual contribution limits, individual-to-party contribution limits, and PAC contribution limits.
-For each of these independent variables, I construct two variables to use in the model.
+For each of these independent variables, I construct two variables for use in the model.
 The first is a dummy variable indicating whether there are contribution limits in that state in that year, coded as “0” if there are no limits and “1” if there are.
@@
 After performing this transformation on all three independent variables, I test two initial sets of models: (1) Corruption Convictions Index versus campaign contribution limits in a given state-year, and (2) Corruption Reflections Index versus campaign contributions in a given state-year.
-The models are are as follows:
+These basic models are included in Appendix X.
+
+I build a model of political corruption using control variables previously demonstrated by Alt and Lassen to be correlated with corruption arrests, resulting in a data set covering 1990-2004, the period of overlap among the data sets listed above.
+These include controlling for the size and education levels of the population, the ideology of a population, income levels and inequality, education levels, the number and relative income of government employees, and urbanization.
+Building a model of corruption that includes variables previously demonstrated to be correlated with corruption levels, then adding in campaign finance data, I can better identify the association of campaign finance laws with corruption levels.
+For each of these models, I test fixed state and year effects and random effects.
+The models are as follows:
 
@@
 $Reflections = \alpha_{state} + \beta_{1}{indiv.dummy} + \beta_{2}{indiv.dummy}*{indiv.limit} + \beta_{3}{pac.dummy} + \beta_{4}{pac.dummy}*{pac.limit} + \beta_{5}{indiv-to-party.dummy} + \beta_{6}{indiv-to-party.dummy}*{indiv-to-party.limit} + Controls + \epsilon$
-
-As demonstrated below, this model fails to uncover any initial correlation between changes in campaign finance law and CCI or CRI scores.
-This may be due to the confounding effect of absent variables.
-In order to test that, I build a model of political corruption using control variables previously demonstrated to be correlated with corruption arrests, resulting in a data set covering 1990-2004, the period of overlap among the data sets listed above.
-These include controlling for the size and education levels of the population, the ideology of a population, income levels and inequality, education levels, the number and relative income of government employees, and urbanization.
-Building a model of corruption that includes variables previously demonstrated to be correlated with corruption levels, then adding in campaign finance data, I can better identify the association of campaign finance laws with corruption levels.
 
@@
 
-### Model II: Difference-in-Difference Model
-<!--Add specification, formulas?-->
-Even if the panel models above fail to capture correlation between state level campaign finance laws and corruption arrests, it could be the case that changes in campaign finance laws, rather than relative campaign finance limits, are correlated with decreases in corruption.
-A difference-in-difference regression can help identify this by comparing the state-years in which campaign finance laws changed to state-years where they remained constant.
-If tighter campaign finance laws are correlated with lower corruption levels, then a change in one year should lead to lower corruption convictions in the years following.
-
-<!--add something to show what change occurred-->
+### Model II: First Differences Model
+Even if the panel modeling above fails to capture correlation between state level campaign finance laws and corruption arrests, it could be the case that changes in campaign finance laws, rather than relative campaign finance limits, are correlated with decreases in corruption.
+In addition to the panel model above, I ran a first differences regression compare the state-years in which campaign finance laws changed to state-years where they remained constant.
+If tighter campaign finance laws are correlated with lower corruption levels, then a change in one year should be associated with lower CCI (corruption convictions) and CRI (reflections) in the years following.
 
@@
 # Erin: What this doesn't have is an average treatment effect. So add the interaction of the dummy variable of the change having happened and the law occurring. Time dummy, maybe? 
+# •	Again, writing out a model for the D-in-D in Table 4 might help readers to understand what is being isolated. Right now, I’m not sure I fully follow the estimation choices.
+# o	At a minimum, the state-level control variables changed during this time (and hence wouldn’t get differenced out), and ought to be included.
+# o	Column 1 (and 2): the large standard errors on individual limits removed and imposed suggest multicollinearity and needs to be investigated. 
+# Consider adding state fixed effects to the DiD model, for robustness.
+
 CCIDID02 <- lm(CCI ~ pac_dummy_f*pac_d, data = DiDsmall)
@@
 # No effects
+
 # Next: Lag?  
@@
 
-```{r post-Lentz DID effects modeling, eval=F}
-# From Erin: 
-# •	Again, writing out a model for the D-in-D in Table 4 might help readers to understand what is being isolated. Right now, I’m not sure I fully follow the estimation choices.
-# o	At a minimum, the state-level control variables changed during this time (and hence wouldn’t get differenced out), and ought to be included.
-# o	Column 1 (and 2): the large standard errors on individual limits removed and imposed suggest multicollinearity and needs to be investigated. 
-# Are presence of campaign finance laws in a state year associated with a different level of corruption? No, according to that panel model. 
-# Consider adding state fixed effects to the DiD model, for robustness. 
-```
-
 ##Results
+
 ### Modeling campaign limits and corruption arrests 
@@
 The first set of models (Table X) measures the association of various campaign contribution limits with the Corruption Convictions Index.
-The sign of each coefficient is negative, indicating that the presence of limits is associated with lower corruption levels, but that where limits exist, higher (weaker) donation limits are associated with lower levels of corruption.
-None of those results are significant at the p<0.05 level, however, meaning that we cannot claim their effect is statistically distinguishable from zero.
+The first model includes only control variables; the second model adds in campaign finance limit variables.
+The third layers in fixed effects at the state level, and the fourth incorporates fixed time effects.
+Not included are random effects models, which showed no improvement in the models.
+None of those results are significant at the p<0.05 level, implying that we cannot claim their effect is distinguishable from no effect.
 I interpret these results as showing no relationship between the presence or amount of state-level contribution limits and levels of corruption as measured by the Corruption Convictions Index.
 
-The second set of models (Table X) also fails to find a relationship between state-level campaign contribution limits and media mentions of corruption as measured by the Corruption Reflections Index, with one exception: The presence of limits on what an individual can give to a party is associated with a 0.10 point decline in the Corruption Reflection Index.
-The Corruption Reflections Index operates on a scale of zero to one (with a few outlying exceptions), indicating that the presence of individual-to-party limits is associated with a 10% decrease in the index.
-
-The third set of models (Table X) incorporates a number of control variables in order to isolate the effect of campaign finance laws on corruption arrest levels.
-As in the models above, the only correlation significant at the p<0.05 level is the presence of limits on what an individual can give to a party.
-As above, the presence of limits in what an individual can give to a party is associated with a decline in the Corruption Reflections Index.
+The second set of models (Table X) also fails to find a relationship between state-level campaign contribution limits and media mentions of corruption as measured by the Corruption Reflections Index, with one exception: The presence of limits on what an individual can give to a party is associated with a 0.11 point decline in the Corruption Reflections Index.
+The Corruption Reflections Index operates on a scale of zero to one (with a few outlying exceptions), indicating that the presence of individual-to-party limits is associated with a 11% decrease in the index.
 
@@
 
-The final set of models (Table X) displays results from multiple difference-in-difference models designed to isolate the effect of changes in campaign finance laws on corruption arrests.
+The final set of models (Table X) displays results from multiple first difference models designed to isolate the effect of changes in campaign finance laws on corruption arrests.
 None of the models find correlation between campaign finance limits and either corruption convictions or corruption reflections.
@@
           type="latex",
-          title = "Are the presence or amounts of campaign limits correlated with corruption convictions?",
+          title = "Panel Model of Campaign Finance Limits and Corruption Convictions",
           dep.var.labels = "Corruption Convictions Index",
@@
           type="latex",
-          title = "Are the presence or amounts of campaign limits correlated with the Corruption Reflections Index?",
+          title = "Panel Model of Campaign Finance Limits and Corruption Reflections",
           dep.var.labels = "Corruption Convictions Index",
@@
 
+\blandscape
+```{r DiD to table latex, results="asis", eval=T}
+stargazer(CCIDID01, CCIDID02, CCIDID03, CRIDID01, CRIDID02, CRIDID03,
+  type="latex", 
+  title = "First Differences Model: Do Changes in Limits Lead to Lower Levels of Corruption?",
+  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
+  covariate.labels=c("Individual limits removed","Individual limits imposed","Individual limit amount","Individual limits removed*amount","Individual limits imposed*amount",
+                     "PAC limits removed","PAC limits imposed","PAC limit amount","PAC limits removed*amount","PAC limits imposed*amount",
+                     "Individual-to-party limits removed","Individual-to-party limits imposed","Individual-to-party limit amount","Individual-to-party limits removed*amount","Individual-to-party limits imposed*amount"),
+  header=FALSE, 
+  font.size = "small",
+  # column.sep.width = "-5pt",
+  digits = 2, digits.extra = 0,
+  no.space = TRUE,
+  omit.stat = "f"
+  )
+```
+\elandscape
+
 ## Discussion
@@
 
-## Appendix A: Initital modeling of independent and dependent variables
+## Appendix X: Initital modeling of independent and dependent variables
 ```{r output of initial correlations, results="asis", eval=T}
@@
 \newpage
-##Appendix B: Descriptions and Descriptive Statistics of Control Variables 
+
+##Appendix X: Descriptions and Descriptive Statistics of Control Variables 
 In their 2006 paper "Corruption in America," Glaeser and Saks make use of the following control variables, which we have included here:
 
-* Divided government
-* Binding one-term limit
-* Binding two-term limit
-* Real per capita income ($1000)
-* AUSAs per million population
-* Unemployment
-* Citizen ideology measure
-* Percent high school graduates
-* Real per capita gov revenues ($1000)
-* Inequality: Male wages
-* Relative government wages
-* Urbanization
-* Log of population (millions)
+* *AUSAs per million population*, where the number of general attorneys in the U.S. Attorney's office serves as a proxy for the number of federal resources focused on corruption in a particular state
+* *Relative government wages*, the wages of government workers relative to that of the state in which they live, under the hypothesis that lower relative wages will make government workers more prone to corruption
+* *Divided government*, where legislature and executive are controlled by different parties, *Binding one-term limits* and *Binding two-term limits*, which Alt and Lassen call "shadow of the future" variables
+* *Real per capita income ($1000)*, *Unemployment*, *Citizen ideology measure*, *Percent high school graduates*, *Real per capita gov revenues ($1000)*, *Inequality: Male wages*, *Urbanization* and *Log of population (millions)*, which are included as social and demographic controls
 
@@
 \newpage
+
 ##References 

### 2019-01-16 Paper 2019.Rmd
Presentation, paper, collateral

@@
 title: | 
-  | Campaign Contribution Limits and Corruption: 
+  | Campaign Contribution Limits and Corruption 
   | Evidence from the 50 states
@@
 
-[^SPSA]: Working paper presented at the Annual Meeting of the Southern Political Science Association, January 2019.
+[^SPSA]: Working paper presented at the Annual Meeting of the Southern Political Science Association, January 2019. Analysis available on [GitHub](https://github.com/markchand/Money-in-Politics).
 
@@
 library(pglm) # For panel + binomial 
+library(webshot) # For screenshots 
 # library(psych) # Also for summary statistics
@@
 In 1976, the Supreme Court ruled in _Buckley v.
-Valeo_ that political campaign contributions are the equivalent of free speech, and therefore protected by the first amendment.
-At the same time, the Court laid out one mechanism and two permissible reasons for limiting those contributions.
-First, it argued that more money spent does not amount of “more” speech, allowing for the use of campaign contribution dollar amount limits.
+Valeo_ that political campaign expenditures are the equivalent of free speech, and therefore protected by the first amendment.
+At the same time, the Court laid out one mechanism and two permissible reasons for limiting campaign contributions that enable those expenditures.
+First, it argued that more money contributed does not amount to “more” speech, allowing for the use of campaign contribution dollar amount limits.
 Donating one dollar or $5,000 to a political campaign amounts to a speech act, the Court held, and so it is permissible to impose limits on the amount of contributions as long as contributions are not prevented.
@@
 Sorrell_, 2006).
+
 <!--Those rulings have often been driven by the question of corporations’ participation in the political process.
@@
 -->
+
 The passage of the McCain-Feingold in 2002 inspired a wave of challenges to campaign contributions and expenditures, driven mostly by conservative and religious political groups.
@@
 # This is what fails to knit (see error below)
-stargazer(as.data.frame(subset(BarberNAs[,3:6])), digits=0, type="latex", title="Descriptive Statistics for State Level Campaign Finance Limits (n=1150 state-years)", covariate.labels = c("Individual Limits","Individual-to-Party Limits","Party Limits", "PAC Limits"), header=F)
+stargazer(as.data.frame(subset(BarberNAs[,3:6])), digits=0, type="latex", title="Descriptive Statistics for State Level Campaign Finance Limits", covariate.labels = c("Individual Limits","Individual-to-Party Limits","Party Limits", "PAC Limits"), header=F,
+          notes = "Notes: 'N' equals number of state-years (out of n=1150) in which that type of limit is present") 
 ```
@@
 Alt and Lassen's data set runs from 1976-2004.
-When included in the second and third models, this limits the analysis to the years from 1990-2004.
+When included in the second and third models, this limits the analysis to the years from 1990-2004 and n=720.
 
@@
           type="latex",
+          title = "Panel Model of Contribution Limits and Corruption Convictions",
+          dep.var.labels = "Corruption Convictions Index",
+          covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)","Divided government","Binding one-term limit","Binding two-term limit","Real per capita income (1000s)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (1000s)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)"),
+  add.lines = list(c("Effects","Pooled","Pooled","Fixed","Two-Way")),     
+  header=FALSE, 
+  font.size = "small",
+  # column.sep.width = "-5pt",
+  digits = 2, digits.extra = 0,
+  no.space = TRUE,
+  omit.stat = "f"
+  )
+
+```
+
+```{r CCI output to png, eval=F}
+# Maaaaaybe figure out how to add back in those $ signs. 
+stargazer(cci.base.pooled, 
+          cci.limits.pooled, 
+          cci.limits.fixed,
+          cci.limits.fixed.time, 
+          type="html",
+          out="collateral/CCI.htm",
           title = "Panel Model of Campaign Finance Limits and Corruption Convictions",
@@
           type="latex",
-          title = "Panel Model of Campaign Finance Limits and Corruption Reflections",
-          dep.var.labels = "Corruption Convictions Index",
+          title = "Panel Model of Contribution Limits and Corruption Reflections",
+          dep.var.labels = "Corruption Reflections Index",
           covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)","Divided government","Binding one-term limit","Binding two-term limit","Real per capita income (1000s)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (1000s)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)"),
@@
 
+```{r CRI output to html, eval=F}
+stargazer(cri.base.pooled, 
+          cri.limits.pooled, 
+          cri.limits.fixed,
+          cri.limits.fixed.time, 
+          type="html",
+          out = "collateral/CRI.htm",
+          title = "Panel Model of Campaign Finance Limits and Corruption Reflections",
+          dep.var.labels = "Corruption Reflections Index",
+          covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)","Divided government","Binding one-term limit","Binding two-term limit","Real per capita income (1000s)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (1000s)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)"),
+          add.lines = list(c("Effects","Pooled","Pooled","Fixed","Two-Way")),
+  header=FALSE, 
+  font.size = "small",
+  # column.sep.width = "-5pt", 
+  digits = 2, digits.extra = 0, 
+  no.space = TRUE,
+  omit.stat = "f" 
+  ) 
+```
+
 \blandscape
@@
   type="latex", 
-  title = "First Differences Model: Do Changes in Limits Lead to Lower Levels of Corruption?",
+  title = "First Differences Model of Changes in Contribution Limits Versus Convictions and Reflections",
   dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
@@
 ```
+
+```{r DiD to htm, eval=F}
+stargazer(CCIDID01, CCIDID02, CCIDID03, CRIDID01, CRIDID02, CRIDID03,
+  type="html", 
+  title = "First Differences Model: Do Changes in Limits Lead to Lower Levels of Corruption?",
+  out = "collateral/DiD.htm",
+  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
+  covariate.labels=c("Individual limits removed","Individual limits imposed","Individual limit amount","Individual limits removed*amount","Individual limits imposed*amount",
+                     "PAC limits removed","PAC limits imposed","PAC limit amount","PAC limits removed*amount","PAC limits imposed*amount",
+                     "Individual-to-party limits removed","Individual-to-party limits imposed","Individual-to-party limit amount","Individual-to-party limits removed*amount","Individual-to-party limits imposed*amount"),
+  header=FALSE, 
+  font.size = "small",
+  # column.sep.width = "-5pt",
+  digits = 2, digits.extra = 0,
+  no.space = TRUE,
+  omit.stat = "f"
+  )
+```
+
+```{r webshots, eval=F}
+webshot("collateral/CCI.htm", "collateral/CCI.png")
+```
+
 \elandscape

### 2019-01-17 Paper 2019.Rmd
Fixing arrests -> convictions

@@
 As current challenges to contribution limits wind their way through federal courts, the answer to this question will inform the Supreme Court’s decision to uphold or strike down remaining limits on political campaign contributions.
-Using state-level data from 1990-2012 on contribution limits, corruption arrests, and media mentions of corruption, this paper employs linear panel regression and first differences analyses to test whether campaign contribution limits are associated with lower levels of corruption convictions or media mentions of corruption.
+Using state-level data from 1990-2012 on contribution limits, corruption convictions, and media mentions of corruption, this paper employs linear panel regression and first differences analyses to test whether campaign contribution limits are associated with lower levels of corruption convictions or media mentions of corruption.
 These methods find no relationship between the presence or level of campaign finance laws and quid pro quo corruption.[^SPSA]
@@
 In 2007, the Court examined the McCain-Feingold ban on airing issue advertisements close to election.
-Banning such ads, the Court argued, would have a chilling effect on free speech, and it struck down the ban (_FEC v.
+Banning such ads, the Court argued, would have a chilling effect on free speech, and it struck down the ban ( _FEC v.
 Wisconsin Right to Life_).
@@
 In yet another, _Lair v.
-Motl_ (2017), Bopp once again took aim at individual contribution limits, arguing that the state of Montana had not shown compelling evidence that campaign contribution limits decreased the risk of corruption.
+Mangan_ (2018), Bopp once again took aim at individual contribution limits, arguing that the state of Montana had not shown compelling evidence that campaign contribution limits decreased the risk of corruption.
 
@@
 
-I build a model of political corruption using control variables previously demonstrated by Alt and Lassen to be correlated with corruption arrests, resulting in a data set covering 1990-2004, the period of overlap among the data sets listed above.
+I build a model of political corruption using control variables previously demonstrated by Alt and Lassen to be correlated with corruption convictions, resulting in a data set covering 1990-2004, the period of overlap among the data sets listed above.
 These include controlling for the size and education levels of the population, the ideology of a population, income levels and inequality, education levels, the number and relative income of government employees, and urbanization.
@@
 ### Model II: First Differences Model
-Even if the panel modeling above fails to capture correlation between state level campaign finance laws and corruption arrests, it could be the case that changes in campaign finance laws, rather than relative campaign finance limits, are correlated with decreases in corruption.
+Even if the panel modeling above fails to capture correlation between state level campaign finance laws and corruption convictions, it could be the case that changes in campaign finance laws, rather than relative campaign finance limits, are correlated with decreases in corruption.
 In addition to the panel model above, I ran a first differences regression compare the state-years in which campaign finance laws changed to state-years where they remained constant.
@@
 
-### Modeling campaign limits and corruption arrests 
+### Modeling campaign limits and corruption convictions 
 The results of the panel regressions reveal no correlation between state-level campaign contribution limits and corruption, with one exception: There is a statistically significant relationship between the presence of individual-to-party limits and the Corruption Reflections Index.
@@
 
-### Modeling changes in campaign limits and corruption arrests
-
-The final set of models (Table X) displays results from multiple first difference models designed to isolate the effect of changes in campaign finance laws on corruption arrests.
-None of the models find correlation between campaign finance limits and either corruption convictions or corruption reflections.
+### Modeling changes in campaign limits and corruption convictions
+
+The final set of models (Table X) displays results from multiple first difference models designed to isolate the effect of changes in campaign finance laws on corruption convictions.
+None of the models find correlation between campaign finance limits and corruption convictions or corruption reflections.
 

### 2019-01-17 Paper 2019.Rmd
Powerpoint and some date fixes

@@
 Boylan and Long make use of surveys of state reporters (2003).
-Cordis and Milyo deploy the recently available Transactional Records Access Clearinghouse (TRAC) database of political corruption (2016).
+Cordis and Milyo deploy the recently available Transactional Records Access Clearinghouse (TRAC) database of political corruption (2013).
 Dincer and Jonhston introduce a Corruption Reflections Index, which tracks mentions of corruption in Associated Press reports (2016).
 
-A smaller number of scholars have begun connecting these bodies of work to examine the impact of state-level campaign finance regulations on measures of quid pro quo corruption--one of only two questions of import to the Supreme Court as it considers the constitutionality of contribution limits.
-The exception to this is a 2013 working paper by Cordis and Milyo.
-In line with Persily and Lammie (2004), Milyo argues that campaign reform efforts have little effect on public perceptions of corruption.
-This paper seeks to address this gap, putting state level campaign finance data in direct conversation with state level corruption data.
+Fewer scholars have begun connecting these bodies of work to examine the impact of state-level campaign finance regulations on measures of quid pro quo corruption--one of only two questions of import to the Supreme Court as it considers the constitutionality of contribution limits.
+The exception to this is a 2013 working paper by Cordis and Milyo, which campaign contribution limits have little effect on public perceptions of corruption.
+This paper seeks to address this gap in research, building on Cordis and Milyo's work putting state level campaign finance data in direct conversation with state level corruption data.
 
@@
 The results for the models examining the relationship between campaign finance limits and the Corruption Reflections Index are less clear.
-The pair of stars that suggest the presence of individual-to-party limits is associated with a decrease in the Corruption Reflections Index.
+The pair of stars in the fourth model suggest that the presence of individual-to-party limits is associated with a decrease in the Corruption Reflections Index.
 There is a less than 1% probability that the results are due to chance.
@@
 
-The legal implications of the second interpretation are clear and material.
+The legal implications of this interpretation are clear and material.
 The Supreme Court presently equates political donations with political speech, meaning that it is protected by the first amendment, but that preventing corruption or its appearance in the political system is so important that first amendment rights can be abridged to ensure it.
@@
 
-The anti-reform/pro-speech interpretation must also more fully take into account the second half of the court’s reasoning for limiting free speech, the “appearance of corruption.” Cordis and Milyo’s working paper on confidence and trust in state government is an important step in that direction, though they acknowledges that “survey measures that relate to opinion on the integrity of democracy are likely to reflect a much more expansive view of ‘corruption’ than what any Court would consider appropriate (2012).
+The anti-reform/pro-speech interpretation must also more fully take into account the second half of the court’s reasoning for limiting free speech, the “appearance of corruption.” Primo and Milyo 2006 on confidence and trust in state government is an important step in that direction, though they acknowledges that “survey measures that relate to opinion on the integrity of democracy are likely to reflect a much more expansive view of ‘corruption’ than what any Court would consider appropriate (2006).
 Dincer and Johnston’s surveys of state reporters is another step, but is limited by its design: State reporters’ perceptions are just a proxy, not a direct measure, of public perceptions of corruption (2017).
@@
 ##Appendix X: Descriptions and Descriptive Statistics of Control Variables 
-In their 2006 paper "Corruption in America," Glaeser and Saks make use of the following control variables, which we have included here:
+In their 2012 paper "Enforcement and Public Corruption: Evidence from the American States," Glaeser and Saks make use of the following control variables, which we have included here:
 

### 2020-04-03 Paper 2019.Rmd
Includes submitted JOPskeleton

@@
   | Evidence from the 50 states
-author: "Mark Hand"
+author: "Mark C. Hand"
 date: "01/06/2018"
@@
 ```{r Barber summary, eval=T}
-# This is a summary it, but includes all the 99999s and doesn't have skew in it. 
+# This is a summary, but includes all the 99999s and doesn't have skew in it. 
 # stargazer(as.data.frame(subset(Barber[,3:6])), type="text", digits=0)

### 2020-04-03 Paper 2020.Rmd
Includes submitted JOPskeleton

--- 2020-04-03 Paper 2019.Rmd
@@
 author: "Mark C. Hand"
-date: "01/06/2018"
+date: ""
 output: pdf_document
@@
 As current challenges to contribution limits wind their way through federal courts, the answer to this question will inform the Supreme Court’s decision to uphold or strike down remaining limits on political campaign contributions.
-Using state-level data from 1990-2012 on contribution limits, corruption convictions, and media mentions of corruption, this paper employs linear panel regression and first differences analyses to test whether campaign contribution limits are associated with lower levels of corruption convictions or media mentions of corruption.
-These methods find no relationship between the presence or level of campaign finance laws and quid pro quo corruption.[^SPSA]
-
-[^SPSA]: Working paper presented at the Annual Meeting of the Southern Political Science Association, January 2019. Analysis available on [GitHub](https://github.com/markchand/Money-in-Politics).
+Using state-level data from 1990-2012 on contribution limits, corruption convictions, and media mentions of corruption, this paper employs linear panel regressio to test whether campaign contribution limits are associated with lower levels of corruption convictions or media mentions of corruption.
+These methods find associations between corruption convictions and the presence of limits on donations to political action committees (PACs), the amount of those limits, and the presence of limts on donations to parties.
+Applying these methods to recently developed measures of media mentions of corruption suggests that these data may require further development.[^SPSA]
+
+[^SPSA]: An earlier version of this paper was presented at the Annual Meeting of the Southern Political Science Association in January 2019.
+Analyses available on [GitHub](https://github.com/markchand/Money-in-Politics).
 
 ```{r setup, include=FALSE}
-# This is all necessary setup stuff, including packages and for Markdown
 knitr::opts_chunk$set(echo = FALSE, eval=FALSE, cache = TRUE, message=FALSE, warning=FALSE)
 library(haven) # import .dta
-suppressMessages(library("tidyverse")) # everything 
+library (MASS) # For binomial regression 
+library(tidyverse) # everything; placed here because of MASS::select() overlap 
 library(plm) # For linear panel regression
@@
 library(knitr) # Because Matt Worthington said so 
-library (MASS) # For binomial regression 
 library(pglm) # For panel + binomial 
 library(webshot) # For screenshots 
-# library(psych) # Also for summary statistics
-# library(texreg) # For regression outputs #fail 
-# library(kableExtra) # For regression outputs 
-# library(broom) # Because Matt Worthington said so 
-# library(summarytools) # For summary statistics 
+library(viridis) # For colorblindedness
+library(GGally) # For ggpairs
+library(lm.beta) # For standardized regression coefficients 
+library(broom) # for augment()
+theme_set(theme_classic()) # Sets default theme
+
 ```
@@
 
-```{r panel data wrangling, eval=T}
+```{r panel data wrangling,eval=T}
 # Combining Barber and ICS  
@@
 In 1981, the Court struck down contribution limits related to ballot measures (_Citizens against Rent Control v.
-City of Berkeley-).
+City of Berkeley_).
 Just before the passage of McCain-Feingold, the courts considered state-level limits, allowing low limits in Missouri (_Nixon v.
@@
 Sorrell_, 2006).
-
-<!--Those rulings have often been driven by the question of corporations’ participation in the political process.
-In 1978, the Court extended free speech protections to corporations (First National Bank of Boston v.
-Bellotti).
-
-Then in 1990, it upheld a ban on corporations using treasury funds to pay for issue advertisements, arguing for an extended definition of corruption, "the corrosive and distorting effects of immense aggregations of wealth that are accumulated with the help of the corporate form and that have little or no correlation to the public's support for the corporation's political ideas" (Austin v.
-Michigan State Chamber of Commerce, later overturned).
-
-In 1986, it  and struck down efforts to restrict their expenditures to FEC-registered Political Action Committees (FEC v. Massachusetts Right to Life). 
--->
 
@@
 
-```{r Barber summary, eval=T}
+```{r Barber summary, eval=T,include=F}
 # This is a summary, but includes all the 99999s and doesn't have skew in it.  
@@
 
-```{r Barber summary statistics latex, results="asis", eval=TRUE}
+```{r Barber summary stats latex, results="asis",eval=T,include=F}
 # This is what fails to knit (see error below) 
@@
 ## Methods
-
-### Model I: Panel Regression
-Having constructed a full 1990-2012 panel data set from these three data sets, I then run a set of time series regressions testing the relationship between contribution limits and both dependent variables, the Corruption Convictions Index and the Corruption Reflections Index.
-
-I include three predictor variables in both sets of models: Individual contribution limits, individual-to-party contribution limits, and PAC contribution limits.
-For each of these independent variables, I construct two variables for use in the model.
+Having constructed a full 1990-2012 panel data set from these three data sets, I then run a series of time series regressions testing the relationship between contribution limits and both dependent variables, the Corruption Convictions Index and the Corruption Reflections Index.
+
+I include three study variables in both sets of models: Individual contribution limits, individual-to-party contribution limits, and PAC contribution limits.
+For each of these independent variables, I construct two variables for use in the models.
 The first is a dummy variable indicating whether there are contribution limits in that state in that year, coded as “0” if there are no limits and “1” if there are.
@@
 After performing this transformation on all three independent variables, I test two initial sets of models: (1) Corruption Convictions Index versus campaign contribution limits in a given state-year, and (2) Corruption Reflections Index versus campaign contributions in a given state-year.
-These basic models are included in Appendix X.
+<!--These basic models are included in Appendix X.-->
 
@@
 For each of these models, I test fixed state and year effects and random effects.
+I also test appropriate transformations of both dependent and independent variables.
 The models are as follows:
@@
 #### Corruption Convictions Index versus campaign contribution limits in a given state-year: 
-$Convictions = \alpha_{state} + \beta_{1}{indiv.dummy} + \beta_{2}{indiv.dummy}*{indiv.limit} + \beta_{3}{pac.dummy} + \beta_{4}{pac.dummy}*{pac.limit} + \beta_{5}{indiv-to-party.dummy} + \beta_{6}{indiv-to-party.dummy}*{indiv-to-party.limit} + Controls + \epsilon$
+$(log)Convictions = \alpha_{state} + \beta_{1}{indiv.dummy} + \beta_{2}{indiv.dummy}*{indiv.limit} + \beta_{3}{pac.dummy} + \beta_{4}{pac.dummy}*{pac.limit} + \beta_{5}{indiv-to-party.dummy} + \beta_{6}{indiv-to-party.dummy}*{indiv-to-party.limit} + Controls + \epsilon$
 
 #### Corruption Reflections Index versus campaign contributions in a given state-year: 
-$Reflections = \alpha_{state} + \beta_{1}{indiv.dummy} + \beta_{2}{indiv.dummy}*{indiv.limit} + \beta_{3}{pac.dummy} + \beta_{4}{pac.dummy}*{pac.limit} + \beta_{5}{indiv-to-party.dummy} + \beta_{6}{indiv-to-party.dummy}*{indiv-to-party.limit} + Controls + \epsilon$
-
-```{r modeling of initial correlations (with fixed effects), eval=T}
-## CCI 
-# Individual limits and corruption
-CCIreg1  <- plm(CCI ~ ind_limits_2010*ind_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
-# No signifigance
-
-# Individual-to-party limits and corruption
-CCIreg2  <- plm(CCI ~ ind2pty_limits_2010*ind2pty_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
-# No Signifigance
-
-# PAC Limits and corruption
-CCIreg3  <- plm(CCI ~ pac_limits_2010*pac_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
-# No Signifigance
-
-# Total Limits and corruption
-CCIreg4  <- plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
-# One star. Hmm...
-
-# Everybody? 
-CCIreg5 <- plm(CCI ~ ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = BarberICC, index = c("st","year"), effect="twoways")
-
-## CRI
-CRIreg1  <- plm(CRI ~ ind_limits_2010*ind_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
-# No signifigance
-
-# Individual-to-party limits and reflection
-CRIreg2  <- plm(CRI ~ ind2pty_limits_2010*ind2pty_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
-# One star. Hmm...
-
-# PAC Limits and reflection
-CRIreg3  <- plm(CRI ~ pac_limits_2010*pac_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
-# No Signifigance
-
-# All Limits and reflection
-CRIreg4  <- plm(CRI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
-# No Signifigance
-
-# Everybody? 
-CRIreg5 <- plm(CRI ~ ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = BarberICC, index = c("st","year"), effect="twoways")
-```
-
-```{r output of initial correlations (with fixed effects), include=F}
-stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,CRIreg1, CRIreg2, CRIreg3, CRIreg5,
-  type="text", 
-  title = "Appendix A: Are campaign limits correlated with corruption convictions or reflections?",
-  out="collateral/AppendixA.htm",
-  dep.var.labels = c("Corruption Convictions Index","Corruption Reflections Index"),
-  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"),
-  add.lines = list(c("Effects","Two-Way","Two-Way","Two-Way","Two-Way","Two-Way","Two-Way","Two-Way","Two-Way"))
-  )
-```
-
-```{r modeling of CCI base model effects, eval=T}
-# Base model with no Two-Way or random effects 
-cci.base.pooled <- plm(CCI ~ jdiv  # Divided government 
+$(log)Reflections = \alpha_{state} + \beta_{1}{indiv.dummy} + \beta_{2}{indiv.dummy}*{indiv.limit} + \beta_{3}{pac.dummy} + \beta_{4}{pac.dummy}*{pac.limit} + \beta_{5}{indiv-to-party.dummy} + \beta_{6}{indiv-to-party.dummy}*{indiv-to-party.limit} + Controls + \epsilon$
+
+##Results
+
+```{r data visualization, eval=T,include=F}
+# Per Bill's request to see about logging data:  
+AltBarber %>% 
+  #select(CCI,CRI,ind_limits_2010,ind_limits_dummy,ind2pty_limits_2010,ind2pty_limits_dummy,pac_limits_2010,pac_limits_dummy,jdiv,bindingonetermlimit,bindingtwotermlimit,rpcinc_annual_new,eopop,unemp,citi6006,high_school,rgenrevpc,men_ineqincwag,grelimp,urbanization_2,logpop) %>%
+  dplyr::select(CCI,CRI,ind_limits_2010,ind_limits_dummy,ind2pty_limits_2010,ind2pty_limits_dummy,pac_limits_2010,pac_limits_dummy) %>%
+  ggpairs(cardinality_threshold = 21)
+
+AltBarber %>% 
+  ggplot() +
+  geom_histogram(aes(log(CRI))) # LOG
+
+AltBarber %>% 
+  ggplot() +
+  geom_histogram(aes(log(CCI))) # LOG
+
+AltBarber %>% 
+  filter(ind_limits_2010!=99999) %>% 
+  ggplot() +
+  geom_histogram(aes(log(ind_limits_2010))) # Log. Remember that 99999s == no limit. Have to leave as 99999 for the same reason that Barber did; otherwise NAs get dropped.
+
+AltBarber %>% 
+  filter(pac_limits_2010!=99999) %>% 
+  ggplot() +
+  geom_histogram(aes(log(pac_limits_2010))) # Log
+
+AltBarber %>% 
+  filter(ind2pty_limits_2010!=99999) %>% 
+  ggplot() +
+  geom_histogram(aes(log(ind2pty_limits_2010))) # Log 
+```
+
+```{r CCI models, eval=T, include=F}
+cci <- plm(CCI ~ jdiv  # Divided government  
            + bindingonetermlimit # Binding one-term limit 
@@
 
-# Base model with fixed effects (NB: effect="individual" is redundant here)
-cci.base.fixed <- plm(CCI ~ jdiv  # Divided government 
+cci.log <- plm(log(CCI+1) ~ jdiv  # Divided government 
            + bindingonetermlimit # Binding one-term limit 
@@
            data = AltBarber, 
+           model="pooling")
+
+cci.log.pars <- plm(log(CCI+1) ~ 
+             jdiv  # Divided government 
+           # + bindingonetermlimit # Binding one-term limit 
+           # + bindingtwotermlimit # Binding two-term limit 
+           # + rpcinc_annual_new # Real per capita income ($1000)
+           + eopop # AUSAs per million population
+           # + unemp # Unemployment 
+           # + citi6006 # Citizen ideology measure 
+           + high_school + # Percent high school graduates
+           + rgenrevpc # Real per capita gov revenues ($1000)
+           # + men_ineqincwag # Inequality: Male wages
+           # + grelimp # Relative government wages
+           + urbanization_2 # Urbanization 
+           + logpop, # Log of population (millions)
+           data = AltBarber, 
+           model="pooling")
+
+cci.log.iv <- plm(log(CCI+1) ~ 
+           ind_limits_2010*ind_limits_dummy 
+           + ind2pty_limits_2010*ind2pty_limits_dummy 
+           + pac_limits_2010*pac_limits_dummy
+           + jdiv  # Divided government 
+           # + bindingonetermlimit # Binding one-term limit 
+           # + bindingtwotermlimit # Binding two-term limit 
+           # + rpcinc_annual_new # Real per capita income ($1000)
+           + eopop # AUSAs per million population
+           # + unemp # Unemployment 
+           # + citi6006 # Citizen ideology measure 
+           + high_school + # Percent high school graduates
+           + rgenrevpc # Real per capita gov revenues ($1000)
+           # + men_ineqincwag # Inequality: Male wages
+           # + grelimp # Relative government wages
+           + urbanization_2 # Urbanization 
+           + logpop, # Log of population (millions)
+           data = AltBarber, 
+           model="pooling")
+
+cci.log.iv.log <- plm(
+           log(CCI+1) ~ log(ind_limits_2010)*ind_limits_dummy 
+           + log(ind2pty_limits_2010)*ind2pty_limits_dummy 
+           + log(pac_limits_2010)*pac_limits_dummy
+           + jdiv  # Divided government 
+           # + bindingonetermlimit # Binding one-term limit 
+           # + bindingtwotermlimit # Binding two-term limit 
+           # + rpcinc_annual_new # Real per capita income ($1000)
+           + eopop # AUSAs per million population
+           # + unemp # Unemployment 
+           # + citi6006 # Citizen ideology measure 
+           + high_school + # Percent high school graduates
+           + rgenrevpc # Real per capita gov revenues ($1000)
+           # + men_ineqincwag # Inequality: Male wages
+           # + grelimp # Relative government wages
+           + urbanization_2 # Urbanization 
+           + logpop, # Log of population (millions)
+           data = AltBarber, 
+           model="pooling")
+
+cci.log.iv.fixed <- plm(
+           log(CCI+1) ~ 
+           ind_limits_2010*ind_limits_dummy 
+           + ind2pty_limits_2010*ind2pty_limits_dummy 
+           + pac_limits_2010*pac_limits_dummy
+           + jdiv  # Divided government 
+           # + bindingonetermlimit # Binding one-term limit 
+           # + bindingtwotermlimit # Binding two-term limit 
+           # + rpcinc_annual_new # Real per capita income ($1000)
+           + eopop # AUSAs per million population
+           # + unemp # Unemployment 
+           # + citi6006 # Citizen ideology measure 
+           + high_school + # Percent high school graduates
+           + rgenrevpc # Real per capita gov revenues ($1000)
+           # + men_ineqincwag # Inequality: Male wages
+           # + grelimp # Relative government wages
+           + urbanization_2 # Urbanization 
+           + logpop, # Log of population (millions)
+           data = AltBarber, 
            model="within")
 
-# Base model with random effects 
-cci.base.random <- plm(CCI ~ jdiv  # Divided government 
+cci.log.iv.fixed.time <- plm(log(CCI+1) ~ 
+           ind_limits_2010*ind_limits_dummy 
+           + ind2pty_limits_2010*ind2pty_limits_dummy 
+           + pac_limits_2010*pac_limits_dummy
+           + jdiv  # Divided government 
+           # + bindingonetermlimit # Binding one-term limit 
+           # + bindingtwotermlimit # Binding two-term limit 
+           # + rpcinc_annual_new # Real per capita income ($1000)
+           + eopop # AUSAs per million population
+           # + unemp # Unemployment 
+           # + citi6006 # Citizen ideology measure 
+           + high_school + # Percent high school graduates
+           + rgenrevpc # Real per capita gov revenues ($1000)
+           # + men_ineqincwag # Inequality: Male wages
+           # + grelimp # Relative government wages
+           + urbanization_2 # Urbanization 
+           + logpop, # Log of population (millions)
+           data = AltBarber, 
+           model="within",
+           effect="twoways")
+
+```
+
+```{r CCI models output, eval=T,results="asis"}
+stargazer(
+  cci.log.pars, 
+  cci.log.iv, # F Stat down? 
+  cci.log.iv.log, # F Stat down further 
+  #cci.log.iv.fixed, # AR2 Stat bottoms out 
+  cci.log.iv.fixed.time, 
+  type="latex",
+  #out = "collateral/test.htm",
+  font.size = "small",
+  header=FALSE, 
+  column.sep.width = "-15pt", 
+  digits = 2, digits.extra = 0, 
+  no.space = TRUE,
+  title = "Models of Contribution Limits and Corruption Convictions",
+  dep.var.labels = "Corruption Convictions Index (logged)",
+  covariate.labels=c("Individual limit (amount)",
+                     "Individual limit (logged)",
+                     "Individual limit (dummy)",
+                     "Individual-to-party limit (amount)",
+                     "Individual-to-party limit (logged)",
+                     "Individual-to-party limit (dummy)",
+                     "PAC limit (amount)",
+                     "PAC limit (logged)",
+                     "PAC limit (dummy)",
+                     "Divided government",
+                     "AUSAs per population (MMs)"),
+                     # "% high school grads",
+                     # "Govt revenues/capita ($1000s)",
+                     # "Urbanization",
+                     # "Log of population (MMs)"),
+  add.lines = list(c(" ","Base Model","With IVs","Pooled","FE"))
+  )
+
+# If I'm interpreting stuff correctly, then: The model that performed best was a logged CCI, non-logged IVs, with no fixed time or state effects.
+In that model, one campaign finance limits (ind2pty_limits_dummy) was associated with higher corruption; one (pac_limits_2010) was associated with lower corruption.
+This is even theoretically stranger than the preivous model.
+
+```
+
+```{r CRI models, eval=T, include=F}
+cri <- plm(CRI ~ jdiv  # Divided government  
            + bindingonetermlimit # Binding one-term limit 
@@
            data = AltBarber, 
-                   model="random")
-
-#Base model with fixed effects and time fixed effects 
-cci.base.fixed.time <- plm(CCI ~ jdiv  # Divided government 
+           model="pooling")
+
+cri.log <- plm(log(CRI+1) ~ jdiv  # Divided government 
            + bindingonetermlimit # Binding one-term limit 
@@
            data = AltBarber, 
-                   model="within", 
-                   effect = "twoways")
-
-# Base model with random effects doesn't work: 
-# Error in solve.default(crossprod(ZBmu)) : 
-  # system is computationally singular: reciprocal condition number = 1.96767e-18
-```
-
-```{r Hausman for CCI base model, eval=F}
-phtest(cci.base.pooled, cci.base.fixed, cci.base.random, cci.base.fixed.time)
-
-```
-
-```{r output of CCI base model effects}
-stargazer(cci.base.pooled, 
-          cci.base.fixed, 
-          cci.base.random, 
-          cci.base.fixed.time, 
-          type="text",
-          add.lines = list(c("Effects", "Pooled", "Fixed", "Random", "Two-Way"))
-          )
-```
-
-```{r modeling of CRI base model effects, eval=T}
-# Base model with no fixed or random effects 
- cri.base.pooled <- plm(CRI ~ jdiv  # Divided government 
-                   + bindingonetermlimit # Binding one-term limit 
-                   + bindingtwotermlimit # Binding two-term limit 
-                   + rpcinc_annual_new # Real per capita income ($1000)
-                   + eopop # AUSAs per million population
-                   + unemp # Unemployment 
-                   + citi6006 # Citizen ideology measure 
-                   + high_school + # Percent high school graduates
-                   + rgenrevpc # Real per capita gov revenues ($1000)
-                   + men_ineqincwag # Inequality: Male wages
-                   + grelimp # Relative government wages
-                   + urbanization_2 # Urbanization 
-                   + logpop, # Log of population (millions)
-                   data = AltBarber, 
-                   model="pooling")
-
-# Base model with fixed effects (NB: effect="individual" is redundant here)
-cri.base.fixed <- plm(CRI ~ jdiv  # Divided government 
-                   + bindingonetermlimit # Binding one-term limit 
-                   + bindingtwotermlimit # Binding two-term limit 
-                   + rpcinc_annual_new # Real per capita income ($1000)
-                   + eopop # AUSAs per million population
-                   + unemp # Unemployment 
-                   + citi6006 # Citizen ideology measure 
-                   + high_school + # Percent high school graduates
-                   + rgenrevpc # Real per capita gov revenues ($1000)
-                   + men_ineqincwag # Inequality: Male wages
-                   + grelimp # Relative government wages
-                   + urbanization_2 # Urbanization 
-                   + logpop, # Log of population (millions)
-                   data = AltBarber, 
-                   model="within")
-
-# Base model with random effects 
-cri.base.random <- plm(CRI ~ jdiv  # Divided government 
-                   + bindingonetermlimit # Binding one-term limit 
-                   + bindingtwotermlimit # Binding two-term limit 
-                   + rpcinc_annual_new # Real per capita income ($1000)
-                   + eopop # AUSAs per million population
-                   + unemp # Unemployment 
-                   + citi6006 # Citizen ideology measure 
-                   + high_school + # Percent high school graduates
-                   + rgenrevpc # Real per capita gov revenues ($1000)
-                   + men_ineqincwag # Inequality: Male wages
-                   + grelimp # Relative government wages
-                   + urbanization_2 # Urbanization 
-                   + logpop, # Log of population (millions)
-                   data = AltBarber, 
-                   model="random")
-
-#Base model with fixed effects and time fixed effects 
-cri.base.fixed.time <- plm(CRI ~ jdiv  # Divided government 
-                   + bindingonetermlimit # Binding one-term limit 
-                   + bindingtwotermlimit # Binding two-term limit 
-                   + rpcinc_annual_new # Real per capita income ($1000)
-                   + eopop # AUSAs per million population
-                   + unemp # Unemployment 
-                   + citi6006 # Citizen ideology measure 
-                   + high_school + # Percent high school graduates
-                   + rgenrevpc # Real per capita gov revenues ($1000)
-                   + men_ineqincwag # Inequality: Male wages
-                   + grelimp # Relative government wages
-                   + urbanization_2 # Urbanization 
-                   + logpop, # Log of population (millions)
-                   data = AltBarber, 
-                   model="within", 
-                   effect = "twoways")
-```
-
-```{r Hausman for CRI base model, eval=F}
-phtest(cri.base.pooled, cri.base.fixed, cri.base.random, cri.base.fixed.time)
-```
-
-```{r output of CRI base model effects}
-stargazer(cri.base.pooled, 
-          cri.base.fixed, 
-          cri.base.random, 
-          cri.base.fixed.time, 
-          type="text",
-          add.lines = list(c("Effects", "Pooled", "Fixed", "Random", "Two-Way"))
-          )
-```
-
-```{r modeling of CCI with campaign finance variables, eval=T}
-# Base model with no fixed or random effects 
- cci.limits.pooled <- plm(CCI 
-                   ~ ind_limits_2010*ind_limits_dummy 
+           model="pooling")
+
+cri.log.pars <- plm(
+           log(CRI+1) ~ 
+           # jdiv  # Divided government 
+           # + bindingonetermlimit # Binding one-term limit 
+           # + bindingtwotermlimit # Binding two-term limit 
+           # + rpcinc_annual_new # Real per capita income ($1000)
+           + eopop # AUSAs per million population
+           # + unemp # Unemployment 
+           + citi6006 # Citizen ideology measure 
+           + high_school + # Percent high school graduates
+           + rgenrevpc # Real per capita gov revenues ($1000)
+           + men_ineqincwag # Inequality: Male wages
+           # + grelimp # Relative government wages
+           + urbanization_2 # Urbanization 
+           + logpop, # Log of population (millions)
+           data = AltBarber, 
+           model="pooling")
+
+cri.log.iv <- plm(log(CRI+1) ~ 
+             ind_limits_2010*ind_limits_dummy 
            + ind2pty_limits_2010*ind2pty_limits_dummy 
            + pac_limits_2010*pac_limits_dummy
-                   + jdiv  # Divided government 
-                   + bindingonetermlimit # Binding one-term limit 
-                   + bindingtwotermlimit # Binding two-term limit 
-                   + rpcinc_annual_new # Real per capita income ($1000)
-                   + eopop # AUSAs per million population
-                   + unemp # Unemployment 
-                   + citi6006 # Citizen ideology measure 
-                   + high_school + # Percent high school graduates
-                   + rgenrevpc # Real per capita gov revenues ($1000)
-                   + men_ineqincwag # Inequality: Male wages
-                   + grelimp # Relative government wages
-                   + urbanization_2 # Urbanization 
-                   + logpop, # Log of population (millions)
-                   data = AltBarber, 
-                   model="pooling")
-
-# Base model with fixed effects (NB: effect="individual" is redundant here)
-cci.limits.fixed <- plm(CCI 
-                   ~ ind_limits_2010*ind_limits_dummy 
+           # jdiv  # Divided government 
+           # + bindingonetermlimit # Binding one-term limit 
+           # + bindingtwotermlimit # Binding two-term limit 
+           # + rpcinc_annual_new # Real per capita income ($1000)
+           + eopop # AUSAs per million population
+           # + unemp # Unemployment 
+           + citi6006 # Citizen ideology measure 
+           + high_school + # Percent high school graduates
+           + rgenrevpc # Real per capita gov revenues ($1000)
+           + men_ineqincwag # Inequality: Male wages
+           # + grelimp # Relative government wages
+           + urbanization_2 # Urbanization 
+           + logpop, # Log of population (millions)
+           data = AltBarber, 
+           model="pooling")
+
+cri.log.iv.log <- plm(log(CRI+1) ~ 
+             log(ind_limits_2010)*ind_limits_dummy 
+           + log(ind2pty_limits_2010)*ind2pty_limits_dummy 
+           + log(pac_limits_2010)*pac_limits_dummy
+           # jdiv  # Divided government 
+           # + bindingonetermlimit # Binding one-term limit 
+           # + bindingtwotermlimit # Binding two-term limit 
+           # + rpcinc_annual_new # Real per capita income ($1000)
+           + eopop # AUSAs per million population
+           # + unemp # Unemployment 
+           + citi6006 # Citizen ideology measure 
+           + high_school + # Percent high school graduates
+           + rgenrevpc # Real per capita gov revenues ($1000)
+           + men_ineqincwag # Inequality: Male wages
+           # + grelimp # Relative government wages
+           + urbanization_2 # Urbanization 
+           + logpop, # Log of population (millions)
+           data = AltBarber, 
+           model="pooling")
+
+cri.log.iv.fixed <- plm(log(CRI+1) ~ 
+           + ind_limits_2010*ind_limits_dummy
            + ind2pty_limits_2010*ind2pty_limits_dummy
            + pac_limits_2010*pac_limits_dummy
-                   + jdiv  # Divided government 
-                   + bindingonetermlimit # Binding one-term limit 
-                   + bindingtwotermlimit # Binding two-term limit 
-                   + rpcinc_annual_new # Real per capita income ($1000)
-                   + eopop # AUSAs per million population
-                   + unemp # Unemployment 
-                   + citi6006 # Citizen ideology measure 
-                   + high_school + # Percent high school graduates
-                   + rgenrevpc # Real per capita gov revenues ($1000)
-                   + men_ineqincwag # Inequality: Male wages
-                   + grelimp # Relative government wages
+           # jdiv  # Divided government 
+           # + bindingonetermlimit # Binding one-term limit 
+           # + bindingtwotermlimit # Binding two-term limit 
+           # + rpcinc_annual_new # Real per capita income ($1000)
+           + eopop # AUSAs per million population
+           # + unemp # Unemployment 
+           + citi6006 # Citizen ideology measure 
+           + high_school + # Percent high school graduates
+           + rgenrevpc # Real per capita gov revenues ($1000)
+           + men_ineqincwag # Inequality: Male wages
+           # + grelimp # Relative government wages
            + urbanization_2 # Urbanization 
@@
 
-# Base model with random effects (failed)  
-# cci.limits.random <- plm(CCI 
-#                    ~ ind_limits_2010*ind_limits_dummy 
-#                    + ind2pty_limits_2010*ind2pty_limits_dummy 
-#                    + pac_limits_2010*pac_limits_dummy
-#                    + jdiv  # Divided government 
-#                    + bindingonetermlimit # Binding one-term limit 
-#                    + bindingtwotermlimit # Binding two-term limit 
-#                    + rpcinc_annual_new # Real per capita income ($1000)
-#                    + eopop # AUSAs per million population
-#                    + unemp # Unemployment 
-#                    + citi6006 # Citizen ideology measure 
-#                    + high_school + # Percent high school graduates
-#                    + rgenrevpc # Real per capita gov revenues ($1000)
-#                    + men_ineqincwag # Inequality: Male wages
-#                    + grelimp # Relative government wages
-#                    + urbanization_2 # Urbanization 
-#                    + logpop, # Log of population (millions)
-#                    data = AltBarber, 
-#                    model="random")
-
-#Base model with fixed effects and time fixed effects 
-cci.limits.fixed.time <- plm(CCI 
-                   ~ ind_limits_2010*ind_limits_dummy 
+cri.log.iv.fixed.time <- plm(log(CRI+1) ~ 
+             ind_limits_2010*ind_limits_dummy 
            + ind2pty_limits_2010*ind2pty_limits_dummy 
            + pac_limits_2010*pac_limits_dummy
-                   + jdiv  # Divided government 
-                   + bindingonetermlimit # Binding one-term limit 
-                   + bindingtwotermlimit # Binding two-term limit 
-                   + rpcinc_annual_new # Real per capita income ($1000)
-                   + eopop # AUSAs per million population
-                   + unemp # Unemployment 
-                   + citi6006 # Citizen ideology measure 
-                   + high_school + # Percent high school graduates
-                   + rgenrevpc # Real per capita gov revenues ($1000)
-                   + men_ineqincwag # Inequality: Male wages
-                   + grelimp # Relative government wages
+           # jdiv  # Divided government 
+           # + bindingonetermlimit # Binding one-term limit 
+           # + bindingtwotermlimit # Binding two-term limit 
+           # + rpcinc_annual_new # Real per capita income ($1000)
+           + eopop # AUSAs per million population
+           # + unemp # Unemployment 
+           + citi6006 # Citizen ideology measure 
+           + high_school + # Percent high school graduates
+           + rgenrevpc # Real per capita gov revenues ($1000)
+           + men_ineqincwag # Inequality: Male wages
+           # + grelimp # Relative government wages
            + urbanization_2 # Urbanization 
@@
            model="within",
-                   effect = "twoways")
-
-```
-
-```{r Hausman test for CCI with campaign finance variables, eval=F}
-phtest(cci.limits.pooled, cci.limits.fixed, cci.limits.random, cci.limits.fixed.time)
-```
-
-```{r output of CCI with campaign finance variables}
-stargazer(cci.limits.pooled, 
-          cci.limits.fixed, 
-          cci.limits.fixed.time, 
-          type="text",
-          add.lines = list(c("Effects", "Pooled", "Fixed", "Two-Way"))
+           effect="twoways")
+
+```
+
+```{r CRI models output, eval=T,results="asis"}
+stargazer(
+  #cri, # started here, with other peoples' models 
+  #cri.log, # Logged DVs; better results
+  cri.log.pars, # Slimmed down model, no explanatory power lost 
+  cri.log.iv, # Adding in IVs. AR2 up, F Stat down 
+  cri.log.iv.log, # Logging IVS. AR2 down, F Stat down 
+  #cri.log.iv.fixed, # AR2 to zero 
+  cri.log.iv.fixed.time, # AR2 now negative 
+  type="latex",
+  #out = "collateral/test.htm",
+  font.size = "small",
+  header=FALSE, 
+  column.sep.width = "-15pt", 
+  digits = 2, digits.extra = 0, 
+  no.space = TRUE,
+  title = "Models of Contribution Limits and Corruption Reflections",
+  dep.var.labels = "Corruption Reflections Index (logged)",
+  covariate.labels=c("Individual limit (amount)",
+                     "Individual limit (logged)",
+                     "Individual limit (dummy)",
+                     "Individual-to-party limit (amount)",
+                     "Individual-to-party limit (logged)",
+                     "Individual-to-party limit (dummy)",
+                     "PAC limit (amount)",
+                     "PAC limit (logged)",
+                     "PAC limit (dummy)",
+                     "AUSAs per million population",
+                     "Citizen ideology measure",
+                     "Percent high school graduates",
+                     "Real per capita gov revenues (1000s)",
+                     "Inequality: Male wages","Urbanization",
+                     "Log of population (millions)"),
+  add.lines = list(c(" ","Base Model","With IVs","Pooled","FE"))
   )
-```
-
-```{r modeling of CRI with campaign finance variables, eval=T}
-# Base model with no fixed or random effects 
-cri.limits.pooled <- plm(CRI 
-                   ~ ind_limits_2010*ind_limits_dummy 
-                   + ind2pty_limits_2010*ind2pty_limits_dummy 
-                   + pac_limits_2010*pac_limits_dummy
-                   + jdiv  # Divided government 
-                   + bindingonetermlimit # Binding one-term limit 
-                   + bindingtwotermlimit # Binding two-term limit 
-                   + rpcinc_annual_new # Real per capita income ($1000)
-                   + eopop # AUSAs per million population
-                   + unemp # Unemployment 
-                   + citi6006 # Citizen ideology measure 
-                   + high_school + # Percent high school graduates
-                   + rgenrevpc # Real per capita gov revenues ($1000)
-                   + men_ineqincwag # Inequality: Male wages
-                   + grelimp # Relative government wages
-                   + urbanization_2 # Urbanization 
-                   + logpop, # Log of population (millions)
-                   data = AltBarber, 
-                   model="pooling")
-
-# Base model with fixed effects (NB: effect="individual" is redundant here)
-cri.limits.fixed <- plm(CRI 
-                   ~ ind_limits_2010*ind_limits_dummy 
-                   + ind2pty_limits_2010*ind2pty_limits_dummy 
-                   + pac_limits_2010*pac_limits_dummy
-                   + jdiv  # Divided government 
-                   + bindingonetermlimit # Binding one-term limit 
-                   + bindingtwotermlimit # Binding two-term limit 
-                   + rpcinc_annual_new # Real per capita income ($1000)
-                   + eopop # AUSAs per million population
-                   + unemp # Unemployment 
-                   + citi6006 # Citizen ideology measure 
-                   + high_school + # Percent high school graduates
-                   + rgenrevpc # Real per capita gov revenues ($1000)
-                   + men_ineqincwag # Inequality: Male wages
-                   + grelimp # Relative government wages
-                   + urbanization_2 # Urbanization 
-                   + logpop, # Log of population (millions)
-                   data = AltBarber, 
-                   model="within")
-
-# Base model with random effects (failed)  
-cri.limits.random <- plm(CRI
-                   ~ ind_limits_2010*ind_limits_dummy
-                   + ind2pty_limits_2010*ind2pty_limits_dummy
-                   + pac_limits_2010*pac_limits_dummy
-                   + jdiv  # Divided government
-                   + bindingonetermlimit # Binding one-term limit
-                   + bindingtwotermlimit # Binding two-term limit
-                   + rpcinc_annual_new # Real per capita income ($1000)
-                   + eopop # AUSAs per million population
-                   + unemp # Unemployment
-                   + citi6006 # Citizen ideology measure
-                   + high_school + # Percent high school graduates
-                   + rgenrevpc # Real per capita gov revenues ($1000)
-                   + men_ineqincwag # Inequality: Male wages
-                   + grelimp # Relative government wages
-                   + urbanization_2 # Urbanization
-                   + logpop, # Log of population (millions)
-                   data = AltBarber,
-                   model="random")
-
-#Base model with fixed effects and time fixed effects 
-cri.limits.fixed.time <- plm(CRI 
-                   ~ ind_limits_2010*ind_limits_dummy 
-                   + ind2pty_limits_2010*ind2pty_limits_dummy 
-                   + pac_limits_2010*pac_limits_dummy
-                   + jdiv  # Divided government 
-                   + bindingonetermlimit # Binding one-term limit 
-                   + bindingtwotermlimit # Binding two-term limit 
-                   + rpcinc_annual_new # Real per capita income ($1000)
-                   + eopop # AUSAs per million population
-                   + unemp # Unemployment 
-                   + citi6006 # Citizen ideology measure 
-                   + high_school + # Percent high school graduates
-                   + rgenrevpc # Real per capita gov revenues ($1000)
-                   + men_ineqincwag # Inequality: Male wages
-                   + grelimp # Relative government wages
-                   + urbanization_2 # Urbanization 
-                   + logpop, # Log of population (millions)
-                   data = AltBarber, 
-                   model="within", 
-                   effect = "twoways")
-```
-
-```{r Hausman test for CRI with campaign finance variables}
-phtest(cri.limits.pooled, cri.limits.fixed, cri.limits.random, cri.limits.fixed.time)
-```
-
-```{r output of CRI with campaign finance variables}
-stargazer(cri.limits.pooled, 
-          cri.limits.fixed, 
-          cri.limits.random,
-          cri.limits.fixed.time, 
-          type="text",
-          add.lines = list(c("Effects", "Pooled", "Fixed", "Random", "Two-Way"))
-          )
-```
-
-```{r Empty, Binomial, and Poisson models FAIL}
-# First, trying to run the model above but with the pglm() package
-# pglm(formula, data, subset, na.action, effect = c("individual", "time", "twoways"), model = c("random", "pooling", "within", "between"), family, other = NULL, index = NULL, start = NULL, R = 20, ...)
-
-# Initial correlations of independent variables with CCI 
-pglm(CCI ~ ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = BarberICC, model = "within", index = c("st","year"), effect = "twoways", family = gaussian)
-# Return code 100: Initial value out of range. May have something to do with the interaction terms, because when I strip those out, the model at least returns something.
-
-# What about Cale's empty model? 
-cci.empty.pooling <- plm(CCI ~ st + year,
-                   data = AltBarber, 
-                   model="pooling")
-summary(cci.empty.pooling)
-
-cci.empty.within <- plm(CCI ~ st + year,
-                   data = AltBarber, 
-                   model="within")
-summary(cci.empty.within)
-
-# Verifying that I didn't screw up by not having st and year as variables in my preivous model 
-cci.base.fixed.time.redo <- plm(CCI ~ st + year 
-                   + jdiv  # Divided government
-                   + bindingonetermlimit # Binding one-term limit 
-                   + bindingtwotermlimit # Binding two-term limit 
-                   + rpcinc_annual_new # Real per capita income ($1000)
-                   + eopop # AUSAs per million population
-                   + unemp # Unemployment 
-                   + citi6006 # Citizen ideology measure 
-                   + high_school + # Percent high school graduates
-                   + rgenrevpc # Real per capita gov revenues ($1000)
-                   + men_ineqincwag # Inequality: Male wages
-                   + grelimp # Relative government wages
-                   + urbanization_2 # Urbanization 
-                   + logpop, # Log of population (millions)
-                   data = AltBarber, 
-                   model="within", 
-                   effect = "twoways")
-# stargazer(cci.base.fixed.time, cci.base.fixed.time.redo, type="text")
-```
-
-### Model II: First Differences Model
-Even if the panel modeling above fails to capture correlation between state level campaign finance laws and corruption convictions, it could be the case that changes in campaign finance laws, rather than relative campaign finance limits, are correlated with decreases in corruption.
-In addition to the panel model above, I ran a first differences regression compare the state-years in which campaign finance laws changed to state-years where they remained constant.
-If tighter campaign finance laws are correlated with lower corruption levels, then a change in one year should be associated with lower CCI (corruption convictions) and CRI (reflections) in the years following.
-
-```{r DiD wrangling, eval=T}
-BarberICC %>% arrange(year) %>% group_by(st) %>% mutate(
-  ind_d = (ind_limits_2010 - dplyr::lag(ind_limits_2010)),
-  ind_dummy_d = (ind_limits_dummy - dplyr::lag(ind_limits_dummy)),
-  pac_d = (pac_limits_2010 - dplyr::lag(pac_limits_2010)),
-  pac_dummy_d = (pac_limits_dummy - dplyr::lag(pac_limits_dummy)),
-  ind2pty_d = (ind2pty_limits_2010 - dplyr::lag(ind2pty_limits_2010)),
-  ind2pty_dummy_d = (ind2pty_limits_dummy - dplyr::lag(ind2pty_limits_dummy))
-  ) -> testframe
-
-testframe %>% dplyr::select(1:2,8,11,3:7,12:21) -> DiDsmall
-
-# Now I have what I think are three multi-level categorical independent variables. 
-# https://stats.idre.ucla.edu/r/modules/coding-for-categorical-variables-in-regression-models/
-#1. When limits were imposed (1) or went down, did corruption go down? 
-#2. When limits were removed (-1) or went up, did corruption go up?
-
-DiDsmall$ind_dummy_f <- factor(DiDsmall$ind_dummy_d)
-DiDsmall <- within(DiDsmall, ind_dummy_f <- relevel(ind_dummy_f, ref = "0"))
-DiDsmall$pac_dummy_f <- factor(DiDsmall$pac_dummy_d)
-DiDsmall <- within(DiDsmall, pac_dummy_f <- relevel(pac_dummy_f, ref = "0"))
-DiDsmall$ind2pty_dummy_f <- factor(DiDsmall$ind2pty_dummy_d)
-DiDsmall <- within(DiDsmall, ind2pty_dummy_f <- relevel(ind2pty_dummy_f, ref = "0"))
-```
-
-```{r DiD modeling, eval=T}
-#summary(lm(CCI ~ ind_dummy_f, data = DiDsmall))
-#summary(lm(CCI ~ pac_dummy_f, data = DiDsmall))
-#summary(lm(CCI ~ ind2pty_dummy_f, data = DiDsmall))
-#summary(lm(CRI ~ ind_dummy_f, data = DiDsmall)) 
-#summary(lm(CRI ~ pac_dummy_f, data = DiDsmall))
-#summary(lm(CRI ~ ind2pty_dummy_f, data = DiDsmall))
-# No effects
-
-CCIDID01 <- lm(CCI ~ ind_dummy_f*ind_d, data = DiDsmall)
-# Erin: What this doesn't have is an average treatment effect. So add the interaction of the dummy variable of the change having happened and the law occurring. Time dummy, maybe? 
-# •	Again, writing out a model for the D-in-D in Table 4 might help readers to understand what is being isolated. Right now, I’m not sure I fully follow the estimation choices.
-# o	At a minimum, the state-level control variables changed during this time (and hence wouldn’t get differenced out), and ought to be included.
-# o	Column 1 (and 2): the large standard errors on individual limits removed and imposed suggest multicollinearity and needs to be investigated. 
-# Consider adding state fixed effects to the DiD model, for robustness.
-
-CCIDID02 <- lm(CCI ~ pac_dummy_f*pac_d, data = DiDsmall)
-CCIDID03 <- lm(CCI ~ ind2pty_dummy_f*ind2pty_d, data = DiDsmall)
-
-CRIDID01 <- lm(CRI ~ ind_dummy_f*ind_d, data = DiDsmall)
-CRIDID02 <- lm(CRI ~ pac_dummy_f*pac_d, data = DiDsmall)
-CRIDID03 <- lm(CRI ~ ind2pty_dummy_f*ind2pty_d, data = DiDsmall)
-# No effects
-
-# Next: Lag?  
-```
-
-##Results
+
+# What to make of this? 
+# First, Bill was right about the logging. 
+# Second, Bill was right about not needing fixed effects (why?). 
+# Third, I added in the F Scores and they line up with the adjusted R squared (why?)
+# If I'm interpreting stuff correctly, then: The model that performed best was a logged CRI, non-logged IV, with no fixed time or state effects.
+In that model, a number of campaign finance limits (ind2pty_limits_dummy,pac_limits_2010,pac_limits_dummy) were associated with lower levels of corruption.
+This is theoretically strange; the only possibility that immediately strikes me is that it is party and pac money that is associated with corruption, not individual donations.
+```
 
@@
 The Corruption Reflections Index operates on a scale of zero to one (with a few outlying exceptions), indicating that the presence of individual-to-party limits is associated with a 11% decrease in the index.
-
-### Modeling changes in campaign limits and corruption convictions
-
-The final set of models (Table X) displays results from multiple first difference models designed to isolate the effect of changes in campaign finance laws on corruption convictions.
-None of the models find correlation between campaign finance limits and corruption convictions or corruption reflections.
-
-```{r CCI output to table latex, results="asis", eval=T}
-# Maaaaaybe figure out how to add back in those $ signs. 
-stargazer(cci.base.pooled, 
-          cci.limits.pooled, 
-          cci.limits.fixed,
-          cci.limits.fixed.time, 
-          type="latex",
-          title = "Panel Model of Contribution Limits and Corruption Convictions",
-          dep.var.labels = "Corruption Convictions Index",
-          covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)","Divided government","Binding one-term limit","Binding two-term limit","Real per capita income (1000s)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (1000s)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)"),
-  add.lines = list(c("Effects","Pooled","Pooled","Fixed","Two-Way")),     
-  header=FALSE, 
-  font.size = "small",
-  # column.sep.width = "-5pt",
-  digits = 2, digits.extra = 0,
-  no.space = TRUE,
-  omit.stat = "f"
-  )
-
-```
-
-```{r CCI output to png, eval=F}
-# Maaaaaybe figure out how to add back in those $ signs. 
-stargazer(cci.base.pooled, 
-          cci.limits.pooled, 
-          cci.limits.fixed,
-          cci.limits.fixed.time, 
-          type="html",
-          out="collateral/CCI.htm",
-          title = "Panel Model of Campaign Finance Limits and Corruption Convictions",
-          dep.var.labels = "Corruption Convictions Index",
-          covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)","Divided government","Binding one-term limit","Binding two-term limit","Real per capita income (1000s)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (1000s)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)"),
-  add.lines = list(c("Effects","Pooled","Pooled","Fixed","Two-Way")),     
-  header=FALSE, 
-  font.size = "small",
-  # column.sep.width = "-5pt",
-  digits = 2, digits.extra = 0,
-  no.space = TRUE,
-  omit.stat = "f"
-  )
-
-```
-
-```{r CRI output to table latex, results="asis", eval=T}
-stargazer(cri.base.pooled, 
-          cri.limits.pooled, 
-          cri.limits.fixed,
-          cri.limits.fixed.time, 
-          type="latex",
-          title = "Panel Model of Contribution Limits and Corruption Reflections",
-          dep.var.labels = "Corruption Reflections Index",
-          covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)","Divided government","Binding one-term limit","Binding two-term limit","Real per capita income (1000s)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (1000s)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)"),
-          add.lines = list(c("Effects","Pooled","Pooled","Fixed","Two-Way")),
-  header=FALSE, 
-  font.size = "small",
-  # column.sep.width = "-5pt", 
-  digits = 2, digits.extra = 0, 
-  no.space = TRUE,
-  omit.stat = "f" 
-  ) 
-```
-
-```{r CRI output to html, eval=F}
-stargazer(cri.base.pooled, 
-          cri.limits.pooled, 
-          cri.limits.fixed,
-          cri.limits.fixed.time, 
-          type="html",
-          out = "collateral/CRI.htm",
-          title = "Panel Model of Campaign Finance Limits and Corruption Reflections",
-          dep.var.labels = "Corruption Reflections Index",
-          covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)","Divided government","Binding one-term limit","Binding two-term limit","Real per capita income (1000s)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (1000s)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)"),
-          add.lines = list(c("Effects","Pooled","Pooled","Fixed","Two-Way")),
-  header=FALSE, 
-  font.size = "small",
-  # column.sep.width = "-5pt", 
-  digits = 2, digits.extra = 0, 
-  no.space = TRUE,
-  omit.stat = "f" 
-  ) 
-```
-
-\blandscape
-```{r DiD to table latex, results="asis", eval=T}
-stargazer(CCIDID01, CCIDID02, CCIDID03, CRIDID01, CRIDID02, CRIDID03,
-  type="latex", 
-  title = "First Differences Model of Changes in Contribution Limits Versus Convictions and Reflections",
-  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
-  covariate.labels=c("Individual limits removed","Individual limits imposed","Individual limit amount","Individual limits removed*amount","Individual limits imposed*amount",
-                     "PAC limits removed","PAC limits imposed","PAC limit amount","PAC limits removed*amount","PAC limits imposed*amount",
-                     "Individual-to-party limits removed","Individual-to-party limits imposed","Individual-to-party limit amount","Individual-to-party limits removed*amount","Individual-to-party limits imposed*amount"),
-  header=FALSE, 
-  font.size = "small",
-  # column.sep.width = "-5pt",
-  digits = 2, digits.extra = 0,
-  no.space = TRUE,
-  omit.stat = "f"
-  )
-```
-
-```{r DiD to htm, eval=F}
-stargazer(CCIDID01, CCIDID02, CCIDID03, CRIDID01, CRIDID02, CRIDID03,
-  type="html", 
-  title = "First Differences Model: Do Changes in Limits Lead to Lower Levels of Corruption?",
-  out = "collateral/DiD.htm",
-  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
-  covariate.labels=c("Individual limits removed","Individual limits imposed","Individual limit amount","Individual limits removed*amount","Individual limits imposed*amount",
-                     "PAC limits removed","PAC limits imposed","PAC limit amount","PAC limits removed*amount","PAC limits imposed*amount",
-                     "Individual-to-party limits removed","Individual-to-party limits imposed","Individual-to-party limit amount","Individual-to-party limits removed*amount","Individual-to-party limits imposed*amount"),
-  header=FALSE, 
-  font.size = "small",
-  # column.sep.width = "-5pt",
-  digits = 2, digits.extra = 0,
-  no.space = TRUE,
-  omit.stat = "f"
-  )
-```
-
-```{r webshots, eval=F}
-webshot("collateral/CCI.htm", "collateral/CCI.png")
-```
-
-\elandscape
 
@@
 Yet if the Court decides the burden of proof is on those looking to restrict political spending on narrow corruption grounds, reform advocates worried about money in politics have a steep empirical hill to climb, and likely only a few short years to do it.
-
-\newpage
-\blandscape
-
-## Appendix X: Initital modeling of independent and dependent variables
-```{r output of initial correlations, results="asis", eval=T}
-stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,CRIreg1, CRIreg2, CRIreg3, CRIreg5,
-  title = "Are campaign limits correlated with corruption convictions or reflections?",
-  type="latex",
-  dep.var.labels = c("Corruption Convictions Index","Corruption Reflections Index"),
-  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"),
-  add.lines = list(c("Effects","Two-Way","Two-Way","Two-Way","Two-Way","Two-Way","Two-Way","Two-Way","Two-Way")),
-  font.size = "small",
-  header = FALSE,
-  column.sep.width = "-5pt",
-  digits = 2, digits.extra = 0,
-  no.space = TRUE, 
-  omit.stat = "f"
-  )
-```
-\elandscape
 
@@
 
-<!-- Old code
-
-```{r (old) controlled panel modeling}
-#Next: Panel model of corruption against unemployment and high school? 
-testmodel01 <- plm(CCI ~ rpcinc_annual_new + unemp + high_school + logNumpop + citi6006 + grelimp, data = AltBarber, index = c("st","year"), effect="twoways")
-
-testmodel02 <- plm(CCI ~ jdiv + bindingonetermlimit + bindingtwotermlimit + rpcinc_annual_new + eousa + unemp + citi6006 + high_school + rgenrevpc + logNumpop + eopop + men_ineqincwag + grelimp + fedrepcons + urbanization_2 + logpop + inspop, data = AltBarber, index = c("st","year"), effect="twoways")
-
-testmodel03 <- plm(CCI ~ jdiv + bindingonetermlimit + bindingtwotermlimit + rpcinc_annual_new + eousa + unemp + citi6006 + high_school + rgenrevpc + logNumpop + eopop + men_ineqincwag + grelimp + fedrepcons + urbanization_2 + logpop + inspop + ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = AltBarber, index = c("st","year"), effect="twoways")
-
-testmodel05 <- plm(CCI ~ jdiv + bindingonetermlimit + bindingtwotermlimit + rpcinc_annual_new + eousa + unemp + citi6006 + high_school + rgenrevpc + logNumpop + eopop + men_ineqincwag + grelimp + urbanization_2 + logpop + inspop, data = AltBarber, index = c("st","year"), effect="twoways")
-```
-
-```{r controlled panel modeling}
-
-CCIcontrol01 <- plm(CCI ~ jdiv  # Divided government 
-                   + bindingonetermlimit # Binding one-term limit 
-                   + bindingtwotermlimit # Binding two-term limit 
-                   + rpcinc_annual_new # Real per capita income ($1000)
-                   + eopop # AUSAs per million population
-                   + unemp # Unemployment 
-                   + citi6006 # Citizen ideology measure 
-                   + high_school + # Percent high school graduates
-                   + rgenrevpc # Real per capita gov revenues ($1000)
-                   + men_ineqincwag # Inequality: Male wages
-                   + grelimp # Relative government wages
-                   + urbanization_2 # Urbanization 
-                   + logpop, # Log of population (millions)
-                   data = AltBarber, 
-                   index = c("st","year"), 
-                   effect="twoways")
-
-CCIcontrol02 <- plm(CCI ~ jdiv  # Divided government 
-                   + bindingonetermlimit # Binding one-term limit 
-                   + bindingtwotermlimit # Binding two-term limit 
-                   + rpcinc_annual_new # Real per capita income ($1000)
-                   + eopop # AUSAs per million population
-                   + unemp # Unemployment 
-                   + citi6006 # Citizen ideology measure 
-                   + high_school + # Percent high school graduates
-                   + rgenrevpc # Real per capita gov revenues ($1000)
-                   + men_ineqincwag # Inequality: Male wages
-                   + grelimp # Relative government wages
-                   + urbanization_2 # Urbanization 
-                   + logpop # Log of population (millions)
-                   + ind_limits_2010*ind_limits_dummy 
+```{r CRI heteroskedasticity checks,include=F}
+AltBarber2 <- AltBarber %>% drop_na()
+
+cri.log.iv2 <- plm(log(CRI+1) ~ 
+             ind_limits_2010*ind_limits_dummy 
            + ind2pty_limits_2010*ind2pty_limits_dummy 
-                   + pac_limits_2010*pac_limits_dummy, 
-                   data = AltBarber, 
-                   index = c("st","year"), 
-                   effect="twoways")
-
-CRIcontrol01 <- plm(CRI ~ jdiv  # Divided government 
-                   + bindingonetermlimit # Binding one-term limit 
-                   + bindingtwotermlimit # Binding two-term limit 
-                   + rpcinc_annual_new # Real per capita income ($1000)
-                   + eopop # AUSAs per million population
-                   + unemp # Unemployment 
-                   + citi6006 # Citizen ideology measure 
-                   + high_school + # Percent high school graduates
-                   + rgenrevpc # Real per capita gov revenues ($1000)
-                   + men_ineqincwag # Inequality: Male wages
-                   + grelimp # Relative government wages
-                   + urbanization_2 # Urbanization 
-                   + logpop, # Log of population (millions)
-                   data = AltBarber, 
-                   index = c("st","year"), 
-                   effect="twoways")
-
-CRIcontrol02 <- plm(CRI ~ jdiv  # Divided government 
-                   + bindingonetermlimit # Binding one-term limit 
-                   + bindingtwotermlimit # Binding two-term limit 
-                   + rpcinc_annual_new # Real per capita income ($1000)
-                   + eopop # AUSAs per million population
-                   + unemp # Unemployment 
-                   + citi6006 # Citizen ideology measure 
-                   + high_school + # Percent high school graduates
-                   + rgenrevpc # Real per capita gov revenues ($1000)
-                   + men_ineqincwag # Inequality: Male wages
-                   + grelimp # Relative government wages
-                   + urbanization_2 # Urbanization 
-                   + logpop # Log of population (millions)
-                   + ind_limits_2010*ind_limits_dummy 
+           + pac_limits_2010*pac_limits_dummy
+           + eopop # AUSAs per million population
+           + citi6006 # Citizen ideology measure 
+           + high_school + # Percent high school graduates
+           + rgenrevpc # Real per capita gov revenues ($1000)
+           + men_ineqincwag # Inequality: Male wages
+           + urbanization_2 # Urbanization 
+           + logpop, # Log of population (millions)
+           data = AltBarber2, 
+           model="pooling")
+
+# https://towardsdatascience.com/linear-and-bayesian-modelling-in-r-predicting-movie-popularity-6c8ef0a44184
+
+# Each numerical explanatory variable is linearly related to the response variable
+ggplot(augment(cri.log.iv2), aes(x = (AltBarber2$pac_limits_2010*AltBarber2$pac_limits_dummy), y = .resid))+
+ geom_point(colour = "red", size = 2, alpha = 0.5)+
+ theme_classic()+
+ geom_smooth(se=FALSE)+
+ labs(x = "?", y= "residuals")+
+ geom_hline(yintercept = 0, linetype = "dashed")
+
+# Residuals are distributed nearly normal with a mean of 0 
+par(mfrow=c(1,2))
+hist(cri.log.iv2$residuals, main = "Residual Distribution", 
+ xlab = "Residuals", col = "lightgreen")
+qqnorm(cri.log.iv2$residuals, col = "blue")
+qqline(cri.log.iv2$residuals, col = "red")
+
+# Variability of residuals is nearly constant 
+ggplot(augment(cri.log.iv2), aes(x= .fitted, y= .resid))+
+ geom_point(colour = "blue", size = 2, alpha = 0.5)+
+ theme_classic()+
+ geom_smooth()+
+ geom_hline(yintercept = 0, linetype = "dashed")+
+ labs(x = "Fitted", y = "Residuals")
+
+# The residuals are independant 
+ggplot(augment(cri.log.iv2), aes(x = seq_along(.resid), y = .resid)) + 
+ geom_point(colour = "lightgreen", size = 2.5, alpha = 0.6)+
+ theme_classic()+
+ labs(x = "Order of Collection", y = "Residuals", title = "Residuals vs. Order of Collection")
+
+# Do this for the other two independent variable pairs? 
+```
+
+```{r CCI Standardized coefficients,eval=T,include=F}
+# https://stackoverflow.com/questions/42076903/including-standardized-coefficients-in-a-stargazer-table
+cci.log.iv.lm <- lm(log(CCI+1) ~ 
+           ind_limits_2010*ind_limits_dummy 
            + ind2pty_limits_2010*ind2pty_limits_dummy 
-                   + pac_limits_2010*pac_limits_dummy, 
-                   data = AltBarber, 
-                   index = c("st","year"), 
-                   effect="twoways")
-
-```
-
-```{r post-Lentz panel effects modeling 1}
-# Include lagged dependent variables here. 
-# Erin's question: Are these "pooled"? 
-# Her effort to understand: Write out the formulas. 
-# Maybe helpful? https://onlinecourses.science.psu.edu/stat502/node/162/
-# Erin's suggestion https://www.princeton.edu/~otorres/Panel101R.pdf
-# On robust standard errors https://stats.stackexchange.com/questions/117052/replicating-statas-robust-option-in-r
-# And https://cran.r-project.org/web/packages/sandwich/vignettes/sandwich.pdf
-# And https://www.brodrigues.co/blog/2018-07-08-rob_stderr/, 
-# Pretty good explanation here https://www.methodsconsultants.com/tutorial/introduction-to-random-effects-models-including-hlm/
-# Go through this? https://github.com/tyleransom/EconometricsLabs/blob/master/tidyRcheatsheet.pdf
-summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC))
-summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways"))
-summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="within", effect="twoways"))
-summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="within"))
-summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="random")) #FAIL 
-summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC), model="pooling")
-summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC), model="within")
-
-#From Erin: 
-# •	Based on the results in Table 3, it appears that neither fixed effects or random effects were included in the panel estimation results.
-If that is correct, I’d argue including one of them could materially change the results.
-# o	I’m not sure which would be better: state fixed effects would limit the interpretation of results to effects within states, as opposed to across states but fixed effects are not a good idea when the error terms of each state are correlated (use a Hausman to check).
-Random effects assume no omitted variables, which can be a strong assumption.
-# o	This might be a useful resource: https://www.princeton.edu/~otorres/Panel101.pdf
-# o	Explain your treatment of standard errors (e.g., are you using robust se?).
-
-```
-
-```{r stargazer CCI latex, results="asis"}
-stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,
+           + pac_limits_2010*pac_limits_dummy
+           + jdiv  # Divided government 
+           # + bindingonetermlimit # Binding one-term limit 
+           # + bindingtwotermlimit # Binding two-term limit 
+           # + rpcinc_annual_new # Real per capita income ($1000)
+           + eopop # AUSAs per million population
+           # + unemp # Unemployment 
+           # + citi6006 # Citizen ideology measure 
+           + high_school + # Percent high school graduates
+           + rgenrevpc # Real per capita gov revenues ($1000)
+           # + men_ineqincwag # Inequality: Male wages
+           # + grelimp # Relative government wages
+           + urbanization_2 # Urbanization 
+           + logpop, # Log of population (millions)
+           data=AltBarber)
+
+cci.beta <- lm.beta(cci.log.iv.lm)
+```
+
+```{r CCI standardized coefficients,eval=T,results="asis",include=F}
+stargazer(
+  #cri.log.iv,
+  cci.log.iv.lm,
+  cci.beta,
   type="latex",
-  title = "Are campaign limits and corruption convictions correlated?",
-  dep.var.labels = c("Corruption Convictions Index"),
-  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"),
-  font.size = "small",
-  header=FALSE,
-  column.sep.width = "-15pt",
-  digits = 2, digits.extra = 2)
-```
-
-```{r stargzer CCI html}
-stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,
-  type="text", 
-  title = "Are campaign limits and corruption convictions correlated?",
-  out="collateral/CCI.htm",
-  dep.var.labels = c("Corruption Convictions Index"),
-  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
-```
-
-```{r stargazer CRI html}
-stargazer(CRIreg1, CRIreg2, CRIreg3, CRIreg5,
-  type="text", 
-  title = "Are campaign limits and corruption reflections correlated?",
-  out="collateral/CRI.htm",
-  dep.var.labels = c("Corruption Reflections Index"),
-  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
-```
-
-```{r stargazer CRI latex, results="asis"}
-stargazer(CRIreg1, CRIreg2, CRIreg3, CRIreg5,
+  coef = list(
+    cci.log.iv.lm$coefficients,
+    cci.beta$standardized.coefficients),
+  header=F,
+  font.size = "small")
+```
+
+```{r CRI Standardized coefficients,eval=T,include=F}
+# https://stackoverflow.com/questions/42076903/including-standardized-coefficients-in-a-stargazer-table
+cri.log.iv.lm <- lm(log(CRI+1) ~ 
+             ind_limits_2010*ind_limits_dummy 
+           + ind2pty_limits_2010*ind2pty_limits_dummy 
+           + pac_limits_2010*pac_limits_dummy
+           # jdiv  # Divided government 
+           # + bindingonetermlimit # Binding one-term limit 
+           # + bindingtwotermlimit # Binding two-term limit 
+           # + rpcinc_annual_new # Real per capita income ($1000)
+           + eopop # AUSAs per million population
+           # + unemp # Unemployment 
+           + citi6006 # Citizen ideology measure 
+           + high_school + # Percent high school graduates
+           + rgenrevpc # Real per capita gov revenues ($1000)
+           + men_ineqincwag # Inequality: Male wages
+           # + grelimp # Relative government wages
+           + urbanization_2 # Urbanization 
+           + logpop, # Log of population (millions)
+           data = AltBarber)
+
+cri.beta <- lm.beta(cri.log.iv.lm)
+
+# What in the world does any of *this* mean? It generates a bunch of stars on each standardized coefficient, which seems unlikely. 
+```
+
+```{r CRI standardized coefficients,eval=T,results="asis", include=F}
+stargazer(
+  #cri.log.iv,
+  cri.log.iv.lm,
+  cri.beta,
   type="latex",
-  title = "Are campaign limits and corruption reflections correlated?",
-  dep.var.labels = c("Corruption Reflections Index"),
-  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"),
-  font.size = "small",
-  header=FALSE,
-  column.sep.width = "-15pt",
-  digits = 2, digits.extra = 2)
-```
-
-```{r stargazer controlled panel}
-stargazer(CCIcontrol01,CCIcontrol02,CRIcontrol01,CRIcontrol02,
-  type="text", 
-  title = "Are campaign limits and correlated with corruption convictions or reflections?",
-  out="collateral/CCICRIcontrol.htm",
-  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
-  covariate.labels=c("Divided government", "Binding one-term limit"," Binding two-term limit","Real per capita income ($1000)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues ($1000)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)","Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)")
-  )
-```
-
-```{r 3 stargazer controlled panel latex, results="asis"}
-stargazer(CCIcontrol01,CCIcontrol02,CRIcontrol01,CRIcontrol02,
-  title = "Are campaign limits and correlated with corruption convictions or reflections?",
-  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
-  covariate.labels=c("Divided government", "Binding one-term limit"," Binding two-term limit","Real per capita income (thousands)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (thousands)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)","Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"),
-  font.size = "small",
-  header=FALSE,
-  column.sep.width = "-15pt",
-  no.space = T,
-  digits = 2, digits.extra = 2)
-```
-
-```{r stargazer DiD}
-stargazer(CCIDID01, CCIDID02, CCIDID03, CRIDID01, CRIDID02, CRIDID03,
-  type="text", 
-  title = "Do changes in limits lead to lower levels of corruption?",
-  out="collateral/DiD.htm",
-  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
-  covariate.labels=c("Individual limits removed","Individual limits imposed","Individual limit amount","Individual limits removed*amount","Individual limits imposed*amount",
-                     "PAC limits removed","PAC limits imposed","PAC limit amount","PAC limits removed*amount","PAC limits imposed*amount",
-                     "Individual-to-party limits removed","Individual-to-party limits imposed","Individual-to-party limit amount","Individual-to-party limits removed*amount","Individual-to-party limits imposed*amount"))
-
-```
-
-\blandscape
-```{r stargazer DiD latex, results="asis"}
-stargazer(CCIDID01, CCIDID02, CCIDID03, CRIDID01, CRIDID02, CRIDID03,
-  title = "Do changes in limits lead to lower levels of corruption?",
-  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
-  covariate.labels=c("Individual limits removed","Individual limits imposed","Individual limit amount","Individual limits removed*amount","Individual limits imposed*amount",
-                     "PAC limits removed","PAC limits imposed","PAC limit amount","PAC limits removed*amount","PAC limits imposed*amount",
-                     "Individual-to-party limits removed","Individual-to-party limits imposed","Individual-to-party limit amount","Individual-to-party limits removed*amount","Individual-to-party limits imposed*amount"),
-  font.size = "small", 
-  header = FALSE,
-  column.sep.width = "-15pt",
-  digits = 2, digits.extra = 2,
-  no.space = TRUE)
-
-```
-\elandscape
-
-old code -->
+  coef = list(
+    cri.log.iv.lm$coefficients,
+    cri.beta$standardized.coefficients),
+  header = F,
+  font.size = "small")
+```

### 2020-04-03 Paper-2020.Rmd
Includes submitted JOPskeleton

--- 2020-04-03 Paper 2020.Rmd
@@
 Using state-level data from 1990-2012 on contribution limits, corruption convictions, and media mentions of corruption, this paper employs linear panel regressio to test whether campaign contribution limits are associated with lower levels of corruption convictions or media mentions of corruption.
-These methods find associations between corruption convictions and the presence of limits on donations to political action committees (PACs), the amount of those limits, and the presence of limts on donations to parties.
-Applying these methods to recently developed measures of media mentions of corruption suggests that these data may require further development.[^SPSA]
+These methods find associations between corruption convictions and the presence of limits on donations to political action committees (PACs), the amount of those limits, and the presence of limits on donations to parties; individual donation limits do not prove associated with either measure of corruption.[^SPSA]
 
@@
 
-```{r Barber summary stats latex, results="asis",eval=T,include=F}
-# This is what fails to knit (see error below) 
+```{r Barber summary stats latex, results="asis",eval=T}
 stargazer(as.data.frame(subset(BarberNAs[,3:6])), digits=0, type="latex", title="Descriptive Statistics for State Level Campaign Finance Limits", covariate.labels = c("Individual Limits","Individual-to-Party Limits","Party Limits", "PAC Limits"), header=F,
@@
 The fourth data set provides controls for the panel model.
-In their 2012 work examining variation in prosecutorial resources, Alt and Lassen follow Glaeser and Saks (2006) in controlling for income and education levels, size of government, legislature control, and urbanization (see Appendix X).
+In their 2012 work examining variation in prosecutorial resources, Alt and Lassen follow Glaeser and Saks (2006) in controlling for income and education levels, size of government, legislature control, and urbanization (see Appendix A).
 Alt and Lassen's data set runs from 1976-2004.
@@
 #### Corruption Convictions Index versus campaign contribution limits in a given state-year: 
-$(log)Convictions = \alpha_{state} + \beta_{1}{indiv.dummy} + \beta_{2}{indiv.dummy}*{indiv.limit} + \beta_{3}{pac.dummy} + \beta_{4}{pac.dummy}*{pac.limit} + \beta_{5}{indiv-to-party.dummy} + \beta_{6}{indiv-to-party.dummy}*{indiv-to-party.limit} + Controls + \epsilon$
+$(log)Convictions = \alpha_{state} + \\ \hspace{3.2cm} \beta_{1}{indiv.dummy} + \beta_{2}{indiv.dummy}\times{indiv.limit} + \\ \hspace{3.2cm} \beta_{3}{pac.dummy} + \beta_{4}{pac.dummy}\times{pac.limit} + \\ \hspace{3.2cm} \beta_{5}{indiv-to-party.dummy} + \beta_{6}{indiv-to-party.dummy}\times{indiv-to-party.limit} + \\ \hspace{3.2cm} Controls\times\gamma + \epsilon$ <!---->
 
 #### Corruption Reflections Index versus campaign contributions in a given state-year: 
-$(log)Reflections = \alpha_{state} + \beta_{1}{indiv.dummy} + \beta_{2}{indiv.dummy}*{indiv.limit} + \beta_{3}{pac.dummy} + \beta_{4}{pac.dummy}*{pac.limit} + \beta_{5}{indiv-to-party.dummy} + \beta_{6}{indiv-to-party.dummy}*{indiv-to-party.limit} + Controls + \epsilon$
+$(log)Reflections = \alpha_{state} + \\ \hspace{3.1cm} \beta_{1}{indiv.dummy} + \beta_{2}{indiv.dummy}\times{indiv.limit} + \\ \hspace{3.1cm} \beta_{3}{pac.dummy} + \beta_{4}{pac.dummy}\times{pac.limit} + \\ \hspace{3.1cm} \beta_{5}{indiv.to.party.dummy} + \beta_{6}{indiv.to.party.dummy}\times{indiv.to.party.limit} + \\ \hspace{3.1cm} Controls\times\gamma + \epsilon$
 
 ##Results 
+The results of the panel regressions reveal multiple correlations between state-level campaign limits and Corruption Convictions; and one correlation between those limits and the Corruption Reflections Index.
+
+The first set of models (Table 3) measures the association of various campaign contribution limits with the Corruption Convictions Index.
+The first model includes only control variables; the second model adds in campaign finance limit variables.
+The third layers in fixed effects at the state level, fixed time effects, and logged study variables; the fourth removes fixed effects but maintains the logged variables.
+Not included here are: models with random effects, models with unlogged dependent variables, and models with other combinations of fixed effects and variable transformations.
+The resulting models identify correlations between the CCI and the existence individual-to-party limits: The presence of such limits is associated with _greater_ corruption as measured by convictions.
+In Model 2, with unlogged independent variables, both the presence and amount of limits on PAC contributions to campaigns is associated with lower levels of corruption measured in terms of convictions.
+
+The second set of models (Table 4) walks through the same progression of models, measuring the association of various campaign contribution limits and the Corruption Reflections Index (CRI).
+Model 4, which includes logged independent and dependent variables but not fixed effects, demonstrates that the presence of individual-to-party limits is associated with lower levels of corruption as measured by media mention of corruption.
+As with the CCI models in Table 3, the presence and amount of PAC limits, when unlogged, are associated with lower levels of corruption reflections.
+
+<!--also fails to find a relationship between state-level campaign contribution limits and media mentions of corruption as measured by the Corruption Reflections Index, with one exception: The presence of limits on what an individual can give to a party is associated with a 0.11 point decline in the Corruption Reflections Index.
+The Corruption Reflections Index operates on a scale of zero to one (with a few outlying exceptions), indicating that the presence of individual-to-party limits is associated with a 11% decrease in the index.
+-->
 
@@
 
-cci.log.iv.fixed.time <- plm(log(CCI+1) ~ 
-           ind_limits_2010*ind_limits_dummy 
-           + ind2pty_limits_2010*ind2pty_limits_dummy 
-           + pac_limits_2010*pac_limits_dummy
+cci.log.iv.fixed.time <- plm(log(CCI+1) 
+           ~ log(ind_limits_2010)*ind_limits_dummy 
+           + log(ind2pty_limits_2010)*ind2pty_limits_dummy 
+           + log(pac_limits_2010)*pac_limits_dummy
            + jdiv  # Divided government 
@@
            effect="twoways")
+
+#### Single-variable models ####
+cci.ind <- plm(
+           log(CCI+1) ~ 
+           log(ind_limits_2010)*ind_limits_dummy + 
+           #log(ind2pty_limits_2010)*ind2pty_limits_dummy + 
+           #log(pac_limits_2010)*pac_limits_dummy + 
+           jdiv  # Divided government
+           # + bindingonetermlimit # Binding one-term limit
+           # + bindingtwotermlimit # Binding two-term limit
+           # + rpcinc_annual_new # Real per capita income ($1000)
+           + eopop # AUSAs per million population
+           # + unemp # Unemployment
+           # + citi6006 # Citizen ideology measure
+           + high_school + # Percent high school graduates
+           + rgenrevpc # Real per capita gov revenues ($1000)
+           # + men_ineqincwag # Inequality: Male wages
+           # + grelimp # Relative government wages
+           + urbanization_2 # Urbanization
+           + logpop, # Log of population (millions)
+           data = AltBarber,
+           model="pooling")
+
+cci.ind2pty <- plm(
+           log(CCI+1) ~ 
+           #log(ind_limits_2010)*ind_limits_dummy + 
+           log(ind2pty_limits_2010)*ind2pty_limits_dummy + 
+           #log(pac_limits_2010)*pac_limits_dummy + 
+           jdiv  # Divided government
+           # + bindingonetermlimit # Binding one-term limit
+           # + bindingtwotermlimit # Binding two-term limit
+           # + rpcinc_annual_new # Real per capita income ($1000)
+           + eopop # AUSAs per million population
+           # + unemp # Unemployment
+           # + citi6006 # Citizen ideology measure
+           + high_school + # Percent high school graduates
+           + rgenrevpc # Real per capita gov revenues ($1000)
+           # + men_ineqincwag # Inequality: Male wages
+           # + grelimp # Relative government wages
+           + urbanization_2 # Urbanization
+           + logpop, # Log of population (millions)
+           data = AltBarber,
+           model="pooling")
+
+cci.pac <- plm(
+           log(CCI+1) ~ 
+           #log(ind_limits_2010)*ind_limits_dummy + 
+           #log(ind2pty_limits_2010)*ind2pty_limits_dummy + 
+           log(pac_limits_2010)*pac_limits_dummy + 
+           jdiv  # Divided government
+           # + bindingonetermlimit # Binding one-term limit
+           # + bindingtwotermlimit # Binding two-term limit
+           # + rpcinc_annual_new # Real per capita income ($1000)
+           + eopop # AUSAs per million population
+           # + unemp # Unemployment
+           # + citi6006 # Citizen ideology measure
+           + high_school + # Percent high school graduates
+           + rgenrevpc # Real per capita gov revenues ($1000)
+           # + men_ineqincwag # Inequality: Male wages
+           # + grelimp # Relative government wages
+           + urbanization_2 # Urbanization
+           + logpop, # Log of population (millions)
+           data = AltBarber,
+           model="pooling")
+
+stargazer(cci.ind,cci.ind2pty,cci.pac,type="text")
 
@@
   cci.log.iv, # F Stat down? 
+  cci.log.iv.fixed.time, # F stat way down 
   cci.log.iv.log, # F Stat down further 
   #cci.log.iv.fixed, # AR2 Stat bottoms out 
-  cci.log.iv.fixed.time, 
   type="latex",
@@
                      "Divided government",
-                     "AUSAs per population (MMs)"),
-                     # "% high school grads",
-                     # "Govt revenues/capita ($1000s)",
-                     # "Urbanization",
-                     # "Log of population (MMs)"),
-  add.lines = list(c(" ","Base Model","With IVs","Pooled","FE"))
+                     "AUSAs per population (MMs)",
+                     "Percent high school grads",
+                     "Gov revenues per capita (1000s)",
+                     "Urbanization",
+                     "Log of population (MMs)"),
+  add.lines = list(c(" ","Base Model","Full Model","Fixed Effects","Pooled"))
   )
@@
 cri.log.iv.fixed.time <- plm(log(CRI+1) ~ 
-             ind_limits_2010*ind_limits_dummy 
-           + ind2pty_limits_2010*ind2pty_limits_dummy 
-           + pac_limits_2010*pac_limits_dummy
+             log(ind_limits_2010)*ind_limits_dummy 
+           + log(ind2pty_limits_2010)*ind2pty_limits_dummy 
+           + log(pac_limits_2010)*pac_limits_dummy
            # jdiv  # Divided government 
@@
            effect="twoways")
+
+#### Single-variable models ####
+cri.ind <- plm(
+           log(CRI+1) ~ 
+           log(ind_limits_2010)*ind_limits_dummy + 
+           #log(ind2pty_limits_2010)*ind2pty_limits_dummy + 
+           #log(pac_limits_2010)*pac_limits_dummy + 
+           # jdiv  # Divided government 
+           # + bindingonetermlimit # Binding one-term limit 
+           # + bindingtwotermlimit # Binding two-term limit 
+           # + rpcinc_annual_new # Real per capita income ($1000)
+           + eopop # AUSAs per million population
+           # + unemp # Unemployment 
+           + citi6006 # Citizen ideology measure 
+           + high_school + # Percent high school graduates
+           + rgenrevpc # Real per capita gov revenues ($1000)
+           + men_ineqincwag # Inequality: Male wages
+           # + grelimp # Relative government wages
+           + urbanization_2 # Urbanization 
+           + logpop, # Log of population (millions)
+           data = AltBarber,
+           model="pooling")
+
+cri.ind2pty <- plm(
+           log(CRI+1) ~ 
+           #log(ind_limits_2010)*ind_limits_dummy + 
+           log(ind2pty_limits_2010)*ind2pty_limits_dummy + 
+           #log(pac_limits_2010)*pac_limits_dummy + 
+           # jdiv  # Divided government 
+           # + bindingonetermlimit # Binding one-term limit 
+           # + bindingtwotermlimit # Binding two-term limit 
+           # + rpcinc_annual_new # Real per capita income ($1000)
+           + eopop # AUSAs per million population
+           # + unemp # Unemployment 
+           + citi6006 # Citizen ideology measure 
+           + high_school + # Percent high school graduates
+           + rgenrevpc # Real per capita gov revenues ($1000)
+           + men_ineqincwag # Inequality: Male wages
+           # + grelimp # Relative government wages
+           + urbanization_2 # Urbanization 
+           + logpop, # Log of population (millions)
+           data = AltBarber,
+           model="pooling")
+
+cri.pac <- plm(
+           log(CRI+1) ~ 
+           #log(ind_limits_2010)*ind_limits_dummy + 
+           #log(ind2pty_limits_2010)*ind2pty_limits_dummy + 
+           log(pac_limits_2010)*pac_limits_dummy + 
+           # jdiv  # Divided government 
+           # + bindingonetermlimit # Binding one-term limit 
+           # + bindingtwotermlimit # Binding two-term limit 
+           # + rpcinc_annual_new # Real per capita income ($1000)
+           + eopop # AUSAs per million population
+           # + unemp # Unemployment 
+           + citi6006 # Citizen ideology measure 
+           + high_school + # Percent high school graduates
+           + rgenrevpc # Real per capita gov revenues ($1000)
+           + men_ineqincwag # Inequality: Male wages
+           # + grelimp # Relative government wages
+           + urbanization_2 # Urbanization 
+           + logpop, # Log of population (millions)
+           data = AltBarber,
+           model="pooling")
+
+stargazer(cri.ind,cri.ind2pty,cri.pac,type="text")
 
@@
   cri.log.iv, # Adding in IVs. AR2 up, F Stat down 
+  cri.log.iv.fixed.time, # AR2 now negative 
   cri.log.iv.log, # Logging IVS. AR2 down, F Stat down 
   #cri.log.iv.fixed, # AR2 to zero 
-  cri.log.iv.fixed.time, # AR2 now negative 
   type="latex",
@@
                      "Log of population (millions)"),
-  add.lines = list(c(" ","Base Model","With IVs","Pooled","FE"))
+  add.lines = list(c(" ","Base Model","Full Model","Fixed Effects","Pooled"))
   )
@@
 
-### Modeling campaign limits and corruption convictions 
-The results of the panel regressions reveal no correlation between state-level campaign contribution limits and corruption, with one exception: There is a statistically significant relationship between the presence of individual-to-party limits and the Corruption Reflections Index.
-
-The first set of models (Table X) measures the association of various campaign contribution limits with the Corruption Convictions Index.
-The first model includes only control variables; the second model adds in campaign finance limit variables.
-The third layers in fixed effects at the state level, and the fourth incorporates fixed time effects.
-Not included are random effects models, which showed no improvement in the models.
-None of those results are significant at the p<0.05 level, implying that we cannot claim their effect is distinguishable from no effect.
-I interpret these results as showing no relationship between the presence or amount of state-level contribution limits and levels of corruption as measured by the Corruption Convictions Index.
-
-The second set of models (Table X) also fails to find a relationship between state-level campaign contribution limits and media mentions of corruption as measured by the Corruption Reflections Index, with one exception: The presence of limits on what an individual can give to a party is associated with a 0.11 point decline in the Corruption Reflections Index.
-The Corruption Reflections Index operates on a scale of zero to one (with a few outlying exceptions), indicating that the presence of individual-to-party limits is associated with a 11% decrease in the index.
-
 ## Discussion
-At least one group of models allows for a straightforward interpretation.
-The panel models examining the relationship between state-level campaign finance laws and the Corruption Convictions Index fail to show any correlation between state level campaign finance laws and levels of corruption as measured by corruptions convictions, even controlling for variation in enforcement across the states.
-
-The results for the models examining the relationship between campaign finance limits and the Corruption Reflections Index are less clear.
-The pair of stars in the fourth model suggest that the presence of individual-to-party limits is associated with a decrease in the Corruption Reflections Index.
-There is a less than 1% probability that the results are due to chance.
-How could this be, given that (a) the presence of individual-to-party limits has no association with a change the Corruption Convictions Index; (b) none of the other contribution limits are associated with a change in the Corruption Reflections Index; and (c) there is no correlation between the dollar amount of the individual-to-party limit and the Corruption Reflections Index?
-In practice, this would mean that states with individual-to-party limits also see lower levels of Associated Press reporting on corruption, but that once limits of any kind are imposed, the level of limit does not matter.
-It would also mean that only individual-to-party limits matter, not individual-to-candidate or PAC-to-candidate limits.
-Lastly, it would imply that the presence of such limits has an effect on reporting about corruption, but not on corruption convictions.
-
-There is limited theoretical explanation for this outcome.
-It could be that AP reporters are somehow more likely to report on conviction allegations against political parties than against individual candidates or PACs, even where those allegations don’t result in greater levels of convictions, and only in states where the absence of contribution limits allows for a clean, “no limits on contributions” narrative.
-It is more likely, however, that these results call into question the robustness of Dincer and Johnston’s Corruption Reflections Index.
-As mentioned above, further research could carry forward their text-mining method into a greater number and variety of outlets, in order to find a measure of corruption reporting more tightly correlated with other measures.
-
-## Conclusion
-There at least two distinct and opposing ways to explain these results, viewpoints that will come into direct and public conflict if the Court chooses to hear a first amendment challenge to campaign contribution limits.
-
-The first interpretation is that campaign finance and quid pro quo corruption are simply not related.
-How could this be?
-One explanation is that the measures of corruption used here fail to capture most corruption, which is never prosecuted.
-This explanation, however, would rest on the assumption that corruption is unequally captured across states over time.
-A second explanation is that corruption occurs regardless of campaign finance laws: Politicians likely to engage in corrupt behavior will do so outside of the campaign finance regime, where their transactions would be most visible.
-
-The legal implications of this interpretation are clear and material.
+```{r skew,include=F}
+library(moments) 
+PAC_limits <- AltBarber$pac_limits_2010*AltBarber$pac_limits_dummy
+skewness(PAC_limits) # 3.468 
+PAC_limits_log <- log(AltBarber$pac_limits_2010)*AltBarber$pac_limits_dummy
+skewness(PAC_limits_log) # -0.2467 
+```
+
+On their face, the models above support two tentative conclusions and present one puzzle: First, in none of the specifications above are limits on individuals' campaign contributions correlated with either corruption convictions or corruption reflections.
+This evidence of absence is not absence of evidence, of course, but consistent with the hypothesis that individual donations are not a primary source of political corruption.
+
+The second tentative conclusion is that there is a yet-unspecified relationship between limits on PAC contributions and corruption.
+This is true in models in which _unlogged_ PAC limits are included in the models, but not when that variable, with a skew of 3.468, is logged.
+Given the non-normality of that variable, even when logged, it may be that a different transformation would more accurately specify these relationships.
+If those relationships hold, two possibilites may explain why limiting PAC donations might be associated with lower levels of corruption convictions and media coverage when individual limits are not.
+First, it may be that actors engaged enough in the political process to be able to corrupt public officials are likely to be entwined with, and work through, political action committees.
+Second, it may be that when corruption is routed through an institution such as a PAC, the number of people involved may make it more likely to be discovered, prosecuted and reported.
+
+```{r corr,include=F}
+cor.test(AltBarber$CRI,AltBarber$CCI) # 0.038
+```
+
+The puzzle in this data is the varying effects of limits on individual-to-party donations.
+The amount of those limits has no relationship in these models to either corruption convictions or reflections.
+But the presence of a limit is associated with _higher_ levels of corruption convictions and _lower_ levels of media coverage of corruption.[^SV] This suggests that states with limits on individual donations to political parties see more corruption, but less reporting on those convictions.
+
+[^SV]: These relationships remain robust to changes in model specification, including when other donation limit variables are removed from the model.
+
+What are the legal and policy implications of these results?
 The Supreme Court presently equates political donations with political speech, meaning that it is protected by the first amendment, but that preventing corruption or its appearance in the political system is so important that first amendment rights can be abridged to ensure it.
 For the Court, no other justification--including creating a more informed electorate, or stimulating more competitive elections, or equality of financial participation in elections--is an important enough concern that we should limit political speech in the form of campaign donations.
-If there is no link between campaign contribution limits and corruption,  the Court may conclude that there is no reason to abridge US citizens’ first amendment rights by limiting campaign donations.
-
-In order to make this anti-reform argument, some important limitations must be dealt with.
+The results above suggest that state-level restrictions on donations from individuals may not be demonstrably associated with lower corruption, but that other types of donation limits (on contributions from PACs to campaigns, and from individuals to parties) may indeed be associated with lowering corruption.
+Such results might allow for courts to be more open to the possibility of restricting donations to and from organized groups such as PACs and parties, without having to restrict individual donations and participation in the electoral process.
+
+<!--In order to make this anti-reform argument, some important limitations must be dealt with.
 First, the Corruptions Conviction Index used above has multiple issues, as summarized above.
@@
 The measures of corruption that academics have used to date have serious limitations.
-Yet if the Court decides the burden of proof is on those looking to restrict political spending on narrow corruption grounds, reform advocates worried about money in politics have a steep empirical hill to climb, and likely only a few short years to do it.
+Yet if the Court decides the burden of proof is on those looking to restrict political spending on narrow corruption grounds, reform advocates worried about money in politics have a steep empirical hill to climb, and likely only a few short years to do it.-->
 
 \newpage
-
-##Appendix X: Descriptions and Descriptive Statistics of Control Variables 
+## Appendix A: Descriptions and Descriptive Statistics of Control Variables 
 In their 2012 paper "Enforcement and Public Corruption: Evidence from the American States," Glaeser and Saks make use of the following control variables, which we have included here:
@@
 \newpage
-
-##References 
+## References 
 <!--Add new authors (see Google doc) and data. R packages?-->

### 2020-04-03 draft-master/inst/rmarkdown/templates/jop/skeleton/JOPskeleton.Rmd
Includes submitted JOPskeleton

--- 2020-04-03 Paper-2020.Rmd
@@
   | Evidence from the 50 states
-author: "Mark C. Hand"
-date: ""
-output: pdf_document
-header-includes:
-- \usepackage{pdflscape}
-- \newcommand{\blandscape}{\begin{landscape}}
-- \newcommand{\elandscape}{\end{landscape}}
-- \usepackage{setspace}
-- \doublespacing
+author: "Mark Hand"
+abstract: "Since its 1976 _Buckley v.
+Valeo_ decision, the Supreme Court has allowed only two potential justifications for limiting campaign donations: To prevent corruption or the appearance of corruption.
+Do campaign finance limits actually mitigate corruption or its appearance?
+As current challenges to contribution limits wind their way through federal courts, the answer to this question will inform the  Supreme Court’s decision to uphold or strike down remaining limits on political campaign contributions.
+Using state-level data from 1990-2012 on contribution limits, corruption convictions, and media mentions of corruption, this paper finds associations between corruption convictions and the presence of limits on donations to political action committees (PACs), the amount of those limits, and the presence of limits on donations to parties.
+Individual donation limits, however, do not prove associated with either measure of corruption."
+anonymized: true
+output:
+    draft::jop_submission:
+        keep_tex: yes
 ---
-
-Since the 1970s, the U.S.
-Supreme Court has maintained that nearly all limits on political spending violate the first amendment’s protection of free speech.
-In its 1976 _Buckley v.
-Valeo_ decision, the Court laid out only two admissible justifications for limiting campaign donations: To prevent corruption or the appearance of corruption.
-But do campaign finance limits actually prevent corruption or its appearance?
-As current challenges to contribution limits wind their way through federal courts, the answer to this question will inform the Supreme Court’s decision to uphold or strike down remaining limits on political campaign contributions.
-Using state-level data from 1990-2012 on contribution limits, corruption convictions, and media mentions of corruption, this paper employs linear panel regressio to test whether campaign contribution limits are associated with lower levels of corruption convictions or media mentions of corruption.
-These methods find associations between corruption convictions and the presence of limits on donations to political action committees (PACs), the amount of those limits, and the presence of limits on donations to parties; individual donation limits do not prove associated with either measure of corruption.[^SPSA]
-
-[^SPSA]: An earlier version of this paper was presented at the Annual Meeting of the Southern Political Science Association in January 2019.
-Analyses available on [GitHub](https://github.com/markchand/Money-in-Politics).
 
@@
 library(haven) # import .dta
-library (MASS) # For binomial regression 
+library(MASS) # For binomial regression 
 library(tidyverse) # everything; placed here because of MASS::select() overlap 
@@
 library(broom) # for augment()
+library(devtools) # For downloading packages from github 
+install_github("duckmayr/draft") # For JOP template 
 theme_set(theme_classic()) # Sets default theme
@@
 # http://epstein.wustl.edu/research/LPE.Alt.pdf
-AltLassen <- read_dta("data/Replication/AltLassenJLEO.dta")
+AltLassen <- read_dta("~/Documents/GitHub/Money-in-Politics/data/Replication/AltLassenJLEO.dta")
 
@@
 
-##Introduction
+## Introduction
 In 1976, the Supreme Court ruled in _Buckley v.
@@
 
-##Prior Work 
+## Prior Work 
 Since the Buckley v.
@@
 
-##Data and Design  
+## Data and Design  
 In this paper, I build upon the growing body of state-level political science research to ask whether campaign contribution limits at the state level associated with lower levels of corruption.
@@
 
-##Results 
+## Results 
 The results of the panel regressions reveal multiple correlations between state-level campaign limits and Corruption Convictions; and one correlation between those limits and the Corruption Reflections Index.
@@
 \newpage
+
 ## Appendix A: Descriptions and Descriptive Statistics of Control Variables 
@@
 \newpage
+
 ## References 
@@
 
-```{r CRI heteroskedasticity checks,include=F}
-AltBarber2 <- AltBarber %>% drop_na()
-
-cri.log.iv2 <- plm(log(CRI+1) ~ 
-             ind_limits_2010*ind_limits_dummy 
-           + ind2pty_limits_2010*ind2pty_limits_dummy 
-           + pac_limits_2010*pac_limits_dummy
-           + eopop # AUSAs per million population
-           + citi6006 # Citizen ideology measure 
-           + high_school + # Percent high school graduates
-           + rgenrevpc # Real per capita gov revenues ($1000)
-           + men_ineqincwag # Inequality: Male wages
-           + urbanization_2 # Urbanization 
-           + logpop, # Log of population (millions)
-           data = AltBarber2, 
-           model="pooling")
-
-# https://towardsdatascience.com/linear-and-bayesian-modelling-in-r-predicting-movie-popularity-6c8ef0a44184
-
-# Each numerical explanatory variable is linearly related to the response variable
-ggplot(augment(cri.log.iv2), aes(x = (AltBarber2$pac_limits_2010*AltBarber2$pac_limits_dummy), y = .resid))+
- geom_point(colour = "red", size = 2, alpha = 0.5)+
- theme_classic()+
- geom_smooth(se=FALSE)+
- labs(x = "?", y= "residuals")+
- geom_hline(yintercept = 0, linetype = "dashed")
-
-# Residuals are distributed nearly normal with a mean of 0 
-par(mfrow=c(1,2))
-hist(cri.log.iv2$residuals, main = "Residual Distribution", 
- xlab = "Residuals", col = "lightgreen")
-qqnorm(cri.log.iv2$residuals, col = "blue")
-qqline(cri.log.iv2$residuals, col = "red")
-
-# Variability of residuals is nearly constant 
-ggplot(augment(cri.log.iv2), aes(x= .fitted, y= .resid))+
- geom_point(colour = "blue", size = 2, alpha = 0.5)+
- theme_classic()+
- geom_smooth()+
- geom_hline(yintercept = 0, linetype = "dashed")+
- labs(x = "Fitted", y = "Residuals")
-
-# The residuals are independant 
-ggplot(augment(cri.log.iv2), aes(x = seq_along(.resid), y = .resid)) + 
- geom_point(colour = "lightgreen", size = 2.5, alpha = 0.6)+
- theme_classic()+
- labs(x = "Order of Collection", y = "Residuals", title = "Residuals vs. Order of Collection")
-
-# Do this for the other two independent variable pairs? 
-```
-
-```{r CCI Standardized coefficients,eval=T,include=F}
-# https://stackoverflow.com/questions/42076903/including-standardized-coefficients-in-a-stargazer-table
-cci.log.iv.lm <- lm(log(CCI+1) ~ 
-           ind_limits_2010*ind_limits_dummy 
-           + ind2pty_limits_2010*ind2pty_limits_dummy 
-           + pac_limits_2010*pac_limits_dummy
-           + jdiv  # Divided government 
-           # + bindingonetermlimit # Binding one-term limit 
-           # + bindingtwotermlimit # Binding two-term limit 
-           # + rpcinc_annual_new # Real per capita income ($1000)
-           + eopop # AUSAs per million population
-           # + unemp # Unemployment 
-           # + citi6006 # Citizen ideology measure 
-           + high_school + # Percent high school graduates
-           + rgenrevpc # Real per capita gov revenues ($1000)
-           # + men_ineqincwag # Inequality: Male wages
-           # + grelimp # Relative government wages
-           + urbanization_2 # Urbanization 
-           + logpop, # Log of population (millions)
-           data=AltBarber)
-
-cci.beta <- lm.beta(cci.log.iv.lm)
-```
-
-```{r CCI standardized coefficients,eval=T,results="asis",include=F}
-stargazer(
-  #cri.log.iv,
-  cci.log.iv.lm,
-  cci.beta,
-  type="latex",
-  coef = list(
-    cci.log.iv.lm$coefficients,
-    cci.beta$standardized.coefficients),
-  header=F,
-  font.size = "small")
-```
-
-```{r CRI Standardized coefficients,eval=T,include=F}
-# https://stackoverflow.com/questions/42076903/including-standardized-coefficients-in-a-stargazer-table
-cri.log.iv.lm <- lm(log(CRI+1) ~ 
-             ind_limits_2010*ind_limits_dummy 
-           + ind2pty_limits_2010*ind2pty_limits_dummy 
-           + pac_limits_2010*pac_limits_dummy
-           # jdiv  # Divided government 
-           # + bindingonetermlimit # Binding one-term limit 
-           # + bindingtwotermlimit # Binding two-term limit 
-           # + rpcinc_annual_new # Real per capita income ($1000)
-           + eopop # AUSAs per million population
-           # + unemp # Unemployment 
-           + citi6006 # Citizen ideology measure 
-           + high_school + # Percent high school graduates
-           + rgenrevpc # Real per capita gov revenues ($1000)
-           + men_ineqincwag # Inequality: Male wages
-           # + grelimp # Relative government wages
-           + urbanization_2 # Urbanization 
-           + logpop, # Log of population (millions)
-           data = AltBarber)
-
-cri.beta <- lm.beta(cri.log.iv.lm)
-
-# What in the world does any of *this* mean? It generates a bunch of stars on each standardized coefficient, which seems unlikely. 
-```
-
-```{r CRI standardized coefficients,eval=T,results="asis", include=F}
-stargazer(
-  #cri.log.iv,
-  cri.log.iv.lm,
-  cri.beta,
-  type="latex",
-  coef = list(
-    cri.log.iv.lm$coefficients,
-    cri.beta$standardized.coefficients),
-  header = F,
-  font.size = "small")
-```
+<!-- As instructed by Noorah:  
+rmarkdown::render("/Users/markchand/Documents/GitHub/Money-in-Politics/draft-master/inst/rmarkdown/templates/jop/skeleton/JOPskeleton.Rmd", output_format="latex_document") -->

### 2020-04-03 draft-master/inst/rmarkdown/templates/jop/skeleton/JOPskeleton.tex
Includes submitted JOPskeleton

--- 2020-04-03 draft-master/inst/rmarkdown/templates/jop/skeleton/JOPskeleton.Rmd
@@
----
-title: | 
-  | Campaign Contribution Limits and Corruption 
-  | Evidence from the 50 states
-author: "Mark Hand"
-abstract: "Since its 1976 _Buckley v.
-Valeo_ decision, the Supreme Court has allowed only two potential justifications for limiting campaign donations: To prevent corruption or the appearance of corruption.
-Do campaign finance limits actually mitigate corruption or its appearance?
-As current challenges to contribution limits wind their way through federal courts, the answer to this question will inform the  Supreme Court’s decision to uphold or strike down remaining limits on political campaign contributions.
-Using state-level data from 1990-2012 on contribution limits, corruption convictions, and media mentions of corruption, this paper finds associations between corruption convictions and the presence of limits on donations to political action committees (PACs), the amount of those limits, and the presence of limits on donations to parties.
-Individual donation limits, however, do not prove associated with either measure of corruption."
-anonymized: true
-output:
-    draft::jop_submission:
-        keep_tex: yes
----
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, eval=FALSE, cache = TRUE, message=FALSE, warning=FALSE)
-library(haven) # import .dta
-library(MASS) # For binomial regression 
-library(tidyverse) # everything; placed here because of MASS::select() overlap 
-library(plm) # For linear panel regression
-library(stargazer) # For regression outputs #fail 
-library(knitr) # Because Matt Worthington said so 
-library(pglm) # For panel + binomial 
-library(webshot) # For screenshots 
-library(viridis) # For colorblindedness
-library(GGally) # For ggpairs
-library(lm.beta) # For standardized regression coefficients 
-library(broom) # for augment()
-library(devtools) # For downloading packages from github 
-install_github("duckmayr/draft") # For JOP template 
-theme_set(theme_classic()) # Sets default theme
+\documentclass{jopsubmission}
 
-```
+%% Math support
+\usepackage{amssymb} % Note: loads amsfonts
+\usepackage{amsmath}
 
-```{r data import, eval=T, message=F, warning=F}
-# Alt and Lassen's "Enforcement and Public Corruption: Evidence from US States" 
-# http://epstein.wustl.edu/research/LPE.Alt.pdf
-AltLassen <- read_dta("~/Documents/GitHub/Money-in-Politics/data/Replication/AltLassenJLEO.dta")
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
+\usepackage{textcomp} % provide euro and other symbols
 
-# Michael Barber's "Ideological Donors, Contribution Limits, and the Polarization of American Legislatures"  
-# https://doi.org/10.1086/683453
-Barber <- read_csv("~/Documents/GitHub/Money-in-Politics/data/Barber/Barber_Limits_Data.csv")
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
 
-# Data from ICC 
-# www.greasethewheels.org/cci/
-convictions <- read_csv("~/Documents/GitHub/Money-in-Politics/data/ICS/CCI19762015.csv")
-reflections <- read_csv("~/Documents/GitHub/Money-in-Politics/data/ICS/CRI19772013.csv")
-```
+\usepackage{float} % Noorah says this will help with \newpage in References 
+\usepackage{xcolor}
 
-```{r panel data wrangling,eval=T}
-# Combining Barber and ICS  
-corruption <- full_join(convictions, reflections)
-corruption <- corruption %>% 
-  rename("st"="State", "year"="Year")
-corruption$st <- state.abb[match(corruption$st,state.name)]
-BarberICC <- left_join(Barber, corruption)
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
 
-BarberICC <- BarberICC %>% 
-  mutate(
-    ind_limits_dummy = ifelse(ind_limits_2010==99999,0,1),
-    ind2pty_limits_dummy = ifelse(ind2pty_limits_2010==99999,0,1),
-    pac_limits_dummy = ifelse(pac_limits_2010==99999,0,1),
-    total_limits_dummy = ifelse(total_limits_2010==99999,0,1)
-  )
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+          hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
-# Adding AltLassen
-# table(AltLassen$state_name)
-AltLassen$state_name[AltLassen$state_name=="Californ"] = "California"
-AltLassen$state_name[AltLassen$state_name=="Connecti"] = "Connecticut"
-AltLassen$state_name[AltLassen$state_name=="Louisian"] = "Louisiana"
-AltLassen$state_name[AltLassen$state_name=="Massachu"] = "Massachusetts"
-AltLassen$state_name[AltLassen$state_name=="Minnesot"] = "Minnesota"
-AltLassen$state_name[AltLassen$state_name=="Mississi"] = "Mississippi"
-AltLassen$state_name[AltLassen$state_name=="NewHamps"] = "New Hampshire"
-AltLassen$state_name[AltLassen$state_name=="NewJerse"] = "New Jersey"
-AltLassen$state_name[AltLassen$state_name=="NewMexic"] = "New Mexico"
-AltLassen$state_name[AltLassen$state_name=="NewYork"] = "New York"
-AltLassen$state_name[AltLassen$state_name=="NorthCar"] = "North Carolina"
-AltLassen$state_name[AltLassen$state_name=="NorthDak"] = "North Dakota"
-AltLassen$state_name[AltLassen$state_name=="Pennsylv"] = "Pennsylvania"
-AltLassen$state_name[AltLassen$state_name=="RhodeIsl"] = "Rhode Island"
-AltLassen$state_name[AltLassen$state_name=="SouthCar"] = "South Carolina"
-AltLassen$state_name[AltLassen$state_name=="SouthDak"] = "South Dakota"
-AltLassen$state_name[AltLassen$state_name=="Tennesse"] = "Tennessee"
-AltLassen$state_name[AltLassen$state_name=="Washingt"] = "Washington"
-AltLassen$state_name[AltLassen$state_name=="WestVirg"] = "West Virginia"
-AltLassen$state_name[AltLassen$state_name=="Wisconsi"] = "Wisconsin"
-AltLassen$state_name <- state.abb[match(AltLassen$state_name,state.name)]
-AltLassen <- AltLassen %>% 
-  rename("st"="state_name")
-AltLassen$year <-as.integer(AltLassen$year)
+\urlstyle{same} % disable monospaced font for URLs
 
-AltBarber <- inner_join(BarberICC, AltLassen)
-```
+%% For tables
+\usepackage{booktabs}
+
+%% For figures
+\usepackage{graphicx}
+\usepackage{adjustbox,lipsum} % Alternate to \resizebox, maybe? 
+\usepackage{grffile}
+
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
+% We don't want a date in there
+\date{\vspace{-5ex}}
+
+    \title{Campaign Contribution Limits and Corruption\\
+Evidence from the 50 states}
+
+% We need to remove section numbering
+\setcounter{secnumdepth}{-\maxdimen}
+
+\begin{document}
+
+    \maketitle
+            \begin{abstract}
+        Since its 1976 \emph{Buckley v. Valeo} decision, the Supreme Court has
+        allowed only two potential justifications for limiting campaign
+        donations: To prevent corruption or the appearance of corruption. Do
+        campaign finance limits actually mitigate corruption or its appearance?
+        As current challenges to contribution limits wind their way through
+        federal courts, the answer to this question will inform the Supreme
+        Court's decision to uphold or strike down remaining limits on political
+        campaign contributions. Using state-level data from 1990-2012 on
+        contribution limits, corruption convictions, and media mentions of
+        corruption, this paper finds associations between corruption convictions
+        and the presence of limits on donations to political action committees
+        (PACs), the amount of those limits, and the presence of limits on
+        donations to parties. Individual donation limits, however, do not prove
+        associated with either measure of corruption.
+        \end{abstract}
 
@@
 
-## Introduction
-In 1976, the Supreme Court ruled in _Buckley v.
-Valeo_ that political campaign expenditures are the equivalent of free speech, and therefore protected by the first amendment.
-At the same time, the Court laid out one mechanism and two permissible reasons for limiting campaign contributions that enable those expenditures.
-First, it argued that more money contributed does not amount to “more” speech, allowing for the use of campaign contribution dollar amount limits.
-Donating one dollar or $5,000 to a political campaign amounts to a speech act, the Court held, and so it is permissible to impose limits on the amount of contributions as long as contributions are not prevented.
-Second, having laid out this mechanism by which money in politics might be limited, the court laid out only two constitutionally permissible reasons for limiting contributions: To prevent corruption or the appearance thereof.
-As Kang (2012) argues, the holdings in _Buckley v.
-Valeo_ provided “the basic framework of contribution limits and disclosure requirements” for the following four decades.
-Since _Buckley v.
-Valeo_, Congress has passed only one campaign finance law, the Bipartisan Campaign Reform Act of 2002.
-Better know as McCain-Feingold, the bill took aim at unlimited “soft money” contributions to political parties and expanded the Federal Election Commission’s disclosure requirements to what it called “electioneering communications,” political ads not paid for by campaigns themselves.
+\subsection{Introduction}\label{introduction}
 
-Apart from McCain-Feingold, for forty years all changes in the landscape of campaign finance have come from the Supreme Court and appellate courts, which have worked to balance questions of corruption with those of free speech.
-In 1981, the Court struck down contribution limits related to ballot measures (_Citizens against Rent Control v.
-City of Berkeley_).
-Just before the passage of McCain-Feingold, the courts considered state-level limits, allowing low limits in Missouri (_Nixon v.
-Shrink Missouri_, 2000), though it would later finding Vermont's to be low enough that they had a meaningful impact on political speech (_Randall v.
-Sorrell_, 2006).
+In 1976, the Supreme Court ruled in \emph{Buckley v. Valeo} that
+political campaign expenditures are the equivalent of free speech, and
+therefore protected by the first amendment. At the same time, the Court
+laid out one mechanism and two permissible reasons for limiting campaign
+contributions that enable those expenditures. First, it argued that more
+money contributed does not amount to ``more'' speech, allowing for the
+use of campaign contribution dollar amount limits. Donating one dollar
+or \$5,000 to a political campaign amounts to a speech act, the Court
+held, and so it is permissible to impose limits on the amount of
+contributions as long as contributions are not prevented. Second, having
+laid out this mechanism by which money in politics might be limited, the
+court laid out only two constitutionally permissible reasons for
+limiting contributions: To prevent corruption or the appearance thereof.
+As Kang (2012) argues, the holdings in \emph{Buckley v. Valeo} provided
+``the basic framework of contribution limits and disclosure
+requirements'' for the following four decades. Since \emph{Buckley v.
+Valeo}, Congress has passed only one campaign finance law, the
+Bipartisan Campaign Reform Act of 2002. Better know as McCain-Feingold,
+the bill took aim at unlimited ``soft money'' contributions to political
+parties and expanded the Federal Election Commission's disclosure
+requirements to what it called ``electioneering communications,''
+political ads not paid for by campaigns themselves.
 
-The passage of the McCain-Feingold in 2002 inspired a wave of challenges to campaign contributions and expenditures, driven mostly by conservative and religious political groups.
-In 2007, the Court examined the McCain-Feingold ban on airing issue advertisements close to election.
-Banning such ads, the Court argued, would have a chilling effect on free speech, and it struck down the ban ( _FEC v.
-Wisconsin Right to Life_).
-Then, in 2010, the Court issued what has become one of its most well-known rulings: In _Citizens United v.
-FEC_ (2010), it struck down limits on independent expenditures by outside groups, including corporations and unions.
-One critical aspect of _Citizens United_ is the establishment of the principle that, according to Justice Anthony Kennedy, “independent expenditures do not lead to, or create the appearance of, quid pro quo corruption.” The Court’s emphasis on quid pro quo corruption as the only justification for contribution limits extended the following year, as it struck down an Arizona effort to level the political playing field with matching state campaign funds (_Arizona Free Enterprise Club v.
-Bennett_, 2011).
+Apart from McCain-Feingold, for forty years all changes in the landscape
+of campaign finance have come from the Supreme Court and appellate
+courts, which have worked to balance questions of corruption with those
+of free speech. In 1981, the Court struck down contribution limits
+related to ballot measures (\emph{Citizens against Rent Control v. City
+of Berkeley}). Just before the passage of McCain-Feingold, the courts
+considered state-level limits, allowing low limits in Missouri
+(\emph{Nixon v. Shrink Missouri}, 2000), though it would later finding
+Vermont's to be low enough that they had a meaningful impact on
+political speech (\emph{Randall v. Sorrell}, 2006).
 
-Since 2011, the network of conservative legal groups behind Citizens United has continued to take aim at contribution limits as an unnecessary restriction of political speech, with a focus on individual contribution limits.
-The 1971 Federal Election Campaign Act placed a limit on the amount an individual could give to one campaign, in addition to two-year limits on the total amount an individual could give to political campaigns.
-In _McCutcheon v.
-FEC_ (2014) James Bopp, one of the attorneys behind the Citizens United challenge, convinced the Court of the unconstitutionality of total individual limits.
-Another case, _Holmes v.
-FEC_ (2017), targeted the distribution of individual campaign contribution across primary and general elections.
-In yet another, _Lair v.
-Mangan_ (2018), Bopp once again took aim at individual contribution limits, arguing that the state of Montana had not shown compelling evidence that campaign contribution limits decreased the risk of corruption.
+The passage of the McCain-Feingold in 2002 inspired a wave of challenges
+to campaign contributions and expenditures, driven mostly by
+conservative and religious political groups. In 2007, the Court examined
+the McCain-Feingold ban on airing issue advertisements close to
+election. Banning such ads, the Court argued, would have a chilling
+effect on free speech, and it struck down the ban ( \emph{FEC v.
+Wisconsin Right to Life}). Then, in 2010, the Court issued what has
+become one of its most well-known rulings: In \emph{Citizens United v.
+FEC} (2010), it struck down limits on independent expenditures by
+outside groups, including corporations and unions. One critical aspect
+of \emph{Citizens United} is the establishment of the principle that,
+according to Justice Anthony Kennedy, ``independent expenditures do not
+lead to, or create the appearance of, quid pro quo corruption.'' The
+Court's emphasis on quid pro quo corruption as the only justification
+for contribution limits extended the following year, as it struck down
+an Arizona effort to level the political playing field with matching
+state campaign funds (\emph{Arizona Free Enterprise Club v. Bennett},
+2011).
 
-The Ninth Circuit Court of Appeals upheld Montana’s campaign contribution limits, and the Fifth Circuit similarly upheld limits in Austin, TX (_Zimmerman v.
-City of Austin_, 2018).
-But further challenges to contribution limits are likely.
-Bopp said that he planned to appeal the Ninth Circuit’s ruling.
-Even if that fails, Bopp and other conservative groups plan to carry on.
-“I handle a lot of cases,” he said after the 2014 McCutcheon ruling, “and I‘m not done yet.” Supreme Court Justice Clarence Thomas laid the groundwork for future challenges in his commentary on the McCutcheon decision by arguing that more dollars did, in fact, equate to more speech.
-Once established, that principle supports the argument that campaign contribution dollar amount limits are a potentially unconstitutional restriction on speech (Hurley & Debenedetti 2014, Zall 2017).
+Since 2011, the network of conservative legal groups behind Citizens
+United has continued to take aim at contribution limits as an
+unnecessary restriction of political speech, with a focus on individual
+contribution limits. The 1971 Federal Election Campaign Act placed a
+limit on the amount an individual could give to one campaign, in
+addition to two-year limits on the total amount an individual could give
+to political campaigns. In \emph{McCutcheon v. FEC} (2014) James Bopp,
+one of the attorneys behind the Citizens United challenge, convinced the
+Court of the unconstitutionality of total individual limits. Another
+case, \emph{Holmes v. FEC} (2017), targeted the distribution of
+individual campaign contribution across primary and general elections.
+In yet another, \emph{Lair v. Mangan} (2018), Bopp once again took aim
+at individual contribution limits, arguing that the state of Montana had
+not shown compelling evidence that campaign contribution limits
+decreased the risk of corruption.
 
-## Prior Work 
-Since the Buckley v.
-Valeo decision, a wave of scholarship has taken advantage of the campaign contribution data collected by the Federal Election Commission to examine the causes and consequences of political campaign contributions, including whether contributions buy access (not to a meaningful degree, find Welch 1982 and Langbein 1986) and the effectiveness of contributions relative to lobbying efforts (yes, according to Wright 1990).
-Since the 2010 Citizens United and speechnow.org decisions, another arm of scholarship has examined the flows of money to groups engaging in independent expenditures (Spencer and Wood 2014, Werner and Coleman 2014).
+The Ninth Circuit Court of Appeals upheld Montana's campaign
+contribution limits, and the Fifth Circuit similarly upheld limits in
+Austin, TX (\emph{Zimmerman v. City of Austin}, 2018). But further
+challenges to contribution limits are likely. Bopp said that he planned
+to appeal the Ninth Circuit's ruling. Even if that fails, Bopp and other
+conservative groups plan to carry on. ``I handle a lot of cases,'' he
+said after the 2014 McCutcheon ruling, ``and I`m not done yet.'' Supreme
+Court Justice Clarence Thomas laid the groundwork for future challenges
+in his commentary on the McCutcheon decision by arguing that more
+dollars did, in fact, equate to more speech. Once established, that
+principle supports the argument that campaign contribution dollar amount
+limits are a potentially unconstitutional restriction on speech (Hurley
+\& Debenedetti 2014, Zall 2017).
 
-But lobbying, money for access, and independent expenditures all fall outside of the narrow definition of quid pro corruption that the Supreme Court considers a compelling enough state interest to justify campaign contribution limits.
-The scholarly research on corruption thus narrowly defined is mixed and heated.
-Stratmann finds evidence that donations determined votes in at least one instance (1991); he also finds that the timing of political action committees (PAC) donations suggests that corporations believe those donations do affect legislators’ votes (1998).
-Reacting to the absence of evidence that donations lead to favorable final votes on bills, Hall and Wayman (1990) look for and find a positive relationship between political donations and the amount of attention that legislators give to a particular issue.
-Other scholars, however, are not so convinced.
-Wright finds that once lobbying efforts are factored in, the effects of contributions on voting outcomes washes out (1990).
-And it is notoriously difficult to tease out whether political donations change legislators’ minds or instead flow to legislators with established, friendly positions (Ansolabehere et al 2003).
+\subsection{Prior Work}\label{prior-work}
 
-As mentioned above, the Court is also interested in the appearance of corruption.
-On this score, results are more consonant: There seems to be little association between campaign spending and public trust in government (Primo 2002).
-Other factors, including media coverage of campaign finance law and the professionalization of legislatures, are more predictive of public perceptions of corruptions (Rosenson 2009).
-And while the public does seem to report viewing campaign finance as a contributor to corruption, there is not evidence that reform efforts will have an effect on those views (Persily & Lammie 2004).
+Since the Buckley v. Valeo decision, a wave of scholarship has taken
+advantage of the campaign contribution data collected by the Federal
+Election Commission to examine the causes and consequences of political
+campaign contributions, including whether contributions buy access (not
+to a meaningful degree, find Welch 1982 and Langbein 1986) and the
+effectiveness of contributions relative to lobbying efforts (yes,
+according to Wright 1990). Since the 2010 Citizens United and
+speechnow.org decisions, another arm of scholarship has examined the
+flows of money to groups engaging in independent expenditures (Spencer
+and Wood 2014, Werner and Coleman 2014).
 
-One fundamental limitation of these federal level studies on campaign contributions and corruption is the absence of a counter-factual.
-Given that contribution limits have been in place since the 1970s, it is difficult to argue what might have happened in their absence.
-Recent work on campaign finance has attempted to address this problem by focusing on the effects of differences in campaign finance laws at the state level.
-Variation across states and over time allows room for studying the causes and consequences of campaign finance limits, separate from the question of corruption.
-Studies suggest that campaign finance limits are associated with less electoral competition (Gross et al 2002, Lott 2006), but that disclosure rules and some organizational limits are associated with greater levels of government trust (Primo and Milyo 2006) and may increase the return on campaign expenditures (Stratmann 2006).
-As mentioned, Michael Barber’s 2016 work finds that lower limits on PAC donations relative to individual donations are associated with higher polarization.
+But lobbying, money for access, and independent expenditures all fall
+outside of the narrow definition of quid pro corruption that the Supreme
+Court considers a compelling enough state interest to justify campaign
+contribution limits. The scholarly research on corruption thus narrowly
+defined is mixed and heated. Stratmann finds evidence that donations
+determined votes in at least one instance (1991); he also finds that the
+timing of political action committees (PAC) donations suggests that
+corporations believe those donations do affect legislators' votes
+(1998). Reacting to the absence of evidence that donations lead to
+favorable final votes on bills, Hall and Wayman (1990) look for and find
+a positive relationship between political donations and the amount of
+attention that legislators give to a particular issue. Other scholars,
+however, are not so convinced. Wright finds that once lobbying efforts
+are factored in, the effects of contributions on voting outcomes washes
+out (1990). And it is notoriously difficult to tease out whether
+political donations change legislators' minds or instead flow to
+legislators with established, friendly positions (Ansolabehere et al
+2003).
 
-A largely separate body of work has examined the causes and consequences of corruption at the state level, separate from campaign finance.
-Most use the Department of Justice’s Annual Public Integrity Report, which correlate highly with state level perceptions of corruption (Walker and Calcagno 2011, Glaeser and Saks 2006, Liu & Mikesell 2014).
-Using that data, researchers have found evidence that political corruption leads to inflated state budgets and that the presence of casinos and subsequent corruption (Liu & Mikesell 2014, Walker & Calcagno 2013).
-They have also shown the absence of a link between state ethics commissions and reduced corruption (Crider and Milyo 2013).
+As mentioned above, the Court is also interested in the appearance of
+corruption. On this score, results are more consonant: There seems to be
+little association between campaign spending and public trust in
+government (Primo 2002). Other factors, including media coverage of
+campaign finance law and the professionalization of legislatures, are
+more predictive of public perceptions of corruptions (Rosenson 2009).
+And while the public does seem to report viewing campaign finance as a
+contributor to corruption, there is not evidence that reform efforts
+will have an effect on those views (Persily \& Lammie 2004).
 
-In response to criticisms of corruption convictions as a proper measure of corruption, researchers have also developed alternative measures of state level corruption.
-Boylan and Long make use of surveys of state reporters (2003).
-Cordis and Milyo deploy the recently available Transactional Records Access Clearinghouse (TRAC) database of political corruption (2013).
-Dincer and Jonhston introduce a Corruption Reflections Index, which tracks mentions of corruption in Associated Press reports (2016).
+One fundamental limitation of these federal level studies on campaign
+contributions and corruption is the absence of a counter-factual. Given
+that contribution limits have been in place since the 1970s, it is
+difficult to argue what might have happened in their absence. Recent
+work on campaign finance has attempted to address this problem by
+focusing on the effects of differences in campaign finance laws at the
+state level. Variation across states and over time allows room for
+studying the causes and consequences of campaign finance limits,
+separate from the question of corruption. Studies suggest that campaign
+finance limits are associated with less electoral competition (Gross et
+al 2002, Lott 2006), but that disclosure rules and some organizational
+limits are associated with greater levels of government trust (Primo and
+Milyo 2006) and may increase the return on campaign expenditures
+(Stratmann 2006). As mentioned, Michael Barber's 2016 work finds that
+lower limits on PAC donations relative to individual donations are
+associated with higher polarization.
 
-Fewer scholars have begun connecting these bodies of work to examine the impact of state-level campaign finance regulations on measures of quid pro quo corruption--one of only two questions of import to the Supreme Court as it considers the constitutionality of contribution limits.
-The exception to this is a 2013 working paper by Cordis and Milyo, which campaign contribution limits have little effect on public perceptions of corruption.
-This paper seeks to address this gap in research, building on Cordis and Milyo's work putting state level campaign finance data in direct conversation with state level corruption data.
+A largely separate body of work has examined the causes and consequences
+of corruption at the state level, separate from campaign finance. Most
+use the Department of Justice's Annual Public Integrity Report, which
+correlate highly with state level perceptions of corruption (Walker and
+Calcagno 2011, Glaeser and Saks 2006, Liu \& Mikesell 2014). Using that
+data, researchers have found evidence that political corruption leads to
+inflated state budgets and that the presence of casinos and subsequent
+corruption (Liu \& Mikesell 2014, Walker \& Calcagno 2013). They have
+also shown the absence of a link between state ethics commissions and
+reduced corruption (Crider and Milyo 2013).
 
-## Data and Design  
-In this paper, I build upon the growing body of state-level political science research to ask whether campaign contribution limits at the state level associated with lower levels of corruption.
-Given open debate about the proper measure of state-level corruption, I use two measures.
-The first, a Corruptions Convictions Index, is the traditional measure of state level corruption, built from Department of Justice convictions data.
-The second, the Corruptions Reflection Index, is a new measure put forward by Dincer and Johnston (2016).
-I combine these measures with a third data set from Michael Barber’s 2016 work on campaign contribution limits and political polarization; and a fourth data set from James Alt and David Dryer Lassen, to provide controls for the full model (Alt and Lassen 2012).
+In response to criticisms of corruption convictions as a proper measure
+of corruption, researchers have also developed alternative measures of
+state level corruption. Boylan and Long make use of surveys of state
+reporters (2003). Cordis and Milyo deploy the recently available
+Transactional Records Access Clearinghouse (TRAC) database of political
+corruption (2013). Dincer and Jonhston introduce a Corruption
+Reflections Index, which tracks mentions of corruption in Associated
+Press reports (2016).
 
-Barber’s data set is a panel of contribution limits from 1990-2012 for the lower house of every state legislature.
-Barber compiled this data set from the FEC, Westlaw, and the Nation Council of State Legislatures.
-Each dollar amount is inflation indexed to 2010 dollar amounts, and bi-annualized.
-There are three different types of limits in the Barber database: Individual contribution limits, individual-to-party limits, and PAC limits.
-Barber utilized individual and PAC contributions in his analysis of polarization, leaving out individual-to-party limits given that party contributions typically make up less than 10% of total political fundraising; I include it this analysis to determine whether parties, rather than PACs or individuals, might be the locus of corruption as measured by our other two data sets (Barber 2016).
+Fewer scholars have begun connecting these bodies of work to examine the
+impact of state-level campaign finance regulations on measures of quid
+pro quo corruption--one of only two questions of import to the Supreme
+Court as it considers the constitutionality of contribution limits. The
+exception to this is a 2013 working paper by Cordis and Milyo, which
+campaign contribution limits have little effect on public perceptions of
+corruption. This paper seeks to address this gap in research, building
+on Cordis and Milyo's work putting state level campaign finance data in
+direct conversation with state level corruption data.
 
-```{r Barber summary, eval=T,include=F}
-# This is a summary, but includes all the 99999s and doesn't have skew in it.  
-# stargazer(as.data.frame(subset(Barber[,3:6])), type="text", digits=0)
+\subsection{Data and Design}\label{data-and-design}
 
-# This replaces all the 99999s. 
-BarberNAs <- Barber %>% dplyr::na_if(99999)
+In this paper, I build upon the growing body of state-level political
+science research to ask whether campaign contribution limits at the
+state level associated with lower levels of corruption. Given open
+debate about the proper measure of state-level corruption, I use two
+measures. The first, a Corruptions Convictions Index, is the traditional
+measure of state level corruption, built from Department of Justice
+convictions data. The second, the Corruptions Reflection Index, is a new
+measure put forward by Dincer and Johnston (2016). I combine these
+measures with a third data set from Michael Barber's 2016 work on
+campaign contribution limits and political polarization; and a fourth
+data set from James Alt and David Dryer Lassen, to provide controls for
+the full model (Alt and Lassen 2012).
 
-# These are (highly skewed) histograms of the remaining values 
-ind_limits_2010.plot <- ggplot(BarberNAs, aes(ind_limits_2010)) + geom_density() + theme_minimal()
-ind2pty_limits_2010.plot <- ggplot(BarberNAs, aes(ind2pty_limits_2010)) + geom_density() + theme_minimal()
-pac_limits_2010.plot <- ggplot(BarberNAs, aes(pac_limits_2010)) + geom_density() + theme_minimal()
+Barber's data set is a panel of contribution limits from 1990-2012 for
+the lower house of every state legislature. Barber compiled this data
+set from the FEC, Westlaw, and the Nation Council of State Legislatures.
+Each dollar amount is inflation indexed to 2010 dollar amounts, and
+bi-annualized. There are three different types of limits in the Barber
+database: Individual contribution limits, individual-to-party limits,
+and PAC limits. Barber utilized individual and PAC contributions in his
+analysis of polarization, leaving out individual-to-party limits given
+that party contributions typically make up less than 10\% of total
+political fundraising; I include it this analysis to determine whether
+parties, rather than PACs or individuals, might be the locus of
+corruption as measured by our other two data sets (Barber 2016).
 
-# How about correlations? Unclear what this shows us. 
-# pairs(BarberNAs[3:6])
+% \begin{adjustbox}{max width=\textwidth}
+\begin{table}[!htbp]\centering 
+\caption{Descriptive Statistics for State Level Campaign Finance Limits} 
+\label{} 
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St.
+Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\
+\hline \\[-1.8ex] 
+Individual Limits & 802 & 3,801 & 4,236 & 143 & 827 & 5,078 & 23,164 \\ 
+Individual-to-Party Limits & 472 & 33,222 & 45,732 & 834 & 7,243 & 32,882 & 196,470 \\ 
+Party Limits & 543 & 23,804 & 32,616 & 246 & 5,246 & 24,976 & 150,904 \\ 
+PAC Limits & 742 & 6,396 & 9,440 & 223 & 1,231 & 9,302 & 96,940 \\ 
+\hline \\[-1.8ex] 
+\multicolumn{8}{l}{Notes: 'N' equals number of state-years (out of n=1150) in which that type of limit is present} \\ 
+\end{tabular} 
+}
+\end{table}
+% \end{adjustbox}
 
-# An alternative, perhaps to combine if I can figure out how to print: 
-# psych::describe(subset(BarberNAs[,3:6]))
+The second data set comes from the Department of Justice's ``Report to
+Congress on the Activities and Operations of the Public Integrity
+Section'' by way of the Institute for Corruption Studies.\footnote{N.B.
+  According to one of the researchers'
+  \href{https://about.illinoisstate.edu/odincer/Documents/CVDincerApril2016.docx}{curricula
+  vitae}, the Institute for Corruption Studies is funded in part by a
+  grant from the Charles Koch Research Foundation. Organizations funded
+  by Charles and David Koch are also funders of legal groups driving
+  legal battles mentioned in the introduction, according to a
+  \href{https://www.publicintegrity.org/2017/11/15/21279/kochs-key-among-small-group-quietly-funding-legal-assault-campaign-finance}{report}
+  by the Center for Public Integrity.} Since 1976, the FBI has tracked
+political corruption at the state level, and the Corruption Convictions
+Index (CCI) used here includes the number of corruption convictions in a
+year normalized by the population in each state. This measure of
+corruption is widely used in academic research, though not without
+criticism. Descriptive statistics for corruption convictions are
+included below.
 
-# This is a summary table for all the state-years where limits exist:  
-# stargazer(as.data.frame(subset(BarberNAs[,3:6])), type="text", digits=0, title="Descriptive Statistics (n=1150 state-years)", covariate.labels = c("Individual Limits","Individual-to-Party Limits","Party Limits", "PAC Limits"))
-```
+The third data set is the Institute for Corruption Studies' Corruption
+Reflections Index (CRI), put together by Dincer and Johnston for their
+2016 article on state-level corruption, and which they create in
+response to the limitations of the Corruption Convictions. The
+Corruption Reflections Index represents the fraction of Associated Press
+stories about politics in a particular state that mention political
+corruption (Dincer and Johnston 2016).
 
-```{r Barber summary stats latex, results="asis",eval=T}
-stargazer(as.data.frame(subset(BarberNAs[,3:6])), digits=0, type="latex", title="Descriptive Statistics for State Level Campaign Finance Limits", covariate.labels = c("Individual Limits","Individual-to-Party Limits","Party Limits", "PAC Limits"), header=F,
-          notes = "Notes: 'N' equals number of state-years (out of n=1150) in which that type of limit is present") 
-```
+\begin{table}[!htbp] \centering 
+  \caption{Descriptive Statistics for Corruption and Reflections} 
+  \label{} 
+  \resizebox{\textwidth}{!}{%
+\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St.
+Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\
+\hline \\[-1.8ex] 
+Corruption Convictions Index (CCI) & 1,999 & 2.96 & 2.99 & 0.00 & 1.03 & 3.97 & 33.85 \\ 
+Corruption Reflections Index (CRI) & 1,887 & 0.28 & 0.19 & 0.00 & 0.15 & 0.37 & 2.16 \\ 
+\hline \\[-1.8ex] 
+\end{tabular} 
+}
+\end{table}
 
-The second data set comes from the Department of Justice’s “Report to Congress on the Activities and Operations of the Public Integrity Section” by way of the Institute for Corruption Studies.[^Koch]  Since 1976, the FBI has tracked political corruption at the state level, and the Corruption Convictions Index (CCI) used here includes the number of corruption convictions in a year normalized by the population in each state.
-This measure of corruption is widely used in academic research, though not without criticism.
-Descriptive statistics for corruption convictions are included below.
+The fourth data set provides controls for the panel model. In their 2012
+work examining variation in prosecutorial resources, Alt and Lassen
+follow Glaeser and Saks (2006) in controlling for income and education
+levels, size of government, legislature control, and urbanization (see
+Appendix A). Alt and Lassen's data set runs from 1976-2004. When
+included in the second and third models, this limits the analysis to the
+years from 1990-2004 and n=720.
 
-The third data set is the Institute for Corruption Studies’ Corruption Reflections Index (CRI), put together by Dincer and Johnston for their 2016 article on state-level corruption, and which they create in response to the limitations of the Corruption Convictions.
-The Corruption Reflections Index represents the fraction of Associated Press stories about politics in a particular state that mention political corruption (Dincer and Johnston 2016).
+This analysis has its limitations, beginning with the data sets
+themselves. Barber's state campaign contributions data lacks information
+about upper houses of state legislatures, which are included in both the
+CCI and CRI. The Corruption Convictions Index suffers from a number of
+issues, as outlined by Dincer and Johnston in their introduction to the
+Corruption Reflections Index. They argue that the CCI includes only
+federal data; that the resources available to prosecutors varies from
+state to state; that US Attorneys are political appointees; and that the
+measure records only convictions, which is at best a reflection of
+underlying corruption.
 
-```{r CRI summary latex, results="asis", eval=T}
-stargazer(as.data.frame(subset(corruption[,c(3,6)])), type="latex", digits=2, title="Descriptive Statistics for Corruption and Reflections", covariate.labels = c("Corruption Convictions Index (CCI)","Corruption Reflections Index (CRI)"), header=F)
+The Corruption Reflections Index, too, has its flaws: It relies on a
+single news source, the Associated Press. Similar to federal
+prosecutors' offices, the resources available to each AP office vary. It
+also demonstrates high variation in the data; Utah, for example, has a
+mean CRI score of 0.46 and standard deviation of 0.38, in a data set
+with an overall mean of 0.28 and standard deviation of 0.19. The
+Corruption Reflections Index also seems to assume in its name that media
+reports of corruption are a mere reflection of corruption, rather than
+an endogenous variable in the ecosystem that enables corrupt behavior.
+Previous work, in contrast, has argued that media have a clear bias and
+play an important role in shaping public perceptions of corruption,
+rather than just reflecting it (Sorauf 1987; Ansolabehere, Snowberg and
+Snyder 2005).
 
-# Next: How to demonstrate skew? # Test whether these are correlated? 
-# ggplot(BarberICC, aes(CCI,CRI)) + geom_point() + theme_minimal() + geom_abline()
-```
+Most broadly, this analysis does not directly address the ``appearance
+of corruption,'' the second of the Supreme Court's reasons for allowing
+campaign contribution limits; to do so effectively would require time
+series, state-level data specifically about quid pro quo corruption. It
+is also the case that this analysis looks to the states intentionally in
+order to address the issue of the counter-factual inherent in looking at
+federal data, it may not be the case that statewide results are
+generalizable to, or distinct from, what is occurring at the federal
+level. Third, it is also the case that campaign finance laws may not be
+equally enforced across states, even though the enforcement measures
+used here are from federal rather than state authorities. Finally, the
+period in question (1990-2004) is short enough that there may be some
+factor that influences corruption arrest across a meaningful portion of
+the data set.
 
-The fourth data set provides controls for the panel model.
-In their 2012 work examining variation in prosecutorial resources, Alt and Lassen follow Glaeser and Saks (2006) in controlling for income and education levels, size of government, legislature control, and urbanization (see Appendix A).
-Alt and Lassen's data set runs from 1976-2004.
-When included in the second and third models, this limits the analysis to the years from 1990-2004 and n=720.
+\subsection{Methods}\label{methods}
 
-This analysis has its limitations, beginning with the data sets themselves.
-Barber’s state campaign contributions data lacks information about upper houses of state legislatures, which are included in both the CCI and CRI.
-The Corruption Convictions Index suffers from a number of issues, as outlined by Dincer and Johnston in their introduction to the Corruption Reflections Index.
-They argue that the CCI includes only federal data; that the resources available to prosecutors varies from state to state; that US Attorneys are political appointees; and that the measure records only convictions, which is at best a reflection of underlying corruption.
+Having constructed a full 1990-2012 panel data set from these three data
+sets, I then run a series of time series regressions testing the
+relationship between contribution limits and both dependent variables,
+the Corruption Convictions Index and the Corruption Reflections Index.
 
-The Corruption Reflections Index, too, has its flaws: It relies on a single news source, the Associated Press.
-Similar to federal prosecutors’ offices, the resources available to each AP office vary.
-It also demonstrates high variation in the data; Utah, for example, has a mean CRI score of 0.46 and standard deviation of 0.38, in a data set with an overall mean of 0.28 and standard deviation of 0.19.
-The Corruption Reflections Index also seems to assume in its name that media reports of corruption are a mere reflection of corruption, rather than an endogenous variable in the ecosystem that enables corrupt behavior.
-Previous work, in contrast, has argued that media have a clear bias and play an important role in shaping public perceptions of corruption, rather than just reflecting it (Sorauf 1987; Ansolabehere, Snowberg and Snyder 2005).
+I include three study variables in both sets of models: Individual
+contribution limits, individual-to-party contribution limits, and PAC
+contribution limits. For each of these independent variables, I
+construct two variables for use in the models. The first is a dummy
+variable indicating whether there are contribution limits in that state
+in that year, coded as ``0'' if there are no limits and ``1'' if there
+are. The second is a continuous variable indicating the dollar amount of
+the limit in the state in that year. By interacting these two variables,
+I test two separate associations. The dummy variable tests whether there
+is a difference in the CCI and CRI in states with limits versus states
+without limits. The continuous variable tests whether higher or lower
+limits are associated with higher or lower CCI and CRI scores, within
+the group of states that have limits in a given year. After performing
+this transformation on all three independent variables, I test two
+initial sets of models: (1) Corruption Convictions Index versus campaign
+contribution limits in a given state-year, and (2) Corruption
+Reflections Index versus campaign contributions in a given state-year.
 
-Most broadly, this analysis does not directly address the “appearance of corruption,” the second of the Supreme Court’s reasons for allowing campaign contribution limits; to do so effectively would require time series, state-level data specifically about quid pro quo corruption.
-It is also the case that this analysis looks to the states intentionally in order to address the issue of the counter-factual inherent in looking at federal data, it may not be the case that statewide results are generalizable to, or distinct from, what is occurring at the federal level.
-Third, it is also the case that campaign finance laws may not be equally enforced across states, even though the enforcement measures used here are from federal rather than state authorities.
-Finally, the period in question (1990-2004) is short enough that there may be some factor that influences corruption arrest across a meaningful portion of the data set.
+I build a model of political corruption using control variables
+previously demonstrated by Alt and Lassen to be correlated with
+corruption convictions, resulting in a data set covering 1990-2004, the
+period of overlap among the data sets listed above. These include
+controlling for the size and education levels of the population, the
+ideology of a population, income levels and inequality, education
+levels, the number and relative income of government employees, and
+urbanization. Building a model of corruption that includes variables
+previously demonstrated to be correlated with corruption levels, then
+adding in campaign finance data, I can better identify the association
+of campaign finance laws with corruption levels. For each of these
+models, I test fixed state and year effects and random effects. I also
+test appropriate transformations of both dependent and independent
+variables. The models are as follows:
 
-[^Koch]: N.B.
-According to one of the researchers’ [curricula vitae](https://about.illinoisstate.edu/odincer/Documents/CVDincerApril2016.docx), the Institute for Corruption Studies is funded in part by a grant from the Charles Koch Research Foundation.
-Organizations funded by Charles and David Koch are also funders of legal groups driving legal battles mentioned in the introduction, according to a [report](https://www.publicintegrity.org/2017/11/15/21279/kochs-key-among-small-group-quietly-funding-legal-assault-campaign-finance) by the Center for Public Integrity.
+\paragraph{Corruption Convictions Index versus campaign contribution
+limits in a given
+state-year:}\label{corruption-convictions-index-versus-campaign-contribution-limits-in-a-given-state-year}
 
-## Methods
-Having constructed a full 1990-2012 panel data set from these three data sets, I then run a series of time series regressions testing the relationship between contribution limits and both dependent variables, the Corruption Convictions Index and the Corruption Reflections Index.
+\((log)Convictions = \alpha_{state} + \\ \hspace{3.2cm} \beta_{1}{indiv.dummy} + \beta_{2}{indiv.dummy}\times{indiv.limit} + \\ \hspace{3.2cm} \beta_{3}{pac.dummy} + \beta_{4}{pac.dummy}\times{pac.limit} + \\ \hspace{3.2cm} \beta_{5}{indiv-to-party.dummy} + \beta_{6}{indiv-to-party.dummy}\times{indiv-to-party.limit} + \\ \hspace{3.2cm} Controls\times\gamma + \epsilon\)
 
-I include three study variables in both sets of models: Individual contribution limits, individual-to-party contribution limits, and PAC contribution limits.
-For each of these independent variables, I construct two variables for use in the models.
-The first is a dummy variable indicating whether there are contribution limits in that state in that year, coded as “0” if there are no limits and “1” if there are.
-The second is a continuous variable indicating the dollar amount of the limit in the state in that year.
-By interacting these two variables, I test two separate associations.
-The dummy variable tests whether there is a difference in the CCI and CRI in states with limits versus states without limits.
-The continuous variable tests whether higher or lower limits are associated with higher or lower CCI and CRI scores, within the group of states that have limits in a given year.
-After performing this transformation on all three independent variables, I test two initial sets of models: (1) Corruption Convictions Index versus campaign contribution limits in a given state-year, and (2) Corruption Reflections Index versus campaign contributions in a given state-year.
-<!--These basic models are included in Appendix X.-->
+\paragraph{Corruption Reflections Index versus campaign contributions in
+a given
+state-year:}\label{corruption-reflections-index-versus-campaign-contributions-in-a-given-state-year}
 
-I build a model of political corruption using control variables previously demonstrated by Alt and Lassen to be correlated with corruption convictions, resulting in a data set covering 1990-2004, the period of overlap among the data sets listed above.
-These include controlling for the size and education levels of the population, the ideology of a population, income levels and inequality, education levels, the number and relative income of government employees, and urbanization.
-Building a model of corruption that includes variables previously demonstrated to be correlated with corruption levels, then adding in campaign finance data, I can better identify the association of campaign finance laws with corruption levels.
-For each of these models, I test fixed state and year effects and random effects.
-I also test appropriate transformations of both dependent and independent variables.
-The models are as follows:
+\((log)Reflections = \alpha_{state} + \\ \hspace{3.1cm} \beta_{1}{indiv.dummy} + \beta_{2}{indiv.dummy}\times{indiv.limit} + \\ \hspace{3.1cm} \beta_{3}{pac.dummy} + \beta_{4}{pac.dummy}\times{pac.limit} + \\ \hspace{3.1cm} \beta_{5}{indiv.to.party.dummy} + \beta_{6}{indiv.to.party.dummy}\times{indiv.to.party.limit} + \\ \hspace{3.1cm} Controls\times\gamma + \epsilon\)
 
-#### Corruption Convictions Index versus campaign contribution limits in a given state-year: 
-$(log)Convictions = \alpha_{state} + \\ \hspace{3.2cm} \beta_{1}{indiv.dummy} + \beta_{2}{indiv.dummy}\times{indiv.limit} + \\ \hspace{3.2cm} \beta_{3}{pac.dummy} + \beta_{4}{pac.dummy}\times{pac.limit} + \\ \hspace{3.2cm} \beta_{5}{indiv-to-party.dummy} + \beta_{6}{indiv-to-party.dummy}\times{indiv-to-party.limit} + \\ \hspace{3.2cm} Controls\times\gamma + \epsilon$ <!---->
+\subsection{Results}\label{results}
 
-#### Corruption Reflections Index versus campaign contributions in a given state-year: 
-$(log)Reflections = \alpha_{state} + \\ \hspace{3.1cm} \beta_{1}{indiv.dummy} + \beta_{2}{indiv.dummy}\times{indiv.limit} + \\ \hspace{3.1cm} \beta_{3}{pac.dummy} + \beta_{4}{pac.dummy}\times{pac.limit} + \\ \hspace{3.1cm} \beta_{5}{indiv.to.party.dummy} + \beta_{6}{indiv.to.party.dummy}\times{indiv.to.party.limit} + \\ \hspace{3.1cm} Controls\times\gamma + \epsilon$
+The results of the panel regressions reveal multiple correlations
+between state-level campaign limits and Corruption Convictions; and one
+correlation between those limits and the Corruption Reflections Index.
 
-## Results 
-The results of the panel regressions reveal multiple correlations between state-level campaign limits and Corruption Convictions; and one correlation between those limits and the Corruption Reflections Index.
+The first set of models (Table 3) measures the association of various
+campaign contribution limits with the Corruption Convictions Index. The
+first model includes only control variables; the second model adds in
+campaign finance limit variables. The third layers in fixed effects at
+the state level, fixed time effects, and logged study variables; the
+fourth removes fixed effects but maintains the logged variables. Not
+included here are: models with random effects, models with unlogged
+dependent variables, and models with other combinations of fixed effects
+and variable transformations. The resulting models identify correlations
+between the CCI and the existence individual-to-party limits: The
+presence of such limits is associated with \emph{greater} corruption as
+measured by convictions. In Model 2, with unlogged independent
+variables, both the presence and amount of limits on PAC contributions
+to campaigns is associated with lower levels of corruption measured in
+terms of convictions.
 
-The first set of models (Table 3) measures the association of various campaign contribution limits with the Corruption Convictions Index.
-The first model includes only control variables; the second model adds in campaign finance limit variables.
-The third layers in fixed effects at the state level, fixed time effects, and logged study variables; the fourth removes fixed effects but maintains the logged variables.
-Not included here are: models with random effects, models with unlogged dependent variables, and models with other combinations of fixed effects and variable transformations.
-The resulting models identify correlations between the CCI and the existence individual-to-party limits: The presence of such limits is associated with _greater_ corruption as measured by convictions.
-In Model 2, with unlogged independent variables, both the presence and amount of limits on PAC contributions to campaigns is associated with lower levels of corruption measured in terms of convictions.
+The second set of models (Table 4) walks through the same progression of
+models, measuring the association of various campaign contribution
+limits and the Corruption Reflections Index (CRI). Model 4, which
+includes logged independent and dependent variables but not fixed
+effects, demonstrates that the presence of individual-to-party limits is
+associated with lower levels of corruption as measured by media mention
+of corruption. As with the CCI models in Table 3, the presence and
+amount of PAC limits, when unlogged, are associated with lower levels of
+corruption reflections.
 
-The second set of models (Table 4) walks through the same progression of models, measuring the association of various campaign contribution limits and the Corruption Reflections Index (CRI).
-Model 4, which includes logged independent and dependent variables but not fixed effects, demonstrates that the presence of individual-to-party limits is associated with lower levels of corruption as measured by media mention of corruption.
-As with the CCI models in Table 3, the presence and amount of PAC limits, when unlogged, are associated with lower levels of corruption reflections.
+\begin{table}[!htbp] \centering 
+  \caption{Models of Contribution Limits and Corruption Convictions} 
+  \label{} 
+\small 
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{@{\extracolsep{-15pt}}lcccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-5} 
+\\[-1.8ex] & \multicolumn{4}{c}{Corruption Convictions Index (logged)} \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
+\hline \\[-1.8ex] 
+ Individual limit (amount) &  & 0.00 &  &  \\ 
+  &  & (0.00) &  &  \\ 
+  Individual limit (logged) &  &  & 0.14 & 0.05 \\ 
+  &  &  & (0.09) & (0.04) \\ 
+  Individual limit (dummy) &  & 0.69 & 0.47 & 0.12 \\ 
+  &  & (0.79) & (0.38) & (0.16) \\ 
+  Individual-to-party limit (amount) &  & 0.00 &  &  \\ 
+  &  & (0.00) &  &  \\ 
+  Individual-to-party limit (logged) &  &  & 0.02 & 0.04 \\ 
+  &  &  & (0.07) & (0.03) \\ 
+  Individual-to-party limit (dummy) &  & 0.19$^{**}$ & 0.19 & 0.16$^{*}$ \\ 
+  &  & (0.09) & (0.21) & (0.09) \\ 
+  PAC limit (amount) &  & $-$0.00$^{**}$ &  &  \\ 
+  &  & (0.00) &  &  \\ 
+  PAC limit (logged) &  &  & $-$0.09 & $-$0.06 \\ 
+  &  &  & (0.06) & (0.04) \\ 
+  PAC limit (dummy) &  & $-$0.99$^{**}$ & $-$0.13 & $-$0.14 \\ 
+  &  & (0.41) & (0.24) & (0.13) \\ 
+  Divided government & $-$0.14$^{***}$ & $-$0.13$^{***}$ & $-$0.09$^{*}$ & $-$0.14$^{***}$ \\ 
+  & (0.05) & (0.05) & (0.05) & (0.05) \\ 
+  AUSAs per population (MMs) & 0.03$^{***}$ & 0.03$^{***}$ & 0.03$^{**}$ & 0.03$^{***}$ \\ 
+  & (0.00) & (0.01) & (0.01) & (0.01) \\ 
+  Percent high school grads & $-$2.63$^{***}$ & $-$2.62$^{***}$ & 0.47 & $-$2.73$^{***}$ \\ 
+  & (0.61) & (0.62) & (1.67) & (0.63) \\ 
+  Gov revenues per capita (1000s) & 0.00$^{***}$ & 0.00$^{**}$ & 0.00$^{*}$ & 0.00$^{**}$ \\ 
+  & (0.00) & (0.00) & (0.00) & (0.00) \\ 
+  Urbanization & $-$0.00$^{*}$ & $-$0.00$^{**}$ & $-$0.02 & $-$0.00$^{**}$ \\ 
+  & (0.00) & (0.00) & (0.03) & (0.00) \\ 
+  Log of population (MMs) & 0.22$^{***}$ & 0.21$^{***}$ & 2.08$^{***}$ & 0.22$^{***}$ \\ 
+  & (0.03) & (0.04) & (0.72) & (0.04) \\ 
+  Constant & 1.67$^{***}$ & 2.01$^{**}$ &  & 1.44$^{**}$ \\ 
+  & (0.30) & (0.87) &  & (0.59) \\ 
+ \hline \\[-1.8ex] 
+  & Base Model & Full Model & Fixed Effects & Pooled \\ 
+Observations & 671 & 671 & 671 & 671 \\ 
+R$^{2}$ & 0.13 & 0.14 & 0.03 & 0.14 \\ 
+Adjusted R$^{2}$ & 0.12 & 0.13 & $-$0.08 & 0.12 \\ 
+F Statistic & 16.60$^{***}$ (df = 6; 664) & 9.23$^{***}$ (df = 12; 658) & 1.76$^{*}$ (df = 12; 598) & 8.92$^{***}$ (df = 12; 658) \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+}
+\end{table}
 
-<!--also fails to find a relationship between state-level campaign contribution limits and media mentions of corruption as measured by the Corruption Reflections Index, with one exception: The presence of limits on what an individual can give to a party is associated with a 0.11 point decline in the Corruption Reflections Index.
-The Corruption Reflections Index operates on a scale of zero to one (with a few outlying exceptions), indicating that the presence of individual-to-party limits is associated with a 11% decrease in the index.
--->
+\begin{table}[!htbp] \centering 
+  \caption{Models of Contribution Limits and Corruption Reflections} 
+  \label{} 
+\small 
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{@{\extracolsep{-15pt}}lcccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-5} 
+\\[-1.8ex] & \multicolumn{4}{c}{Corruption Reflections Index (logged)} \\ 
+\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
+\hline \\[-1.8ex] 
+ Individual limit (amount) &  & 0.00 &  &  \\ 
+  &  & (0.00) &  &  \\ 
+  Individual limit (logged) &  &  & $-$0.00 & 0.01 \\ 
+  &  &  & (0.02) & (0.01) \\ 
+  Individual limit (dummy) &  & 0.20 & $-$0.01 & 0.03 \\ 
+  &  & (0.17) & (0.07) & (0.03) \\ 
+  Individual-to-party limit (amount) &  & 0.00 &  &  \\ 
+  &  & (0.00) &  &  \\ 
+  Individual-to-party limit (logged) &  &  & 0.01 & 0.00 \\ 
+  &  &  & (0.01) & (0.01) \\ 
+  Individual-to-party limit (dummy) &  & $-$0.03$^{*}$ & $-$0.05 & $-$0.05$^{***}$ \\ 
+  &  & (0.02) & (0.04) & (0.02) \\ 
+  PAC limit (amount) &  & $-$0.00$^{**}$ &  &  \\ 
+  &  & (0.00) &  &  \\ 
+  PAC limit (logged) &  &  & $-$0.01 & $-$0.01 \\ 
+  &  &  & (0.01) & (0.01) \\ 
+  PAC limit (dummy) &  & $-$0.18$^{**}$ & $-$0.03 & $-$0.01 \\ 
+  &  & (0.09) & (0.04) & (0.03) \\ 
+  AUSAs per million population & 0.00$^{**}$ & 0.00$^{***}$ & $-$0.00 & 0.00$^{***}$ \\ 
+  & (0.00) & (0.00) & (0.00) & (0.00) \\ 
+  Citizen ideology measure & $-$0.00$^{***}$ & $-$0.00$^{***}$ & $-$0.00 & $-$0.00$^{***}$ \\ 
+  & (0.00) & (0.00) & (0.00) & (0.00) \\ 
+  Percent high school graduates & $-$0.42$^{***}$ & $-$0.35$^{***}$ & $-$0.54$^{*}$ & $-$0.38$^{***}$ \\ 
+  & (0.13) & (0.13) & (0.31) & (0.13) \\ 
+  Real per capita gov revenues (1000s) & 0.00$^{***}$ & 0.00$^{***}$ & 0.00$^{**}$ & 0.00$^{***}$ \\ 
+  & (0.00) & (0.00) & (0.00) & (0.00) \\ 
+  Inequality: Male wages & $-$0.01$^{***}$ & $-$0.00$^{**}$ & $-$0.00 & $-$0.00$^{**}$ \\ 
+  & (0.00) & (0.00) & (0.00) & (0.00) \\ 
+  Urbanization & 0.00$^{***}$ & 0.00$^{***}$ & $-$0.01 & 0.00$^{***}$ \\ 
+  & (0.00) & (0.00) & (0.00) & (0.00) \\ 
+  Log of population (millions) & 0.03$^{***}$ & 0.02$^{***}$ & $-$0.04 & 0.03$^{***}$ \\ 
+  & (0.01) & (0.01) & (0.13) & (0.01) \\ 
+  Constant & 0.30$^{***}$ & 0.22 &  & 0.22$^{*}$ \\ 
+  & (0.07) & (0.20) &  & (0.13) \\ 
+ \hline \\[-1.8ex] 
+  & Base Model & Full Model & Fixed Effects & Pooled \\ 
+Observations & 672 & 672 & 672 & 672 \\ 
+R$^{2}$ & 0.21 & 0.24 & 0.04 & 0.24 \\ 
+Adjusted R$^{2}$ & 0.20 & 0.23 & $-$0.08 & 0.22 \\ 
+F Statistic & 24.92$^{***}$ (df = 7; 664) & 16.19$^{***}$ (df = 13; 658) & 1.71$^{*}$ (df = 13; 598) & 15.61$^{***}$ (df = 13; 658) \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+}
+\end{table}
 
-```{r data visualization, eval=T,include=F}
-# Per Bill's request to see about logging data:  
-AltBarber %>% 
-  #select(CCI,CRI,ind_limits_2010,ind_limits_dummy,ind2pty_limits_2010,ind2pty_limits_dummy,pac_limits_2010,pac_limits_dummy,jdiv,bindingonetermlimit,bindingtwotermlimit,rpcinc_annual_new,eopop,unemp,citi6006,high_school,rgenrevpc,men_ineqincwag,grelimp,urbanization_2,logpop) %>%
-  dplyr::select(CCI,CRI,ind_limits_2010,ind_limits_dummy,ind2pty_limits_2010,ind2pty_limits_dummy,pac_limits_2010,pac_limits_dummy) %>%
-  ggpairs(cardinality_threshold = 21)
+\subsection{Discussion}\label{discussion}
 
-AltBarber %>% 
-  ggplot() +
-  geom_histogram(aes(log(CRI))) # LOG
+On their face, the models above support two tentative conclusions and
+present one puzzle: First, in none of the specifications above are
+limits on individuals' campaign contributions correlated with either
+corruption convictions or corruption reflections. This evidence of
+absence is not absence of evidence, of course, but consistent with the
+hypothesis that individual donations are not a primary source of
+political corruption.
 
-AltBarber %>% 
-  ggplot() +
-  geom_histogram(aes(log(CCI))) # LOG
+The second tentative conclusion is that there is a yet-unspecified
+relationship between limits on PAC contributions and corruption. This is
+true in models in which \emph{unlogged} PAC limits are included in the
+models, but not when that variable, with a skew of 3.468, is logged.
+Given the non-normality of that variable, even when logged, it may be
+that a different transformation would more accurately specify these
+relationships. If those relationships hold, two possibilites may explain
+why limiting PAC donations might be associated with lower levels of
+corruption convictions and media coverage when individual limits are
+not. First, it may be that actors engaged enough in the political
+process to be able to corrupt public officials are likely to be entwined
+with, and work through, political action committees. Second, it may be
+that when corruption is routed through an institution such as a PAC, the
+number of people involved may make it more likely to be discovered,
+prosecuted and reported.
 
-AltBarber %>% 
-  filter(ind_limits_2010!=99999) %>% 
-  ggplot() +
-  geom_histogram(aes(log(ind_limits_2010))) # Log. Remember that 99999s == no limit. Have to leave as 99999 for the same reason that Barber did; otherwise NAs get dropped.
+The puzzle in this data is the varying effects of limits on
+individual-to-party donations. The amount of those limits has no
+relationship in these models to either corruption convictions or
+reflections. But the presence of a limit is associated with
+\emph{higher} levels of corruption convictions and \emph{lower} levels
+of media coverage of corruption.\footnote{These relationships remain
+  robust to changes in model specification, including when other
+  donation limit variables are removed from the model.} This suggests
+that states with limits on individual donations to political parties see
+more corruption, but less reporting on those convictions.
 
-AltBarber %>% 
-  filter(pac_limits_2010!=99999) %>% 
-  ggplot() +
-  geom_histogram(aes(log(pac_limits_2010))) # Log
-
-AltBarber %>% 
-  filter(ind2pty_limits_2010!=99999) %>% 
-  ggplot() +
-  geom_histogram(aes(log(ind2pty_limits_2010))) # Log 
-```
-
-```{r CCI models, eval=T, include=F}
-cci <- plm(CCI ~ jdiv  # Divided government  
-           + bindingonetermlimit # Binding one-term limit 
-           + bindingtwotermlimit # Binding two-term limit 
-           + rpcinc_annual_new # Real per capita income ($1000)
-           + eopop # AUSAs per million population
-           + unemp # Unemployment 
-           + citi6006 # Citizen ideology measure 
-           + high_school + # Percent high school graduates
-           + rgenrevpc # Real per capita gov revenues ($1000)
-           + men_ineqincwag # Inequality: Male wages
-           + grelimp # Relative government wages
-           + urbanization_2 # Urbanization 
-           + logpop, # Log of population (millions)
-           data = AltBarber, 
-           model="pooling")
-
-cci.log <- plm(log(CCI+1) ~ jdiv  # Divided government 
-           + bindingonetermlimit # Binding one-term limit 
-           + bindingtwotermlimit # Binding two-term limit 
-           + rpcinc_annual_new # Real per capita income ($1000)
-           + eopop # AUSAs per million population
-           + unemp # Unemployment 
-           + citi6006 # Citizen ideology measure 
-           + high_school + # Percent high school graduates
-           + rgenrevpc # Real per capita gov revenues ($1000)
-           + men_ineqincwag # Inequality: Male wages
-           + grelimp # Relative government wages
-           + urbanization_2 # Urbanization 
-           + logpop, # Log of population (millions)
-           data = AltBarber, 
-           model="pooling")
-
-cci.log.pars <- plm(log(CCI+1) ~ 
-             jdiv  # Divided government 
-           # + bindingonetermlimit # Binding one-term limit 
-           # + bindingtwotermlimit # Binding two-term limit 
-           # + rpcinc_annual_new # Real per capita income ($1000)
-           + eopop # AUSAs per million population
-           # + unemp # Unemployment 
-           # + citi6006 # Citizen ideology measure 
-           + high_school + # Percent high school graduates
-           + rgenrevpc # Real per capita gov revenues ($1000)
-           # + men_ineqincwag # Inequality: Male wages
-           # + grelimp # Relative government wages
-           + urbanization_2 # Urbanization 
-           + logpop, # Log of population (millions)
-           data = AltBarber, 
-           model="pooling")
-
-cci.log.iv <- plm(log(CCI+1) ~ 
-           ind_limits_2010*ind_limits_dummy 
-           + ind2pty_limits_2010*ind2pty_limits_dummy 
-           + pac_limits_2010*pac_limits_dummy
-           + jdiv  # Divided government 
-           # + bindingonetermlimit # Binding one-term limit 
-           # + bindingtwotermlimit # Binding two-term limit 
-           # + rpcinc_annual_new # Real per capita income ($1000)
-           + eopop # AUSAs per million population
-           # + unemp # Unemployment 
-           # + citi6006 # Citizen ideology measure 
-           + high_school + # Percent high school graduates
-           + rgenrevpc # Real per capita gov revenues ($1000)
-           # + men_ineqincwag # Inequality: Male wages
-           # + grelimp # Relative government wages
-           + urbanization_2 # Urbanization 
-           + logpop, # Log of population (millions)
-           data = AltBarber, 
-           model="pooling")
-
-cci.log.iv.log <- plm(
-           log(CCI+1) ~ log(ind_limits_2010)*ind_limits_dummy 
-           + log(ind2pty_limits_2010)*ind2pty_limits_dummy 
-           + log(pac_limits_2010)*pac_limits_dummy
-           + jdiv  # Divided government 
-           # + bindingonetermlimit # Binding one-term limit 
-           # + bindingtwotermlimit # Binding two-term limit 
-           # + rpcinc_annual_new # Real per capita income ($1000)
-           + eopop # AUSAs per million population
-           # + unemp # Unemployment 
-           # + citi6006 # Citizen ideology measure 
-           + high_school + # Percent high school graduates
-           + rgenrevpc # Real per capita gov revenues ($1000)
-           # + men_ineqincwag # Inequality: Male wages
-           # + grelimp # Relative government wages
-           + urbanization_2 # Urbanization 
-           + logpop, # Log of population (millions)
-           data = AltBarber, 
-           model="pooling")
-
-cci.log.iv.fixed <- plm(
-           log(CCI+1) ~ 
-           ind_limits_2010*ind_limits_dummy 
-           + ind2pty_limits_2010*ind2pty_limits_dummy 
-           + pac_limits_2010*pac_limits_dummy
-           + jdiv  # Divided government 
-           # + bindingonetermlimit # Binding one-term limit 
-           # + bindingtwotermlimit # Binding two-term limit 
-           # + rpcinc_annual_new # Real per capita income ($1000)
-           + eopop # AUSAs per million population
-           # + unemp # Unemployment 
-           # + citi6006 # Citizen ideology measure 
-           + high_school + # Percent high school graduates
-           + rgenrevpc # Real per capita gov revenues ($1000)
-           # + men_ineqincwag # Inequality: Male wages
-           # + grelimp # Relative government wages
-           + urbanization_2 # Urbanization 
-           + logpop, # Log of population (millions)
-           data = AltBarber, 
-           model="within")
-
-cci.log.iv.fixed.time <- plm(log(CCI+1) 
-           ~ log(ind_limits_2010)*ind_limits_dummy 
-           + log(ind2pty_limits_2010)*ind2pty_limits_dummy 
-           + log(pac_limits_2010)*pac_limits_dummy
-           + jdiv  # Divided government 
-           # + bindingonetermlimit # Binding one-term limit 
-           # + bindingtwotermlimit # Binding two-term limit 
-           # + rpcinc_annual_new # Real per capita income ($1000)
-           + eopop # AUSAs per million population
-           # + unemp # Unemployment 
-           # + citi6006 # Citizen ideology measure 
-           + high_school + # Percent high school graduates
-           + rgenrevpc # Real per capita gov revenues ($1000)
-           # + men_ineqincwag # Inequality: Male wages
-           # + grelimp # Relative government wages
-           + urbanization_2 # Urbanization 
-           + logpop, # Log of population (millions)
-           data = AltBarber, 
-           model="within",
-           effect="twoways")
-
-#### Single-variable models ####
-cci.ind <- plm(
-           log(CCI+1) ~ 
-           log(ind_limits_2010)*ind_limits_dummy + 
-           #log(ind2pty_limits_2010)*ind2pty_limits_dummy + 
-           #log(pac_limits_2010)*pac_limits_dummy + 
-           jdiv  # Divided government
-           # + bindingonetermlimit # Binding one-term limit
-           # + bindingtwotermlimit # Binding two-term limit
-           # + rpcinc_annual_new # Real per capita income ($1000)
-           + eopop # AUSAs per million population
-           # + unemp # Unemployment
-           # + citi6006 # Citizen ideology measure
-           + high_school + # Percent high school graduates
-           + rgenrevpc # Real per capita gov revenues ($1000)
-           # + men_ineqincwag # Inequality: Male wages
-           # + grelimp # Relative government wages
-           + urbanization_2 # Urbanization
-           + logpop, # Log of population (millions)
-           data = AltBarber,
-           model="pooling")
-
-cci.ind2pty <- plm(
-           log(CCI+1) ~ 
-           #log(ind_limits_2010)*ind_limits_dummy + 
-           log(ind2pty_limits_2010)*ind2pty_limits_dummy + 
-           #log(pac_limits_2010)*pac_limits_dummy + 
-           jdiv  # Divided government
-           # + bindingonetermlimit # Binding one-term limit
-           # + bindingtwotermlimit # Binding two-term limit
-           # + rpcinc_annual_new # Real per capita income ($1000)
-           + eopop # AUSAs per million population
-           # + unemp # Unemployment
-           # + citi6006 # Citizen ideology measure
-           + high_school + # Percent high school graduates
-           + rgenrevpc # Real per capita gov revenues ($1000)
-           # + men_ineqincwag # Inequality: Male wages
-           # + grelimp # Relative government wages
-           + urbanization_2 # Urbanization
-           + logpop, # Log of population (millions)
-           data = AltBarber,
-           model="pooling")
-
-cci.pac <- plm(
-           log(CCI+1) ~ 
-           #log(ind_limits_2010)*ind_limits_dummy + 
-           #log(ind2pty_limits_2010)*ind2pty_limits_dummy + 
-           log(pac_limits_2010)*pac_limits_dummy + 
-           jdiv  # Divided government
-           # + bindingonetermlimit # Binding one-term limit
-           # + bindingtwotermlimit # Binding two-term limit
-           # + rpcinc_annual_new # Real per capita income ($1000)
-           + eopop # AUSAs per million population
-           # + unemp # Unemployment
-           # + citi6006 # Citizen ideology measure
-           + high_school + # Percent high school graduates
-           + rgenrevpc # Real per capita gov revenues ($1000)
-           # + men_ineqincwag # Inequality: Male wages
-           # + grelimp # Relative government wages
-           + urbanization_2 # Urbanization
-           + logpop, # Log of population (millions)
-           data = AltBarber,
-           model="pooling")
-
-stargazer(cci.ind,cci.ind2pty,cci.pac,type="text")
-
-```
-
-```{r CCI models output, eval=T,results="asis"}
-stargazer(
-  cci.log.pars, 
-  cci.log.iv, # F Stat down? 
-  cci.log.iv.fixed.time, # F stat way down 
-  cci.log.iv.log, # F Stat down further 
-  #cci.log.iv.fixed, # AR2 Stat bottoms out 
-  type="latex",
-  #out = "collateral/test.htm",
-  font.size = "small",
-  header=FALSE, 
-  column.sep.width = "-15pt", 
-  digits = 2, digits.extra = 0, 
-  no.space = TRUE,
-  title = "Models of Contribution Limits and Corruption Convictions",
-  dep.var.labels = "Corruption Convictions Index (logged)",
-  covariate.labels=c("Individual limit (amount)",
-                     "Individual limit (logged)",
-                     "Individual limit (dummy)",
-                     "Individual-to-party limit (amount)",
-                     "Individual-to-party limit (logged)",
-                     "Individual-to-party limit (dummy)",
-                     "PAC limit (amount)",
-                     "PAC limit (logged)",
-                     "PAC limit (dummy)",
-                     "Divided government",
-                     "AUSAs per population (MMs)",
-                     "Percent high school grads",
-                     "Gov revenues per capita (1000s)",
-                     "Urbanization",
-                     "Log of population (MMs)"),
-  add.lines = list(c(" ","Base Model","Full Model","Fixed Effects","Pooled"))
-  )
-
-# If I'm interpreting stuff correctly, then: The model that performed best was a logged CCI, non-logged IVs, with no fixed time or state effects.
-In that model, one campaign finance limits (ind2pty_limits_dummy) was associated with higher corruption; one (pac_limits_2010) was associated with lower corruption.
-This is even theoretically stranger than the preivous model.
-
-```
-
-```{r CRI models, eval=T, include=F}
-cri <- plm(CRI ~ jdiv  # Divided government  
-           + bindingonetermlimit # Binding one-term limit 
-           + bindingtwotermlimit # Binding two-term limit 
-           + rpcinc_annual_new # Real per capita income ($1000)
-           + eopop # AUSAs per million population
-           + unemp # Unemployment 
-           + citi6006 # Citizen ideology measure 
-           + high_school + # Percent high school graduates
-           + rgenrevpc # Real per capita gov revenues ($1000)
-           + men_ineqincwag # Inequality: Male wages
-           + grelimp # Relative government wages
-           + urbanization_2 # Urbanization 
-           + logpop, # Log of population (millions)
-           data = AltBarber, 
-           model="pooling")
-
-cri.log <- plm(log(CRI+1) ~ jdiv  # Divided government 
-           + bindingonetermlimit # Binding one-term limit 
-           + bindingtwotermlimit # Binding two-term limit 
-           + rpcinc_annual_new # Real per capita income ($1000)
-           + eopop # AUSAs per million population
-           + unemp # Unemployment 
-           + citi6006 # Citizen ideology measure 
-           + high_school + # Percent high school graduates
-           + rgenrevpc # Real per capita gov revenues ($1000)
-           + men_ineqincwag # Inequality: Male wages
-           + grelimp # Relative government wages
-           + urbanization_2 # Urbanization 
-           + logpop, # Log of population (millions)
-           data = AltBarber, 
-           model="pooling")
-
-cri.log.pars <- plm(
-           log(CRI+1) ~ 
-           # jdiv  # Divided government 
-           # + bindingonetermlimit # Binding one-term limit 
-           # + bindingtwotermlimit # Binding two-term limit 
-           # + rpcinc_annual_new # Real per capita income ($1000)
-           + eopop # AUSAs per million population
-           # + unemp # Unemployment 
-           + citi6006 # Citizen ideology measure 
-           + high_school + # Percent high school graduates
-           + rgenrevpc # Real per capita gov revenues ($1000)
-           + men_ineqincwag # Inequality: Male wages
-           # + grelimp # Relative government wages
-           + urbanization_2 # Urbanization 
-           + logpop, # Log of population (millions)
-           data = AltBarber, 
-           model="pooling")
-
-cri.log.iv <- plm(log(CRI+1) ~ 
-             ind_limits_2010*ind_limits_dummy 
-           + ind2pty_limits_2010*ind2pty_limits_dummy 
-           + pac_limits_2010*pac_limits_dummy
-           # jdiv  # Divided government 
-           # + bindingonetermlimit # Binding one-term limit 
-           # + bindingtwotermlimit # Binding two-term limit 
-           # + rpcinc_annual_new # Real per capita income ($1000)
-           + eopop # AUSAs per million population
-           # + unemp # Unemployment 
-           + citi6006 # Citizen ideology measure 
-           + high_school + # Percent high school graduates
-           + rgenrevpc # Real per capita gov revenues ($1000)
-           + men_ineqincwag # Inequality: Male wages
-           # + grelimp # Relative government wages
-           + urbanization_2 # Urbanization 
-           + logpop, # Log of population (millions)
-           data = AltBarber, 
-           model="pooling")
-
-cri.log.iv.log <- plm(log(CRI+1) ~ 
-             log(ind_limits_2010)*ind_limits_dummy 
-           + log(ind2pty_limits_2010)*ind2pty_limits_dummy 
-           + log(pac_limits_2010)*pac_limits_dummy
-           # jdiv  # Divided government 
-           # + bindingonetermlimit # Binding one-term limit 
-           # + bindingtwotermlimit # Binding two-term limit 
-           # + rpcinc_annual_new # Real per capita income ($1000)
-           + eopop # AUSAs per million population
-           # + unemp # Unemployment 
-           + citi6006 # Citizen ideology measure 
-           + high_school + # Percent high school graduates
-           + rgenrevpc # Real per capita gov revenues ($1000)
-           + men_ineqincwag # Inequality: Male wages
-           # + grelimp # Relative government wages
-           + urbanization_2 # Urbanization 
-           + logpop, # Log of population (millions)
-           data = AltBarber, 
-           model="pooling")
-
-cri.log.iv.fixed <- plm(log(CRI+1) ~ 
-           + ind_limits_2010*ind_limits_dummy
-           + ind2pty_limits_2010*ind2pty_limits_dummy
-           + pac_limits_2010*pac_limits_dummy
-           # jdiv  # Divided government 
-           # + bindingonetermlimit # Binding one-term limit 
-           # + bindingtwotermlimit # Binding two-term limit 
-           # + rpcinc_annual_new # Real per capita income ($1000)
-           + eopop # AUSAs per million population
-           # + unemp # Unemployment 
-           + citi6006 # Citizen ideology measure 
-           + high_school + # Percent high school graduates
-           + rgenrevpc # Real per capita gov revenues ($1000)
-           + men_ineqincwag # Inequality: Male wages
-           # + grelimp # Relative government wages
-           + urbanization_2 # Urbanization 
-           + logpop, # Log of population (millions)
-           data = AltBarber, 
-           model="within")
-
-cri.log.iv.fixed.time <- plm(log(CRI+1) ~ 
-             log(ind_limits_2010)*ind_limits_dummy 
-           + log(ind2pty_limits_2010)*ind2pty_limits_dummy 
-           + log(pac_limits_2010)*pac_limits_dummy
-           # jdiv  # Divided government 
-           # + bindingonetermlimit # Binding one-term limit 
-           # + bindingtwotermlimit # Binding two-term limit 
-           # + rpcinc_annual_new # Real per capita income ($1000)
-           + eopop # AUSAs per million population
-           # + unemp # Unemployment 
-           + citi6006 # Citizen ideology measure 
-           + high_school + # Percent high school graduates
-           + rgenrevpc # Real per capita gov revenues ($1000)
-           + men_ineqincwag # Inequality: Male wages
-           # + grelimp # Relative government wages
-           + urbanization_2 # Urbanization 
-           + logpop, # Log of population (millions)
-           data = AltBarber, 
-           model="within",
-           effect="twoways")
-
-#### Single-variable models ####
-cri.ind <- plm(
-           log(CRI+1) ~ 
-           log(ind_limits_2010)*ind_limits_dummy + 
-           #log(ind2pty_limits_2010)*ind2pty_limits_dummy + 
-           #log(pac_limits_2010)*pac_limits_dummy + 
-           # jdiv  # Divided government 
-           # + bindingonetermlimit # Binding one-term limit 
-           # + bindingtwotermlimit # Binding two-term limit 
-           # + rpcinc_annual_new # Real per capita income ($1000)
-           + eopop # AUSAs per million population
-           # + unemp # Unemployment 
-           + citi6006 # Citizen ideology measure 
-           + high_school + # Percent high school graduates
-           + rgenrevpc # Real per capita gov revenues ($1000)
-           + men_ineqincwag # Inequality: Male wages
-           # + grelimp # Relative government wages
-           + urbanization_2 # Urbanization 
-           + logpop, # Log of population (millions)
-           data = AltBarber,
-           model="pooling")
-
-cri.ind2pty <- plm(
-           log(CRI+1) ~ 
-           #log(ind_limits_2010)*ind_limits_dummy + 
-           log(ind2pty_limits_2010)*ind2pty_limits_dummy + 
-           #log(pac_limits_2010)*pac_limits_dummy + 
-           # jdiv  # Divided government 
-           # + bindingonetermlimit # Binding one-term limit 
-           # + bindingtwotermlimit # Binding two-term limit 
-           # + rpcinc_annual_new # Real per capita income ($1000)
-           + eopop # AUSAs per million population
-           # + unemp # Unemployment 
-           + citi6006 # Citizen ideology measure 
-           + high_school + # Percent high school graduates
-           + rgenrevpc # Real per capita gov revenues ($1000)
-           + men_ineqincwag # Inequality: Male wages
-           # + grelimp # Relative government wages
-           + urbanization_2 # Urbanization 
-           + logpop, # Log of population (millions)
-           data = AltBarber,
-           model="pooling")
-
-cri.pac <- plm(
-           log(CRI+1) ~ 
-           #log(ind_limits_2010)*ind_limits_dummy + 
-           #log(ind2pty_limits_2010)*ind2pty_limits_dummy + 
-           log(pac_limits_2010)*pac_limits_dummy + 
-           # jdiv  # Divided government 
-           # + bindingonetermlimit # Binding one-term limit 
-           # + bindingtwotermlimit # Binding two-term limit 
-           # + rpcinc_annual_new # Real per capita income ($1000)
-           + eopop # AUSAs per million population
-           # + unemp # Unemployment 
-           + citi6006 # Citizen ideology measure 
-           + high_school + # Percent high school graduates
-           + rgenrevpc # Real per capita gov revenues ($1000)
-           + men_ineqincwag # Inequality: Male wages
-           # + grelimp # Relative government wages
-           + urbanization_2 # Urbanization 
-           + logpop, # Log of population (millions)
-           data = AltBarber,
-           model="pooling")
-
-stargazer(cri.ind,cri.ind2pty,cri.pac,type="text")
-
-```
-
-```{r CRI models output, eval=T,results="asis"}
-stargazer(
-  #cri, # started here, with other peoples' models 
-  #cri.log, # Logged DVs; better results
-  cri.log.pars, # Slimmed down model, no explanatory power lost 
-  cri.log.iv, # Adding in IVs. AR2 up, F Stat down 
-  cri.log.iv.fixed.time, # AR2 now negative 
-  cri.log.iv.log, # Logging IVS. AR2 down, F Stat down 
-  #cri.log.iv.fixed, # AR2 to zero 
-  type="latex",
-  #out = "collateral/test.htm",
-  font.size = "small",
-  header=FALSE, 
-  column.sep.width = "-15pt", 
-  digits = 2, digits.extra = 0, 
-  no.space = TRUE,
-  title = "Models of Contribution Limits and Corruption Reflections",
-  dep.var.labels = "Corruption Reflections Index (logged)",
-  covariate.labels=c("Individual limit (amount)",
-                     "Individual limit (logged)",
-                     "Individual limit (dummy)",
-                     "Individual-to-party limit (amount)",
-                     "Individual-to-party limit (logged)",
-                     "Individual-to-party limit (dummy)",
-                     "PAC limit (amount)",
-                     "PAC limit (logged)",
-                     "PAC limit (dummy)",
-                     "AUSAs per million population",
-                     "Citizen ideology measure",
-                     "Percent high school graduates",
-                     "Real per capita gov revenues (1000s)",
-                     "Inequality: Male wages","Urbanization",
-                     "Log of population (millions)"),
-  add.lines = list(c(" ","Base Model","Full Model","Fixed Effects","Pooled"))
-  )
-
-# What to make of this? 
-# First, Bill was right about the logging. 
-# Second, Bill was right about not needing fixed effects (why?). 
-# Third, I added in the F Scores and they line up with the adjusted R squared (why?)
-# If I'm interpreting stuff correctly, then: The model that performed best was a logged CRI, non-logged IV, with no fixed time or state effects.
-In that model, a number of campaign finance limits (ind2pty_limits_dummy,pac_limits_2010,pac_limits_dummy) were associated with lower levels of corruption.
-This is theoretically strange; the only possibility that immediately strikes me is that it is party and pac money that is associated with corruption, not individual donations.
-```
-
-## Discussion
-```{r skew,include=F}
-library(moments) 
-PAC_limits <- AltBarber$pac_limits_2010*AltBarber$pac_limits_dummy
-skewness(PAC_limits) # 3.468 
-PAC_limits_log <- log(AltBarber$pac_limits_2010)*AltBarber$pac_limits_dummy
-skewness(PAC_limits_log) # -0.2467 
-```
-
-On their face, the models above support two tentative conclusions and present one puzzle: First, in none of the specifications above are limits on individuals' campaign contributions correlated with either corruption convictions or corruption reflections.
-This evidence of absence is not absence of evidence, of course, but consistent with the hypothesis that individual donations are not a primary source of political corruption.
-
-The second tentative conclusion is that there is a yet-unspecified relationship between limits on PAC contributions and corruption.
-This is true in models in which _unlogged_ PAC limits are included in the models, but not when that variable, with a skew of 3.468, is logged.
-Given the non-normality of that variable, even when logged, it may be that a different transformation would more accurately specify these relationships.
-If those relationships hold, two possibilites may explain why limiting PAC donations might be associated with lower levels of corruption convictions and media coverage when individual limits are not.
-First, it may be that actors engaged enough in the political process to be able to corrupt public officials are likely to be entwined with, and work through, political action committees.
-Second, it may be that when corruption is routed through an institution such as a PAC, the number of people involved may make it more likely to be discovered, prosecuted and reported.
-
-```{r corr,include=F}
-cor.test(AltBarber$CRI,AltBarber$CCI) # 0.038
-```
-
-The puzzle in this data is the varying effects of limits on individual-to-party donations.
-The amount of those limits has no relationship in these models to either corruption convictions or reflections.
-But the presence of a limit is associated with _higher_ levels of corruption convictions and _lower_ levels of media coverage of corruption.[^SV] This suggests that states with limits on individual donations to political parties see more corruption, but less reporting on those convictions.
-
-[^SV]: These relationships remain robust to changes in model specification, including when other donation limit variables are removed from the model.
-
-What are the legal and policy implications of these results?
-The Supreme Court presently equates political donations with political speech, meaning that it is protected by the first amendment, but that preventing corruption or its appearance in the political system is so important that first amendment rights can be abridged to ensure it.
-For the Court, no other justification--including creating a more informed electorate, or stimulating more competitive elections, or equality of financial participation in elections--is an important enough concern that we should limit political speech in the form of campaign donations.
-The results above suggest that state-level restrictions on donations from individuals may not be demonstrably associated with lower corruption, but that other types of donation limits (on contributions from PACs to campaigns, and from individuals to parties) may indeed be associated with lowering corruption.
-Such results might allow for courts to be more open to the possibility of restricting donations to and from organized groups such as PACs and parties, without having to restrict individual donations and participation in the electoral process.
-
-<!--In order to make this anti-reform argument, some important limitations must be dealt with.
-First, the Corruptions Conviction Index used above has multiple issues, as summarized above.
-Second, Dincer and Johnston’s Corruption Reflections Index, while a worthy effort, needs to be developed further.
-It relies on a single news source; a second version could examine state-level reporting, or include outlets from across the political spectrum.
-Second, the Corruption Reflections Index carries with it the assumption that media mentions are a mere reflection of corruption, whereas other work has demonstrated that media reporting on corruption has its own biases, and its own effects on perceptions of corruption.
-Further research could more fully explore these relationships, including the manner in which public perceptions of corruption provide enabling or constraining environments for corruption itself.
-Given the importance of these limitations, all that can be concluded from the analysis above is that no link between contribution limits and corruption has been demonstrated with this data, not that no link exists.
-
-The anti-reform/pro-speech interpretation must also more fully take into account the second half of the court’s reasoning for limiting free speech, the “appearance of corruption.” Primo and Milyo 2006 on confidence and trust in state government is an important step in that direction, though they acknowledges that “survey measures that relate to opinion on the integrity of democracy are likely to reflect a much more expansive view of ‘corruption’ than what any Court would consider appropriate (2006).
-Dincer and Johnston’s surveys of state reporters is another step, but is limited by its design: State reporters’ perceptions are just a proxy, not a direct measure, of public perceptions of corruption (2017).
-
-The second, pro-reform interpretation of these results would highlight further issues.
-Using corruption convictions as a measure may be inherently flawed, as effectively corrupt officials would never be arrested.
-The Corruption Reflections Index, likewise, sits uncomfortably between measuring actual corruption and its appearance, saying nothing conclusive about either.
-Furthermore, this design does not speak to causality: It could very well be that in states with high levels of corruption, the public agitates for campaign contribution limits.
-
-If Jim Bopp and other conservative legal scholars have their way, the Supreme Court will soon take a closer look at the logic laid out by their predecessors in 1976 in support of campaign contribution limits.
-Justice Thomas's comments in _McCutcheon v.
-FEC_ suggest that commitment to the Buckley v.
-Valeo structure is weakening, and not in the way that campaign finance reformers might hope.
-Despite effort, scholars have failed to provide compelling evidence of a link between campaign contribution limits and corruption as defined by the Court.
-The measures of corruption that academics have used to date have serious limitations.
-Yet if the Court decides the burden of proof is on those looking to restrict political spending on narrow corruption grounds, reform advocates worried about money in politics have a steep empirical hill to climb, and likely only a few short years to do it.-->
+What are the legal and policy implications of these results? The Supreme
+Court presently equates political donations with political speech,
+meaning that it is protected by the first amendment, but that preventing
+corruption or its appearance in the political system is so important
+that first amendment rights can be abridged to ensure it. For the Court,
+no other justification--including creating a more informed electorate,
+or stimulating more competitive elections, or equality of financial
+participation in elections--is an important enough concern that we
+should limit political speech in the form of campaign donations. The
+results above suggest that state-level restrictions on donations from
+individuals may not be demonstrably associated with lower corruption,
+but that other types of donation limits (on contributions from PACs to
+campaigns, and from individuals to parties) may indeed be associated
+with lowering corruption. Such results might allow for courts to be more
+open to the possibility of restricting donations to and from organized
+groups such as PACs and parties, without having to restrict individual
+donations and participation in the electoral process.
 
@@
 
-## Appendix A: Descriptions and Descriptive Statistics of Control Variables 
-In their 2012 paper "Enforcement and Public Corruption: Evidence from the American States," Glaeser and Saks make use of the following control variables, which we have included here:
+\subsection{Appendix A: Descriptions and Descriptive Statistics of
+Control
+Variables}\label{appendix-a-descriptions-and-descriptive-statistics-of-control-variables}
 
-* *AUSAs per million population*, where the number of general attorneys in the U.S. Attorney's office serves as a proxy for the number of federal resources focused on corruption in a particular state
-* *Relative government wages*, the wages of government workers relative to that of the state in which they live, under the hypothesis that lower relative wages will make government workers more prone to corruption
-* *Divided government*, where legislature and executive are controlled by different parties, *Binding one-term limits* and *Binding two-term limits*, which Alt and Lassen call "shadow of the future" variables
-* *Real per capita income ($1000)*, *Unemployment*, *Citizen ideology measure*, *Percent high school graduates*, *Real per capita gov revenues ($1000)*, *Inequality: Male wages*, *Urbanization* and *Log of population (millions)*, which are included as social and demographic controls
+In their 2012 paper ``Enforcement and Public Corruption: Evidence from
+the American States,'' Glaeser and Saks make use of the following
+control variables, which we have included here:
 
-```{r Alt and Lassen summary, results="asis", eval=T}
-stargazer(as.data.frame(subset(AltLassen[,c("jdiv","bindingonetermlimit","bindingtwotermlimit","rpcinc_annual_new","eopop","unemp","citi6006","high_school","rgenrevpc","men_ineqincwag","grelimp","urbanization_2","logpop")])),
-          type="latex", 
-          digits=2, 
-          title="Descriptive Statistics of Control Variables", 
-          covariate.labels = c("Divided government","Binding one-term limit","Binding two-term limit","Real per capita income (1000s)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (1000s)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)"),
-          header=FALSE,
-          font.size = "small",
-          column.sep.width = "-5pt",
-          # digits = 2, digits.extra = 0,
-          no.space = TRUE) 
-```
+\begin{itemize}
+\tightlist
+\item
+  \emph{AUSAs per million population}, where the number of general
+  attorneys in the U.S. Attorney's office serves as a proxy for the
+  number of federal resources focused on corruption in a particular
+  state
+\item
+  \emph{Relative government wages}, the wages of government workers
+  relative to that of the state in which they live, under the hypothesis
+  that lower relative wages will make government workers more prone to
+  corruption
+\item
+  \emph{Divided government}, where legislature and executive are
+  controlled by different parties, \emph{Binding one-term limits} and
+  \emph{Binding two-term limits}, which Alt and Lassen call ``shadow of
+  the future'' variables
+\item
+  \emph{Real per capita income (\$1000)}, \emph{Unemployment},
+  \emph{Citizen ideology measure}, \emph{Percent high school graduates},
+  \emph{Real per capita gov revenues (\$1000)}, \emph{Inequality: Male
+  wages}, \emph{Urbanization} and \emph{Log of population (millions)},
+  which are included as social and demographic controls
+\end{itemize}
+
+\begin{table}[H]\centering % Changed !htbp to H per Noorah's suggestion 
+  \caption{Descriptive Statistics of Control Variables} 
+  \label{} 
+\small 
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{@{\extracolsep{-5pt}}lccccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St.
+Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\
+\hline \\[-1.8ex] 
+Divided government & 1,392 & 0.45 & 0.50 & 0 & 0 & 1 & 1 \\ 
+Binding one-term limit & 1,392 & 0.06 & 0.23 & 0 & 0 & 0 & 1 \\ 
+Binding two-term limit & 1,392 & 0.21 & 0.41 & 0 & 0 & 0 & 1 \\ 
+Real per capita income (1000s) & 1,392 & 13,117.77 & 2,830.47 & 7,707.26 & 11,042.72 & 14,894.11 & 23,280.97 \\ 
+AUSAs per million population & 1,344 & 12.36 & 5.61 & 2.18 & 8.21 & 15.34 & 36.53 \\ 
+Unemployment & 1,296 & 5.88 & 2.01 & 2.30 & 4.50 & 6.90 & 17.40 \\ 
+Citizen ideology measure & 1,392 & 46.94 & 15.05 & 8.45 & 36.12 & 56.86 & 95.97 \\ 
+Percent high school graduates & 1,392 & 0.48 & 0.08 & 0.27 & 0.42 & 0.54 & 0.62 \\ 
+Real per capita gov revenues (1000s) & 1,392 & 1,666.10 & 459.65 & 825.12 & 1,327.91 & 1,957.08 & 4,184.86 \\ 
+Inequality: Male wages & 1,392 & 17.08 & 3.72 & 8.24 & 14.45 & 19.38 & 31.42 \\ 
+Relative government wages & 1,392 & 0.10 & 0.01 & 0.08 & 0.09 & 0.10 & 0.12 \\ 
+Urbanization & 1,392 & 67.14 & 21.25 & 24.99 & 48.80 & 83.66 & 100.00 \\ 
+Log of population (millions) & 1,392 & 1.19 & 0.99 & $-$0.93 & 0.47 & 1.79 & 3.57 \\ 
+\hline \\[-1.8ex] 
+\end{tabular} 
+}
+\end{table}
 
@@
 
-## References 
-<!--Add new authors (see Google doc) and data. R packages?-->
-Ansolabehere, Stephen, John M de Figueiredo, and James M Snyder Jr. 2003. “Why is there so Little Money in US Politics?” Journal of Economic Perspectives. 17(1): 105–130.
+\subsection{References}\label{references}
 
-Alt, J. E., & Lassen, D. D. (2012). Enforcement and public corruption: evidence from the American states. The Journal of Law, Economics, and Organization, 30(2), 306-338.
+Ansolabehere, Stephen, John M de Figueiredo, and James M Snyder Jr.
+2003. ``Why is there so Little Money in US Politics?'' Journal of
+Economic Perspectives. 17(1): 105--130.
 
-Barber, Michael J. "Ideological Donors, Contribution Limits, and the Polarization of American Legislatures." The Journal of Politics 78.1 (2016): 296-310.
+Alt, J. E., \& Lassen, D. D. (2012). Enforcement and public corruption:
+evidence from the American states. The Journal of Law, Economics, and
+Organization, 30(2), 306-338.
 
-Boylan, R. T., & Long, C. X. (2003). Measuring public corruption in the American states: A survey of state house reporters. State Politics & Policy Quarterly, 3(4), 420-438.
+Barber, Michael J. ``Ideological Donors, Contribution Limits, and the
+Polarization of American Legislatures.'' The Journal of Politics 78.1
+(2016): 296-310.
 
-Cordis, A., & Milyo, J. (2013). Do state campaign finance reforms reduce public corruption?. George Mason University, Mercatus Center, Working Paper, (13-09).
+Boylan, R. T., \& Long, C. X. (2003). Measuring public corruption in the
+American states: A survey of state house reporters. State Politics \&
+Policy Quarterly, 3(4), 420-438.
 
-Cordis, A. S., & Milyo, J. (2016). Measuring public corruption in the United States: evidence from administrative records of federal prosecutions. Public Integrity, 18(2), 127-148.
+Cordis, A., \& Milyo, J. (2013). Do state campaign finance reforms
+reduce public corruption?. George Mason University, Mercatus Center,
+Working Paper, (13-09).
 
-Crider, K., & Milyo, J. (2013). Do State Ethics Commissions Reduce Political Corruption: An Exploratory Investigation. UC Irvine L. Rev., 3, 717.
+Cordis, A. S., \& Milyo, J. (2016). Measuring public corruption in the
+United States: evidence from administrative records of federal
+prosecutions. Public Integrity, 18(2), 127-148.
 
-Dincer, O., & Johnston, M.
-(2016).
-Political Culture and Corruption Issues in State Politics: A New Measure of Corruption Issues and a Test of Relationships to Political Culture.
-Publius: The Journal of Federalism, 47(1), 131-148.
+Crider, K., \& Milyo, J. (2013). Do State Ethics Commissions Reduce
+Political Corruption: An Exploratory Investigation. UC Irvine L. Rev.,
+3, 717.
 
-Glaeser, E. L., & Saks, R. E. (2006). Corruption in america. Journal of public Economics, 90(6), 1053-1072.
+Dincer, O., \& Johnston, M. (2016). Political Culture and Corruption
+Issues in State Politics: A New Measure of Corruption Issues and a Test
+of Relationships to Political Culture. Publius: The Journal of
+Federalism, 47(1), 131-148.
 
-Gross, D. A., Goidel, R. K., & Shields, T. G. (2002). State campaign finance regulations and electoral competition. American Politics Research, 30(2), 143-165.
+Glaeser, E. L., \& Saks, R. E. (2006). Corruption in america. Journal of
+public Economics, 90(6), 1053-1072.
 
-Hall, R. L., & Wayman, F. W. (1990). Buying time: Moneyed interests and the mobilization of bias in congressional committees. American political science review, 84(3), 797-820.
+Gross, D. A., Goidel, R. K., \& Shields, T. G. (2002). State campaign
+finance regulations and electoral competition. American Politics
+Research, 30(2), 143-165.
 
-Hurley, L.
-& Debenedetti, G.
-(2014, April 04).
-Legal victory for big-money campaign donors to be felt in states, courts.
-Retrieved December 16, 2017, from https://www.reuters.com/article/us-usa-court-election-analysis/legal-victory-for-big-money-campaign-donors-to-be-felt-in-states-courts-idUSBREA3308620140404
+Hall, R. L., \& Wayman, F. W. (1990). Buying time: Moneyed interests and
+the mobilization of bias in congressional committees. American political
+science review, 84(3), 797-820.
 
-Langbein, L. I. (1986). Money and access: Some empirical evidence. The journal of politics, 48(4), 1052-1062.
+Hurley, L. \& Debenedetti, G. (2014, April 04). Legal victory for
+big-money campaign donors to be felt in states, courts. Retrieved
+December 16, 2017, from
+\url{https://www.reuters.com/article/us-usa-court-election-analysis/legal-victory-for-big-money-campaign-donors-to-be-felt-in-states-courts-idUSBREA3308620140404}
 
-Liu, C., & Mikesell, J. L. (2014). The impact of public officials’ corruption on the size and allocation of US state spending. Public Administration Review, 74(3), 346-359.
+Langbein, L. I. (1986). Money and access: Some empirical evidence. The
+journal of politics, 48(4), 1052-1062.
 
-Lott, J. R. (2006). Campaign finance reform and electoral competition. Public Choice, 129(3-4), 263-300.
+Liu, C., \& Mikesell, J. L. (2014). The impact of public officials'
+corruption on the size and allocation of US state spending. Public
+Administration Review, 74(3), 346-359.
 
-Persily, N., & Lammie, K. (2004). Perceptions of corruption and campaign finance: When public opinion determines constitutional law. University of Pennsylvania Law Review, 119-180.
+Lott, J. R. (2006). Campaign finance reform and electoral competition.
+Public Choice, 129(3-4), 263-300.
 
-Primo, D. M. (2002). Public opinion and campaign finance: Reformers versus reality. The independent review, 7(2), 207-219.
+Persily, N., \& Lammie, K. (2004). Perceptions of corruption and
+campaign finance: When public opinion determines constitutional law.
+University of Pennsylvania Law Review, 119-180.
 
-Primo, D. M., & Milyo, J. (2006). Campaign finance laws and political efficacy: evidence from the states. Election Law Journal, 5(1), 23-39.
+Primo, D. M. (2002). Public opinion and campaign finance: Reformers
+versus reality. The independent review, 7(2), 207-219.
 
-Rosenson, B. A. (2009). The effect of political reform measures on perceptions of corruption. Election Law Journal, 8(1), 31-46.
+Primo, D. M., \& Milyo, J. (2006). Campaign finance laws and political
+efficacy: evidence from the states. Election Law Journal, 5(1), 23-39.
 
-Spencer, Douglas M., and Abby K. Wood. 2014. "Citizens United, states divided: an empirical analysis of independent political spending." LJ 89: 315.
+Rosenson, B. A. (2009). The effect of political reform measures on
+perceptions of corruption. Election Law Journal, 8(1), 31-46.
 
-Stratmann, Thomas. 1991. “What Do Campaign Contributions Buy? Deciphering Causal Effects of Money and Votes.” Southern Economic Journal. Pp.606-620.
+Spencer, Douglas M., and Abby K. Wood. 2014. ``Citizens United, states
+divided: an empirical analysis of independent political spending.'' LJ
+89: 315.
 
-Stratmann, T. (1998). The market for congressional votes: Is timing of contributions everything?. The Journal of Law and Economics, 41(1), 85-114.
+Stratmann, Thomas. 1991. ``What Do Campaign Contributions Buy?
+Deciphering Causal Effects of Money and Votes.'' Southern Economic
+Journal. Pp.606-620.
 
-Stratmann, T. (2006). Contribution limits and the effectiveness of campaign spending. Public Choice, 129(3), 461-474.
+Stratmann, T. (1998). The market for congressional votes: Is timing of
+contributions everything?. The Journal of Law and Economics, 41(1),
+85-114.
 
-Walker, D. M., & Calcagno, P. T. (2013). Casinos and political corruption in the United States: A Granger causality analysis. Applied Economics, 45(34), 4781-4795.
+Stratmann, T. (2006). Contribution limits and the effectiveness of
+campaign spending. Public Choice, 129(3), 461-474.
 
-Walker, D. M., & Jackson, J. D. (2011). The effect of legalized gambling on state government revenue. Contemporary Economic Policy, 29(1), 101-114.
+Walker, D. M., \& Calcagno, P. T. (2013). Casinos and political
+corruption in the United States: A Granger causality analysis. Applied
+Economics, 45(34), 4781-4795.
 
-Werner, Timothy, and John J.
-Coleman.
-2014.
-"Citizens United, independent expenditures, and agency costs: Reexamining the political economy of state antitakeover statutes." The Journal of Law, Economics, & Organization.
-127-159.
+Walker, D. M., \& Jackson, J. D. (2011). The effect of legalized
+gambling on state government revenue. Contemporary Economic Policy,
+29(1), 101-114.
 
-Welch, W. P. (1982). Campaign contributions and legislative voting: Milk money and dairy price supports. Western Political Quarterly, 35(4), 478-495.
+Werner, Timothy, and John J. Coleman. 2014. ``Citizens United,
+independent expenditures, and agency costs: Reexamining the political
+economy of state antitakeover statutes.'' The Journal of Law, Economics,
+\& Organization. 127-159.
 
-Zall, B.
-(2017, October 24).
-Ninth Circuit Tees Up Latest Challenge to Citizens United and McCutcheon.
-Retrieved November 22, 2017, from https://publicpolicylegal.com/2017/10/24/ninth-circuit-tees-up-latest-challenge-to-citizens-united-and-mccutcheon/
+Welch, W. P. (1982). Campaign contributions and legislative voting: Milk
+money and dairy price supports. Western Political Quarterly, 35(4),
+478-495.
 
-<!-- As instructed by Noorah:  
-rmarkdown::render("/Users/markchand/Documents/GitHub/Money-in-Politics/draft-master/inst/rmarkdown/templates/jop/skeleton/JOPskeleton.Rmd", output_format="latex_document") -->
+Zall, B. (2017, October 24). Ninth Circuit Tees Up Latest Challenge to
+Citizens United and McCutcheon. Retrieved November 22, 2017, from
+\url{https://publicpolicylegal.com/2017/10/24/ninth-circuit-tees-up-latest-challenge-to-citizens-united-and-mccutcheon/}
+
+\end{document}

### 2020-04-03 draft-master/inst/rmarkdown/templates/jop/skeleton/skeleton.tex
Includes submitted JOPskeleton

--- 2020-04-03 draft-master/inst/rmarkdown/templates/jop/skeleton/JOPskeleton.tex
@@
 
-\usepackage{float} % Noorah says this will help with \newpage in References 
 \usepackage{xcolor}
@@
 \hypersetup{
+  pdftitle={Your Title},
           hidelinks,
@@
 \usepackage{graphicx}
-\usepackage{adjustbox,lipsum} % Alternate to \resizebox, maybe? 
 \usepackage{grffile}
@@
 
-    \title{Campaign Contribution Limits and Corruption\\
-Evidence from the 50 states}
+    \title{Your Title}
 
@@
             \begin{abstract}
-        Since its 1976 \emph{Buckley v. Valeo} decision, the Supreme Court has
-        allowed only two potential justifications for limiting campaign
-        donations: To prevent corruption or the appearance of corruption. Do
-        campaign finance limits actually mitigate corruption or its appearance?
-        As current challenges to contribution limits wind their way through
-        federal courts, the answer to this question will inform the Supreme
-        Court's decision to uphold or strike down remaining limits on political
-        campaign contributions. Using state-level data from 1990-2012 on
-        contribution limits, corruption convictions, and media mentions of
-        corruption, this paper finds associations between corruption convictions
-        and the presence of limits on donations to political action committees
-        (PACs), the amount of those limits, and the presence of limits on
-        donations to parties. Individual donation limits, however, do not prove
-        associated with either measure of corruption.
+        Your abstract should go here. It should not exceed 150 words.
         \end{abstract}
 
-\newpage
+Your introduction should go at the very beginning. It should not have a
+section heading. Note that your initial submission should be anonymized.
+This is, in part (I cannot stop you from referencing your identity in
+the text), enforced by the YAML option ``anonymized'', which is true by
+default. If you set it to false, your name (as provided in the
+``author'' option) will be displayed via
+\texttt{\textbackslash{}maketitle}.
 
-\subsection{Introduction}\label{introduction}
+Short article submissions must be 10 pages or less, including tables,
+figures, footnotes, and references, but excluding the title page,
+abstract page, and online appendix. Research articles must be 35 pages
+or less (same counting).
 
-In 1976, the Supreme Court ruled in \emph{Buckley v. Valeo} that
-political campaign expenditures are the equivalent of free speech, and
-therefore protected by the first amendment. At the same time, the Court
-laid out one mechanism and two permissible reasons for limiting campaign
-contributions that enable those expenditures. First, it argued that more
-money contributed does not amount to ``more'' speech, allowing for the
-use of campaign contribution dollar amount limits. Donating one dollar
-or \$5,000 to a political campaign amounts to a speech act, the Court
-held, and so it is permissible to impose limits on the amount of
-contributions as long as contributions are not prevented. Second, having
-laid out this mechanism by which money in politics might be limited, the
-court laid out only two constitutionally permissible reasons for
-limiting contributions: To prevent corruption or the appearance thereof.
-As Kang (2012) argues, the holdings in \emph{Buckley v. Valeo} provided
-``the basic framework of contribution limits and disclosure
-requirements'' for the following four decades. Since \emph{Buckley v.
-Valeo}, Congress has passed only one campaign finance law, the
-Bipartisan Campaign Reform Act of 2002. Better know as McCain-Feingold,
-the bill took aim at unlimited ``soft money'' contributions to political
-parties and expanded the Federal Election Commission's disclosure
-requirements to what it called ``electioneering communications,''
-political ads not paid for by campaigns themselves.
+\section{Section headings should be
+short}\label{section-headings-should-be-short}
 
-Apart from McCain-Feingold, for forty years all changes in the landscape
-of campaign finance have come from the Supreme Court and appellate
-courts, which have worked to balance questions of corruption with those
-of free speech. In 1981, the Court struck down contribution limits
-related to ballot measures (\emph{Citizens against Rent Control v. City
-of Berkeley}). Just before the passage of McCain-Feingold, the courts
-considered state-level limits, allowing low limits in Missouri
-(\emph{Nixon v. Shrink Missouri}, 2000), though it would later finding
-Vermont's to be low enough that they had a meaningful impact on
-political speech (\emph{Randall v. Sorrell}, 2006).
-
-The passage of the McCain-Feingold in 2002 inspired a wave of challenges
-to campaign contributions and expenditures, driven mostly by
-conservative and religious political groups. In 2007, the Court examined
-the McCain-Feingold ban on airing issue advertisements close to
-election. Banning such ads, the Court argued, would have a chilling
-effect on free speech, and it struck down the ban ( \emph{FEC v.
-Wisconsin Right to Life}). Then, in 2010, the Court issued what has
-become one of its most well-known rulings: In \emph{Citizens United v.
-FEC} (2010), it struck down limits on independent expenditures by
-outside groups, including corporations and unions. One critical aspect
-of \emph{Citizens United} is the establishment of the principle that,
-according to Justice Anthony Kennedy, ``independent expenditures do not
-lead to, or create the appearance of, quid pro quo corruption.'' The
-Court's emphasis on quid pro quo corruption as the only justification
-for contribution limits extended the following year, as it struck down
-an Arizona effort to level the political playing field with matching
-state campaign funds (\emph{Arizona Free Enterprise Club v. Bennett},
-2011).
-
-Since 2011, the network of conservative legal groups behind Citizens
-United has continued to take aim at contribution limits as an
-unnecessary restriction of political speech, with a focus on individual
-contribution limits. The 1971 Federal Election Campaign Act placed a
-limit on the amount an individual could give to one campaign, in
-addition to two-year limits on the total amount an individual could give
-to political campaigns. In \emph{McCutcheon v. FEC} (2014) James Bopp,
-one of the attorneys behind the Citizens United challenge, convinced the
-Court of the unconstitutionality of total individual limits. Another
-case, \emph{Holmes v. FEC} (2017), targeted the distribution of
-individual campaign contribution across primary and general elections.
-In yet another, \emph{Lair v. Mangan} (2018), Bopp once again took aim
-at individual contribution limits, arguing that the state of Montana had
-not shown compelling evidence that campaign contribution limits
-decreased the risk of corruption.
-
-The Ninth Circuit Court of Appeals upheld Montana's campaign
-contribution limits, and the Fifth Circuit similarly upheld limits in
-Austin, TX (\emph{Zimmerman v. City of Austin}, 2018). But further
-challenges to contribution limits are likely. Bopp said that he planned
-to appeal the Ninth Circuit's ruling. Even if that fails, Bopp and other
-conservative groups plan to carry on. ``I handle a lot of cases,'' he
-said after the 2014 McCutcheon ruling, ``and I`m not done yet.'' Supreme
-Court Justice Clarence Thomas laid the groundwork for future challenges
-in his commentary on the McCutcheon decision by arguing that more
-dollars did, in fact, equate to more speech. Once established, that
-principle supports the argument that campaign contribution dollar amount
-limits are a potentially unconstitutional restriction on speech (Hurley
-\& Debenedetti 2014, Zall 2017).
-
-\subsection{Prior Work}\label{prior-work}
-
-Since the Buckley v. Valeo decision, a wave of scholarship has taken
-advantage of the campaign contribution data collected by the Federal
-Election Commission to examine the causes and consequences of political
-campaign contributions, including whether contributions buy access (not
-to a meaningful degree, find Welch 1982 and Langbein 1986) and the
-effectiveness of contributions relative to lobbying efforts (yes,
-according to Wright 1990). Since the 2010 Citizens United and
-speechnow.org decisions, another arm of scholarship has examined the
-flows of money to groups engaging in independent expenditures (Spencer
-and Wood 2014, Werner and Coleman 2014).
-
-But lobbying, money for access, and independent expenditures all fall
-outside of the narrow definition of quid pro corruption that the Supreme
-Court considers a compelling enough state interest to justify campaign
-contribution limits. The scholarly research on corruption thus narrowly
-defined is mixed and heated. Stratmann finds evidence that donations
-determined votes in at least one instance (1991); he also finds that the
-timing of political action committees (PAC) donations suggests that
-corporations believe those donations do affect legislators' votes
-(1998). Reacting to the absence of evidence that donations lead to
-favorable final votes on bills, Hall and Wayman (1990) look for and find
-a positive relationship between political donations and the amount of
-attention that legislators give to a particular issue. Other scholars,
-however, are not so convinced. Wright finds that once lobbying efforts
-are factored in, the effects of contributions on voting outcomes washes
-out (1990). And it is notoriously difficult to tease out whether
-political donations change legislators' minds or instead flow to
-legislators with established, friendly positions (Ansolabehere et al
-2003).
-
-As mentioned above, the Court is also interested in the appearance of
-corruption. On this score, results are more consonant: There seems to be
-little association between campaign spending and public trust in
-government (Primo 2002). Other factors, including media coverage of
-campaign finance law and the professionalization of legislatures, are
-more predictive of public perceptions of corruptions (Rosenson 2009).
-And while the public does seem to report viewing campaign finance as a
-contributor to corruption, there is not evidence that reform efforts
-will have an effect on those views (Persily \& Lammie 2004).
-
-One fundamental limitation of these federal level studies on campaign
-contributions and corruption is the absence of a counter-factual. Given
-that contribution limits have been in place since the 1970s, it is
-difficult to argue what might have happened in their absence. Recent
-work on campaign finance has attempted to address this problem by
-focusing on the effects of differences in campaign finance laws at the
-state level. Variation across states and over time allows room for
-studying the causes and consequences of campaign finance limits,
-separate from the question of corruption. Studies suggest that campaign
-finance limits are associated with less electoral competition (Gross et
-al 2002, Lott 2006), but that disclosure rules and some organizational
-limits are associated with greater levels of government trust (Primo and
-Milyo 2006) and may increase the return on campaign expenditures
-(Stratmann 2006). As mentioned, Michael Barber's 2016 work finds that
-lower limits on PAC donations relative to individual donations are
-associated with higher polarization.
-
-A largely separate body of work has examined the causes and consequences
-of corruption at the state level, separate from campaign finance. Most
-use the Department of Justice's Annual Public Integrity Report, which
-correlate highly with state level perceptions of corruption (Walker and
-Calcagno 2011, Glaeser and Saks 2006, Liu \& Mikesell 2014). Using that
-data, researchers have found evidence that political corruption leads to
-inflated state budgets and that the presence of casinos and subsequent
-corruption (Liu \& Mikesell 2014, Walker \& Calcagno 2013). They have
-also shown the absence of a link between state ethics commissions and
-reduced corruption (Crider and Milyo 2013).
-
-In response to criticisms of corruption convictions as a proper measure
-of corruption, researchers have also developed alternative measures of
-state level corruption. Boylan and Long make use of surveys of state
-reporters (2003). Cordis and Milyo deploy the recently available
-Transactional Records Access Clearinghouse (TRAC) database of political
-corruption (2013). Dincer and Jonhston introduce a Corruption
-Reflections Index, which tracks mentions of corruption in Associated
-Press reports (2016).
-
-Fewer scholars have begun connecting these bodies of work to examine the
-impact of state-level campaign finance regulations on measures of quid
-pro quo corruption--one of only two questions of import to the Supreme
-Court as it considers the constitutionality of contribution limits. The
-exception to this is a 2013 working paper by Cordis and Milyo, which
-campaign contribution limits have little effect on public perceptions of
-corruption. This paper seeks to address this gap in research, building
-on Cordis and Milyo's work putting state level campaign finance data in
-direct conversation with state level corruption data.
-
-\subsection{Data and Design}\label{data-and-design}
-
-In this paper, I build upon the growing body of state-level political
-science research to ask whether campaign contribution limits at the
-state level associated with lower levels of corruption. Given open
-debate about the proper measure of state-level corruption, I use two
-measures. The first, a Corruptions Convictions Index, is the traditional
-measure of state level corruption, built from Department of Justice
-convictions data. The second, the Corruptions Reflection Index, is a new
-measure put forward by Dincer and Johnston (2016). I combine these
-measures with a third data set from Michael Barber's 2016 work on
-campaign contribution limits and political polarization; and a fourth
-data set from James Alt and David Dryer Lassen, to provide controls for
-the full model (Alt and Lassen 2012).
-
-Barber's data set is a panel of contribution limits from 1990-2012 for
-the lower house of every state legislature. Barber compiled this data
-set from the FEC, Westlaw, and the Nation Council of State Legislatures.
-Each dollar amount is inflation indexed to 2010 dollar amounts, and
-bi-annualized. There are three different types of limits in the Barber
-database: Individual contribution limits, individual-to-party limits,
-and PAC limits. Barber utilized individual and PAC contributions in his
-analysis of polarization, leaving out individual-to-party limits given
-that party contributions typically make up less than 10\% of total
-political fundraising; I include it this analysis to determine whether
-parties, rather than PACs or individuals, might be the locus of
-corruption as measured by our other two data sets (Barber 2016).
-
-% \begin{adjustbox}{max width=\textwidth}
-\begin{table}[!htbp]\centering 
-\caption{Descriptive Statistics for State Level Campaign Finance Limits} 
-\label{} 
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St.
-Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\
-\hline \\[-1.8ex] 
-Individual Limits & 802 & 3,801 & 4,236 & 143 & 827 & 5,078 & 23,164 \\ 
-Individual-to-Party Limits & 472 & 33,222 & 45,732 & 834 & 7,243 & 32,882 & 196,470 \\ 
-Party Limits & 543 & 23,804 & 32,616 & 246 & 5,246 & 24,976 & 150,904 \\ 
-PAC Limits & 742 & 6,396 & 9,440 & 223 & 1,231 & 9,302 & 96,940 \\ 
-\hline \\[-1.8ex] 
-\multicolumn{8}{l}{Notes: 'N' equals number of state-years (out of n=1150) in which that type of limit is present} \\ 
-\end{tabular} 
-}
-\end{table}
-% \end{adjustbox}
-
-The second data set comes from the Department of Justice's ``Report to
-Congress on the Activities and Operations of the Public Integrity
-Section'' by way of the Institute for Corruption Studies.\footnote{N.B.
-  According to one of the researchers'
-  \href{https://about.illinoisstate.edu/odincer/Documents/CVDincerApril2016.docx}{curricula
-  vitae}, the Institute for Corruption Studies is funded in part by a
-  grant from the Charles Koch Research Foundation. Organizations funded
-  by Charles and David Koch are also funders of legal groups driving
-  legal battles mentioned in the introduction, according to a
-  \href{https://www.publicintegrity.org/2017/11/15/21279/kochs-key-among-small-group-quietly-funding-legal-assault-campaign-finance}{report}
-  by the Center for Public Integrity.} Since 1976, the FBI has tracked
-political corruption at the state level, and the Corruption Convictions
-Index (CCI) used here includes the number of corruption convictions in a
-year normalized by the population in each state. This measure of
-corruption is widely used in academic research, though not without
-criticism. Descriptive statistics for corruption convictions are
-included below.
-
-The third data set is the Institute for Corruption Studies' Corruption
-Reflections Index (CRI), put together by Dincer and Johnston for their
-2016 article on state-level corruption, and which they create in
-response to the limitations of the Corruption Convictions. The
-Corruption Reflections Index represents the fraction of Associated Press
-stories about politics in a particular state that mention political
-corruption (Dincer and Johnston 2016).
-
-\begin{table}[!htbp] \centering 
-  \caption{Descriptive Statistics for Corruption and Reflections} 
-  \label{} 
-  \resizebox{\textwidth}{!}{%
-\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St.
-Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\
-\hline \\[-1.8ex] 
-Corruption Convictions Index (CCI) & 1,999 & 2.96 & 2.99 & 0.00 & 1.03 & 3.97 & 33.85 \\ 
-Corruption Reflections Index (CRI) & 1,887 & 0.28 & 0.19 & 0.00 & 0.15 & 0.37 & 2.16 \\ 
-\hline \\[-1.8ex] 
-\end{tabular} 
-}
-\end{table}
-
-The fourth data set provides controls for the panel model. In their 2012
-work examining variation in prosecutorial resources, Alt and Lassen
-follow Glaeser and Saks (2006) in controlling for income and education
-levels, size of government, legislature control, and urbanization (see
-Appendix A). Alt and Lassen's data set runs from 1976-2004. When
-included in the second and third models, this limits the analysis to the
-years from 1990-2004 and n=720.
-
-This analysis has its limitations, beginning with the data sets
-themselves. Barber's state campaign contributions data lacks information
-about upper houses of state legislatures, which are included in both the
-CCI and CRI. The Corruption Convictions Index suffers from a number of
-issues, as outlined by Dincer and Johnston in their introduction to the
-Corruption Reflections Index. They argue that the CCI includes only
-federal data; that the resources available to prosecutors varies from
-state to state; that US Attorneys are political appointees; and that the
-measure records only convictions, which is at best a reflection of
-underlying corruption.
-
-The Corruption Reflections Index, too, has its flaws: It relies on a
-single news source, the Associated Press. Similar to federal
-prosecutors' offices, the resources available to each AP office vary. It
-also demonstrates high variation in the data; Utah, for example, has a
-mean CRI score of 0.46 and standard deviation of 0.38, in a data set
-with an overall mean of 0.28 and standard deviation of 0.19. The
-Corruption Reflections Index also seems to assume in its name that media
-reports of corruption are a mere reflection of corruption, rather than
-an endogenous variable in the ecosystem that enables corrupt behavior.
-Previous work, in contrast, has argued that media have a clear bias and
-play an important role in shaping public perceptions of corruption,
-rather than just reflecting it (Sorauf 1987; Ansolabehere, Snowberg and
-Snyder 2005).
-
-Most broadly, this analysis does not directly address the ``appearance
-of corruption,'' the second of the Supreme Court's reasons for allowing
-campaign contribution limits; to do so effectively would require time
-series, state-level data specifically about quid pro quo corruption. It
-is also the case that this analysis looks to the states intentionally in
-order to address the issue of the counter-factual inherent in looking at
-federal data, it may not be the case that statewide results are
-generalizable to, or distinct from, what is occurring at the federal
-level. Third, it is also the case that campaign finance laws may not be
-equally enforced across states, even though the enforcement measures
-used here are from federal rather than state authorities. Finally, the
-period in question (1990-2004) is short enough that there may be some
-factor that influences corruption arrest across a meaningful portion of
-the data set.
-
-\subsection{Methods}\label{methods}
-
-Having constructed a full 1990-2012 panel data set from these three data
-sets, I then run a series of time series regressions testing the
-relationship between contribution limits and both dependent variables,
-the Corruption Convictions Index and the Corruption Reflections Index.
-
-I include three study variables in both sets of models: Individual
-contribution limits, individual-to-party contribution limits, and PAC
-contribution limits. For each of these independent variables, I
-construct two variables for use in the models. The first is a dummy
-variable indicating whether there are contribution limits in that state
-in that year, coded as ``0'' if there are no limits and ``1'' if there
-are. The second is a continuous variable indicating the dollar amount of
-the limit in the state in that year. By interacting these two variables,
-I test two separate associations. The dummy variable tests whether there
-is a difference in the CCI and CRI in states with limits versus states
-without limits. The continuous variable tests whether higher or lower
-limits are associated with higher or lower CCI and CRI scores, within
-the group of states that have limits in a given year. After performing
-this transformation on all three independent variables, I test two
-initial sets of models: (1) Corruption Convictions Index versus campaign
-contribution limits in a given state-year, and (2) Corruption
-Reflections Index versus campaign contributions in a given state-year.
-
-I build a model of political corruption using control variables
-previously demonstrated by Alt and Lassen to be correlated with
-corruption convictions, resulting in a data set covering 1990-2004, the
-period of overlap among the data sets listed above. These include
-controlling for the size and education levels of the population, the
-ideology of a population, income levels and inequality, education
-levels, the number and relative income of government employees, and
-urbanization. Building a model of corruption that includes variables
-previously demonstrated to be correlated with corruption levels, then
-adding in campaign finance data, I can better identify the association
-of campaign finance laws with corruption levels. For each of these
-models, I test fixed state and year effects and random effects. I also
-test appropriate transformations of both dependent and independent
-variables. The models are as follows:
-
-\paragraph{Corruption Convictions Index versus campaign contribution
-limits in a given
-state-year:}\label{corruption-convictions-index-versus-campaign-contribution-limits-in-a-given-state-year}
-
-\((log)Convictions = \alpha_{state} + \\ \hspace{3.2cm} \beta_{1}{indiv.dummy} + \beta_{2}{indiv.dummy}\times{indiv.limit} + \\ \hspace{3.2cm} \beta_{3}{pac.dummy} + \beta_{4}{pac.dummy}\times{pac.limit} + \\ \hspace{3.2cm} \beta_{5}{indiv-to-party.dummy} + \beta_{6}{indiv-to-party.dummy}\times{indiv-to-party.limit} + \\ \hspace{3.2cm} Controls\times\gamma + \epsilon\)
-
-\paragraph{Corruption Reflections Index versus campaign contributions in
-a given
-state-year:}\label{corruption-reflections-index-versus-campaign-contributions-in-a-given-state-year}
-
-\((log)Reflections = \alpha_{state} + \\ \hspace{3.1cm} \beta_{1}{indiv.dummy} + \beta_{2}{indiv.dummy}\times{indiv.limit} + \\ \hspace{3.1cm} \beta_{3}{pac.dummy} + \beta_{4}{pac.dummy}\times{pac.limit} + \\ \hspace{3.1cm} \beta_{5}{indiv.to.party.dummy} + \beta_{6}{indiv.to.party.dummy}\times{indiv.to.party.limit} + \\ \hspace{3.1cm} Controls\times\gamma + \epsilon\)
-
-\subsection{Results}\label{results}
-
-The results of the panel regressions reveal multiple correlations
-between state-level campaign limits and Corruption Convictions; and one
-correlation between those limits and the Corruption Reflections Index.
-
-The first set of models (Table 3) measures the association of various
-campaign contribution limits with the Corruption Convictions Index. The
-first model includes only control variables; the second model adds in
-campaign finance limit variables. The third layers in fixed effects at
-the state level, fixed time effects, and logged study variables; the
-fourth removes fixed effects but maintains the logged variables. Not
-included here are: models with random effects, models with unlogged
-dependent variables, and models with other combinations of fixed effects
-and variable transformations. The resulting models identify correlations
-between the CCI and the existence individual-to-party limits: The
-presence of such limits is associated with \emph{greater} corruption as
-measured by convictions. In Model 2, with unlogged independent
-variables, both the presence and amount of limits on PAC contributions
-to campaigns is associated with lower levels of corruption measured in
-terms of convictions.
-
-The second set of models (Table 4) walks through the same progression of
-models, measuring the association of various campaign contribution
-limits and the Corruption Reflections Index (CRI). Model 4, which
-includes logged independent and dependent variables but not fixed
-effects, demonstrates that the presence of individual-to-party limits is
-associated with lower levels of corruption as measured by media mention
-of corruption. As with the CCI models in Table 3, the presence and
-amount of PAC limits, when unlogged, are associated with lower levels of
-corruption reflections.
-
-\begin{table}[!htbp] \centering 
-  \caption{Models of Contribution Limits and Corruption Convictions} 
-  \label{} 
-\small 
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{@{\extracolsep{-15pt}}lcccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-5} 
-\\[-1.8ex] & \multicolumn{4}{c}{Corruption Convictions Index (logged)} \\ 
-\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
-\hline \\[-1.8ex] 
- Individual limit (amount) &  & 0.00 &  &  \\ 
-  &  & (0.00) &  &  \\ 
-  Individual limit (logged) &  &  & 0.14 & 0.05 \\ 
-  &  &  & (0.09) & (0.04) \\ 
-  Individual limit (dummy) &  & 0.69 & 0.47 & 0.12 \\ 
-  &  & (0.79) & (0.38) & (0.16) \\ 
-  Individual-to-party limit (amount) &  & 0.00 &  &  \\ 
-  &  & (0.00) &  &  \\ 
-  Individual-to-party limit (logged) &  &  & 0.02 & 0.04 \\ 
-  &  &  & (0.07) & (0.03) \\ 
-  Individual-to-party limit (dummy) &  & 0.19$^{**}$ & 0.19 & 0.16$^{*}$ \\ 
-  &  & (0.09) & (0.21) & (0.09) \\ 
-  PAC limit (amount) &  & $-$0.00$^{**}$ &  &  \\ 
-  &  & (0.00) &  &  \\ 
-  PAC limit (logged) &  &  & $-$0.09 & $-$0.06 \\ 
-  &  &  & (0.06) & (0.04) \\ 
-  PAC limit (dummy) &  & $-$0.99$^{**}$ & $-$0.13 & $-$0.14 \\ 
-  &  & (0.41) & (0.24) & (0.13) \\ 
-  Divided government & $-$0.14$^{***}$ & $-$0.13$^{***}$ & $-$0.09$^{*}$ & $-$0.14$^{***}$ \\ 
-  & (0.05) & (0.05) & (0.05) & (0.05) \\ 
-  AUSAs per population (MMs) & 0.03$^{***}$ & 0.03$^{***}$ & 0.03$^{**}$ & 0.03$^{***}$ \\ 
-  & (0.00) & (0.01) & (0.01) & (0.01) \\ 
-  Percent high school grads & $-$2.63$^{***}$ & $-$2.62$^{***}$ & 0.47 & $-$2.73$^{***}$ \\ 
-  & (0.61) & (0.62) & (1.67) & (0.63) \\ 
-  Gov revenues per capita (1000s) & 0.00$^{***}$ & 0.00$^{**}$ & 0.00$^{*}$ & 0.00$^{**}$ \\ 
-  & (0.00) & (0.00) & (0.00) & (0.00) \\ 
-  Urbanization & $-$0.00$^{*}$ & $-$0.00$^{**}$ & $-$0.02 & $-$0.00$^{**}$ \\ 
-  & (0.00) & (0.00) & (0.03) & (0.00) \\ 
-  Log of population (MMs) & 0.22$^{***}$ & 0.21$^{***}$ & 2.08$^{***}$ & 0.22$^{***}$ \\ 
-  & (0.03) & (0.04) & (0.72) & (0.04) \\ 
-  Constant & 1.67$^{***}$ & 2.01$^{**}$ &  & 1.44$^{**}$ \\ 
-  & (0.30) & (0.87) &  & (0.59) \\ 
- \hline \\[-1.8ex] 
-  & Base Model & Full Model & Fixed Effects & Pooled \\ 
-Observations & 671 & 671 & 671 & 671 \\ 
-R$^{2}$ & 0.13 & 0.14 & 0.03 & 0.14 \\ 
-Adjusted R$^{2}$ & 0.12 & 0.13 & $-$0.08 & 0.12 \\ 
-F Statistic & 16.60$^{***}$ (df = 6; 664) & 9.23$^{***}$ (df = 12; 658) & 1.76$^{*}$ (df = 12; 598) & 8.92$^{***}$ (df = 12; 658) \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-}
-\end{table}
-
-\begin{table}[!htbp] \centering 
-  \caption{Models of Contribution Limits and Corruption Reflections} 
-  \label{} 
-\small 
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{@{\extracolsep{-15pt}}lcccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-5} 
-\\[-1.8ex] & \multicolumn{4}{c}{Corruption Reflections Index (logged)} \\ 
-\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
-\hline \\[-1.8ex] 
- Individual limit (amount) &  & 0.00 &  &  \\ 
-  &  & (0.00) &  &  \\ 
-  Individual limit (logged) &  &  & $-$0.00 & 0.01 \\ 
-  &  &  & (0.02) & (0.01) \\ 
-  Individual limit (dummy) &  & 0.20 & $-$0.01 & 0.03 \\ 
-  &  & (0.17) & (0.07) & (0.03) \\ 
-  Individual-to-party limit (amount) &  & 0.00 &  &  \\ 
-  &  & (0.00) &  &  \\ 
-  Individual-to-party limit (logged) &  &  & 0.01 & 0.00 \\ 
-  &  &  & (0.01) & (0.01) \\ 
-  Individual-to-party limit (dummy) &  & $-$0.03$^{*}$ & $-$0.05 & $-$0.05$^{***}$ \\ 
-  &  & (0.02) & (0.04) & (0.02) \\ 
-  PAC limit (amount) &  & $-$0.00$^{**}$ &  &  \\ 
-  &  & (0.00) &  &  \\ 
-  PAC limit (logged) &  &  & $-$0.01 & $-$0.01 \\ 
-  &  &  & (0.01) & (0.01) \\ 
-  PAC limit (dummy) &  & $-$0.18$^{**}$ & $-$0.03 & $-$0.01 \\ 
-  &  & (0.09) & (0.04) & (0.03) \\ 
-  AUSAs per million population & 0.00$^{**}$ & 0.00$^{***}$ & $-$0.00 & 0.00$^{***}$ \\ 
-  & (0.00) & (0.00) & (0.00) & (0.00) \\ 
-  Citizen ideology measure & $-$0.00$^{***}$ & $-$0.00$^{***}$ & $-$0.00 & $-$0.00$^{***}$ \\ 
-  & (0.00) & (0.00) & (0.00) & (0.00) \\ 
-  Percent high school graduates & $-$0.42$^{***}$ & $-$0.35$^{***}$ & $-$0.54$^{*}$ & $-$0.38$^{***}$ \\ 
-  & (0.13) & (0.13) & (0.31) & (0.13) \\ 
-  Real per capita gov revenues (1000s) & 0.00$^{***}$ & 0.00$^{***}$ & 0.00$^{**}$ & 0.00$^{***}$ \\ 
-  & (0.00) & (0.00) & (0.00) & (0.00) \\ 
-  Inequality: Male wages & $-$0.01$^{***}$ & $-$0.00$^{**}$ & $-$0.00 & $-$0.00$^{**}$ \\ 
-  & (0.00) & (0.00) & (0.00) & (0.00) \\ 
-  Urbanization & 0.00$^{***}$ & 0.00$^{***}$ & $-$0.01 & 0.00$^{***}$ \\ 
-  & (0.00) & (0.00) & (0.00) & (0.00) \\ 
-  Log of population (millions) & 0.03$^{***}$ & 0.02$^{***}$ & $-$0.04 & 0.03$^{***}$ \\ 
-  & (0.01) & (0.01) & (0.13) & (0.01) \\ 
-  Constant & 0.30$^{***}$ & 0.22 &  & 0.22$^{*}$ \\ 
-  & (0.07) & (0.20) &  & (0.13) \\ 
- \hline \\[-1.8ex] 
-  & Base Model & Full Model & Fixed Effects & Pooled \\ 
-Observations & 672 & 672 & 672 & 672 \\ 
-R$^{2}$ & 0.21 & 0.24 & 0.04 & 0.24 \\ 
-Adjusted R$^{2}$ & 0.20 & 0.23 & $-$0.08 & 0.22 \\ 
-F Statistic & 24.92$^{***}$ (df = 7; 664) & 16.19$^{***}$ (df = 13; 658) & 1.71$^{*}$ (df = 13; 598) & 15.61$^{***}$ (df = 13; 658) \\ 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-}
-\end{table}
-
-\subsection{Discussion}\label{discussion}
-
-On their face, the models above support two tentative conclusions and
-present one puzzle: First, in none of the specifications above are
-limits on individuals' campaign contributions correlated with either
-corruption convictions or corruption reflections. This evidence of
-absence is not absence of evidence, of course, but consistent with the
-hypothesis that individual donations are not a primary source of
-political corruption.
-
-The second tentative conclusion is that there is a yet-unspecified
-relationship between limits on PAC contributions and corruption. This is
-true in models in which \emph{unlogged} PAC limits are included in the
-models, but not when that variable, with a skew of 3.468, is logged.
-Given the non-normality of that variable, even when logged, it may be
-that a different transformation would more accurately specify these
-relationships. If those relationships hold, two possibilites may explain
-why limiting PAC donations might be associated with lower levels of
-corruption convictions and media coverage when individual limits are
-not. First, it may be that actors engaged enough in the political
-process to be able to corrupt public officials are likely to be entwined
-with, and work through, political action committees. Second, it may be
-that when corruption is routed through an institution such as a PAC, the
-number of people involved may make it more likely to be discovered,
-prosecuted and reported.
-
-The puzzle in this data is the varying effects of limits on
-individual-to-party donations. The amount of those limits has no
-relationship in these models to either corruption convictions or
-reflections. But the presence of a limit is associated with
-\emph{higher} levels of corruption convictions and \emph{lower} levels
-of media coverage of corruption.\footnote{These relationships remain
-  robust to changes in model specification, including when other
-  donation limit variables are removed from the model.} This suggests
-that states with limits on individual donations to political parties see
-more corruption, but less reporting on those convictions.
-
-What are the legal and policy implications of these results? The Supreme
-Court presently equates political donations with political speech,
-meaning that it is protected by the first amendment, but that preventing
-corruption or its appearance in the political system is so important
-that first amendment rights can be abridged to ensure it. For the Court,
-no other justification--including creating a more informed electorate,
-or stimulating more competitive elections, or equality of financial
-participation in elections--is an important enough concern that we
-should limit political speech in the form of campaign donations. The
-results above suggest that state-level restrictions on donations from
-individuals may not be demonstrably associated with lower corruption,
-but that other types of donation limits (on contributions from PACs to
-campaigns, and from individuals to parties) may indeed be associated
-with lowering corruption. Such results might allow for courts to be more
-open to the possibility of restricting donations to and from organized
-groups such as PACs and parties, without having to restrict individual
-donations and participation in the electoral process.
-
-\newpage
-
-\subsection{Appendix A: Descriptions and Descriptive Statistics of
-Control
-Variables}\label{appendix-a-descriptions-and-descriptive-statistics-of-control-variables}
-
-In their 2012 paper ``Enforcement and Public Corruption: Evidence from
-the American States,'' Glaeser and Saks make use of the following
-control variables, which we have included here:
-
-\begin{itemize}
-\tightlist
-\item
-  \emph{AUSAs per million population}, where the number of general
-  attorneys in the U.S. Attorney's office serves as a proxy for the
-  number of federal resources focused on corruption in a particular
-  state
-\item
-  \emph{Relative government wages}, the wages of government workers
-  relative to that of the state in which they live, under the hypothesis
-  that lower relative wages will make government workers more prone to
-  corruption
-\item
-  \emph{Divided government}, where legislature and executive are
-  controlled by different parties, \emph{Binding one-term limits} and
-  \emph{Binding two-term limits}, which Alt and Lassen call ``shadow of
-  the future'' variables
-\item
-  \emph{Real per capita income (\$1000)}, \emph{Unemployment},
-  \emph{Citizen ideology measure}, \emph{Percent high school graduates},
-  \emph{Real per capita gov revenues (\$1000)}, \emph{Inequality: Male
-  wages}, \emph{Urbanization} and \emph{Log of population (millions)},
-  which are included as social and demographic controls
-\end{itemize}
-
-\begin{table}[H]\centering % Changed !htbp to H per Noorah's suggestion 
-  \caption{Descriptive Statistics of Control Variables} 
-  \label{} 
-\small 
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{@{\extracolsep{-5pt}}lccccccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St.
-Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\
-\hline \\[-1.8ex] 
-Divided government & 1,392 & 0.45 & 0.50 & 0 & 0 & 1 & 1 \\ 
-Binding one-term limit & 1,392 & 0.06 & 0.23 & 0 & 0 & 0 & 1 \\ 
-Binding two-term limit & 1,392 & 0.21 & 0.41 & 0 & 0 & 0 & 1 \\ 
-Real per capita income (1000s) & 1,392 & 13,117.77 & 2,830.47 & 7,707.26 & 11,042.72 & 14,894.11 & 23,280.97 \\ 
-AUSAs per million population & 1,344 & 12.36 & 5.61 & 2.18 & 8.21 & 15.34 & 36.53 \\ 
-Unemployment & 1,296 & 5.88 & 2.01 & 2.30 & 4.50 & 6.90 & 17.40 \\ 
-Citizen ideology measure & 1,392 & 46.94 & 15.05 & 8.45 & 36.12 & 56.86 & 95.97 \\ 
-Percent high school graduates & 1,392 & 0.48 & 0.08 & 0.27 & 0.42 & 0.54 & 0.62 \\ 
-Real per capita gov revenues (1000s) & 1,392 & 1,666.10 & 459.65 & 825.12 & 1,327.91 & 1,957.08 & 4,184.86 \\ 
-Inequality: Male wages & 1,392 & 17.08 & 3.72 & 8.24 & 14.45 & 19.38 & 31.42 \\ 
-Relative government wages & 1,392 & 0.10 & 0.01 & 0.08 & 0.09 & 0.10 & 0.12 \\ 
-Urbanization & 1,392 & 67.14 & 21.25 & 24.99 & 48.80 & 83.66 & 100.00 \\ 
-Log of population (millions) & 1,392 & 1.19 & 0.99 & $-$0.93 & 0.47 & 1.79 & 3.57 \\ 
-\hline \\[-1.8ex] 
-\end{tabular} 
-}
-\end{table}
-
-\newpage
-
-\subsection{References}\label{references}
-
-Ansolabehere, Stephen, John M de Figueiredo, and James M Snyder Jr.
-2003. ``Why is there so Little Money in US Politics?'' Journal of
-Economic Perspectives. 17(1): 105--130.
-
-Alt, J. E., \& Lassen, D. D. (2012). Enforcement and public corruption:
-evidence from the American states. The Journal of Law, Economics, and
-Organization, 30(2), 306-338.
-
-Barber, Michael J. ``Ideological Donors, Contribution Limits, and the
-Polarization of American Legislatures.'' The Journal of Politics 78.1
-(2016): 296-310.
-
-Boylan, R. T., \& Long, C. X. (2003). Measuring public corruption in the
-American states: A survey of state house reporters. State Politics \&
-Policy Quarterly, 3(4), 420-438.
-
-Cordis, A., \& Milyo, J. (2013). Do state campaign finance reforms
-reduce public corruption?. George Mason University, Mercatus Center,
-Working Paper, (13-09).
-
-Cordis, A. S., \& Milyo, J. (2016). Measuring public corruption in the
-United States: evidence from administrative records of federal
-prosecutions. Public Integrity, 18(2), 127-148.
-
-Crider, K., \& Milyo, J. (2013). Do State Ethics Commissions Reduce
-Political Corruption: An Exploratory Investigation. UC Irvine L. Rev.,
-3, 717.
-
-Dincer, O., \& Johnston, M. (2016). Political Culture and Corruption
-Issues in State Politics: A New Measure of Corruption Issues and a Test
-of Relationships to Political Culture. Publius: The Journal of
-Federalism, 47(1), 131-148.
-
-Glaeser, E. L., \& Saks, R. E. (2006). Corruption in america. Journal of
-public Economics, 90(6), 1053-1072.
-
-Gross, D. A., Goidel, R. K., \& Shields, T. G. (2002). State campaign
-finance regulations and electoral competition. American Politics
-Research, 30(2), 143-165.
-
-Hall, R. L., \& Wayman, F. W. (1990). Buying time: Moneyed interests and
-the mobilization of bias in congressional committees. American political
-science review, 84(3), 797-820.
-
-Hurley, L. \& Debenedetti, G. (2014, April 04). Legal victory for
-big-money campaign donors to be felt in states, courts. Retrieved
-December 16, 2017, from
-\url{https://www.reuters.com/article/us-usa-court-election-analysis/legal-victory-for-big-money-campaign-donors-to-be-felt-in-states-courts-idUSBREA3308620140404}
-
-Langbein, L. I. (1986). Money and access: Some empirical evidence. The
-journal of politics, 48(4), 1052-1062.
-
-Liu, C., \& Mikesell, J. L. (2014). The impact of public officials'
-corruption on the size and allocation of US state spending. Public
-Administration Review, 74(3), 346-359.
-
-Lott, J. R. (2006). Campaign finance reform and electoral competition.
-Public Choice, 129(3-4), 263-300.
-
-Persily, N., \& Lammie, K. (2004). Perceptions of corruption and
-campaign finance: When public opinion determines constitutional law.
-University of Pennsylvania Law Review, 119-180.
-
-Primo, D. M. (2002). Public opinion and campaign finance: Reformers
-versus reality. The independent review, 7(2), 207-219.
-
-Primo, D. M., \& Milyo, J. (2006). Campaign finance laws and political
-efficacy: evidence from the states. Election Law Journal, 5(1), 23-39.
-
-Rosenson, B. A. (2009). The effect of political reform measures on
-perceptions of corruption. Election Law Journal, 8(1), 31-46.
-
-Spencer, Douglas M., and Abby K. Wood. 2014. ``Citizens United, states
-divided: an empirical analysis of independent political spending.'' LJ
-89: 315.
-
-Stratmann, Thomas. 1991. ``What Do Campaign Contributions Buy?
-Deciphering Causal Effects of Money and Votes.'' Southern Economic
-Journal. Pp.606-620.
-
-Stratmann, T. (1998). The market for congressional votes: Is timing of
-contributions everything?. The Journal of Law and Economics, 41(1),
-85-114.
-
-Stratmann, T. (2006). Contribution limits and the effectiveness of
-campaign spending. Public Choice, 129(3), 461-474.
-
-Walker, D. M., \& Calcagno, P. T. (2013). Casinos and political
-corruption in the United States: A Granger causality analysis. Applied
-Economics, 45(34), 4781-4795.
-
-Walker, D. M., \& Jackson, J. D. (2011). The effect of legalized
-gambling on state government revenue. Contemporary Economic Policy,
-29(1), 101-114.
-
-Werner, Timothy, and John J. Coleman. 2014. ``Citizens United,
-independent expenditures, and agency costs: Reexamining the political
-economy of state antitakeover statutes.'' The Journal of Law, Economics,
-\& Organization. 127-159.
-
-Welch, W. P. (1982). Campaign contributions and legislative voting: Milk
-money and dairy price supports. Western Political Quarterly, 35(4),
-478-495.
-
-Zall, B. (2017, October 24). Ninth Circuit Tees Up Latest Challenge to
-Citizens United and McCutcheon. Retrieved November 22, 2017, from
-\url{https://publicpolicylegal.com/2017/10/24/ninth-circuit-tees-up-latest-challenge-to-citizens-united-and-mccutcheon/}
+Section headings should not take up more than a single line of text.
+There should be no section heading for the introduction. Do not use
+headings immediately after one another without text in between. You
+generally should not use headings at the sub-sub-heading level or below.
+Do not refer to sections by number, as sections are not numbered.
 

### 2020-04-03 draft-master/R/formats.R

@@ -1,0 +1,31 @@
+#' R Markdown Output Formats
+#'
+#' A number of additional \code{yaml} options are made available:
+#' \describe{
+#'     \item{tikz}{If \code{true}, the \code{tikz} LaTeX package is loaded.}
+#'     \item{theorems}{If \code{true}, the \code{amsthm} LaTeX package is loaded,
+#'                     and a number of default theorem environments are created:
+#'                     theorem (theorem number prefaced by "Theorem"),
+#'                     proposition (theorem number prefaced by "Proposition"),
+#'                     lemma (theorem number prefaced by "Lemma"),
+#'                     corollary (theorem number prefaced by "Corollary",
+#'                                numbered with reference to the last
+#'                                \code{proposition}; i.e., if after
+#'                                "Proposition 1", the first \code{corollary}
+#'                                will be "Corollary 1.1"),
+#'                     and thm_corollary (theorem number prefaced by "Corollary",
+#'                                        numbered with reference to the last
+#'                                        \code{theorem}).}
+#' }
+#'
+#' @param ... Arguments passed to \code{\link[rmarkdown]{pdf_document}}.
+#'
+#' @return An R Markdown output format.
+#' @name formats
+NULL
+
+#' @export
+#' @rdname formats
+jop_submission <- function(...) {
+    return(pdf_document_format("jop", ...))
+}
